### 2016-09-16 paper_intersections.tex
Research and first steps in algorithm description.

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%% SP 2008/03/01

%\documentclass[preprint,12pt]{elsarticle}
 \documentclass{elsarticle}
%\documentclass[3p,12pt,authoryear]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,3p,times,authoryear]{elsarticle}
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = red %Colour of citations
}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}
\usepackage{subfig}

%tables
\usepackage{booktabs}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{esint}

%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

% just for our notes
\usepackage[usenames,dvipsnames]{color}   %colors

\journal{Applied Mathematics and Computation}

%commands:
%\newcommand{\defref}[1]{\hyperref[#1]{Def.~\ref{#1}}}
\newcommand{\prob}[1]{Problem~{#1}}
\newcommand{\fig}[1]{\hyperref[#1]{Figure \ref{#1}}}
\newcommand{\figpath}{figures/}

%math:
\def\vc#1{\mathbf{\boldsymbol{#1}}}     % vector
\def\abs#1{\left|#1\right|}
\def\avg#1{\langle#1\rangle}
\def\d{\mathrm{d}}
\def\norm#1{\| #1 \|}
\def\abs#1{| #1 |}
\def\prtl{\partial}
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\bx}{\vc{x}}
\newcommand*\rfrac[2]{{}^{#1}\!/_{#2}}

\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
\newcommand{\plucker}{Pl\"{u}cker}

\newdefinition{mdef}{Definition}%[section]

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Intersection of non-matching grids of different dimensions}
% Self-intersection of non-matching grid of mixed dimensions

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author[adr]{Jan B{\v r}ezina\corref{cor1}}
\ead{jan.brezina@tul.cz}
\cortext[cor1]{Corresponding author.}

\author[adr]{Pavel Exner}
\ead{pavel.exner@tul.cz}
%\ead[url]{https://github.com/Paulie14/xfem\_project}

\address[adr]{Technical University of Liberec, Studentsk{\' a} 1402/2, 461 17 Liberec 1, Czech Republic}

\begin{abstract}
TODO: An abstract.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
non-matching gird \sep 
intersections \sep
mixed-dimensional mesh \sep
\plucker coordinates

%% PACS codes here, in the form: \PACS code \sep code
%\PACS 02.60.Lj \sep        %Ordinary and partial differential equations; boundary value problems
%\PACS 02.60.Jh             %Numerical differentiation and integration

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC[2010] 65N30 \sep %    Finite elements, Rayleigh-Ritz and Galerkin methods, finite methods
%\MSC[2010] 35J05  %    Laplacian operator, reduced wave equation (Helmholtz equation), Poisson equation

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
Structure of introduction:

- motivation for computing mesh intersections, other applications
- basic overview of existing work, approaches
- our contribution
    - new algorithms for element intersectins based on Pl\"ucker coordinates
    - improvement of the front tracking algorithm

\cite{sukumar_extended_2000} - Use {\emph geometric predicates} incircle and orientation. Use mesh of bounding boxes to search for intersection candidates. 
Only use point queries for all vertices of triangle/tetrahedron. Use compatible partitioning of elements by the crack elements.

\cite{massing_efficient_2013} - Implementation of the Nitche method in Fenics. They need 2d-3d intersections, but only for distribution od quadrature points. 
So they do not store whole intersection data, but only the quad points. The boundary of one domain is partitioned into intersections with elements of the other domain.
Use {\\emph collision relations} ( pairs of faces of boundary and elmements of the background mesh) and {\emph collision maps} 
( map face to all intersections and background element to all intersections, can be constructed from the collision relation), They cite books from computer graphics ..
Mention geometric predicates. Present algorithms for:  find intersection candidates, comput intersections, integrate over complex domains.

\cite{elsheikh_reliable_2012} Claim to provide robust algorithm covering all tiangle-trinagle degenerate cases. Basic idea is the same as our: use some tree 
(Binary SPace Tree) structure to find initial point on intersection curve and trace the curve in both directions. Quite clever data structure for the mesh. Adaptive precision 
geometric predicates. Store topological information about the intersection points (point on triangle, edge, vertex). Resolve various degenerate cases, 
dicuss mesh optimization after subdivision.

\cite{gander_algorithm_2013} Full algorithm for 2d=3D called PANG. Implemented in DUNE in 2010 (Bastian). Other software (Hecht, MpCCI). 
Triangle-Triangle and Tetra-Triangle intersections done similarly as in aur approach: set of points including vertices and then sort them countercolckwise.
Local intersection algorithm do not provide neighbouring information so the traversal algorithm do not use it.

Review of algorithms: \cite{gander_algorithm_2009}

\cite{boon_robust_2016} Robust discretization of porous media. Complete error analysis with mortar non-compatible case. Seems they use normal fluxes accros
fracture instead of pressure traces. This allows conforming discretization and error results.

\cite{bournival_mesh-geometry_2008} Application of mixed-dimensional approach in mechanics. Beam and shell elements ...

\cite{reichenberger_mixed-dimensional_2006} Finite volume method, fully implicit two phase flow. Cite usage of FRAC3D generator.

\cite{sladkova_bakalarka} Space-time DG with adaptive mesh, need integration of product of functions on different meshes (in 2D). An algorithm 
for computing triangle-triangle intersections in 2D.

\cite{pichot_generalized_2012} DFN + MHFEM. Mortar method for intersections. Focused on formulation not on intersections.

\cite{flemisch_non-matching_2012} (Barbara) Mortad, non=matching, acustics. Theory, structured gird case. No complex intersections.

\cite{mustapha_hybrid_2014} Patent for curiosity.

\cite{mittal_immersed_2005} Immersed boundary. ??

\cite{owen_survey_1998} ??

\cite{kuznetsov_overlapping_1998}

\cite{platis_fast_2003} Original algorithm for line-thetrahedra intersections.

\cite{haines_fast_1991} Line-convex Polyhedra intersections using generalisation of line-clipping algorithm

The initial problem that occurs when working with incompatible meshes of combined dimensions is the efficient 
computation of intersections of the mesh subdomains, in particular 1D-2D, 1D-3D, 2D-3D.
There is a piece of code in Flow123d at the moment which uses means of analytic geometry. In particular, it computes 
an intersection of a line and a plane in 3D by solving Gaussian elimination. However it is not effiecient
and it does not provide barycentric coordinates explicitly.
In this section, we present our latest work on this problematics.

The topic is studied in the bachelor and master thesis of Viktor Fri{\v s} \cite{fris_dp_2015}, who was supervised by 
Jan B{\v r}ezina.
They suggested a solution, based on \cite{yuan_efficient_2003} for the two aspects of the problem: 
\begin{enumerate}[itemsep=-3pt]
\item an efficient identification of the intersecting pairs of elements,
\item an efficient computation of the actual intersection for the single element pair.
\end{enumerate}
The algorithm is based on the methods used in the computer graphics, in particular for the task (b) \plucker
coordinates are employed to efficiently compute 1D-2D intersection in three-dimensional space.

\begin{figure}[!htb]
  \centering
  \setcounter{subfigure}{0}
  \subfloat[1D-3D]{
    \includegraphics[width=0.3\textwidth]{\figpath intersection_13.pdf} }
  \hspace{10pt}
  \subfloat[2D-3D]{
    \includegraphics[width=0.3\textwidth]{\figpath intersection_23.pdf} }
\end{figure}

For the 1D-3D and 2D-3D cases, the basic algorithm is applied on sides and edges of the simplices and 
all the topological information coming from the performed \plucker products is carefully collected
to obtain final intersecting object.
Further in 2D-3D case, an optimized tracing algorithm is suggested to directly obtain the correct order and 
orientation of the edges of the intersection polygon.

\subsection{Element Intersections}
\label{sec:elements_intersections}
In this section, we present algorithms for computing intersection of a pair of simpicial elements of different dimension in the 3D ambient space.

\subsection{\plucker coordinates}
\plucker coordinates represent a line in 3D space.
Considering a line $p$, given by a point $\vc A$ and its directional vector $\vc{u}$, 
the \plucker coordinates of $p$ are defined as
\[ \pi_p = (\vc{u}_p, \vc{v}_p) = (\vc{u}_p, \vc{u}_p\times A). \]
Further we use a permuted inner product
\[\pi_p \odot \pi_q = \vc{u}_p\cdot \vc{v}_q + \vc{u}_q \cdot \vc{v}_p. \]

The sign of the inner product product gives us the relative position of the two lines, 
see \fig{fig:plucker_products}.

\begin{figure}[!htb]
  \begin{center}        
    %\def\svgwidth{0.7\textwidth}
    \includegraphics{\figpath plucker_products.pdf}
  \end{center}
  \caption{Sign of the \plucker product (from \cite{fris_dp_2015}). Dashed line symbolizes that the line 
           is in the back. In the case (c), product is zero which means the lines intersect.}
  \label{fig:plucker_products}
\end{figure}

%Notice the condition on the orientation of the triangle sides. To always satisfy it, we use a
%reference simplex, in which the numbering of nodes and sides and also the orientation is fixed.
%The barycentric coordinates of the intersection point can be computed directly from the \plucker products
%and then we can easily obtain its real coordinates (see \cite{fris_dp_2015} for derivations and details).

\subsection{Intersection Line-Triangle (1D-2D)}
Let us consider a line segment $p$ with end points $\vc A$ and $\vc A + \vc u$ and a triangle $(\vc V_0, \vc V_1, \vc V_2)$ with oriented sides 
$s_i=(V_j, V_k)$, $j=(i+1) mod 3$, $k=(i+2) mod 3$. The inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same sign if and only if there
is an intersection point inside the triangle. In such a case, the inner products provides scaled barycentric coordinates of the intersection on the triangle.
In particular for the barycentric coordinate $w_i$ related to the vertex $V_i$ we have
\[
   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum{j=0}^{2} \pi_p \odot \pi_{s_i} }
\]
Indeed, using the barycentric coordinates the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
The line $p$ have \plucker coordinates $(\vc u, \vc u \times \vc X)$ (\plucker coordinates are invariant to change of initial point). Combining these two expressions we get
\[
   \pi_p \odot \pi_{s_1} = \vc u \cdot (\vc s_1 \times V_2) + \vc s_1 \cdot ( \vc u \times [\vc V_0 + w_1\vc s_2 - w_2 \vc s_1])
   =-w_1 \vc u \cdot (\vc s_1 \times \vc s_2).
\]
Since $\vc s_0 + \vc s_1 + \vc s_2=0$ we have $ \vc s_1 \times \vc s_2 = \vc s_2 \times s_0 = \vc s_0 \times \vc s_1$ and thus
\[
   \pi_p \odot \pi_{s_i} = -w_i \vc u \cdot (\vc v_1 \times \vc v_2).
\]
Having the barycentric coordinates of the intersection on the triangle we can compute also its local coordinate on $p$ from its parametric form:
\[
   X_i  = A_i + t u_i, \text{ for } i=1,2,3
\]
In practical computation we consider $i$ with maximal $|u_i|$.

Next, we shell discuss the case when some of the permuted inner products is zero. Various {\emph pathological} cases are detected and further topological 
information is atached to the intersection data. In fact we test if a barycentric coordinate is under given tolerance 
($\abs{w_i} \le \epsilon$). In the case of one zero coordinate (non-coplanar intersection on the edge)
or two zero coordinates, we add the local edge index or the local vertex index to the intersection, respectively.
When all coordinates are (close to) zero, the line and the triangle are (nearly) coplanar. For every edge $s_i$ we compute
its intersection with the line segment $p$ in terms of the local coordinates $t_i$ and $t_p$. Only intersections with $t_i \in (-\epsilon, 1+\epsilon)$
are accepted, for $t_i$ close to $0$ and $1$ we append the vertex index to the intersection. Edges parallel to $p$ are skipped. 
Finally, we obtain zero, one, or two intersection points with additional topological information. Degenerated case of $p$ laying on the triangle edge is also detected....

Starting with 1D-2D intersecting simplices, all the \plucker coordinates and products must be computed at first.
In case that all \plucker products are nonzero and the intersection point exists, its barycentric coordinates 
can be obtained directly. Otherwise one of the pathologic cases occurs
%
\begin{itemize}[itemsep=-3pt]
\item 1 zero product: line intersects triangle side,
\item 2 zero products: line intersects triangle at its vertex,
\item 3 zero products: line intersects triangle at its vertex and:
  \begin{enumerate}[ itemsep=-3pt]
    \item intersects also the opposite side,
    \item is parallel to the opposite side,
    \item intersects also another triangle vertex.
  \end{enumerate}
\end{itemize}
%
Anyway, in the pathologic case, the intersection of a line and triangle side is solved analyticaly which leads
to a system of two equations with three unknowns. This is then solved using Crammer's rule.

So far, we considered the line and the triangle sides as bisectors. If the 1D-2D intersection is the final object,
we check that the found intersection point lies on the abscissas. Otherwise all the computed data are used for 
further computation. Apart from the coordinates of the intersection points, we also save temporarily its topology
information (vertex, side or edge index).

\paragraph{1D-3D (abscissa-tetrahedron)}
Tetrahedron has six edges, so six \plucker coordinates and products are computed at most. These data are
passed to 1D-2D algorithm described above, which is then run for each pair line -- tetrahedron side. 
There might be two intersection points maximally, which are finally checked that they belong o abscissas.
If the line has its boundary point inside the tetrahedron, the intersection line must be cut
and coordinates of intersection point are interpolated.
Pathologic cases are again carefully processed so we obtain the most extensive topology information we can.
See \cite{fris_dp_2015} for detailed description of all possible cases.

\paragraph{2D-3D (abscissa-tetrahedron)}
The intersection of a triangle and a tetrahedron is a polygon with 7 vertices at maximum. The vertices
are found as intersection points of either triangle side and tetrahedron or tetrahedron edge and triangle.
Therefore we use both algorithms above for 1D-3D and 1D-2D, respectively. Data are again efficiently passed
to lower dimensional problems, so 9 \plucker coordinates and 18 \plucker products are computed.

The array of intersection points is generally not sorted. We use two so called \emph{tracing} algorithms and we
intend to orient the edges of the polygon in the same direction as the triangle is oriented.
If one of the intersection point is pathologic, a general convex hull method is applied using the Monotone 
chain\footnote{Wikibooks, [online 2016-03-01], 
      \url{http://en.wikibooks.org/wiki/Algorithm_Implementation/Geometry/Convex_hull/Monotone_chain}} 
algorithm. The points are sorted using only their barycentric coordinates.

An optimized algorithm has been suggested for non-pathologic cases. At this moment all the collected topology 
data come into play. The algorithm takes advantage by using only the data already computed and also lowers
the complexity to $O(N)$, compared with the Monotone chain complexity $O(N\log N)$ 
($N$ being number of intersection points).

\subsection{Prolongation algorithm}
Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
elements of the same dimension (1D, 2D), in the space of 3D elements (tetrahedrons). 
Obtaining of all the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.
Then we can prolongate the intersection by investigating neighbouring elements of the component.
%
\begin{figure}[!htb]
%   \vspace{0pt}
  \centering    
    \includegraphics[width=\textwidth]{\figpath prolongation_scheme.pdf}
  \caption{Prolongation algorithm for 1D-2D and 2D-3D intersections. }
  \label{fig:prolongation}
\end{figure}

The prolongation algorithm is the same for both 1D and 2D components, see \fig{fig:prolongation}. 
It can be seen as a \emph{breadth-first search}
\footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
algorithm on the graph of 1D and 2D elements, respectively.

After computing the intersection of a pair of elements (line or triangle vs tetrahedron), we fill
two queues with element pairs as candidates for further intersection. If the intersection edge 
(point of line in 1D, edge of polygon in 2D) is inside the tetrahedron, not on its surface, we
get a neighbouring element of the component and push it back together with the current tetrahedron into 
\emph{component prolongation queue}. If the intersection edge is inside the \emph{slave} element 
(line or triangle), i.e. is on the surface of tetrahedron, we get a neighbouring element of the tetrahedron
and push it back together with the current slave element into \emph{3D prolongation queue}.

Then we empty the prolongation queues -- the 3D prolongation queue at first, then the component prolongation queue.
When both queues are empty, all intersections of a component have been found and we continue to look for
another component.

The algorithm is now unified for 1D and 2D in contrast to \cite{fris_dp_2015}, where the component prolongation
queue is emptied at first.

\section{Front tracking algorithm}
\section{Benchmarks}

\section{Conclusions}
TODO:
- line intersection tracking for accelerate 2D-2D intersections
- better handling of special cases in paarticular in relation to prolongations
- better calculation reuse (pass with prolongations)
- optimisation of element intersection - skip unnecessary calculations
\section{Acknowledgement}
The paper was supported in part by the Project OP
VaVpI Centre for Nanomaterials, Advanced Technologies  and Innovations
CZ.1.05/2.1.00/01.0005.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-harv} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

% \begin{thebibliography}{00}
% 
% %% \bibitem[Author(year)]{label}
% %% Text of bibliographic item
% 
% \bibitem[ ()]{}
% 
% \end{thebibliography}
 %\nocite{dip}
 %\bibliographystyle{elsarticle-harv} 
 %\bibliographystyle{elsarticle-num-names} 
 \bibliographystyle{elsarticle-num} 
 \bibliography{paper_intersections.bib}
\end{document}

%\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

-

### 2016-09-21 paper_intersections.tex
Add 13d prolongation description.

@@
 
+\subsubsection{1D-3D prolongation}
+
+\notePE{I suggest to denote IP, IPs intersection point and its plural respectively.}
+% 1d-3d prolongation logic
+% IP is:
+% - 1D element node
+%     - inside tetrahedron
+%         - get the neighboring 1D element
+%         - push to component queue candidate pair [1D neigbor -- tetrahedron]
+%     - on the surface of tetrahedron
+%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%         - get the tetrahedron neighbors on the faces
+%         - push to bulk queue new candidates pairs:
+%             - [current 1D element -- tetrahedron neighbor]
+%             - [1D neighbor -- tetragedron neighbor]
+%             - check whether the candidate pair has not been computed yet
+%             (- if no new prolongation, push empty pair; means IP is on the boundary; 
+%                the element is not closed then -- not fully covered with tetrahedrons)
+% - inside 1D element
+%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%     - get the tetrahedron neighbors on the faces
+%     - push to bulk queue candidate pair [current 1D element -- tetrahedron neighbor]
+%     - check whether the candidate pair has not been computed yet
+%     (- if no new prolongation, push empty pair; same meaning as above)
+
+A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:
+
+\begin{itemize}
+    \item \textbf{IP lies at 1D element node and inside 3D element} \\
+            We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
+    \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
+            We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
+            or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
+            push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
+            If the candidates pair has been investigated already, we skip it.
+    \item \textbf{IP lies inside 1D element node (therefore must be on the surface of 3D element)} \\
+            The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
+            there is no 1D neighbor.
+\end{itemize}
+
 \section{Front tracking algorithm}

### 2016-09-21 paper_intersections.tex
Add general description of prolongation logic.

@@
 
-A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:
+% A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:
 
+% \begin{itemize}
+%     \item \textbf{IP lies at 1D element node and inside 3D element} \\
+%             We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
+%     \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
+%             We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
+%             or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
+%             push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
+%             If the candidates pair has been investigated already, we skip it.
+%     \item \textbf{IP lies inside 1D element (therefore must be on the surface of 3D element)} \\
+%             The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
+%             there is no 1D neighbor.
+% \end{itemize}
+
+A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases (applies both for 1D-3D and 2D-3D):
 \begin{itemize}
-    \item \textbf{IP lies at 1D element node and inside 3D element} \\
-            We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
-    \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
-            We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
-            or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
-            push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
+    \item \textbf{IP lies on component element side and inside bulk element} \\
+            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
+            We find the component neighboring elements over the sides and push a new candidate pair
+            [component neighbor -- current bulk element] into component queue.
+    \item \textbf{IP lies on component element side and on the surface of bulk element} \\
+            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
+            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
+            push the following new candidates pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
             If the candidates pair has been investigated already, we skip it.
-    \item \textbf{IP lies inside 1D element node (therefore must be on the surface of 3D element)} \\
-            The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
-            there is no 1D neighbor.
+    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
+            The same as before, but we push only [current component element -- bulk neighbor] candidates pairs, since
+            there is no component neighbor.
 \end{itemize}
+
+% 2d-3d prolongation logic CURRENT
+% IP is:
+% - inside 2D element side
+%     - inside 3D element
+%         - get the neighboring 2D elements over the side
+%         - push to component queue candidates pair [2D neigbor -- current 3D element]
+% - inside the face of 3D element
+%     - get the neighboring 3D element over the face
+%     - push to bulk queue candidate pair [2D neighbor -- 3D element]
+% 
+% 2d-3d prolongation logic WITH FUTURE CORRECTIONS
+% IP is:
+% - on 2D element side
+%     - find 2D element sides (if at node) and the corresponding neighbors
+%     - inside 3D element
+%         - push to component queue candidates pairs [2D neigbor -- current 3D element]
+%     - on the surface of 3D element
+%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%         - get the 3D neighbors over the faces
+%         - push to bulk queue new candidates pairs
+%             - [current 2D element -- 3D neighbor]
+%             - [2D neighbor -- 3D neighbor] (all combinations)
+%             - check whether the candidate pair has not been computed yet
+% - inside the 2D element (=> on the surface of 3D element)
+%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%     - get the 3D neighbors over the faces
+%     - push to bulk queue new candidates pairs [current 2D element -- 3D neighbor]
+%     - check whether the candidate pair has not been computed yet
 

### 2016-09-22 paper_intersections.tex
Add text diagram of prolongation from presentation, add some comments.

@@
 
+\notePE{I suggest to denote IP, IPs intersection point and its plural respectively.}
+
+\notePE{It seems to me, that we can really describe the prolongation in general, for 1D and 2D, 
+refering to them as components. I tried to do so..}
+
+\notePE{We need proper definitions of terms we use: \\
+\emph{component} is a set of connected elements of the same lower dimension (1D, 2D)\\
+\emph{bulk} is a set of 3D elements\\
+% or slave, master...
+\emph{candidates pair}  is a pair of a component element and a bulk element, that might intersect
+each other (due to intersection of their bounding boxes or prolongation result)
+\emph{pathologic, special, degenerate case ??}
+}
+
+\notePE{Do you want to use American 'neighbor' or all other English 'neighbour'? (I prefer non-american.. to be unified at the end..)}
+
 \subsection{Prolongation algorithm}
 Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same dimension (1D, 2D), in the space of 3D elements (tetrahedrons). 
-Obtaining of all the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.
-Then we can prolongate the intersection by investigating neighbouring elements of the component.
+elements of the same lower dimension (1D, 2D), in the space of 3D elements. 
+Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.
+Then we can prolongate the intersection by investigating neighbouring elements.
 %
@@
 \footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
-algorithm on the graph of 1D and 2D elements, respectively.
+algorithm on the graph of component elements.
+
+\textbf{breadth first search} algorithm:
+  \begin{enumerate}
+    \item\label{en:first} Get next unprocessed component element $k$.
+    \item Find intersection candidates $\mathcal K$ in bulk mesh (3D elements).
+    \item \label{en:q2}For $K\in \mathcal K$ compute intersection $(k, K)$.  
+    \item Push the intersection neigbours into queues: $(k, L) \to Q_b$, $(l, K) \to Q_c$. 
+    \item While $(l, L) \in Q_b$ check intersection $(l, L)$. Append queues.
+    \item Pop pair from $Q_c$. (move to the next component element: go to \ref{en:q2}).
+    \item If $Q_c$ is empty, go to \ref{en:first}.
+  \end{enumerate}
+  Prerequisites:
+  \begin{itemize}
+   \item need information about element connectivity (mesh preprocessing)
+%   \item mark and check already inspected pairs. Marking elements + hashing.
+   \item find the starting intersection -- AABB (Axes Aligned Bounding Boxes) 
+   \item possibly create Bounding Interval Hierarchy (BIH)
+%   \item Pass already known information with pairs.
+%   \item Deal with degenerated cases.
+  \end{itemize}
 
@@
 
-\subsubsection{1D-3D prolongation}
-
-\notePE{I suggest to denote IP, IPs intersection point and its plural respectively.}
+% \subsubsection{1D-3D prolongation}
 % 1d-3d prolongation logic

### 2016-09-22 paper_intersections.tex
Change plucker sign figure.
Add new tracing algorithm.

--- 2016-09-21 paper_intersections.tex
@@
 \usepackage{booktabs}
+\usepackage[vlined, linesnumbered, ruled]{algorithm2e}
+%\usepackage{float}
+%\newfloat{algorithm}{t}{lop}
 
@@
 \newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
-\newcommand{\plucker}{Pl\"{u}cker}
+\newcommand{\plucker}{Pl\"{u}cker }
 
@@
 
-\subsection{Element Intersections}
+\section{Element Intersections}
 \label{sec:elements_intersections}
 In this section, we present algorithms for computing intersection of a pair of simpicial elements of different dimension in the 3D ambient space.
+In particular we are interested in intersection of 1D-2D, 1D-3D, 2D-2D, 2D-3D simplices. In general the intersection can be a point, a line segment or a polygon.
+All these three objects are represented as a vector of the vertices called \emph{intersection points}. Basic idea is to compute 1D-2D case using the 
+\plucker coordinates and reduce all other cases to that case.
 
-\subsection{\plucker coordinates}
+The intersection point data structure keeps for each of the two intersection simplices:
+\begin{itemize}
+ \item Barycentric coordinate of the intersection.
+ \item Dimenstion of the most specific subsimplex (face, edge, vertex) where the point lies.
+ \item Indice of the most specific subelement.
+\end{itemize}
+Further, keep sign of the permuted inner product  we store
+In order to catch various degenerate cases, the intersec
+
+\subsection{\plucker Coordinates}
 \plucker coordinates represent a line in 3D space.
@@
   \begin{center}        
-    %\def\svgwidth{0.7\textwidth}
-    \includegraphics{\figpath plucker_products.pdf}
+    \def\svgwidth{0.7\textwidth}
+    \input{\figpath plucker_products.pdf_tex}
+%    \includegraphics{\figpath plucker_products.pdf}
   \end{center}
-  \caption{Sign of the \plucker product (from \cite{fris_dp_2015}). Dashed line symbolizes that the line 
-           is in the back. In the case (c), product is zero which means the lines intersect.}
+  \caption{Sign of the permuted inner product is related to the relative position of two oriented lines. Dashed line symbolizes that the line 
+           is in the back, the llines intersect in the last case.}
   \label{fig:plucker_products}
@@
 \subsection{Intersection Line-Triangle (1D-2D)}
-Let us consider a line segment $p$ with end points $\vc A$ and $\vc A + \vc u$ and a triangle $(\vc V_0, \vc V_1, \vc V_2)$ with oriented sides 
-$s_i=(V_j, V_k)$, $j=(i+1) mod 3$, $k=(i+2) mod 3$. The inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same sign if and only if there
-is an intersection point inside the triangle. In such a case, the inner products provides scaled barycentric coordinates of the intersection on the triangle.
+Let us consider a line $p$, with parametric equation $\vc X = \vc A + t\vc u$, $t\in(0,1)$ and a triangle given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
+with oriented sides $s_i=(V_j, V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same sign if and only if there
+is an intersection point with the       line $p$ inside the triangle. In such a case, the inner products provides scaled barycentric coordinates of the intersection on the triangle.
 In particular for the barycentric coordinate $w_i$ related to the vertex $V_i$ we have
 \[
-   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum{j=0}^{2} \pi_p \odot \pi_{s_i} }
+   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum_{j=0}^{2} \pi_p \odot \pi_{s_i} }
 \]
@@
 \]
-Since $\vc s_0 + \vc s_1 + \vc s_2=0$ we have $ \vc s_1 \times \vc s_2 = \vc s_2 \times s_0 = \vc s_0 \times \vc s_1$ and thus
+Since $\vc s_0 + \vc s_1 + \vc s_2=0$ we have $ \vc s_1 \times \vc s_2 = \vc s_2 \times \vc s_0 = \vc s_0 \times \vc s_1$ and thus
 \[
@@
 \]
-In practical computation we consider $i$ with maximal $|u_i|$.
+For practical computation we use $i$ with maximal $|u_i|$.
 
-Next, we shell discuss the case when some of the permuted inner products is zero. Various {\emph pathological} cases are detected and further topological 
-information is atached to the intersection data. In fact we test if a barycentric coordinate is under given tolerance 
-($\abs{w_i} \le \epsilon$). In the case of one zero coordinate (non-coplanar intersection on the edge)
-or two zero coordinates, we add the local edge index or the local vertex index to the intersection, respectively.
+Next, we shell discuss the case when some of the permuted inner products is zero. In fact we test if any barycentric coordinate is under given tolerance 
+($\abs{w_i} \le \epsilon$). Various \emph{pathological} cases are detected and further topological 
+information is atached to the intersection data.  In the case of one zero coordinate (non-coplanar intersection on the edge)
+or two zero coordinates (intersection in the vertex), we add the local edge index or the local vertex index to the intersection, respectively.
 When all coordinates are (close to) zero, the line and the triangle are (nearly) coplanar. For every edge $s_i$ we compute
 its intersection with the line segment $p$ in terms of the local coordinates $t_i$ and $t_p$. Only intersections with $t_i \in (-\epsilon, 1+\epsilon)$
-are accepted, for $t_i$ close to $0$ and $1$ we append the vertex index to the intersection. Edges parallel to $p$ are skipped. 
-Finally, we obtain zero, one, or two intersection points with additional topological information. Degenerated case of $p$ laying on the triangle edge is also detected....
+are accepted, for $t_i$ close to $0$ and $1$ we append the vertex index to the intersection. Edges parallel to $p$ or lying on the $p$ are skipped.
+Finally, we obtain zero, one, or two intersection points with additional topological information.
 
-Starting with 1D-2D intersecting simplices, all the \plucker coordinates and products must be computed at first.
-In case that all \plucker products are nonzero and the intersection point exists, its barycentric coordinates 
-can be obtained directly. Otherwise one of the pathologic cases occurs
-%
-\begin{itemize}[itemsep=-3pt]
-\item 1 zero product: line intersects triangle side,
-\item 2 zero products: line intersects triangle at its vertex,
-\item 3 zero products: line intersects triangle at its vertex and:
-  \begin{enumerate}[ itemsep=-3pt]
-    \item intersects also the opposite side,
-    \item is parallel to the opposite side,
-    \item intersects also another triangle vertex.
-  \end{enumerate}
-\end{itemize}
-%
-Anyway, in the pathologic case, the intersection of a line and triangle side is solved analyticaly which leads
-to a system of two equations with three unknowns. This is then solved using Crammer's rule.
+TODO:
+We should distinguish "special" case and "degenerate" case. The later one is the case when line lies in the plane of the triangle. The first case should be
+treated as usual only set aditional topology info about vertex or edge. The degenerate case is not necessary to investigate in the case of auxiliary
+intersection only in the case of final intersection. Need to verify it since it is not the case in current code.
 
-So far, we considered the line and the triangle sides as bisectors. If the 1D-2D intersection is the final object,
-we check that the found intersection point lies on the abscissas. Otherwise all the computed data are used for 
-further computation. Apart from the coordinates of the intersection points, we also save temporarily its topology
-information (vertex, side or edge index).
+We distinguis two variants of the desired result: the auxiliary intersection used as subprocedure of the other intersections and the final intersection.
+In the first case we just return the array of the intersection points with the line.
+ Degenerated case of $p$ laying on the triangle edge is also detected....
 
-\paragraph{1D-3D (abscissa-tetrahedron)}
-Tetrahedron has six edges, so six \plucker coordinates and products are computed at most. These data are
-passed to 1D-2D algorithm described above, which is then run for each pair line -- tetrahedron side. 
+Intersection with line segment ... (final 1D-2D intersection)
+
+\subsection{Intersection Line-Teraherdon (1D-3D)}
+We consider a line $p$ and a tetraherdon...
+Tetrahedron has six edges, so six \plucker coordinates and inner products are computed at most. These data are
+passed to the 1D-2D algorithm described above, which is applied to the every face of the tetrahedron face.
+
 There might be two intersection points maximally, which are finally checked that they belong o abscissas.
@@
 
-\paragraph{2D-3D (abscissa-tetrahedron)}
-The intersection of a triangle and a tetrahedron is a polygon with 7 vertices at maximum. The vertices
+\subsection{Intersection Triangle-Tetrahedron (2D-3D)}
+The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is a polygon with 7 vertices at maximum. The sides of the polygon
+are coincident with either sides of $S_3$ or with faces of the $S_4$. So a vertex of the polygon
+can arise from intersection of a side with a face or an edge with $S_3$ or from a vertex of $S_3$.
+So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
+to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
+
+Computation of the intersection polygon consist of three parts. In the first part (Algorithm \ref{algo:colect_23_ip_triangle}), we compute intersection points
+on baundary if $S_3$ using the line-tetrahedron intersection algorithm for every side. There are 0,1, or 2 intersection points
+on every side and the points are already sorted according to the side orientation, which match orientation of the intersection polygon. So, passing
+through the all sides and appending the points into $I$ provides as with incomplete intersectionn polygon but in the correct order.
+Then we proceed to the second part (Algorithm \ref{algo:collect_23_ip_edges}). Using the line-triangle intersection algorithm for edges of $S_4$
+we obtain points from interior of $S_3$ and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
+with faces of $S_4$. Every point $p$ from the first part of the algorithm that is not a veertex of $S_3$ belongs to a face $f$ of $S_4$, we know from the order of the points
+if the face comes before or after the point in the intersection polygon, in the first case we set $F[0,f] =p$ inthe second case we set $F[1,f]=p$. 
+Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
+intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.
+
+Finally in the third part (Algorithm \ref{algo:order_23}), the table $F$ than allows us to modify array of successors $P$ and get $I$ in correct order as the list $K$.
+
+\begin{algorithm}
+  \SetKw{And}{And}
+  \DontPrintSemicolon
+  \KwIn{input data}
+  \KwOut{List of IPs sorted output data}  
+  $I =\emptyset$\tcp*{Intersection polygon.}
+  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
+  \For{side $s$ of $S_3$}{ 
+    \nllabel{line:1_3}
+    $L$ = intersection($s, S_4$)  \tcp*{List of max.\ two points.}
+    process point($L[0]$, 0)\; 
+    process point($L[-1]$, 1)
+  }
+  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
+  \caption{2d-3d intersection, points on triangle boundary}
+  \label{algo:colect_23_ip_triangle}
+\end{algorithm}
+
+\begin{algorithm}
+  \SetKw{And}{And}
+  \DontPrintSemicolon
+  \KwIn{intersection point $p$, face relation indicator $i$}
+  \KwOut{update of $I$ and $F$}
+  \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
+  set $j$ to index of $p$ in $I$\;
+  \lIf{ $p$ is on face $f$}{ F[i,f]=j}
+  \uElseIf{ $p$ is on edge $e$}{
+    compute sign of intersection($e$, $S_3$)\;
+    sort faces $f_0$, $f_1$ coincident with $e$\;
+    F[i, $f_i$]=j
+  }
+  \ElseIf{ $p$ is on vertex $v$ of $S_4$}{
+      \For{face $f$ coincident with $v$}{
+         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
+      }
+  }
+  mark all edges of $S_4$ the $p$ lies on
+
+  \caption{process point( $p$, $i$ )}
+  \label{algo:collect_23_ip_edges}
+\end{algorithm}
+
+\begin{algorithm}
+  \SetKw{And}{And}
+  \DontPrintSemicolon
+  \KwIn{input data}
+  \KwOut{List of IPs sorted output data}  
+  \For{unmarked edge $e$ of $S_4$}{
+    $p$ = intersection($e, S_3$)\;
+    append $p$ to $I$\;
+    set $j$ to index of $p$ in $I$\;
+    \uIf{ $p$ is inside of $e$}{ 
+        sort faces $f_0$, $f_1$ coincident with $e$\;
+        F[0, $f_0$]=j\;
+        F[1, $f_1$]=j
+    } %else
+    \Else($p$ on the vertex $v$ of $S_4$){       
+      \For{face $f$ coincident with $v$}{
+         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
+      }
+    }
+  }
+  \caption{2d-3d intersection, points in triangle interior}
+  \label{algo:order_23}
+\end{algorithm}
+
+\begin{algorithm}
+  \SetKw{To}{To}
+  \DontPrintSemicolon
+  \KwIn{all points in $I$}
+  \KwOut{polygon in $J$ in correct order}  
+  $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
+  \lFor{ $f$ is face of $S_4$}{$P[ F[0,f] ] = F[1, f]$}
+  $i=0$  
+  \lFor{$n=0$ \To $\abs{I}-1$}{
+    $K[n]=I[i]$
+    $i=P[i]$
+  }    
+  \caption{2d-3d intersection, finish sort of points}
+\end{algorithm}
+
+ List $in[f]$ contains index of the intersection point that follows after $f$ on the boundary of traced polygon, 
+ similarly $out[f]$ stores index of the intersection point that preeceeds the face $f$.
+
+Possible cases for processing $L$:
+\begin{enumerate}
+ \item Regular case, $L$ consists of two intersections $p$, $q$ sorted by orientation of $s$, laying inside of $s$.
+
+ If $p$ is on the edge $e$ of $S_4$ compute sign of intersection($e$, $S_3$), sort the faces $f_0$, $f_1$ coincident with $e$
+ and set $in[f_0]$ to index of $p$ in $L$. Similarly if $q$ is on the edge, set $out[f_1]$ to index of $q$ in $L$.
+
+ If $p$ is in vertex $v$ of $S_4$, for every face $f$ coincident with $v$ set
+ in[$f$] to index of $p$ unless there is some index already set. So, we do not over ride
+ entries comming from the edge intersections. Similarly set out[$f$] if $q$ is in vertex of $S_4$.
+
+ If $p$ is on face $f_0$ of $S_4$, set $in[f_0]$ to index of $p$. Similarly, if $q$ is on face $f_1$ of $S_4$, set $out[f_1]$ to index of $q$.
+ laying on faces $f_p$, $f_q$ of $S_4$.
+
+ \item $L$ consists of a single intersection point $p$ (touching $S_4$)
+
+ If $p$ is on edge, compute sign of intersection($e$, $S_3$), sort the faces $f_0$, $f_1$,
+ set $in[f_0]$ and $out[f_1]$ to index of $p$.
+
+ If $p$
+\end{enumerate}
+
+How tracing works.
+\begin{itemize}
+ \item If there are no intersections in vertex of $S_4$. 
+\end{itemize}
+
+intersection polygon
 are found as intersection points of either triangle side and tetrahedron or tetrahedron edge and triangle.
 Therefore we use both algorithms above for 1D-3D and 1D-2D, respectively. Data are again efficiently passed
-to lower dimensional problems, so 9 \plucker coordinates and 18 \plucker products are computed.
+to lower dimensional problems, so
 
@@
 ($N$ being number of intersection points).
+
+\subsection{Tracking boundary of the intersection polygon}
 
@@
 queue is emptied at first.
-
-\subsubsection{1D-3D prolongation}
-
-\notePE{I suggest to denote IP, IPs intersection point and its plural respectively.}
-% 1d-3d prolongation logic
-% IP is:
-% - 1D element node
-%     - inside tetrahedron
-%         - get the neighboring 1D element
-%         - push to component queue candidate pair [1D neigbor -- tetrahedron]
-%     - on the surface of tetrahedron
-%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
-%         - get the tetrahedron neighbors on the faces
-%         - push to bulk queue new candidates pairs:
-%             - [current 1D element -- tetrahedron neighbor]
-%             - [1D neighbor -- tetragedron neighbor]
-%             - check whether the candidate pair has not been computed yet
-%             (- if no new prolongation, push empty pair; means IP is on the boundary; 
-%                the element is not closed then -- not fully covered with tetrahedrons)
-% - inside 1D element
-%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
-%     - get the tetrahedron neighbors on the faces
-%     - push to bulk queue candidate pair [current 1D element -- tetrahedron neighbor]
-%     - check whether the candidate pair has not been computed yet
-%     (- if no new prolongation, push empty pair; same meaning as above)
-
-A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:
-
-\begin{itemize}
-    \item \textbf{IP lies at 1D element node and inside 3D element} \\
-            We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
-    \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
-            We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
-            or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
-            push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
-            If the candidates pair has been investigated already, we skip it.
-    \item \textbf{IP lies inside 1D element node (therefore must be on the surface of 3D element)} \\
-            The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
-            there is no 1D neighbor.
-\end{itemize}
 

### 2016-09-22 paper_intersections.tex

@@
   \begin{center}        
-    \def\svgwidth{0.7\textwidth}
-    \input{\figpath plucker_products.pdf_tex}
+    \includegraphics[width=0.7\textwidth]{\figpath plucker_product.pdf}
 %    \includegraphics{\figpath plucker_products.pdf}
@@
   \caption{Sign of the permuted inner product is related to the relative position of two oriented lines. Dashed line symbolizes that the line 
-           is in the back, the llines intersect in the last case.}
+           is in the back, the lines intersect in the last case.}
   \label{fig:plucker_products}
@@
 \subsection{Tracking boundary of the intersection polygon}
+\notePE{I suggest to denote IP, IPs intersection point and its plural respectively.}
+
+\notePE{It seems to me, that we can really describe the prolongation in general, for 1D and 2D, 
+refering to them as components. I tried to do so..}
+
+\notePE{We need proper definitions of terms we use: \\
+\emph{component} is a set of connected elements of the same lower dimension (1D, 2D)\\
+\emph{bulk} is a set of 3D elements\\
+% or slave, master...
+\emph{candidates pair}  is a pair of a component element and a bulk element, that might intersect
+each other (due to intersection of their bounding boxes or prolongation result)
+\emph{pathologic, special, degenerate case ??}
+}
+
+\notePE{Do you want to use American 'neighbor' or all other English 'neighbour'? (I prefer non-american.. to be unified at the end..)}
 
@@
 Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same dimension (1D, 2D), in the space of 3D elements (tetrahedrons). 
-Obtaining of all the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.
-Then we can prolongate the intersection by investigating neighbouring elements of the component.
+elements of the same lower dimension (1D, 2D), in the space of 3D elements. 
+Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.
+Then we can prolongate the intersection by investigating neighbouring elements.
 %
@@
 queue is emptied at first.
+
+% \subsubsection{1D-3D prolongation}
+% 1d-3d prolongation logic
+% IP is:
+% - 1D element node
+%     - inside tetrahedron
+%         - get the neighboring 1D element
+%         - push to component queue candidate pair [1D neigbor -- tetrahedron]
+%     - on the surface of tetrahedron
+%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%         - get the tetrahedron neighbors on the faces
+%         - push to bulk queue new candidates pairs:
+%             - [current 1D element -- tetrahedron neighbor]
+%             - [1D neighbor -- tetragedron neighbor]
+%             - check whether the candidate pair has not been computed yet
+%             (- if no new prolongation, push empty pair; means IP is on the boundary; 
+%                the element is not closed then -- not fully covered with tetrahedrons)
+% - inside 1D element
+%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%     - get the tetrahedron neighbors on the faces
+%     - push to bulk queue candidate pair [current 1D element -- tetrahedron neighbor]
+%     - check whether the candidate pair has not been computed yet
+%     (- if no new prolongation, push empty pair; same meaning as above)
+
+% A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:
+
+% \begin{itemize}
+%     \item \textbf{IP lies at 1D element node and inside 3D element} \\
+%             We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
+%     \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
+%             We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
+%             or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
+%             push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
+%             If the candidates pair has been investigated already, we skip it.
+%     \item \textbf{IP lies inside 1D element (therefore must be on the surface of 3D element)} \\
+%             The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
+%             there is no 1D neighbor.
+% \end{itemize}
+
+A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases (applies both for 1D-3D and 2D-3D):
+\begin{itemize}
+    \item \textbf{IP lies on component element side and inside bulk element} \\
+            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
+            We find the component neighboring elements over the sides and push a new candidate pair
+            [component neighbor -- current bulk element] into component queue.
+    \item \textbf{IP lies on component element side and on the surface of bulk element} \\
+            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
+            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
+            push the following new candidates pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
+            If the candidates pair has been investigated already, we skip it.
+    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
+            The same as before, but we push only [current component element -- bulk neighbor] candidates pairs, since
+            there is no component neighbor.
+\end{itemize}
+
+% 2d-3d prolongation logic CURRENT
+% IP is:
+% - inside 2D element side
+%     - inside 3D element
+%         - get the neighboring 2D elements over the side
+%         - push to component queue candidates pair [2D neigbor -- current 3D element]
+% - inside the face of 3D element
+%     - get the neighboring 3D element over the face
+%     - push to bulk queue candidate pair [2D neighbor -- 3D element]
+% 
+% 2d-3d prolongation logic WITH FUTURE CORRECTIONS
+% IP is:
+% - on 2D element side
+%     - find 2D element sides (if at node) and the corresponding neighbors
+%     - inside 3D element
+%         - push to component queue candidates pairs [2D neigbor -- current 3D element]
+%     - on the surface of 3D element
+%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%         - get the 3D neighbors over the faces
+%         - push to bulk queue new candidates pairs
+%             - [current 2D element -- 3D neighbor]
+%             - [2D neighbor -- 3D neighbor] (all combinations)
+%             - check whether the candidate pair has not been computed yet
+% - inside the 2D element (=> on the surface of 3D element)
+%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%     - get the 3D neighbors over the faces
+%     - push to bulk queue new candidates pairs [current 2D element -- 3D neighbor]
+%     - check whether the candidate pair has not been computed yet
 

### 2016-09-23 paper_intersections.tex
Fix substantial bug in composing final permutation.
Fix one of the algorithms.
Minor improvements and some notes in plucker coords sections.

@@
 \label{sec:elements_intersections}
-In this section, we present algorithms for computing intersection of a pair of simpicial elements of different dimension in the 3D ambient space.
+In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space.
 In particular we are interested in intersection of 1D-2D, 1D-3D, 2D-2D, 2D-3D simplices. In general the intersection can be a point, a line segment or a polygon.
-All these three objects are represented as a vector of the vertices called \emph{intersection points}. Basic idea is to compute 1D-2D case using the 
-\plucker coordinates and reduce all other cases to that case.
+All these three objects are represented as a vector of vertices called \emph{intersection points}. The fundamental idea is to compute intersection of 1D-2D simplices using the 
+\plucker coordinates and reduce all other cases to this one.
 
 The intersection point data structure keeps for each of the two intersection simplices:
+\notePE{Subsimplex or subelement?}
 \begin{itemize}
  \item Barycentric coordinate of the intersection.
- \item Dimenstion of the most specific subsimplex (face, edge, vertex) where the point lies.
- \item Indice of the most specific subelement.
+ \item Dimension of the most specific subsimplex (face, edge, vertex) where the point lies.
+ \item Index of the most specific subelement.
 \end{itemize}
-Further, keep sign of the permuted inner product  we store
-In order to catch various degenerate cases, the intersec
+Further, we store the sign of the permuted inner product
+in order to detect various special and degenerate cases.
 
@@
 
-The sign of the inner product product gives us the relative position of the two lines, 
+The sign of the permuted inner product gives us the relative position of the two lines, 
 see \fig{fig:plucker_products}.
@@
   \end{center}
-  \caption{Sign of the permuted inner product is related to the relative position of two oriented lines. Dashed line symbolizes that the line 
-           is in the back, the lines intersect in the last case.}
+  \caption{Sign of the permuted inner product is related to the relative position of the two oriented lines.
+Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
+           \notePE{circle dot permuted inner product}}
   \label{fig:plucker_products}
@@
 \subsection{Intersection Line-Triangle (1D-2D)}
-Let us consider a line $p$, with parametric equation $\vc X = \vc A + t\vc u$, $t\in(0,1)$ and a triangle given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
+\notePE{In this paragraph we investigate real lines. Trimming comes later when tolerance is denoted, see next PE note.}
+Let us consider a line $p$ with parametric equation $\vc X = \vc A + t\vc u$, $t\in\R$ and a triangle given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
 with oriented sides $s_i=(V_j, V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same sign if and only if there
@@
 \]
-For practical computation we use $i$ with maximal $|u_i|$.
+We use $i$ with maximal $|u_i|$ for practical computation.
 
-Next, we shell discuss the case when some of the permuted inner products is zero. In fact we test if any barycentric coordinate is under given tolerance 
+Next, we shall discuss the case when some of the permuted inner products are zero. In fact, we test if any barycentric coordinate is under given tolerance 
 ($\abs{w_i} \le \epsilon$). Various \emph{pathological} cases are detected and further topological 
@@
 In the first case we just return the array of the intersection points with the line.
+\notePE{In the first case, we do not trim the line (We need both IPs (if there are two), for 1D-3D).
+In the final case, we need to check that also $t_p \in (-\epsilon, 1+\epsilon)$.
+That is the current state.}
  Degenerated case of $p$ laying on the triangle edge is also detected....
@@
       }
+      mark all edges of $S_4$ coincident with $v$
     }
@@
   $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
-  \lFor{ $f$ is face of $S_4$}{$P[ F[0,f] ] = F[1, f]$}
+  \For{ $f$ is face of $S_4$}{
+    \lIf{$F[1,f] \ne F[1,f]$}{$P[ F[1,f] ] = F[0, f]$} 
+  }
   $i=0$
+
   \lFor{$n=0$ \To $\abs{I}-1$}{

### 2016-09-23 paper_intersections.tex
Comments on 2d-3d.

@@
 
-Computation of the intersection polygon consist of three parts. In the first part (Algorithm \ref{algo:colect_23_ip_triangle}), we compute intersection points
-on baundary if $S_3$ using the line-tetrahedron intersection algorithm for every side. There are 0,1, or 2 intersection points
+Computation of the intersection polygon consists of three parts. In the first part (Algorithm \ref{algo:colect_23_ip_triangle}), we compute intersection points
+on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every of its sides. There are 0,1, or 2 intersection points
 on every side and the points are already sorted according to the side orientation, which match orientation of the intersection polygon. So, passing
-through the all sides and appending the points into $I$ provides as with incomplete intersectionn polygon but in the correct order.
+through all the sides and appending the points into $I$ provides us with incomplete intersection polygon but in the correct order.
+\notePE{Comment on process point (Algorithm \ref{algo:process_point}), face relation indicator, I would move description of face table here, since I looked at algorithm1 here, from it skipped to process point and I got lost..}
+
+\notePE{If IP lies on an edge(s) of $S_4$, we create a mark so we exclude the edges from further computation in Algorithm \ref{algo:collect_23_ip_edges}.}
+
+\notePE{In process point, we set for all the face of the vertex, if we coming through the vertex in or out the $S_4$.
+I understand that the condition on line 10 means, that we do not overwrite info if there is another IP on that face..}
+
+\notePE{I corrected the algorithm references. Please check, it is ok now..}
+
 Then we proceed to the second part (Algorithm \ref{algo:collect_23_ip_edges}). Using the line-triangle intersection algorithm for edges of $S_4$
 we obtain points from interior of $S_3$ and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
-with faces of $S_4$. Every point $p$ from the first part of the algorithm that is not a veertex of $S_3$ belongs to a face $f$ of $S_4$, we know from the order of the points
-if the face comes before or after the point in the intersection polygon, in the first case we set $F[0,f] =p$ inthe second case we set $F[1,f]=p$. 
+with faces of $S_4$.
+Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_3$ belongs to a face $f$ of $S_4$; we know from the order of the points
+whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
 Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
@@
     process point($L[-1]$, 1)
+    \notePE{Isn't it clearer to write the two process point lines into cycle over L?}
   }
   \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
+  \notePE{I am not sure if I understand the notation '($[-1]$)', can be explained?
+The last line then checks if first and last IPs, if they are not duplicates..??}
   \caption{2d-3d intersection, points on triangle boundary}
@@
   \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
+  \notePE{I am missing the check whether IP is vertex of $S_3$ as referred in text.
+  So what if it is a vertex?}\;
   set $j$ to index of $p$ in $I$\;
@@
   \caption{process point( $p$, $i$ )}
-  \label{algo:collect_23_ip_edges}
+  \label{algo:process_point}
 \end{algorithm}
@@
   \caption{2d-3d intersection, points in triangle interior}
-  \label{algo:order_23}
+  \label{algo:collect_23_ip_edges}
 \end{algorithm}
@@
   \KwIn{all points in $I$}
-  \KwOut{polygon in $J$ in correct order}  
+  \KwOut{polygon in $J$ in correct order \notePE{J should be K ?}}  
   $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
@@
     \lIf{$F[1,f] \ne F[1,f]$}{$P[ F[1,f] ] = F[0, f]$} 
+    \notePE{condition should be $F[0,f] \ne F[1,f]$ ? I don't understand: successor indices should be switched?
+    This way there would be same two indices..}
   }
@@
   \caption{2d-3d intersection, finish sort of points}
+  \label{algo:order_23}
 \end{algorithm}

### 2016-09-23 paper_intersections.tex
Partial changes in algorithms.

--- 2016-09-22 paper_intersections.tex
@@
   $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
+  $V =\emptyset$\tcp*{$S_4$ vertex intersections.}
   \For{side $s$ of $S_3$}{ 
@@
 \begin{algorithm}
+  \caption{process point( $p$, $i$ )}
+
   \SetKw{And}{And}
@@
   \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
+  \If{ $p$ is not vertex of $S_3$}{    
     set $j$ to index of $p$ in $I$\;
@@
     \uElseIf{ $p$ is on edge $e$}{
-    compute sign of intersection($e$, $S_3$)\;
-    sort faces $f_0$, $f_1$ coincident with $e$\;
-    F[i, $f_i$]=j
+        F[i, $e$]=j
     }
     \ElseIf{ $p$ is on vertex $v$ of $S_4$}{
-      \For{face $f$ coincident with $v$}{
-         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
+        F[i, $v$] =j
    }
   }    
-  mark all edges of $S_4$ the $p$ lies on
-
-  \caption{process point( $p$, $i$ )}
-  \label{algo:collect_23_ip_edges}
 \end{algorithm}
@@
 \begin{algorithm}
+  \label{algo:collect_23_ip_edges}
+  \caption{2d-3d intersection, points in triangle interior}
+
   \SetKw{And}{And}
@@
   \KwOut{List of IPs sorted output data}  
-  \For{unmarked edge $e$ of $S_4$}{
+  \For{edge $e$ of $S_4$}{
     $p$ = intersection($e, S_3$)\;
+    \uIf{ $p$ is on boundary of $S_3$}{
+
+    }
+    \Else{
         append $p$ to $I$\;
@@
         \Else($p$ on the vertex $v$ of $S_4$){       
+        append $j$ to $V$
         \For{face $f$ coincident with $v$}{
@@
         }
+        mark all edges of $S_4$ coincident with $v$
         }
      }   
-  \caption{2d-3d intersection, points in triangle interior}
-  \label{algo:order_23}
+  }
 \end{algorithm}
@@
 \begin{algorithm}
+  \caption{2d-3d intersection, finish sort of points}  
+  \label{algo:order_23}
+
   \SetKw{To}{To}
@@
   \KwIn{all points in $I$}
-  \KwOut{polygon in $J$ in correct order}  
+  \KwOut{polygon in $K$ in correct order}  
+  \If{\abs{V} = 3}{
+
+  }
   $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
-  \lFor{ $f$ is face of $S_4$}{$P[ F[0,f] ] = F[1, f]$}
+  \For{ $f$ is face of $S_4$}{
+    \lIf{$F[1,f] \ne F[1,f]$}{$P[ F[1,f] ] = F[0, f]$}
   $i=0$  
@@
   }    
-  \caption{2d-3d intersection, finish sort of points}
 \end{algorithm}

### 2016-09-23 paper_intersections.tex
Improve some definitions.

--- 2016-09-23 paper_intersections.tex
@@
 In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
-In particular we are interested in intersection of 1D-2D, 1D-3D, 2D-2D, 2D-3D simplices. In general the intersection can be a point, a line segment or a polygon.
-All these three objects are represented as a vector of vertices called \emph{intersection points}. The fundamental idea is to compute intersection of 1D-2D simplices using the 
+In particular we are interested in the intersections in 1D-2D, 1D-3D, 2D-2D, 2D-3D cases.
+It will be suitable to denote $S_i$ a simplicial element with $i$ vertices (of dimension $i-1$).
+In general, an intersection can be a point, a line segment or a polygon.
+All these three objects are represented as a vector of vertices called \emph{intersection points} 
+(later denoted IP, or IPs in plural).
+
+The fundamental idea is to compute intersection of 1D-2D simplices using the 
 \plucker coordinates and reduce all other cases to this one.
-
-The intersection point data structure keeps for each of the two intersection simplices:
-\notePE{Subsimplex or subelement?}
-\begin{itemize}
- \item Barycentric coordinate of the intersection.
- \item Dimension of the most specific subsimplex (face, edge, vertex) where the point lies.
- \item Index of the most specific subelement.
-\end{itemize}
-Further, we store the sign of the permuted inner product
-in order to detect various special and degenerate cases.
 
@@
 are accepted, for $t_i$ close to $0$ and $1$ we append the vertex index to the intersection. Edges parallel to $p$ or lying on the $p$ are skipped.
+
 Finally, we obtain zero, one, or two intersection points with additional topological information.
+The intersection point data structure keeps for each of the two intersecting elements:
+\begin{itemize}
+ \item Barycentric coordinate of the intersection.
+ \item Dimension of the most specific subelement (face, edge, vertex) where the point lies.
+ \item Local index of the most specific subelement.
+\end{itemize}
+Further, we store the sign of the permuted inner product in order to detect various special and degenerate cases higher dimensional cases.
 
@@
 \subsection{Tracking boundary of the intersection polygon}
-\notePE{I suggest to denote IP, IPs intersection point and its plural respectively.}
 
@@
 \notePE{We need proper definitions of terms we use: \\
-\emph{component} is a set of connected elements of the same lower dimension (1D, 2D)\\
-\emph{bulk} is a set of 3D elements\\
+% \emph{component} is a set of connected elements of the same lower dimension (1D, 2D)\\
+% \emph{bulk} is a set of 3D elements\\
 % or slave, master...
@@
 Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same lower dimension (1D, 2D), in the space of 3D elements. 
+elements of the same lower dimension (1D, 2D), in the space of 3D elements, which we shall call a \emph{bulk}. 
 Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.

### 2016-09-23 paper_intersections.tex
Fix vertex bold notation.

@@
 Let us consider a line $p$ with parametric equation $\vc X = \vc A + t\vc u$, $t\in\R$ and a triangle given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
-with oriented sides $s_i=(V_j, V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same sign if and only if there
+with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same sign if and only if there
 is an intersection point with the       line $p$ inside the triangle. In such a case, the inner products provides scaled barycentric coordinates of the intersection on the triangle.
-In particular for the barycentric coordinate $w_i$ related to the vertex $V_i$ we have
+In particular for the barycentric coordinate $w_i$ related to the vertex $\vc V_i$ we have
 \[
@@
 \[
-   \pi_p \odot \pi_{s_1} = \vc u \cdot (\vc s_1 \times V_2) + \vc s_1 \cdot ( \vc u \times [\vc V_0 + w_1\vc s_2 - w_2 \vc s_1])
+   \pi_p \odot \pi_{s_1} = \vc u \cdot (\vc s_1 \times \vc V_2) + \vc s_1 \cdot ( \vc u \times [\vc V_0 + w_1\vc s_2 - w_2 \vc s_1])
    =-w_1 \vc u \cdot (\vc s_1 \times \vc s_2).

### 2016-09-25 paper_intersections.tex

--- 2016-09-23 paper_intersections.tex
@@
 In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space.
-In particular we are interested in the intersections in 1D-2D, 1D-3D, 2D-2D, 2D-3D cases.
-It will be suitable to denote $S_i$ a simplicial element with $i$ vertices (of dimension $i-1$).
-In general, an intersection can be a point, a line segment or a polygon.
-All these three objects are represented as a vector of vertices called \emph{intersection points} 
-(later denoted IP, or IPs in plural).
+In particular we are interested in intersection of 1D-2D, 1D-3D, 2D-2D, 2D-3D simplices. In general the intersection can be a point, a line segment or a polygon.
+All these three objects are represented as a vector of vertices called \emph{intersection points}. The fundamental idea is to compute intersection of 1D-2D simplices using the 
+\plucker coordinates and reduce all other cases to this one.
 
-The fundamental idea is to compute intersection of 1D-2D simplices using the 
-\plucker coordinates and reduce all other cases to this one.
+The intersection point data structure keeps for each of the two intersection simplices:
+\notePE{Subsimplex or subelement?}
+\begin{itemize}
+ \item Barycentric coordinate of the intersection.
+ \item Dimension of the most specific subsimplex (face, edge, vertex) where the point lies.
+ \item Index of the most specific subelement.
+\end{itemize}
+Further, we store the sign of the permuted inner product
+in order to detect various special and degenerate cases.
 
@@
 are accepted, for $t_i$ close to $0$ and $1$ we append the vertex index to the intersection. Edges parallel to $p$ or lying on the $p$ are skipped.
-
 Finally, we obtain zero, one, or two intersection points with additional topological information.
-The intersection point data structure keeps for each of the two intersecting elements:
-\begin{itemize}
- \item Barycentric coordinate of the intersection.
- \item Dimension of the most specific subelement (face, edge, vertex) where the point lies.
- \item Local index of the most specific subelement.
-\end{itemize}
-Further, we store the sign of the permuted inner product in order to detect various special and degenerate cases higher dimensional cases.
 
@@
   \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
+  \If{ $p$ is not vertex of $S_3$}{    
   \notePE{I am missing the check whether IP is vertex of $S_3$ as referred in text.
@@
     \uElseIf{ $p$ is on edge $e$}{
-    compute sign of intersection($e$, $S_3$)\;
-    sort faces $f_0$, $f_1$ coincident with $e$\;
-    F[i, $f_i$]=j
+        F[i, $e$]=j
     }
     \ElseIf{ $p$ is on vertex $v$ of $S_4$}{
-      \For{face $f$ coincident with $v$}{
-         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
+        F[i, $v$] =j
    }
   }    
-  mark all edges of $S_4$ the $p$ lies on
-
-  \caption{process point( $p$, $i$ )}
   \label{algo:process_point}
@@
      }   
-  \caption{2d-3d intersection, points in triangle interior}
-  \label{algo:collect_23_ip_edges}
+  }
 \end{algorithm}
@@
   \KwIn{all points in $I$}
-  \KwOut{polygon in $J$ in correct order \notePE{J should be K ?}}  
+  \KwOut{polygon in $K$ in correct order}  
+  \If{\abs{V} = 3}{
+
+  }
   $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
@@
   }    
-  \caption{2d-3d intersection, finish sort of points}
   \label{algo:order_23}
@@
 \subsection{Tracking boundary of the intersection polygon}
+\notePE{I suggest to denote IP, IPs intersection point and its plural respectively.}
 
@@
 \notePE{We need proper definitions of terms we use: \\
-% \emph{component} is a set of connected elements of the same lower dimension (1D, 2D)\\
-% \emph{bulk} is a set of 3D elements\\
+\emph{component} is a set of connected elements of the same lower dimension (1D, 2D)\\
+\emph{bulk} is a set of 3D elements\\
 % or slave, master...
@@
 Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same lower dimension (1D, 2D), in the space of 3D elements, which we shall call a \emph{bulk}. 
+elements of the same lower dimension (1D, 2D), in the space of 3D elements. 
 Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.

### 2016-09-25 paper_intersections.tex
Almost finished 23d algo
- seems that it could be done this way and description is almost finished
- rather try to simplify whole thing modifying original approach

@@
 \subsection{Intersection Triangle-Tetrahedron (2D-3D)}
-The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is a polygon with 7 vertices at maximum. The sides of the polygon
-are coincident with either sides of $S_3$ or with faces of the $S_4$. So a vertex of the polygon
-can arise from intersection of a side with a face or an edge with $S_3$ or from a vertex of $S_3$.
+The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
+are coincident with either sides of $S_3$ or with faces of the $S_4$. Thus each vertex of the polygon
+can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_3$.
 So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
 to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
+Computation of the intersection polygon consists of three parts: calculation of IPs on the $S_3$ boundary (Algorithm \ref{algo:colect_23_ip_triangle}),
+calculation of IPs in the interior of $S_3$ (Algorithm \ref{algo:collect_23_ip_edges}), and finalize the correct order of IPs (Algorithm \ref{algo:order_23}).
 
-Computation of the intersection polygon consists of three parts. In the first part (Algorithm \ref{algo:colect_23_ip_triangle}), we compute intersection points
-on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every of its sides. There are 0,1, or 2 intersection points
-on every side and the points are already sorted according to the side orientation, which match orientation of the intersection polygon. So, passing
-through all the sides and appending the points into $I$ provides us with incomplete intersection polygon but in the correct order.
-\notePE{Comment on process point (Algorithm \ref{algo:process_point}), face relation indicator, I would move description of face table here, since I looked at algorithm1 here, from it skipped to process point and I got lost..}
+\begin{algorithm}
+  \caption{2d-3d intersection, points on triangle boundary}
+  \label{algo:colect_23_ip_triangle}
 
-\notePE{If IP lies on an edge(s) of $S_4$, we create a mark so we exclude the edges from further computation in Algorithm \ref{algo:collect_23_ip_edges}.}
+  \DontPrintSemicolon
+  \KwIn{input data}
+  \KwOut{List of IPs on sorted output data}  
+  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
 
-\notePE{In process point, we set for all the face of the vertex, if we coming through the vertex in or out the $S_4$.
-I understand that the condition on line 10 means, that we do not overwrite info if there is another IP on that face..}
+  \For{side $i$ of $S_3$}{ 
+    $L$ = intersection($i, S_4$)\;
+    \For{ $p \in L$, $p \ne I[-1]$ }{append $p$ to $I$}    
+    \lIf{$\abs{L}=2$}{
+        append $0,0$ to $s$
+    } \lElse {
+        append $1$ to $s$
+    }
+  }
+  \nllabel{line:ip_first_vtx_duplicate}
+  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
 
-\notePE{I corrected the algorithm references. Please check, it is ok now..}
+  $l=0$
+  \For{$p \in I$}{
+    set $j$ to index of $p$ in $I$\;
+    \If{ $p$ is on boundary of $S_4$}{
+      $x$ is vertex,edge, or face on which $p$ lies\; 
+      \For{ $i=0,\dots, s[j]$}{
+        $F[l, x]=j$\;
+        $l=1-l$ \tcp*{switch from input to output and vice versa}
+      }  
+    }
+  }  
+\end{algorithm}
 
-Then we proceed to the second part (Algorithm \ref{algo:collect_23_ip_edges}). Using the line-triangle intersection algorithm for edges of $S_4$
-we obtain points from interior of $S_3$ and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
+In Algorithm \ref{algo:colect_23_ip_triangle}, we first compute IPs
+on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. Every IP that is not same as the previous IP 
+(occures at vertices of $S_3$) is appended to $I$. The IPs are added in the order around $S_3$ which match the orientation of the intersection polygon.
+The array $s$ indicates IPs that comes from side touching $S_4$ at its edge or vertex. 
+At line \ref{line:ip_first_vtx_duplicate}, we remove posible dupicate IP for the first vertex.
+Then we pass through $I$ and denote to the table $F$ at which IP ($j$) the polygon's boundary switchs from the $S_4$ boundary to the $S_3$ boundary
+($l=0$) and vice versa ($l=1$). The table $F$ contains the entry ($l=1$) and leave ($l=0$) IP for every geometrical object (vertex, edge, or  face) 
+$x$ on the boundary. In particular the touching IPs appear in both directions. The result of Algorithm \ref{algo:colect_23_ip_triangle} is incomplete 
+list $I$ of IPs lying on the $S_3$ boundary and the table $F$ stores relation of the objects on the $S_4$ boundary to the IPs on the $S_3$ boundary.
+
+\begin{algorithm}  
+  \caption{2d-3d intersection, points in triangle interior}
+  \label{algo:collect_23_ip_edges}
+
+  \SetKw{And}{And}
+  \DontPrintSemicolon
+  \KwIn{$I$ with IPs on $S_3$ boundary, partialy filled $F$}
+  \KwOut{all IPs in $I$, complete $F$}
+
+  \nllabel{line:12edges}
+  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)} 
+  \For{unmarked edge $e$ of $S_4$}{
+    \uIf{ $L[e]$ is inside of $e$}{ 
+        \nllabel{line:edge_faces}        
+        $(f_0,\ f_1)$ = edge faces($e$)
+    } 
+    \Else($p$ on the vertex $v$ of $S_4$){       
+            $(f_0,\ f_1)$ = vertex faces($v$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
+    }    
+    \uIf{ $L[e]$ is on boundary of $S_3$ }{
+         \uIf{ $L[e]$ is inside of $e$}{ 
+             get $i$ such that $F[i,e] = k$, $k\ne -1$
+         }
+         \Else($p$ on the vertex $v$ of $S_4$){ 
+             get $i$ such that $F[i,v] = k$, $k\ne -1$          
+         }         
+         $F[1-i, f_{1-i}] = k$\;
+    }
+    \Else{
+         append $L[e]$ to $I$\;
+         set $j$ to index of $L[e]$ in $I$\;
+         F[0, $f_0$]=j\;
+         F[1, $f_1$]=j\;
+         mark all edges coincident with $L[e]$
+    }   
+  }  
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{2d-3d intersection, vertex faces}  
+  \label{algo:vertex_faces}
+
+  \SetKw{return}{return}
+  \DontPrintSemicolon
+  \KwIn{vertex $v$ of $S_4$, $L[:]$ intersection results for edges of $S_4$}
+  \KwOut{faces $S_4$ intersected by the plane of $S_3$}
+  $e_0,\ e_1,\ e_2$ edges coincident with $v$\;
+  $s[i] = L[e_i]$, for $i=0,1,2$\;
+  \nllabel{line:two_degenerated}
+  \uIf{$s$ have 1 non-degenerate edge $e$}{
+    \return pair of degenerate edges sorted according to \edgefaces($e$)    
+  }
+  \nllabel{line:one_degenerated}
+  \uElseIf{ $s$ have 1 degenerate edge $e$}{
+    $f$ is face opposite to $e$first of faces coincident with $e$\;
+    $g$ is non-degenerate edge coincident with $f$\;
+    \return edge faces($g$)
+  }
+  \nllabel{line:different_sign}
+  \uElseIf{ $s$ have edge $e$ with sign oposite to other two}{
+    \return edge faces($e$)\;
+  }
+  \nllabel{line:same_signs}
+  \Else($s$ have all signs same){
+    \return anything\;
+  }  
+\end{algorithm}
+
+Algorithm \ref{algo:collect_23_ip_edges} use the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
+The loop produce IPs from interior of $S_3$ and possibly those already computed IPs with special position on vertex or edge of $S_4$. 
+Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ apear in the same order on the intersection polygon when the 
+IP of $e$ have negative sign (see Figure \ref{fig:plucker_products}). The function "edge faces" used on line \ref{line:edge_faces} and later on 
+use the sign of the intersection to return the pair of faces in the correct order. 
+Similarly the function "vertex faces" (Algorithm \ref{algo:vertex_faces}) described latter on
+returns pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.
+
+\subsubsection{Vertex Faces Algorithm}
+This function get an IP $p$ at vertex $v$ of $S_4$ as a parameter. The IP is special vertex case of non-degenerate edge-triangle intersection. 
+The functin returns pair of generalized faces of $S_4$ preceeding and succeeding $p$ on the polygons boundary in the case that $p$ is at interior of $S_3$.
+Basic idea is to use the signs of IPs of the three edges coincident with $v$. 
+Possible cases are:
+\begin{itemize}
+ \item {\bf All IPs have same sign.} (line \ref{line:same_signs}) We return any pair of faces.  $S_3$ is touching $S_4$ 
+ in the vertex $v$, the polygon ddegenerates to the single IP $p$, no connectionn information from table $F$ necessary.
+ \item {\bf Single IP have sign oposite to the other two.} (line \ref{line:different_sign}) Let $e$ be the edge of the single $IP$ with different sign. 
+ The plane of $S_3$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. The order is detemined by the function edge faces.
+ \item {\bf Single degenerated IP.} (line \ref{line:one_degenerated}) Let us denote $e$ the edge with degenerated IP and $f$ the face between the other two edges.
+ The other two (non-degenerate) edges may have either oposite sign (the plane cut $S_4$) or the same sign (the plane touching $S_4$ at the edge $e$.
+
+ The edge $e$ lies in the the singel edge
+ \item {\bf Two degenerated IPs.} (line \ref{line:two_degenerated}) A face of $S_4$ lies in the plane of $S_3$, single edge $e$ have non-degenerate IP.
+ We treat the two degenerate edges as special case of faces adjacent to $e$ and return them sorted like the faces given by edge faces fro edge $e$.
+\end{itemize}
+
+Either all signs are equal ($S_3$ touching $S_4$) wee , or
+a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the
+
+and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
 with faces of $S_4$.
@@
 \begin{algorithm}
-  \SetKw{And}{And}
-  \DontPrintSemicolon
-  \KwIn{input data}
-  \KwOut{List of IPs sorted output data}  
-  $I =\emptyset$\tcp*{Intersection polygon.}
-  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
-  $V =\emptyset$\tcp*{$S_4$ vertex intersections.}
-  \For{side $s$ of $S_3$}{ 
-    \nllabel{line:1_3}
-    $L$ = intersection($s, S_4$)  \tcp*{List of max.\ two points.}
-    process point($L[0]$, 0)\; 
-    process point($L[-1]$, 1)
-    \notePE{Isn't it clearer to write the two process point lines into cycle over L?}
-  }
-  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
-  \notePE{I am not sure if I understand the notation '($[-1]$)', can be explained?
-The last line then checks if first and last IPs, if they are not duplicates..??}
-  \caption{2d-3d intersection, points on triangle boundary}
-  \label{algo:colect_23_ip_triangle}
-\end{algorithm}
-
-\begin{algorithm}
-  \caption{process point( $p$, $i$ )}
-
-  \SetKw{And}{And}
-  \DontPrintSemicolon
-  \KwIn{intersection point $p$, face relation indicator $i$}
-  \KwOut{update of $I$ and $F$}
-  \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
-  \If{ $p$ is not vertex of $S_3$}{    
-  \notePE{I am missing the check whether IP is vertex of $S_3$ as referred in text.
-  So what if it is a vertex?}\;
-    set $j$ to index of $p$ in $I$\;
-    \lIf{ $p$ is on face $f$}{ F[i,f]=j}
-    \uElseIf{ $p$ is on edge $e$}{
-        F[i, $e$]=j
-    }
-    \ElseIf{ $p$ is on vertex $v$ of $S_4$}{
-        F[i, $v$] =j
-   }
-  }    
-  \label{algo:process_point}
-\end{algorithm}
-
-\begin{algorithm}
-  \label{algo:collect_23_ip_edges}
-  \caption{2d-3d intersection, points in triangle interior}
-
-  \SetKw{And}{And}
-  \DontPrintSemicolon
-  \KwIn{input data}
-  \KwOut{List of IPs sorted output data}  
-  \For{edge $e$ of $S_4$}{
-    $p$ = intersection($e, S_3$)\;
-    \uIf{ $p$ is on boundary of $S_3$}{
-
-    }
-    \Else{
-        append $p$ to $I$\;
-        set $j$ to index of $p$ in $I$\;
-        \uIf{ $p$ is inside of $e$}{ 
-            sort faces $f_0$, $f_1$ coincident with $e$\;
-            F[0, $f_0$]=j\;
-            F[1, $f_1$]=j
-        } %else
-        \Else($p$ on the vertex $v$ of $S_4$){       
-        append $j$ to $V$
-        \For{face $f$ coincident with $v$}{
-            \lIf{ $F[i,f]==-1$}{F[i,f]=j}
-        }
-        mark all edges of $S_4$ coincident with $v$
-        }
-     }   
-  }
-\end{algorithm}
-
-\begin{algorithm}
   \caption{2d-3d intersection, finish sort of points}  
@@
 
-  \SetKw{To}{To}
+  \SetKw{To}{to}
   \DontPrintSemicolon
@@
   \KwOut{polygon in $K$ in correct order}  
-  \If{\abs{V} = 3}{
-
-  }
   $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
-  \For{ $f$ is face of $S_4$}{
-    \lIf{$F[1,f] \ne F[1,f]$}{$P[ F[1,f] ] = F[0, f]$} 
-    \notePE{condition should be $F[0,f] \ne F[1,f]$ ? I don't understand: successor indices should be switched?
-    This way there would be same two indices..}
-  }
-  $i=0$
-
+  \lFor{ $f$ is face of $S_4$}{$P[ F[1,f] ] = F[0, f]$}
+  $i=0$\;  
   \lFor{$n=0$ \To $\abs{I}-1$}{

### 2016-09-26 paper_intersections.tex
New tracing table algorithm.
- can deal with all cases, but dealing with triangle
touching an edge is ugly

@@
 calculation of IPs in the interior of $S_3$ (Algorithm \ref{algo:collect_23_ip_edges}), and finalize the correct order of IPs (Algorithm \ref{algo:order_23}).
+Correct order of the IPs stored in the list $I$ is defined by tables $F_g(:)$ and $F_p(:)$. Every side of the intersection polygon lies either on side of $S_3$, or
+on face, or on edge of $S_4$. Let us denote $M_3$ the set of sides of $S_3$ and $M_4$ the set of volume, faces, edges, and vertices of $S_4$. 
+Every side of polygon that lies on $x\in M_32$ is folowed by an IP given by $F_g[x]$ and every IP $p$ is folowed by the side that lies on $F_p[p]\in M_32$.
 
@@
   \DontPrintSemicolon
+  \SetKw{continue}{continue}
   \KwIn{input data}
   \KwOut{List of IPs on sorted output data}  
-  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
+  $F_g(:)=-1$\tcp*{Unset IPs of geometric entities.} 
+  $F_p(:)=-1$\tcp*{Unset geometric entities of IPs.}
 
@@
     $L$ = intersection($i, S_4$)\;
-    \For{ $p \in L$, $p \ne I[-1]$ }{append $p$ to $I$}    
-    \lIf{$\abs{L}=2$}{
-        append $0,0$ to $s$
-    } \lElse {
-        append $1$ to $s$
+    \lIf{ \abs{L} = 0}{\continue}
+    \lIf{ \abs{L} = 1}{
+        append $p$ to $J$
+        \continue
+    }
+    \For{$p$ in $L$}{
+        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
+        $p$ lies on $x\in M_4$ and side $s\in M_3$\; 
+        \uIf{$p$ is first in $L$}{
+            $F_g[x] = p$\;
+            $F_p[p] = s$\;
+        }
+        \Else($p$ is the last in $L$){
+            $F_g[s] = p$\;
+            $F_p[p] = x$\;
+            \nllabel{line:back_link43}
+            \lIf{$F_g[x] = -1$}{$F_g[x] = p$}\;
         }
     }
-  \nllabel{line:ip_first_vtx_duplicate}
-  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
-
-  $l=0$
-  \For{$p \in I$}{
-    set $j$ to index of $p$ in $I$\;
-    \If{ $p$ is on boundary of $S_4$}{
-      $x$ is vertex,edge, or face on which $p$ lies\; 
-      \For{ $i=0,\dots, s[j]$}{
-        $F[l, x]=j$\;
-        $l=1-l$ \tcp*{switch from input to output and vice versa}
   }  
-    }
+  \lIf{$I[-1] = I[0]$}{
+    $F_g[F_p[I[-1]]]]=I[0]$\;
+    $F_g[s_2] = I[0]$\;
+    remove $I[-1]$
   }
@@
 In Algorithm \ref{algo:colect_23_ip_triangle}, we first compute IPs
-on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. Every IP that is not same as the previous IP 
-(occures at vertices of $S_3$) is appended to $I$. The IPs are added in the order around $S_3$ which match the orientation of the intersection polygon.
-The array $s$ indicates IPs that comes from side touching $S_4$ at its edge or vertex. 
-At line \ref{line:ip_first_vtx_duplicate}, we remove posible dupicate IP for the first vertex.
-Then we pass through $I$ and denote to the table $F$ at which IP ($j$) the polygon's boundary switchs from the $S_4$ boundary to the $S_3$ boundary
-($l=0$) and vice versa ($l=1$). The table $F$ contains the entry ($l=1$) and leave ($l=0$) IP for every geometrical object (vertex, edge, or  face) 
-$x$ on the boundary. In particular the touching IPs appear in both directions. The result of Algorithm \ref{algo:colect_23_ip_triangle} is incomplete 
-list $I$ of IPs lying on the $S_3$ boundary and the table $F$ stores relation of the objects on the $S_4$ boundary to the IPs on the $S_3$ boundary.
+on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. We store intersections with just single IP ito separate list $J$
+and skip filling the connection tables. This happen when the side just touch $S_4$ in edge or vertex. 
+These IPs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
+this is not the case if the touched edge $e$ of $S_4$ is coplanar with $S_3$ and the IP is inside of $e$. 
+Therefore we keep a separate list of IPs to deal with this case.
+For the intersection $L$ we pass through its IPs. The IP $p$ is added to the list $I$ unless the last point is the same. 
+This condition is effective just for the first point of $L$ and merge IPs at the same vertex of $S_3$. If the vertex $v$ is between sides $s_1$, $s_2$, 
+we effectively set $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
+is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_4$. The condition deals with the case
+when two sides intersect the same object $x\in M_4$.
 
@@
   \For{unmarked edge $e$ of $S_4$}{
-    \uIf{ $L[e]$ is inside of $e$}{ 
+    $p=L[e]$\;
+    \uIf{ $p$ is inside of $e$}{ 
         \nllabel{line:edge_faces}        
@@
     }    
-    \uIf{ $L[e]$ is on boundary of $S_3$ }{
-         \uIf{ $L[e]$ is inside of $e$}{ 
-             get $i$ such that $F[i,e] = k$, $k\ne -1$
-         }
-         \Else($p$ on the vertex $v$ of $S_4$){ 
-             get $i$ such that $F[i,v] = k$, $k\ne -1$          
-         }         
-         $F[1-i, f_{1-i}] = k$\;
+    \uIf{ $p$ is on boundary of $S_3$ }{
+         $p\in x \in M_4$; $x$ is edge or vertex 
+         $q=F_g[x]$\tcp*{$q$ is already computed $p$}
+         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$}
+         \lElse{$F_g[f_0]=q$}
+         $F_g[x]=-1$\tcp*{remove the backlink}
     }
     \Else{
-         append $L[e]$ to $I$\;
-         set $j$ to index of $L[e]$ in $I$\;
-         F[0, $f_0$]=j\;
-         F[1, $f_1$]=j\;
-         mark all edges coincident with $L[e]$
+         append $p$ to $I$\;
+         $F_g[f_0]=p$\tcp*{overwrites the backlink}
+         $F_p[p]=f_1$
+         mark all edges coincident with $p$
     }   
   }
+
+  \lIf{$\abs{I} < 3$}{ \return $J$}
+  \lElse{ return $I$ soter according connectivity in $F_g$ and $F_p$}
 \end{algorithm}
@@
   \SetKw{return}{return}
+  \SetKw{edgefaces}{edge faces}
   \DontPrintSemicolon
   \KwIn{vertex $v$ of $S_4$, $L[:]$ intersection results for edges of $S_4$}
-  \KwOut{faces $S_4$ intersected by the plane of $S_3$}
-  $e_0,\ e_1,\ e_2$ edges coincident with $v$\;
-  $s[i] = L[e_i]$, for $i=0,1,2$\;
+  \KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_4$, coincident with $v$ and intersected by the plane of $S_3$}
+  $e_0,\ e_1,\ e_2$ edges coincident with $v$ oriented out of $v$
+  $s[i] = L[e_i]$, for $i=0,1,2$, \;
   \nllabel{line:two_degenerated}
-  \uIf{$s$ have 1 non-degenerate edge $e$}{
+  \uIf{$s[:]$ have 1 non-degenerate edge $e$}{
     \return pair of degenerate edges sorted according to \edgefaces($e$)    
@@
   \uElseIf{ $s$ have 1 degenerate edge $e$}{
-    $f$ is face opposite to $e$first of faces coincident with $e$\;
-    $g$ is non-degenerate edge coincident with $f$\;
-    \return edge faces($g$)
+    $f$ is face oposite to $e$
+    \uIf{other two edges $e_a$, $e_b$ have different sign}{
+        $z=\edgefaces(e_a)$\;
+        replace $g\in z$, $g\ne f$ with $e$
+        \return $z$
+    }\lElse{
+        append IP of $v$ to $J$
+        \return anything\;
+    }
   }
@@
   \Else($s$ have all signs same){
+    append IP of $v$ to $J$
     \return anything\;
@@
  \item {\bf Single degenerated IP.} (line \ref{line:one_degenerated}) Let us denote $e$ the edge with degenerated IP and $f$ the face between the other two edges.
- The other two (non-degenerate) edges may have either oposite sign (the plane cut $S_4$) or the same sign (the plane touching $S_4$ at the edge $e$.
+ The other two (non-degenerate) edges may have either oposite sign (the plane cut $S_4$) or the same sign (the plane touching $S_4$ at the edge $e$).
+ In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then thr vertex faces function returns $(e, f)$ or $(f, e)$, respectively.
 

### 2016-09-26 paper_intersections.tex
Some fixes in algorithms.
- few notes
- improved description of Algo 1

@@
 
-We distinguis two variants of the desired result: the auxiliary intersection used as subprocedure of the other intersections and the final intersection.
+We distinguish two variants of the desired result: the auxiliary intersection used as subprocedure of the other intersections and the final intersection.
 In the first case we just return the array of the intersection points with the line.
@@
  Degenerated case of $p$ laying on the triangle edge is also detected....
+\noteJB{No, in 1D-3D we doesn't need result of the degenerate case (all products zero), which is the only case we can obtain two IPs. 
+I'm going to do not deal with the two variants and focus more on correctness then on optimality of the described algorithm.}
 
@@
 \subsection{Intersection Line-Teraherdon (1D-3D)}
+\noteJB{Has to be completed yet, however we consider that we obtain 0,1, or 2 distinguish IPs for all cases including various touch cases. Anyway every IP results from 
+some non-degenerate 1d-2d intersection. We also assume that the IPs are in order according to the orientation of the side which is
+counterclockwise aroung the triangle.}
 We consider a line $p$ and a tetraherdon...
@@
 The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
-are coincident with either sides of $S_3$ or with faces of the $S_4$. Thus each vertex of the polygon
+lies either on sides of $S_3$ or on faces of $S_4$. Thus each vertex (IP) of the polygon
 can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_3$.
@@
 to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
-Computation of the intersection polygon consists of three parts: calculation of IPs on the $S_3$ boundary (Algorithm \ref{algo:colect_23_ip_triangle}),
-calculation of IPs in the interior of $S_3$ (Algorithm \ref{algo:collect_23_ip_edges}), and finalize the correct order of IPs (Algorithm \ref{algo:order_23}).
-Correct order of the IPs stored in the list $I$ is defined by tables $F_g(:)$ and $F_p(:)$. Every side of the intersection polygon lies either on side of $S_3$, or
-on face, or on edge of $S_4$. Let us denote $M_3$ the set of sides of $S_3$ and $M_4$ the set of volume, faces, edges, and vertices of $S_4$. 
-Every side of polygon that lies on $x\in M_32$ is folowed by an IP given by $F_g[x]$ and every IP $p$ is folowed by the side that lies on $F_p[p]\in M_32$.
+Computation of the intersection polygon consists of two parts: calculation of side-tetrahedron IPs (Algorithm \ref{algo:colect_23_ip_triangle})
+provides all IPs on the boundary of $S_3$,
+calculation of edge-triangle IPs (Algorithm \ref{algo:collect_23_ip_edges}).
+Correct order of the IPs stored in the list $I$ is defined by the tables $F_g(:)$ and $F_p(:)$. Every side of the intersection polygon 
+lies either on a side of $S_3$, or on a face, or on an edge of $S_4$. Let us denote $M_3$ the set of sides of $S_3$ and $M_4$ the set of volume,
+faces, edges, and vertices of $S_4$. Every side of polygon that lies on $x\in M_3\cup M_4$ is folowed by an IP given by $F_g[x]$ 
+and every IP $p$ is folowed by the side that lies on $F_p[p]\in M_3\cup M_4$.
 
@@
   \KwOut{List of IPs on sorted output data}  
-  $F_g(:)=-1$\tcp*{Unset IPs of geometric entities.} 
-  $F_p(:)=-1$\tcp*{Unset geometric entities of IPs.}
-
-  \For{side $i$ of $S_3$}{ 
-    $L$ = intersection($i, S_4$)\;
-    \lIf{ \abs{L} = 0}{\continue}
-    \lIf{ \abs{L} = 1}{
+  $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
+  \For{side $s$ of $S_3$}{ 
+    $L$ = intersection($s, S_4$)\;
+    \lIf{ $\abs{L} = 0$}{\continue}
+    \lIf{ $\abs{L} = 1$}{
         append $p$ to $J$
@@
         \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
-        $p$ lies on $x\in M_4$ and side $s\in M_3$\; 
+        \nllabel{line:m4_object}
+        $p$ lies on $x\in M_4$\; 
         \uIf{$p$ is first in $L$}{
-            $F_g[x] = p$\;
-            $F_p[p] = s$\;
+            $F_g[x] = p$,\ $F_p[p] = s$\;
         }
         \Else($p$ is the last in $L$){
-            $F_g[s] = p$\;
-            $F_p[p] = x$\;
+            $F_g[s] = p,\ F_p[p] = x$\;
             \nllabel{line:back_link43}
-            \lIf{$F_g[x] = -1$}{$F_g[x] = p$}\;
+            \lIf{$F_g[x] = -1$}{$F_g[x] = p$}
         }
@@
   }  
-  \lIf{$I[-1] = I[0]$}{
-    $F_g[F_p[I[-1]]]]=I[0]$\;
+  \If{$I[-1] = I[0]$}{
+    $x = F_p[I[-1]]$\;
+    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
     $F_g[s_2] = I[0]$\;
@@
 
-In Algorithm \ref{algo:colect_23_ip_triangle}, we first compute IPs
+Algorithm \ref{algo:colect_23_ip_triangle} pass through every side $s$ of the triangle $S_3$ computing the line-tetrahedron intersection $L$.
+In the regular case we process each of the two IPs in $L$. The IP $p$ is added to the list $I$ unless the last point is the same. 
+This condition is effective just for the first IP in $L$ and merge IPs at the same vertex of $S_3$. Then we identify an object $x\in M_4$ the point
+$p$ lies on (line \ref{line:m4_object}).
+
+If the vertex $v$ is between sides $s_1$, $s_2$, 
+we effectively set $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
+is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_4$. The condition deals with the case
+when two sides intersect the same object $x\in M_4$.
+
+, we first compute IPs
 on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. We store intersections with just single IP ito separate list $J$
@@
 Therefore we keep a separate list of IPs to deal with this case.
-For the intersection $L$ we pass through its IPs. The IP $p$ is added to the list $I$ unless the last point is the same. 
-This condition is effective just for the first point of $L$ and merge IPs at the same vertex of $S_3$. If the vertex $v$ is between sides $s_1$, $s_2$, 
-we effectively set $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
-is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_4$. The condition deals with the case
-when two sides intersect the same object $x\in M_4$.
+
+For the intersection $L$ we pass through its IPs.
 
@@
     \uIf{ $p$ is on boundary of $S_3$ }{
-         $p\in x \in M_4$; $x$ is edge or vertex 
+         $p$ lies on edge or vertex $x \in M_4$\;
          $q=F_g[x]$\tcp*{$q$ is already computed $p$}
@@
          $F_g[f_0]=p$\tcp*{overwrites the backlink}
-         $F_p[p]=f_1$
+         $F_p[p]=f_1$\;
          mark all edges coincident with $p$
@@
 
-  \lIf{$\abs{I} < 3$}{ \return $J$}
-  \lElse{ return $I$ soter according connectivity in $F_g$ and $F_p$}
+  \lIf{$\abs{I} < 3$}{ return $J$}
+  \lElse{ return $I$ sorted according to connectivity in $F_g$ and $F_p$}
 \end{algorithm}

### 2016-09-28 paper_intersections.tex
Some fixes and comments on algorithm1 of 23d.

@@
 The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
-lies either on sides of $S_3$ or on faces of $S_4$. Thus each vertex (IP) of the polygon
+lie either on sides of $S_3$ or on faces of $S_4$. Thus each vertex (IP) of the polygon
 can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_3$.
@@
 calculation of edge-triangle IPs (Algorithm \ref{algo:collect_23_ip_edges}).
-Correct order of the IPs stored in the list $I$ is defined by the tables $F_g(:)$ and $F_p(:)$. Every side of the intersection polygon 
+\notePE{The following sentence is somehow weird.. I would say that we store IPs $I$; to sort $I$ during the computation, we use the two tables; at the end, $I$ is ordered correctly.}
+Correct order of the IPs, stored in the list $I$, is defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$.
+\notePE{The following sentece is a copy of the second sentence is this subsection.} Every side of the intersection polygon
 lies either on a side of $S_3$, or on a face, or on an edge of $S_4$. Let us denote $M_3$ the set of sides of $S_3$ and $M_4$ the set of volume,
-faces, edges, and vertices of $S_4$. Every side of polygon that lies on $x\in M_3\cup M_4$ is folowed by an IP given by $F_g[x]$ 
-and every IP $p$ is folowed by the side that lies on $F_p[p]\in M_3\cup M_4$.
+faces, edges, and vertices of $S_4$. Every side of polygon that lies on $x\in M_3\cup M_4$ is followed by an IP given by $F_g[x]$ 
+and every IP $p$ is followed by the side that lies on $F_p[p]\in M_3\cup M_4$.
 
@@
             $F_g[s] = p,\ F_p[p] = x$\;
-            \nllabel{line:back_link43}
-            \lIf{$F_g[x] = -1$}{$F_g[x] = p$}
+            \lIf{$F_g[x] = -1$}{$F_g[x] = p$} \nllabel{line:back_link43}
         }
@@
 
-Algorithm \ref{algo:colect_23_ip_triangle} pass through every side $s$ of the triangle $S_3$ computing the line-tetrahedron intersection $L$.
+Algorithm \ref{algo:colect_23_ip_triangle} passes through every side $s$ of the triangle $S_3$ and computes the line-tetrahedron intersection $L$.
 In the regular case we process each of the two IPs in $L$. The IP $p$ is added to the list $I$ unless the last point is the same. 
-This condition is effective just for the first IP in $L$ and merge IPs at the same vertex of $S_3$. Then we identify an object $x\in M_4$ the point
-$p$ lies on (line \ref{line:m4_object}).
+This condition is effective just for the first IP in $L$ and merges IPs at the same vertex of $S_3$. Then we identify an object $x\in M_4$ the point
+$p$ lies on (line \ref{line:m4_object}). \notePE{I am not sure, if the term 'object' is clear..}
 
+\notePE{Why calling it vertex $v$ instead of IP $p$ here? What is $y$?}
 If the vertex $v$ is between sides $s_1$, $s_2$, 
-we effectively set $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
-is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_4$. The condition deals with the case
-when two sides intersect the same object $x\in M_4$.
+we effectively set connections $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
+is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_4$. The condition at the end deals with the case
+in which two sides intersect the same object $x\in M_4$.
 
-, we first compute IPs
-on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. We store intersections with just single IP ito separate list $J$
-and skip filling the connection tables. This happen when the side just touch $S_4$ in edge or vertex. 
+For the regular intersection $L$, we pass through its IPs, as described above. \notePE{For special cases}, we firstly compute IPs
+on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. We store single point intersections into separate list $J$
+and skip filling the connection tables. This happens when the side touches $S_4$ at its edge or vertex. 
 These IPs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
 this is not the case if the touched edge $e$ of $S_4$ is coplanar with $S_3$ and the IP is inside of $e$. 
-Therefore we keep a separate list of IPs to deal with this case.
-
-For the intersection $L$ we pass through its IPs.
+Therefore we keep a separate list $J$ of IPs to deal with this case.
 
@@
   \DontPrintSemicolon
-  \KwIn{$I$ with IPs on $S_3$ boundary, partialy filled $F$}
+  \KwIn{$I$ with IPs on $S_3$ boundary, partially filled $F$}
   \KwOut{all IPs in $I$, complete $F$}

### 2016-09-28 paper_intersections.tex
Fix an error in algorithm.

--- 2016-09-26 paper_intersections.tex
@@
             $(f_0,\ f_1)$ = vertex faces($v$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
+            \nllabel{line:mark_edges}
+            mark all edges coincident with $p$
     }    
@@
          $F_p[p]=f_1$\;         
-         mark all edges coincident with $p$
     }   
@@
 returns pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.
+On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection point they are degenerate and 
+not processed anyway.
 

### 2016-09-28 paper_intersections.tex
Minor fixes, fix line numbering in algorithm2,3 of intersection 23d.

--- 2016-09-28 paper_intersections.tex
@@
   \SetKw{And}{And}
+  \SetKw{edgefaces}{edge faces}
+  \SetKw{vertexfaces}{vertex faces}
   \DontPrintSemicolon
@@
 
-  \nllabel{line:12edges}
-  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)} 
+  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)}  \nllabel{line:12edges}
   \For{unmarked edge $e$ of $S_4$}{
     $p=L[e]$\;
-    \uIf{ $p$ is inside of $e$}{ 
+    \uIf{ $p$ is inside $e$}{ 
         \nllabel{line:edge_faces}        
-        $(f_0,\ f_1)$ = edge faces($e$)
+        $(f_0,\ f_1)$ = \edgefaces($e$)
     } 
-    \Else($p$ on the vertex $v$ of $S_4$){       
-            $(f_0,\ f_1)$ = vertex faces($v$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
+    \Else($p$ at the vertex $v$ of $S_4$){       
+            $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
     }    
     \uIf{ $p$ is on boundary of $S_3$ }{
-         $p$ lies on edge or vertex $x \in M_4$\;
+         $p$ lies on edge or at vertex $x \in M_4$\;
          $q=F_g[x]$\tcp*{$q$ is already computed $p$}
@@
          append $p$ to $I$\;
-         $F_g[f_0]=p$\tcp*{overwrites the backlink}
+         $F_g[f_0]=p$\tcp*{overwrite the backlink}
          $F_p[p]=f_1$\;
@@
   $s[i] = L[e_i]$, for $i=0,1,2$, \;
-  \nllabel{line:two_degenerated}
-  \uIf{$s[:]$ have 1 non-degenerate edge $e$}{
+
+  \uIf{$s[:]$ have 1 non-degenerate edge $e$}{ \nllabel{line:two_degenerated}
     \return pair of degenerate edges sorted according to \edgefaces($e$)    
   }
-  \nllabel{line:one_degenerated}
-  \uElseIf{ $s$ have 1 degenerate edge $e$}{
-    $f$ is face oposite to $e$
+
+  \uElseIf{ $s$ have 1 degenerate edge $e$}{\nllabel{line:one_degenerated}
+    $f$ is face opposite to $e$
     \uIf{other two edges $e_a$, $e_b$ have different sign}{
@@
   }
-  \nllabel{line:different_sign}
-  \uElseIf{ $s$ have edge $e$ with sign oposite to other two}{
+
+  \uElseIf{ $s$ have edge $e$ with sign oposite to other two}{ \nllabel{line:different_sign}
     \return edge faces($e$)\;
   }
-  \nllabel{line:same_signs}
-  \Else($s$ have all signs same){
+
+  \Else($s$ have all signs same){ \nllabel{line:same_signs}
     append IP of $v$ to $J$
@@
 
-Algorithm \ref{algo:collect_23_ip_edges} use the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
-The loop produce IPs from interior of $S_3$ and possibly those already computed IPs with special position on vertex or edge of $S_4$. 
-Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ apear in the same order on the intersection polygon when the 
-IP of $e$ have negative sign (see Figure \ref{fig:plucker_products}). The function "edge faces" used on line \ref{line:edge_faces} and later on 
-use the sign of the intersection to return the pair of faces in the correct order. 
-Similarly the function "vertex faces" (Algorithm \ref{algo:vertex_faces}) described latter on
-returns pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.
+Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
+The loop produces IPs in the interior of $S_3$ and possibly those IPs with special position on vertex or edge of $S_4$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
+Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
+IP on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
+uses the sign of the intersection to return the pair of faces ordered correctly. 
+Similarly the function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
+returns a pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.
 
 \subsubsection{Vertex Faces Algorithm}
-This function get an IP $p$ at vertex $v$ of $S_4$ as a parameter. The IP is special vertex case of non-degenerate edge-triangle intersection. 
-The functin returns pair of generalized faces of $S_4$ preceeding and succeeding $p$ on the polygons boundary in the case that $p$ is at interior of $S_3$.
-Basic idea is to use the signs of IPs of the three edges coincident with $v$. 
+This function gets an IP $p$ at vertex $v$ of $S_4$ as a parameter. The IP is special vertex case of non-degenerate edge-triangle intersection. 
+The function returns a pair of generalized faces of $S_4$ preceeding and succeeding $p$ on the polygons boundary in the case that $p$ is at interior of $S_3$.
+The basic idea is to use the signs of IPs of the three edges coincident with $v$. 
 Possible cases are:
 \begin{itemize}
- \item {\bf All IPs have same sign.} (line \ref{line:same_signs}) We return any pair of faces.  $S_3$ is touching $S_4$ 
- in the vertex $v$, the polygon ddegenerates to the single IP $p$, no connectionn information from table $F$ necessary.
- \item {\bf Single IP have sign oposite to the other two.} (line \ref{line:different_sign}) Let $e$ be the edge of the single $IP$ with different sign. 
- The plane of $S_3$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. The order is detemined by the function edge faces.
+ \item {\bf All IPs have the same sign.} (line \ref{line:same_signs}) We return any pair of faces.  $S_3$ is touching $S_4$ 
+ at the vertex $v$, the polygon degenerates into the single IP $p$, no connection information from table $F$ is necessary.
+ \item {\bf Single IP has the opposite sign to the other two.} (line \ref{line:different_sign}) Let $e$ be the edge of the single IP with the different sign. 
+ The plane of $S_3$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. The order is detemined by the function \emph{edge faces}.
  \item {\bf Single degenerated IP.} (line \ref{line:one_degenerated}) Let us denote $e$ the edge with degenerated IP and $f$ the face between the other two edges.
- The other two (non-degenerate) edges may have either oposite sign (the plane cut $S_4$) or the same sign (the plane touching $S_4$ at the edge $e$).
- In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then thr vertex faces function returns $(e, f)$ or $(f, e)$, respectively.
+ The other two (non-degenerates) edges may have either the opposite sign (the plane is cutting $S_4$) or the same sign (the plane is touching $S_4$ at the edge $e$).
+ In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then the vertex faces function returns $(e, f)$ or $(f, e)$, respectively.
 
@@
  \item {\bf Two degenerated IPs.} (line \ref{line:two_degenerated}) A face of $S_4$ lies in the plane of $S_3$, single edge $e$ have non-degenerate IP.
- We treat the two degenerate edges as special case of faces adjacent to $e$ and return them sorted like the faces given by edge faces fro edge $e$.
+ We treat the two degenerate edges as special case of faces adjacent to $e$ and return them sorted like the faces given by edge faces of edge $e$.
 \end{itemize}
 
-Either all signs are equal ($S_3$ touching $S_4$) wee , or
-a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the
+% Either all signs are equal ($S_3$ touching $S_4$) wee , or
+% a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the 
+% 
+% 
+% and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
+% with faces of $S_4$.
+Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_3$ belongs to a face $f$ of $S_4$; we know from the order of the points
+% whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
+% Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
+% intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.
 
-and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
-with faces of $S_4$.
-Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_3$ belongs to a face $f$ of $S_4$; we know from the order of the points
-whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
-Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
-intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.
-
-Finally in the third part (Algorithm \ref{algo:order_23}), the table $F$ than allows us to modify array of successors $P$ and get $I$ in correct order as the list $K$.
+Finally in the third part (Algorithm \ref{algo:order_23}), the table $F$ allows us to modify array of successors $P$ and get $I$ in the correct order as the list $K$.
 

### 2016-09-28 paper_intersections.tex
Introduction nearly done.

--- 2016-09-28 paper_intersections.tex
@@
 \section{Introduction}
-Structure of introduction:
+Structure:
+\begin{itemize}
+ \item Introduction of the problem. 
+ \item Overview of methods using some sort of mesh intersections.
+ \item Our motivation from groundwater applications.
+ \item Existing algorithms.
+ \item Our contribution:
+    new algorithms for element intersections based on \plucker coordinates,
+    improvement of the front tracking algorithm
+ \item Paper overview   
+\end{itemize}
 
-- motivation for computing mesh intersections, other applications
-- basic overview of existing work, approaches
-- our contribution
-    - new algorithms for element intersectins based on Pl\"ucker coordinates
-    - improvement of the front tracking algorithm
+The grid intersection algorithms are crucial for several techniques that tries to overcome some limitations of the classical finite element method.
+The Chimera method \cite{brezzi_analysis_2001} also called overset grid and similar Nitche method \cite{massing_efficient_2013}
+allow solution of the problems with changing geometry as in the fluid-structure problems. 
+The Mortar method \cite{belgacem_mortar_1999} allows domain decomposition, independent meshing of domains, and supports sliding boundaries.
+However our primal motivation is usage of XFEM methods and non-matching meshes of mixed dimension in groundwater models.
 
-\cite{sukumar_extended_2000} - Use {\emph geometric predicates} incircle and orientation. Use mesh of bounding boxes to search for intersection candidates. 
-Only use point queries for all vertices of triangle/tetrahedron. Use compatible partitioning of elements by the crack elements.
+The realistic models of groundwater processes including the transport processes and geomechanics have to deal with 
+a complex nature of geological formations including the fractures and wells. Although of small scale, these features may have significant impact 
+on the global behavior of the system and their representation in the numerical model is imperative.
+One possible approach is to model fractures and wells as lower dimensional objects and introduce their coupling with the surrounding continuum. 
+The discretization then leads to the meshes of mixed dimensions, i.e. composed of elements of different dimension. This approach 
+called mixed-dimensional analysis in the mechanics \cite{bournival_mesh-geometry_2008} is also studied in the groundwater context, see e.g. 
+\cite{martin_modeling_2005}, \cite{fumagalli_numerical_2011}, \cite{brezina_analysis_2015} and 
+already adopted by some groundwater simulation software, e.g FeFlow \cite{trefry_feflow:_2007} and Flow123d \cite{flow123d}.
+Nevertheless as the complexity of the geometry increase (e.g. when lot of fractures are randomly generated) the compatible meshing becomes painful or even 
+impossible. In order to avoid these difficulties we may discretize the continuum and every fracture and well independently getting a non-matching 
+(or incompatible) mesh of mixed dimensions and then apply XFEM to represent jumps of the solution on the fractures or singularities 
+around the wells. The prerequisity for such approach is a fast and robust algorithm for calculating intersections of individual meshes.
 
-\cite{massing_efficient_2013} - Implementation of the Nitche method in Fenics. They need 2d-3d intersections, but only for distribution od quadrature points. 
-So they do not store whole intersection data, but only the quad points. The boundary of one domain is partitioned into intersections with elements of the other domain.
-Use {\\emph collision relations} ( pairs of faces of boundary and elmements of the background mesh) and {\emph collision maps} 
-( map face to all intersections and background element to all intersections, can be constructed from the collision relation), They cite books from computer graphics ..
-Mention geometric predicates. Present algorithms for:  find intersection candidates, comput intersections, integrate over complex domains.
+We consider a composed mesh $\mathcal T$ consisting of meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$. 
+We assume that the meshes $\mathcal T_i$ are connected, that is the graph having elements for vertices and their nighbouring for edges is connected.
+We also assume that no submesh intersect itself. Further we assume that only $\mathcal{T}_1$ have $d_1=3$ and $d_i < 3$ for $i>1$. 
+The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
+and compute that intersection. Every (possibly degenerated) intersection polygon (IP) is determined by its corners called intersection corners (IC).
+For every IC we want to compute its barycentric coordinates on $K$ and on $L$.
 
-\cite{elsheikh_reliable_2012} Claim to provide robust algorithm covering all tiangle-trinagle degenerate cases. Basic idea is the same as our: use some tree 
-(Binary SPace Tree) structure to find initial point on intersection curve and trace the curve in both directions. Quite clever data structure for the mesh. Adaptive precision 
-geometric predicates. Store topological information about the intersection points (point on triangle, edge, vertex). Resolve various degenerate cases, 
-dicuss mesh optimization after subdivision.
+The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. Second, compute the intersection for particular pair.
+In order to get candidate pairs efficiently, the existing algorithms use either various space trees \cite{massing_efficient_2013} or front tracing
+\cite{gander_algorithm_2013} or both \cite{elsheikh_reliable_2012} as in our approach. To compute the actual intersections, we 
+use the \plucker coordinates for the line-triangle intersections and a modification of the  Platis and Theoharis algorithm \cite{platis_fast_2003}
+for the line-tetrahedron intersections. These are used as the building block for the triangle-triangle and the trinagle-tetrahedron cases.
 
-\cite{gander_algorithm_2013} Full algorithm for 2d=3D called PANG. Implemented in DUNE in 2010 (Bastian). Other software (Hecht, MpCCI). 
-Triangle-Triangle and Tetra-Triangle intersections done similarly as in aur approach: set of points including vertices and then sort them countercolckwise.
-Local intersection algorithm do not provide neighbouring information so the traversal algorithm do not use it.
-
-Review of algorithms: \cite{gander_algorithm_2009}
-
-\cite{boon_robust_2016} Robust discretization of porous media. Complete error analysis with mortar non-compatible case. Seems they use normal fluxes accros
-fracture instead of pressure traces. This allows conforming discretization and error results.
-
-\cite{bournival_mesh-geometry_2008} Application of mixed-dimensional approach in mechanics. Beam and shell elements ...
-
-\cite{reichenberger_mixed-dimensional_2006} Finite volume method, fully implicit two phase flow. Cite usage of FRAC3D generator.
-
-\cite{sladkova_bakalarka} Space-time DG with adaptive mesh, need integration of product of functions on different meshes (in 2D). An algorithm 
-for computing triangle-triangle intersections in 2D.
-
-\cite{pichot_generalized_2012} DFN + MHFEM. Mortar method for intersections. Focused on formulation not on intersections.
-
-\cite{flemisch_non-matching_2012} (Barbara) Mortad, non=matching, acustics. Theory, structured gird case. No complex intersections.
-
-\cite{mustapha_hybrid_2014} Patent for curiosity.
-
-\cite{mittal_immersed_2005} Immersed boundary. ??
-
-\cite{owen_survey_1998} ??
-
-\cite{kuznetsov_overlapping_1998}
-
-\cite{platis_fast_2003} Original algorithm for line-thetrahedra intersections.
-
-\cite{haines_fast_1991} Line-convex Polyhedra intersections using generalisation of line-clipping algorithm
-
-The initial problem that occurs when working with incompatible meshes of combined dimensions is the efficient 
-computation of intersections of the mesh subdomains, in particular 1D-2D, 1D-3D, 2D-3D.
-There is a piece of code in Flow123d at the moment which uses means of analytic geometry. In particular, it computes 
-an intersection of a line and a plane in 3D by solving Gaussian elimination. However it is not effiecient
-and it does not provide barycentric coordinates explicitly.
-In this section, we present our latest work on this problematics.
-
-The topic is studied in the bachelor and master thesis of Viktor Fri{\v s} \cite{fris_dp_2015}, who was supervised by 
-Jan B{\v r}ezina.
 They suggested a solution, based on \cite{yuan_efficient_2003} for the two aspects of the problem: 
@@
 We use $i$ with maximal $|u_i|$ for practical computation.
+
+adaptive precision arithmetic 
+    \cite{elsheikh_reliable_2012} (based on edge-triangle intersections, 
+        use calculations that are similar to usage of \plucker coordinates), 
+    \cite{shewchuk_adaptive_1997}
 
@@
 
+\cite{sukumar_extended_2000} - Use {\emph geometric predicates} incircle and orientation. Use mesh of bounding boxes to search for intersection candidates. 
+Only use point queries for all vertices of triangle/tetrahedron. Use compatible partitioning of elements by the crack elements.
+
+\cite{boon_robust_2016} Robust discretization of porous media. Complete error analysis with mortar non-compatible case. Seems they use normal fluxes accros
+fracture instead of pressure traces. This allows conforming discretization and error results.
+
+\cite{reichenberger_mixed-dimensional_2006} Finite volume method, fully implicit two phase flow. Cite usage of FRAC3D generator.
+
+\cite{sladkova_bakalarka} Space-time DG with adaptive mesh, need integration of product of functions on different meshes (in 2D). An algorithm 
+for computing triangle-triangle intersections in 2D.
+
+\cite{pichot_generalized_2012} DFN + MHFEM. Mortar method for intersections. Focused on formulation not on intersections.
+
+\cite{flemisch_non-matching_2012} (Barbara) Mortad, non=matching, acustics. Theory, structured gird case. No complex intersections.
+
+\cite{mustapha_hybrid_2014} Patent for curiosity.
+
+\cite{mittal_immersed_2005} Immersed boundary. ??
+
+\cite{owen_survey_1998} ??
+
+\cite{kuznetsov_overlapping_1998}
+
+\cite{platis_fast_2003} Original algorithm for line-thetrahedra intersections.
+
+\cite{haines_fast_1991} Line-convex Polyhedra intersections using generalisation of line-clipping algorithm
+
+USED:
+\cite{massing_efficient_2013} - Implementation of the Nitche method in Fenics. They need 2d-3d intersections, but only for distribution od quadrature points. 
+So they do not store whole intersection data, but only the quad points. The boundary of one domain is partitioned into intersections with elements of the other domain.
+Use {\\emph collision relations} ( pairs of faces of boundary and elmements of the background mesh) and {\emph collision maps} 
+( map face to all intersections and background element to all intersections, can be constructed from the collision relation), They cite books from computer graphics ..
+Mention geometric predicates. Present algorithms for:  find intersection candidates, comput intersections, integrate over complex domains.
+
+\cite{elsheikh_reliable_2012} Claim to provide robust algorithm covering all tiangle-trinagle degenerate cases. Basic idea is the same as our: use some tree 
+(Binary SPace Tree) structure to find initial point on intersection curve and trace the curve in both directions. Quite clever data structure for the mesh. Adaptive precision 
+geometric predicates. Store topological information about the intersection points (point on triangle, edge, vertex). Resolve various degenerate cases, 
+dicuss mesh optimization after subdivision.
+
+\cite{gander_algorithm_2013} Full algorithm for 2d=3D called PANG. Implemented in DUNE in 2010 (Bastian). Other software (Hecht, MpCCI). 
+Triangle-Triangle and Tetra-Triangle intersections done similarly as in aur approach: set of points including vertices and then sort them countercolckwise.
+Local intersection algorithm do not provide neighbouring information so the traversal algorithm do not use it.
+
+Review of algorithms: \cite{gander_algorithm_2009}
+
+\cite{bournival_mesh-geometry_2008} Application of mixed-dimensional approach in mechanics. Beam and shell elements ...
+
 %\endinput

### 2016-09-28 paper_intersections.tex

--- 2016-09-28 paper_intersections.tex
@@
             $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
+            \nllabel{line:mark_edges}
+            mark all edges coincident with $p$
     }    
@@
 returns a pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.
+On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection point they are degenerate and 
+not processed anyway.
 

### 2016-09-28 paper_intersections.tex
Finish introduction (possibly need yet better research on algorithms)

@@
 \section{Introduction}
-Structure:
-\begin{itemize}
- \item Introduction of the problem. 
- \item Overview of methods using some sort of mesh intersections.
- \item Our motivation from groundwater applications.
- \item Existing algorithms.
- \item Our contribution:
-    new algorithms for element intersections based on \plucker coordinates,
-    improvement of the front tracking algorithm
- \item Paper overview   
-\end{itemize}
 
@@
 
-We consider a composed mesh $\mathcal T$ consisting of meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$. 
+We consider a composed mesh $\mathcal T$ consisting of simplicial meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$. 
 We assume that the meshes $\mathcal T_i$ are connected, that is the graph having elements for vertices and their nighbouring for edges is connected.
@@
 use the \plucker coordinates for the line-triangle intersections and a modification of the  Platis and Theoharis algorithm \cite{platis_fast_2003}
-for the line-tetrahedron intersections. These are used as the building block for the triangle-triangle and the trinagle-tetrahedron cases.
+for the line-tetrahedron intersections. These are used as the building block for the triangle-triangle and the triangle-tetrahedron cases.
 
-They suggested a solution, based on \cite{yuan_efficient_2003} for the two aspects of the problem: 
-\begin{enumerate}[itemsep=-3pt]
-\item an efficient identification of the intersecting pairs of elements,
-\item an efficient computation of the actual intersection for the single element pair.
-\end{enumerate}
-The algorithm is based on the methods used in the computer graphics, in particular for the task (b) \plucker
-coordinates are employed to efficiently compute 1D-2D intersection in three-dimensional space.
+\noteJB{Better overview of works, seems that most of works deals with simple intersections, can not find any example of 2d-3d.}
 
-\begin{figure}[!htb]
-  \centering
-  \setcounter{subfigure}{0}
-  \subfloat[1D-3D]{
-    \includegraphics[width=0.3\textwidth]{\figpath intersection_13.pdf} }
-  \hspace{10pt}
-  \subfloat[2D-3D]{
-    \includegraphics[width=0.3\textwidth]{\figpath intersection_23.pdf} }
-\end{figure}
-
-For the 1D-3D and 2D-3D cases, the basic algorithm is applied on sides and edges of the simplices and 
-all the topological information coming from the performed \plucker products is carefully collected
-to obtain final intersecting object.
-Further in 2D-3D case, an optimized tracing algorithm is suggested to directly obtain the correct order and 
-orientation of the edges of the intersection polygon.
+Our contribution is twofold: First, we present family of efficient algorithms based on \plucker coordinates for computing 1d-2d, 1d-3d, 2d-2d, and 2d-3d intersections 
+of simplicies. Second, we use the front tracking algorithm both to minimize set of intersection candidates as well to reuse part of calculations made on neighboring
+intersections. The paper is organized as follows \dots
 

### 2016-09-29 paper_intersections.tex
Minor typo improvements, improve prolongation.

@@
 %% keywords here, in the form: keyword \sep keyword
-non-matching gird \sep 
+non-matching grid \sep 
 intersections \sep
@@
 \section{Introduction}
+\notePE{How did you decided for 'non-matching' term? Instead of e.g. incompatible or non-conforming?}
 
-The grid intersection algorithms are crucial for several techniques that tries to overcome some limitations of the classical finite element method.
-The Chimera method \cite{brezzi_analysis_2001} also called overset grid and similar Nitche method \cite{massing_efficient_2013}
+The grid intersection algorithms are crucial for several techniques that try to overcome some limitations of the classical finite element method.
+The Chimera method \cite{brezzi_analysis_2001}, also called overset grid, and similar Nitche method \cite{massing_efficient_2013}
 allow solution of the problems with changing geometry as in the fluid-structure problems. 
@@
 We consider a composed mesh $\mathcal T$ consisting of simplicial meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$. 
-We assume that the meshes $\mathcal T_i$ are connected, that is the graph having elements for vertices and their nighbouring for edges is connected.
-We also assume that no submesh intersect itself. Further we assume that only $\mathcal{T}_1$ have $d_1=3$ and $d_i < 3$ for $i>1$. 
+We assume that the meshes $\mathcal T_i$ are connected, that is the graph having elements for vertices and their neighbouring for edges is connected.
+We also assume that no submesh intersects itself. Further we assume that only $\mathcal{T}_1$ has $d_1=3$ and $d_i < 3$ for $i>1$. 
 The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
-and compute that intersection. Every (possibly degenerated) intersection polygon (IP) is determined by its corners called intersection corners (IC).
+and to compute that intersection. Every (possibly degenerated) intersection polygon (IP) is determined by its corners called intersection corners (IC).
 For every IC we want to compute its barycentric coordinates on $K$ and on $L$.
@@
 use the \plucker coordinates for the line-triangle intersections and a modification of the  Platis and Theoharis algorithm \cite{platis_fast_2003}
-for the line-tetrahedron intersections. These are used as the building block for the triangle-triangle and the triangle-tetrahedron cases.
+for the line-tetrahedron intersections. These are used as the building blocks for the triangle-triangle and the triangle-tetrahedron cases.
 
@@
 
+\notePE{Unify the term 'front tracing' 'front tracking' 'advancing front'.}
 Our contribution is twofold: First, we present family of efficient algorithms based on \plucker coordinates for computing 1d-2d, 1d-3d, 2d-2d, and 2d-3d intersections 
@@
 
-\subsection{Prolongation algorithm}
+\section{Front tracking algorithm}
+
 Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
@@
 
-A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases (applies both for 1D-3D and 2D-3D):
+\subsection{Prolongation over IPs}
+Having an intersection of a pair of elements, we now look for new candidate pairs among the neighboring elements.
+Therefore, we iterate over the intersection points and further exploit their topological information.
+There are 3 possible cases (applies both for 1D-3D and 2D-3D):
 \begin{itemize}
-    \item \textbf{IP lies on component element side and inside bulk element} \\
+    \item \textbf{IP lies on the component element side and inside the bulk element} \\
             We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
-            We find the component neighboring elements over the sides and push a new candidate pair
-            [component neighbor -- current bulk element] into component queue.
-    \item \textbf{IP lies on component element side and on the surface of bulk element} \\
+            Next, we find the component neighboring elements over the sides and push all new candidate pairs
+            [component neighbor -- current bulk element] into the component queue.
+            Note, that there can be more than one neighbor on a side, if the component has branches.
+    \item \textbf{IP lies on the component element side and on the surface of the bulk element} \\
             We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
             or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
-            push the following new candidates pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
-            If the candidates pair has been investigated already, we skip it.
+            push the following new candidate pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
+            If the candidate pair has been investigated already, we skip it.
     \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
-            The same as before, but we push only [current component element -- bulk neighbor] candidates pairs, since
-            there is no component neighbor.
+            We proceed as in previous case, but we push only [current component element -- bulk neighbor] candidate pairs, since there is no component neighbor.
 \end{itemize}
@@
 
-\section{Front tracking algorithm}
 \section{Benchmarks}

### 2016-09-29 paper_intersections.tex
Improve prolongation scheme.
Improve prolongation and advancing front description.

@@
 \section{Front tracking algorithm}
+Prerequisites:
+  \begin{itemize}
+   \item need information about element connectivity (mesh preprocessing)
+%   \item mark and check already inspected pairs. Marking elements + hashing.
+   \item find the starting intersection -- AABB (Axes Aligned Bounding Boxes) 
+   \item possibly create Bounding Interval Hierarchy (BIH)
+%   \item Pass already known information with pairs.
+%   \item Deal with degenerated cases.
+  \end{itemize}
 
@@
 elements of the same lower dimension (1D, 2D), in the space of 3D elements, which we shall call a \emph{bulk}. 
-Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.
-Then we can prolongate the intersection by investigating neighbouring elements.
-%
-\begin{figure}[!htb]
-%   \vspace{0pt}
-  \centering    
-    \includegraphics[width=\textwidth]{\figpath prolongation_scheme.pdf}
-  \caption{Prolongation algorithm for 1D-2D and 2D-3D intersections. }
-  \label{fig:prolongation}
-\end{figure}
+Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other. Then we can prolongate the intersection by investigating neighbouring elements.
 
-The prolongation algorithm is the same for both 1D and 2D components, see \fig{fig:prolongation}. 
 It can be seen as a \emph{breadth-first search}
@@
   \end{enumerate}
-  Prerequisites:
+
+%
+\begin{figure}[!htb]
+%   \vspace{0pt}
+  \centering    
+    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip.pdf}
+  \caption{Prolongation algorithm for 1D-2D and 2D-3D intersections. }
+  \label{fig:prolongation}
+\end{figure}
+
+The advancing front algorithm works the same way for both 1D and 2D components and is displayed in \fig{fig:prolongation}. The main idea is to compute intersections for a component element with all 
+possible bulk elements, and then move to a~next neighboring component element. For this reason, we define two
+queues of candidate pairs: a~\emph{bulk queue} and a~\emph{component queue} (yellow boxes in \fig{fig:prolongation}). We shall now describe the algorithm in detail.
+
+On input we consider a candidate pair, for which a non-empty intersection is computed.
+Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
+Therefore, we iterate over the intersection points and further exploit their topological information.
+There are 3 possible cases (applies both for 1D-3D and 2D-3D):
 \begin{itemize}
-   \item need information about element connectivity (mesh preprocessing)
-%   \item mark and check already inspected pairs. Marking elements + hashing.
-   \item find the starting intersection -- AABB (Axes Aligned Bounding Boxes) 
-   \item possibly create Bounding Interval Hierarchy (BIH)
-%   \item Pass already known information with pairs.
-%   \item Deal with degenerated cases.
+    \item \textbf{IP lies on the component element side and inside the bulk element} \\
+            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
+            Next, we find the component neighboring elements over the sides and push all new candidate pairs
+            [component neighbor -- current bulk element] into the component queue.
+            Note, that there can be more than one neighbor on a side, if the component has branches.
+    \item \textbf{IP lies on the component element side and on the surface of the bulk element} \\
+            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
+            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
+            push the following new candidate pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
+    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
+            We proceed as in previous case, but we push only [current component element -- bulk neighbor] candidate pairs, since there is no component neighbor.
 \end{itemize}
 
-After computing the intersection of a pair of elements (line or triangle vs tetrahedron), we fill
-two queues with element pairs as candidates for further intersection. If the intersection edge 
-(point of line in 1D, edge of polygon in 2D) is inside the tetrahedron, not on its surface, we
-get a neighbouring element of the component and push it back together with the current tetrahedron into 
-\emph{component prolongation queue}. If the intersection edge is inside the \emph{slave} element 
-(line or triangle), i.e. is on the surface of tetrahedron, we get a neighbouring element of the tetrahedron
-and push it back together with the current slave element into \emph{3D prolongation queue}.
+If the candidate pair has been found already, we skip it.
+We also see that the candidate pairs are of three types:
+[current component element -- bulk neighbor],
+[component neighbor -- current bulk element], 
+[component neighbor -- bulk neighbor],
+from which only the first one goes into the bulk queue, trying to cover the whole component element.
 
-Then we empty the prolongation queues -- the 3D prolongation queue at first, then the component prolongation queue.
-When both queues are empty, all intersections of a component have been found and we continue to look for
-another component.
+% After computing the intersection of a pair of elements (line or triangle vs tetrahedron), we fill
+% two queues with element pairs as candidates for further intersection. If the intersection edge 
+% (point of line in 1D, edge of polygon in 2D) is inside the tetrahedron, not on its surface, we
+% get a neighbouring element of the component and push it back together with the current tetrahedron into 
+% \emph{component prolongation queue}. If the intersection edge is inside the \emph{slave} element 
+% (line or triangle), i.e. is on the surface of tetrahedron, we get a neighbouring element of the tetrahedron
+% and push it back together with the current slave element into \emph{3D prolongation queue}.
 
-The algorithm is now unified for 1D and 2D in contrast to \cite{fris_dp_2015}, where the component prolongation
-queue is emptied at first.
+Then we empty the two queues. 
+We pop out new candidate pairs from the \emph{bulk queue} as long as it is not empty and for every new intersection computed, we repeat the previous part (means that we can further fill both queues).
+The \emph{bulk queue} is empty when the component element is fully covered by bulk elements, or
+when there is no bulk neighbor to which we can advance.
+Then we can pop a new candidate pair from \emph{component prolongation queue} and process it.
+When both queues are empty, all intersections of a component have been found and we start over by looking for the first intersection of another component.
+
+% The algorithm is now unified for 1D and 2D in contrast to \cite{fris_dp_2015}, where the component prolongation
+% queue is emptied at first.
 
@@
 % \end{itemize}
-
-\subsection{Prolongation over IPs}
-Having an intersection of a pair of elements, we now look for new candidate pairs among the neighboring elements.
-Therefore, we iterate over the intersection points and further exploit their topological information.
-There are 3 possible cases (applies both for 1D-3D and 2D-3D):
-\begin{itemize}
-    \item \textbf{IP lies on the component element side and inside the bulk element} \\
-            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
-            Next, we find the component neighboring elements over the sides and push all new candidate pairs
-            [component neighbor -- current bulk element] into the component queue.
-            Note, that there can be more than one neighbor on a side, if the component has branches.
-    \item \textbf{IP lies on the component element side and on the surface of the bulk element} \\
-            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
-            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
-            push the following new candidate pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
-            If the candidate pair has been investigated already, we skip it.
-    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
-            We proceed as in previous case, but we push only [current component element -- bulk neighbor] candidate pairs, since there is no component neighbor.
-\end{itemize}
 

### 2016-09-29 paper_intersections.tex
Finished 1d-2d intersection.

--- 2016-09-28 paper_intersections.tex
@@
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{esint}
+
+\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{definition}[theorem]{Definition}
+%\newtheorem{remark}[theorem]{Remark}
+\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{thmproblem}{Problem}
+%\newtheorem{exercise}[theorem]{Cvičení}
 
@@
 \newcommand{\dd}{\; \mathrm{d}}
-\newcommand{\R}{\mathbf{R}}
+\newcommand{\R}{\mathbb{R}}
 \newcommand{\bx}{\vc{x}}
@@
 \newcommand{\plucker}{Pl\"{u}cker }
+\newcommand{\nface}{$n$-face }
+\newcommand{\nfaces}{$n$-faces }
 
@@
 
-We consider a composed mesh $\mathcal T$ consisting of simplicial meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$. 
-We assume that the meshes $\mathcal T_i$ are connected, that is the graph having elements for vertices and their nighbouring for edges is connected.
-We also assume that no submesh intersect itself. Further we assume that only $\mathcal{T}_1$ have $d_1=3$ and $d_i < 3$ for $i>1$. 
+We consider a composed mesh $\mathcal T$ consisting of simplicial meshes $\mathcal T_i$ of dimensions $d_i \in \{1,2,3\}$, $i=1,\dots,N_\mathcal{T}$
+in the 3d ambient space. We assume that every mesh $\mathcal T_i$ is a connected set with no self intersection.
+Further we assume only single 3d mesh $\mathcal{T}_1$.
 The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
-and compute that intersection. Every (possibly degenerated) intersection polygon (IP) is determined by its corners called intersection corners (IC).
-For every IC we want to compute its barycentric coordinates on $K$ and on $L$.
+and compute that intersection.
 
@@
 
-Our contribution is twofold: First, we present family of efficient algorithms based on \plucker coordinates for computing 1d-2d, 1d-3d, 2d-2d, and 2d-3d intersections 
-of simplicies. Second, we use the front tracking algorithm both to minimize set of intersection candidates as well to reuse part of calculations made on neighboring
-intersections. The paper is organized as follows \dots
+Our contribution is twofold:  First, we use the front tracking algorithm both to minimize set of intersection candidates as well 
+to reuse part of calculations made on neighbouring intersections. Second, we present family of efficient algorithms based on \plucker coordinates 
+for computing 1d-2d, 1d-3d, 2d-2d, and 2d-3d intersections of simplicies. The paper is organized as follows \dots
 
@@
 In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
-In particular we are interested in the intersections in 1D-2D, 1D-3D, 2D-2D, 2D-3D cases.
-It will be suitable to denote $S_i$ a simplicial element with $i$ vertices (of dimension $i-1$).
-In general, an intersection can be a point, a line segment or a polygon.
-All these three objects are represented as a vector of vertices called \emph{intersection points} 
-(later denoted IP, or IPs in plural).
+In particular we are interested in the intersections of 1D-2D, 1D-3D, 2D-2D, 2D-3D pairs of elements. The fundamental idea is to compute intersection of 1D-2D simplices using the 
+\plucker coordinates and reduce all other cases to this one.
 
-The fundamental idea is to compute intersection of 1D-2D simplices using the 
-\plucker coordinates and reduce all other cases to this one.
+We denote $S_i$ a simplicial element with $i+1$ vertices (of dimension $i$). We call vertices, edges, faces and simlices itself the \nfaces and we denote
+$M_i$ the set of all \nfaces of the simplex $S_i$.
+In general, an intersection can be a point, a line segment or a polygon called \emph{intersection polygon} (IP) in common.
+The intersection polygon is represented as a list of its corners called \emph{intersection corners} (IC). The IP data structure keeps also 
+reference to the intersecting simplices. A data structure of a single IC consists of:
+\begin{itemize}
+ \item the barycentric coordinate $\vc w_K$ of IC on $K$,
+ \item the dimension $d_K$ of the most specific \nface the IC lies on,
+ \item the local index $i_K$ of that \nface on $K$,
+\end{itemize}
+for each intersecting element $K$ of the pair. The pair $\tau_K = (d_K, i_K)$
+we call the topological position of the IC on $K$.
 
@@
 %reference simplex, in which the numbering of nodes and sides and also the orientation is fixed.
-%The barycentric coordinates of the intersection point can be computed directly from the \plucker products
+%The barycentric coordinates of the intersection corner can be computed directly from the \plucker products
 %and then we can easily obtain its real coordinates (see \cite{fris_dp_2015} for derivations and details).
@@
 \subsection{Intersection Line-Triangle (1D-2D)}
-\notePE{In this paragraph we investigate real lines. Trimming comes later when tolerance is denoted, see next PE note.}
-Let us consider a line $p$ with parametric equation $\vc X = \vc A + t\vc u$, $t\in\R$ and a triangle given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
-with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same sign if and only if there
-is an intersection point with the       line $p$ inside the triangle. In such a case, the inner products provides scaled barycentric coordinates of the intersection on the triangle.
-In particular for the barycentric coordinate $w_i$ related to the vertex $\vc V_i$ we have
-\[
-   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum_{j=0}^{2} \pi_p \odot \pi_{s_i} }
-\]
-Indeed, using the barycentric coordinates the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
-The line $p$ have \plucker coordinates $(\vc u, \vc u \times \vc X)$ (\plucker coordinates are invariant to change of initial point). Combining these two expressions we get
+Let us consider a line $p$ with parametric equation $\vc X = \vc A + t\vc u$, $t\in\R$ and a triangle $T$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
+with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. 
+\begin{lemma}
+The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
+is an intersection point $X$ on the $p$ and inside the triangle $T$. 
+The barycentric coordinates of $X$ on $T$ are
+\begin{equation}
+  \label{eq:bary_centric}
+   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum_{j=0}^{2} \pi_p \odot \pi_{s_i} }.
+\end{equation}
+\end{lemma}
+\begin{proof}
+Using the barycentric coordinates the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
+The line $p$ have \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
+Combining these two expressions we get
 \[
@@
 \]
-Having the barycentric coordinates of the intersection on the triangle we can compute also its local coordinate on $p$ from its parametric form:
-\[
+The point $X$ is inside of $T$ if and only if $w_i>0$ for all $i=0,1,2$.
+\end{proof}
+Having the barycentric coordinates of $X$ on $T$, we can compute also its local coordinate on $p$ from its parametric form:
+\begin{equation}
+   \label{eq:line}
    X_i  = A_i + t u_i, \text{ for } i=1,2,3
-\]
+\end{equation}
 We use $i$ with maximal $|u_i|$ for practical computation.
 
-adaptive precision arithmetic 
-    \cite{elsheikh_reliable_2012} (based on edge-triangle intersections, 
-        use calculations that are similar to usage of \plucker coordinates), 
-    \cite{shewchuk_adaptive_1997}
+The calculation of the intersection proceeds as follows:
+\begin{enumerate}
+    \item Compute or reuse \plucker coordinates and permuted inner products: $\pi_p$, $\pi_i$, $\pi_s \odot \pi_i$, for $i=1,2,3$.
+    \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
+    \item If any $w_i$ is less then $\epsilon$ there is no intersection, return empty IP.  
+    \item If all $w_i$ are greater then $\epsilon$, we set $\tau_T = (2, 0)$ for the IC.
+    \item If one $w_i$ is less then $\epsilon$, intersection on edge $s_i$, we set $\tau_T =(1,i)$.
+    \item If two $w_i$ are less then $\epsilon$, intersection in the vertex $V_i$, we set $\tau_T=(0,,i)$.
+    \item \label{item:coplanar} If all $w_i$ are less then $\epsilon$, the line is coplanar with the triangle, both objects are 
+        projected to the plane $x_i=0$ where $i$ is the index of maximal component of the triangle's normal vector.
+        Every pair $p$, $s_i$ is checked for an intersection on $T$ boundary either inside $s_i$ or in a vertex $V_i$ setting the topological info $\tau_T$ to 
+        $(1, i)$ or $(0, i)$ respectively. At most two ICs are obtained.
+    \item For each IC the barycentric coordinates $(1-t, t)$ on the line $p$ are computed according to \eqref{eq:line}. 
+    \item If $t\in (-\epsilon, \epsilon)$ or $t\in (1-\epsilon, 1+\epsilon)$, we set $\tau_p = (0,0)$ or $\tau_p = (0,1)$, respectively.
+    \item If $t\notin (-\epsilon, 1+\epsilon)$, the IC is eliminated.
+\end{enumerate}
 
-Next, we shall discuss the case when some of the permuted inner products are zero. In fact, we test if any barycentric coordinate is under given tolerance 
-($\abs{w_i} \le \epsilon$). Various \emph{pathological} cases are detected and further topological 
-information is atached to the intersection data.  In the case of one zero coordinate (non-coplanar intersection on the edge)
-or two zero coordinates (intersection in the vertex), we add the local edge index or the local vertex index to the intersection, respectively.
-When all coordinates are (close to) zero, the line and the triangle are (nearly) coplanar. For every edge $s_i$ we compute
-its intersection with the line segment $p$ in terms of the local coordinates $t_i$ and $t_p$. Only intersections with $t_i \in (-\epsilon, 1+\epsilon)$
-are accepted, for $t_i$ close to $0$ and $1$ we append the vertex index to the intersection. Edges parallel to $p$ or lying on the $p$ are skipped.
+The check for the same sign of the inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
+line with respect to the triangle. Adaptive-precision evaluation of the geometric predicates was designed by Schewchuk \cite{shewchuk_adaptive_1997}
+and used for 2d-2d mesh intersections in \cite{elsheikh_reliable_2012}. However, we rather apply a fixed tolerance check for the zero 
+barycentric coordinates and consistently keep the topological positions in this and related algorithms. \noteJB{Can we make the algorithm 
+\emph{parsimonious} in the spirit of the Fortune \cite{fortune_stable_1989} quoted by Schewchuk? 
+Seems that our problem is more local than the line example that was proven to be NP-hard.}
 
-Finally, we obtain zero, one, or two intersection points with additional topological information.
-The intersection point data structure keeps for each of the two intersecting elements:
-\begin{itemize}
- \item Barycentric coordinate of the intersection.
- \item Dimension of the most specific subelement (face, edge, vertex) where the point lies.
- \item Local index of the most specific subelement.
-\end{itemize}
-Further, we store the sign of the permuted inner product in order to detect various special and degenerate cases higher dimensional cases.
-
-TODO:
-We should distinguish "special" case and "degenerate" case. The later one is the case when line lies in the plane of the triangle. The first case should be
-treated as usual only set aditional topology info about vertex or edge. The degenerate case is not necessary to investigate in the case of auxiliary
-intersection only in the case of final intersection. Need to verify it since it is not the case in current code.
-
-We distinguish two variants of the desired result: the auxiliary intersection used as subprocedure of the other intersections and the final intersection.
-In the first case we just return the array of the intersection points with the line.
-\notePE{In the first case, we do not trim the line (We need both IPs (if there are two), for 1D-3D).
-In the final case, we need to check that also $t_p \in (-\epsilon, 1+\epsilon)$.
-That is the current state.}
- Degenerated case of $p$ laying on the triangle edge is also detected....
-\noteJB{No, in 1D-3D we doesn't need result of the degenerate case (all products zero), which is the only case we can obtain two IPs. 
-I'm going to do not deal with the two variants and focus more on correctness then on optimality of the described algorithm.}
-
-Intersection with line segment ... (final 1D-2D intersection)
+The algorithms for 1d-3d and 2d-3d intersections use simpler version of the 1d-2d intersection algorithm, in particular the search for ICs in the coplanar case 
+(item \ref{item:coplanar}) is not necessary and the test in the last point is not performed.
+and degenerate cases higher dimensional cases.
 
 \subsection{Intersection Line-Teraherdon (1D-3D)}
-\noteJB{Has to be completed yet, however we consider that we obtain 0,1, or 2 distinguish IPs for all cases including various touch cases. Anyway every IP results from 
-some non-degenerate 1d-2d intersection. We also assume that the IPs are in order according to the orientation of the side which is
+\noteJB{Has to be completed yet, however we consider that we obtain 0,1, or 2 distinguish ICs for all cases including various touch cases. Anyway every IC results from 
+some non-degenerate 1d-2d intersection. We also assume that the ICs are in order according to the orientation of the side which is
 counterclockwise aroung the triangle.}
@@
 
-There might be two intersection points maximally, which are finally checked that they belong o abscissas.
+There might be two intersection corners maximally, which are finally checked that they belong o abscissas.
 If the line has its boundary point inside the tetrahedron, the intersection line must be cut
-and coordinates of intersection point are interpolated.
+and coordinates of intersection corner are interpolated.
 Pathologic cases are again carefully processed so we obtain the most extensive topology information we can.
@@
 \subsection{Intersection Triangle-Tetrahedron (2D-3D)}
-The intersection of a triangle $S_3$ and a tetrahedron $S_4$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
-lie either on sides of $S_3$ or on faces of $S_4$. Thus each vertex (IP) of the polygon
-can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_3$.
+The intersection of a triangle $S_2$ and a tetrahedron $S_3$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
+lie either on sides of $S_2$ or on faces of $S_3$. Thus each vertex (IC) of the polygon
+can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_2$.
 So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
 to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
-Computation of the intersection polygon consists of two parts: calculation of side-tetrahedron IPs (Algorithm \ref{algo:colect_23_ip_triangle})
-provides all IPs on the boundary of $S_3$,
-calculation of edge-triangle IPs (Algorithm \ref{algo:collect_23_ip_edges}).
-\notePE{The following sentence is somehow weird.. I would say that we store IPs $I$; to sort $I$ during the computation, we use the two tables; at the end, $I$ is ordered correctly.}
-Correct order of the IPs, stored in the list $I$, is defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$.
+Computation of the intersection polygon consists of two parts: calculation of side-tetrahedron ICs (Algorithm \ref{algo:colect_23_ip_triangle})
+provides all ICs on the boundary of $S_2$,
+calculation of edge-triangle ICs (Algorithm \ref{algo:collect_23_ip_edges}).
+\notePE{The following sentence is somehow weird.. I would say that we store ICs $I$; to sort $I$ during the computation, we use the two tables; at the end, $I$ is ordered correctly.}
+Correct order of the ICs, stored in the list $I$, is defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$.
 \notePE{The following sentece is a copy of the second sentence is this subsection.} Every side of the intersection polygon
-lies either on a side of $S_3$, or on a face, or on an edge of $S_4$. Let us denote $M_3$ the set of sides of $S_3$ and $M_4$ the set of volume,
-faces, edges, and vertices of $S_4$. Every side of polygon that lies on $x\in M_3\cup M_4$ is followed by an IP given by $F_g[x]$ 
-and every IP $p$ is followed by the side that lies on $F_p[p]\in M_3\cup M_4$.
+lies either on a side of $S_2$, or on a face, or on an edge of $S_3$. Let us denote $M_2$ the set of sides of $S_2$ and $M_3$ the set of volume,
+faces, edges, and vertices of $S_3$. Every side of polygon that lies on $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
+and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$.
 
@@
   \KwIn{input data}
-  \KwOut{List of IPs on sorted output data}  
+  \KwOut{List of ICs on sorted output data}  
   $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
-  \For{side $s$ of $S_3$}{ 
-    $L$ = intersection($s, S_4$)\;
+  \For{side $s$ of $S_2$}{ 
+    $L$ = intersection($s, S_3$)\;
     \lIf{ $\abs{L} = 0$}{\continue}
@@
         \nllabel{line:m4_object}
-        $p$ lies on $x\in M_4$\; 
+        $p$ lies on $x\in M_3$\; 
         \uIf{$p$ is first in $L$}{
@@
 
-Algorithm \ref{algo:colect_23_ip_triangle} passes through every side $s$ of the triangle $S_3$ and computes the line-tetrahedron intersection $L$.
-In the regular case we process each of the two IPs in $L$. The IP $p$ is added to the list $I$ unless the last point is the same. 
-This condition is effective just for the first IP in $L$ and merges IPs at the same vertex of $S_3$. Then we identify an object $x\in M_4$ the point
+Algorithm \ref{algo:colect_23_ip_triangle} passes through every side $s$ of the triangle $S_2$ and computes the line-tetrahedron intersection $L$.
+In the regular case we process each of the two ICs in $L$. The IC $p$ is added to the list $I$ unless the last point is the same. 
+This condition is effective just for the first IC in $L$ and merges ICs at the same vertex of $S_2$. Then we identify an object $x\in M_3$ the point
 $p$ lies on (line \ref{line:m4_object}). \notePE{I am not sure, if the term 'object' is clear..}
 
-\notePE{Why calling it vertex $v$ instead of IP $p$ here? What is $y$?}
+\notePE{Why calling it vertex $v$ instead of IC $p$ here? What is $y$?}
 If the vertex $v$ is between sides $s_1$, $s_2$, 
 we effectively set connections $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
-is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_4$. The condition at the end deals with the case
-in which two sides intersect the same object $x\in M_4$.
+is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_3$. The condition at the end deals with the case
+in which two sides intersect the same object $x\in M_3$.
 
-For the regular intersection $L$, we pass through its IPs, as described above. \notePE{For special cases}, we firstly compute IPs
-on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every side. We store single point intersections into separate list $J$
-and skip filling the connection tables. This happens when the side touches $S_4$ at its edge or vertex. 
-These IPs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
-this is not the case if the touched edge $e$ of $S_4$ is coplanar with $S_3$ and the IP is inside of $e$. 
-Therefore we keep a separate list $J$ of IPs to deal with this case.
+For the regular intersection $L$, we pass through its ICs, as described above. \notePE{For special cases}, we firstly compute ICs
+on the boundary of $S_2$ using the line-tetrahedron intersection algorithm for every side. We store single point intersections into separate list $J$
+and skip filling the connection tables. This happens when the side touches $S_3$ at its edge or vertex. 
+These ICs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
+this is not the case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$. 
+Therefore we keep a separate list $J$ of ICs to deal with this case.
 
@@
   \DontPrintSemicolon
-  \KwIn{$I$ with IPs on $S_3$ boundary, partially filled $F$}
-  \KwOut{all IPs in $I$, complete $F$}
+  \KwIn{$I$ with ICs on $S_2$ boundary, partially filled $F$}
+  \KwOut{all ICs in $I$, complete $F$}
 
-  \lFor{edge $e$ of $S_4$}{$L[e]$ = intersection($e, S_3$)}  \nllabel{line:12edges}
-  \For{unmarked edge $e$ of $S_4$}{
+  \lFor{edge $e$ of $S_3$}{$L[e]$ = intersection($e, S_2$)}  \nllabel{line:12edges}
+  \For{unmarked edge $e$ of $S_3$}{
     $p=L[e]$\;
@@
     } 
-    \Else($p$ at the vertex $v$ of $S_4$){       
+    \Else($p$ at the vertex $v$ of $S_3$){       
             $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
@@
     }    
-    \uIf{ $p$ is on boundary of $S_3$ }{
-         $p$ lies on edge or at vertex $x \in M_4$\;
+    \uIf{ $p$ is on boundary of $S_2$ }{
+         $p$ lies on edge or at vertex $x \in M_3$\;
          $q=F_g[x]$\tcp*{$q$ is already computed $p$}
@@
   \DontPrintSemicolon
-  \KwIn{vertex $v$ of $S_4$, $L[:]$ intersection results for edges of $S_4$}
-  \KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_4$, coincident with $v$ and intersected by the plane of $S_3$}
+  \KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
+  \KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
   $e_0,\ e_1,\ e_2$ edges coincident with $v$ oriented out of $v$
@@
     }\lElse{
-        append IP of $v$ to $J$
+        append IC of $v$ to $J$
         \return anything\;
@@
   \Else($s$ have all signs same){ \nllabel{line:same_signs}
-    append IP of $v$ to $J$
+    append IC of $v$ to $J$
     \return anything\;
@@
 
-Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_4$ (line \ref{line:12edges}).
-The loop produces IPs in the interior of $S_3$ and possibly those IPs with special position on vertex or edge of $S_4$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
-Every edge $e$ of $S_4$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
-IP on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
+Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
+The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position on vertex or edge of $S_3$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
+Every edge $e$ of $S_3$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
+IC on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
 uses the sign of the intersection to return the pair of faces ordered correctly. 
 Similarly the function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
-returns a pair of generalized faces (face or edge) possibly adjacent to the IP $L[e]$ at the vertex $v$ of $S_4$.
-On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection point they are degenerate and 
+returns a pair of generalized faces (face or edge) possibly adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$.
+On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection corner they are degenerate and 
 not processed anyway.
@@
 \subsubsection{Vertex Faces Algorithm}
-This function gets an IP $p$ at vertex $v$ of $S_4$ as a parameter. The IP is special vertex case of non-degenerate edge-triangle intersection. 
-The function returns a pair of generalized faces of $S_4$ preceeding and succeeding $p$ on the polygons boundary in the case that $p$ is at interior of $S_3$.
-The basic idea is to use the signs of IPs of the three edges coincident with $v$. 
+This function gets an IC $p$ at vertex $v$ of $S_3$ as a parameter. The IC is special vertex case of non-degenerate edge-triangle intersection. 
+The function returns a pair of generalized faces of $S_3$ preceeding and succeeding $p$ on the polygons boundary in the case that $p$ is at interior of $S_2$.
+The basic idea is to use the signs of ICs of the three edges coincident with $v$. 
 Possible cases are:
 \begin{itemize}
- \item {\bf All IPs have the same sign.} (line \ref{line:same_signs}) We return any pair of faces.  $S_3$ is touching $S_4$ 
- at the vertex $v$, the polygon degenerates into the single IP $p$, no connection information from table $F$ is necessary.
- \item {\bf Single IP has the opposite sign to the other two.} (line \ref{line:different_sign}) Let $e$ be the edge of the single IP with the different sign. 
- The plane of $S_3$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. The order is detemined by the function \emph{edge faces}.
- \item {\bf Single degenerated IP.} (line \ref{line:one_degenerated}) Let us denote $e$ the edge with degenerated IP and $f$ the face between the other two edges.
- The other two (non-degenerates) edges may have either the opposite sign (the plane is cutting $S_4$) or the same sign (the plane is touching $S_4$ at the edge $e$).
+ \item {\bf All ICs have the same sign.} (line \ref{line:same_signs}) We return any pair of faces.  $S_2$ is touching $S_3$ 
+ at the vertex $v$, the polygon degenerates into the single IC $p$, no connection information from table $F$ is necessary.
+ \item {\bf Single IC has the opposite sign to the other two.} (line \ref{line:different_sign}) Let $e$ be the edge of the single IC with the different sign. 
+ The plane of $S_2$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. The order is detemined by the function \emph{edge faces}.
+ \item {\bf Single degenerated IC.} (line \ref{line:one_degenerated}) Let us denote $e$ the edge with degenerated IC and $f$ the face between the other two edges.
+ The other two (non-degenerates) edges may have either the opposite sign (the plane is cutting $S_3$) or the same sign (the plane is touching $S_3$ at the edge $e$).
  In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then the vertex faces function returns $(e, f)$ or $(f, e)$, respectively.
@@
  The edge $e$ lies in the the singel edge
- \item {\bf Two degenerated IPs.} (line \ref{line:two_degenerated}) A face of $S_4$ lies in the plane of $S_3$, single edge $e$ have non-degenerate IP.
+ \item {\bf Two degenerated ICs.} (line \ref{line:two_degenerated}) A face of $S_3$ lies in the plane of $S_2$, single edge $e$ have non-degenerate IC.
  We treat the two degenerate edges as special case of faces adjacent to $e$ and return them sorted like the faces given by edge faces of edge $e$.
@@
 
-% Either all signs are equal ($S_3$ touching $S_4$) wee , or
+% Either all signs are equal ($S_2$ touching $S_3$) wee , or
 % a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the 
@@
 % and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
-% with faces of $S_4$.
-Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_3$ belongs to a face $f$ of $S_4$; we know from the order of the points
+% with faces of $S_3$.
+Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_2$ belongs to a face $f$ of $S_3$; we know from the order of the points
 % whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
@@
   $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
-  \lFor{ $f$ is face of $S_4$}{$P[ F[1,f] ] = F[0, f]$}
+  \lFor{ $f$ is face of $S_3$}{$P[ F[1,f] ] = F[0, f]$}
   $i=0$\;  
@@
 
- List $in[f]$ contains index of the intersection point that follows after $f$ on the boundary of traced polygon, 
- similarly $out[f]$ stores index of the intersection point that preeceeds the face $f$.
+ List $in[f]$ contains index of the intersection corner that follows after $f$ on the boundary of traced polygon, 
+ similarly $out[f]$ stores index of the intersection corner that preeceeds the face $f$.
 
@@
 
- If $p$ is on the edge $e$ of $S_4$ compute sign of intersection($e$, $S_3$), sort the faces $f_0$, $f_1$ coincident with $e$
+ If $p$ is on the edge $e$ of $S_3$ compute sign of intersection($e$, $S_2$), sort the faces $f_0$, $f_1$ coincident with $e$
  and set $in[f_0]$ to index of $p$ in $L$. Similarly if $q$ is on the edge, set $out[f_1]$ to index of $q$ in $L$.
 
- If $p$ is in vertex $v$ of $S_4$, for every face $f$ coincident with $v$ set
+ If $p$ is in vertex $v$ of $S_3$, for every face $f$ coincident with $v$ set
  in[$f$] to index of $p$ unless there is some index already set. So, we do not over ride
- entries comming from the edge intersections. Similarly set out[$f$] if $q$ is in vertex of $S_4$.
+ entries comming from the edge intersections. Similarly set out[$f$] if $q$ is in vertex of $S_3$.
 
- If $p$ is on face $f_0$ of $S_4$, set $in[f_0]$ to index of $p$. Similarly, if $q$ is on face $f_1$ of $S_4$, set $out[f_1]$ to index of $q$.
- laying on faces $f_p$, $f_q$ of $S_4$.
+ If $p$ is on face $f_0$ of $S_3$, set $in[f_0]$ to index of $p$. Similarly, if $q$ is on face $f_1$ of $S_3$, set $out[f_1]$ to index of $q$.
+ laying on faces $f_p$, $f_q$ of $S_3$.
 
- \item $L$ consists of a single intersection point $p$ (touching $S_4$)
+ \item $L$ consists of a single intersection corner $p$ (touching $S_3$)
 
- If $p$ is on edge, compute sign of intersection($e$, $S_3$), sort the faces $f_0$, $f_1$,
+ If $p$ is on edge, compute sign of intersection($e$, $S_2$), sort the faces $f_0$, $f_1$,
  set $in[f_0]$ and $out[f_1]$ to index of $p$.
@@
 \begin{itemize}
- \item If there are no intersections in vertex of $S_4$. 
+ \item If there are no intersections in vertex of $S_3$. 
 \end{itemize}
@@
 intersection polygon
-are found as intersection points of either triangle side and tetrahedron or tetrahedron edge and triangle.
+are found as intersection corners of either triangle side and tetrahedron or tetrahedron edge and triangle.
 Therefore we use both algorithms above for 1D-3D and 1D-2D, respectively. Data are again efficiently passed
@@
 
-The array of intersection points is generally not sorted. We use two so called \emph{tracing} algorithms and we
+The array of intersection corners is generally not sorted. We use two so called \emph{tracing} algorithms and we
 intend to orient the edges of the polygon in the same direction as the triangle is oriented.
-If one of the intersection point is pathologic, a general convex hull method is applied using the Monotone 
+If one of the intersection corner is pathologic, a general convex hull method is applied using the Monotone 
 chain\footnote{Wikibooks, [online 2016-03-01], 
@@
 the complexity to $O(N)$, compared with the Monotone chain complexity $O(N\log N)$ 
-($N$ being number of intersection points).
+($N$ being number of intersection corners).
 
@@
 % 1d-3d prolongation logic
-% IP is:
+% IC is:
 % - 1D element node
@@
 %     - on the surface of tetrahedron
-%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%         - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
 %         - get the tetrahedron neighbors on the faces
@@
 %             - check whether the candidate pair has not been computed yet
-%             (- if no new prolongation, push empty pair; means IP is on the boundary; 
+%             (- if no new prolongation, push empty pair; means IC is on the boundary; 
 %                the element is not closed then -- not fully covered with tetrahedrons)
 % - inside 1D element
-%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%     - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
 %     - get the tetrahedron neighbors on the faces
@@
 
-% A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:
+% A new candidate pair of elements is found during prologantion, based on the topological information of the intersection corner. There are 3 possible cases:
 
 % \begin{itemize}
-%     \item \textbf{IP lies at 1D element node and inside 3D element} \\
+%     \item \textbf{IC lies at 1D element node and inside 3D element} \\
 %             We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
-%     \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
-%             We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
-%             or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
+%     \item \textbf{IC lies at 1D element node and on the surface of 3D element} \\
+%             We find all the faces of 3D element in which the IC lies (1 face, or 2 faces (IC on an edge), 
+%             or 3 faces (IC at a node)). We find the corresponding neghboring 3D elements over the faces and
 %             push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
 %             If the candidates pair has been investigated already, we skip it.
-%     \item \textbf{IP lies inside 1D element (therefore must be on the surface of 3D element)} \\
+%     \item \textbf{IC lies inside 1D element (therefore must be on the surface of 3D element)} \\
 %             The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
@@
 
-A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases (applies both for 1D-3D and 2D-3D):
+A new candidate pair of elements is found during prologantion, based on the topological information of the intersection corner. There are 3 possible cases (applies both for 1D-3D and 2D-3D):
 \begin{itemize}
-    \item \textbf{IP lies on component element side and inside bulk element} \\
-            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
+    \item \textbf{IC lies on component element side and inside bulk element} \\
+            We find all the sides of component element in which the IC lies (IC can be at node and connect more sides).
             We find the component neighboring elements over the sides and push a new candidate pair
             [component neighbor -- current bulk element] into component queue.
-    \item \textbf{IP lies on component element side and on the surface of bulk element} \\
-            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
-            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
+    \item \textbf{IC lies on component element side and on the surface of bulk element} \\
+            We find all the faces of bulk element in which the IC lies (1 face, or 2 faces (IC on an edge), 
+            or 3 faces (IC at a node)). We find the corresponding neighboring bulk elements over the faces and
             push the following new candidates pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
             If the candidates pair has been investigated already, we skip it.
-    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
+    \item \textbf{IC lies inside component element (therefore must be on the surface of bulk element)} \\
             The same as before, but we push only [current component element -- bulk neighbor] candidates pairs, since
@@
 % 2d-3d prolongation logic CURRENT
-% IP is:
+% IC is:
 % - inside 2D element side
@@
 % 2d-3d prolongation logic WITH FUTURE CORRECTIONS
-% IP is:
+% IC is:
 % - on 2D element side
@@
 %     - on the surface of 3D element
-%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%         - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
 %         - get the 3D neighbors over the faces
@@
 % - inside the 2D element (=> on the surface of 3D element)
-%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
+%     - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
 %     - get the 3D neighbors over the faces
@@
 (Binary SPace Tree) structure to find initial point on intersection curve and trace the curve in both directions. Quite clever data structure for the mesh. Adaptive precision 
-geometric predicates. Store topological information about the intersection points (point on triangle, edge, vertex). Resolve various degenerate cases, 
+geometric predicates. Store topological information about the intersection corners (point on triangle, edge, vertex). Resolve various degenerate cases, 
 dicuss mesh optimization after subdivision.

### 2016-09-29 paper_intersections.tex

@@
 The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
-and compute that intersection.
+and to compute that intersection.
 
@@
 
+\notePE{Unify the term 'front tracing' 'front tracking' 'advancing front'.}
 Our contribution is twofold:  First, we use the front tracking algorithm both to minimize set of intersection candidates as well 
@@
 
-\subsection{Prolongation algorithm}
+\section{Front tracking algorithm}
+Prerequisites:
+  \begin{itemize}
+   \item need information about element connectivity (mesh preprocessing)
+%   \item mark and check already inspected pairs. Marking elements + hashing.
+   \item find the starting intersection -- AABB (Axes Aligned Bounding Boxes) 
+   \item possibly create Bounding Interval Hierarchy (BIH)
+%   \item Pass already known information with pairs.
+%   \item Deal with degenerated cases.
+  \end{itemize}
+
 Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
 elements of the same lower dimension (1D, 2D), in the space of 3D elements, which we shall call a \emph{bulk}. 
-Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other.
-Then we can prolongate the intersection by investigating neighbouring elements.
-%
-\begin{figure}[!htb]
-%   \vspace{0pt}
-  \centering    
-    \includegraphics[width=\textwidth]{\figpath prolongation_scheme.pdf}
-  \caption{Prolongation algorithm for 1D-2D and 2D-3D intersections. }
-  \label{fig:prolongation}
-\end{figure}
+Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other. Then we can prolongate the intersection by investigating neighbouring elements.
 
-The prolongation algorithm is the same for both 1D and 2D components, see \fig{fig:prolongation}. 
 It can be seen as a \emph{breadth-first search}
@@
 
-A new candidate pair of elements is found during prologantion, based on the topological information of the intersection corner. There are 3 possible cases (applies both for 1D-3D and 2D-3D):
-\begin{itemize}
-    \item \textbf{IC lies on component element side and inside bulk element} \\
-            We find all the sides of component element in which the IC lies (IC can be at node and connect more sides).
-            We find the component neighboring elements over the sides and push a new candidate pair
-            [component neighbor -- current bulk element] into component queue.
-    \item \textbf{IC lies on component element side and on the surface of bulk element} \\
-            We find all the faces of bulk element in which the IC lies (1 face, or 2 faces (IC on an edge), 
-            or 3 faces (IC at a node)). We find the corresponding neighboring bulk elements over the faces and
-            push the following new candidates pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
-            If the candidates pair has been investigated already, we skip it.
-    \item \textbf{IC lies inside component element (therefore must be on the surface of bulk element)} \\
-            The same as before, but we push only [current component element -- bulk neighbor] candidates pairs, since
-            there is no component neighbor.
-\end{itemize}
-
 % 2d-3d prolongation logic CURRENT

### 2016-09-29 paper_intersections.tex
Minor corrections in prolongations.

--- 2016-09-29 paper_intersections.tex
@@
     \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip.pdf}
-  \caption{Prolongation algorithm for 1D-2D and 2D-3D intersections. }
+  \caption{Advancing front algorithm for 1D-2D and 2D-3D intersections.}
   \label{fig:prolongation}
@@
 
-The advancing front algorithm works the same way for both 1D and 2D components and is displayed in \fig{fig:prolongation}. The main idea is to compute intersections for a component element with all 
+The advancing front algorithm works the same way for both 1D and 2D components and is displayed by the scheme in \fig{fig:prolongation}.
+The main idea is to compute intersections for a component element with all
 possible bulk elements, and then move to a~next neighboring component element. For this reason, we define two
@@
 Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
-Therefore, we iterate over the intersection points and further exploit their topological information.
-There are 3 possible cases (applies both for 1D-3D and 2D-3D):
+Therefore, we iterate over the intersection points and further exploit the topological information.
+There are 3 possible cases (applies both for 1D-3D and 2D-3D), how the intersection might be prolonged:
 \begin{itemize}
@@
             or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
-            push the following new candidate pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
+            push the new candidate pairs [current component element -- bulk neighbor] into the bulk queue and [component neighbor -- bulk neighbor] into the component queue.
     \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\

### 2016-09-30 paper_intersections.tex
intersection 13d fished

--- 2016-09-29 paper_intersections.tex
@@
 
-\title{Intersection of non-matching grids of different dimensions}
-% Self-intersection of non-matching grid of mixed dimensions
+%\title{Algorithm for Intersections of Nonmatching Grids of Different Dimensions}
+\title{Fast Algorithms for Intersection of Nonmatching Grids Using \plucker coordinates.}
 
@@
 \begin{abstract}
-TODO: An abstract.
 \end{abstract}
@@
 \subsection{Intersection Line-Triangle (1D-2D)}
-Let us consider a line $p$ with parametric equation $\vc X = \vc A + t\vc u$, $t\in\R$ and a triangle $T$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
+Let us consider a line segment $p$ with parametric equation 
+\begin{equation}
+    \label{eq:line_parametric}
+    \vc X = \vc A + t\vc u,\ t\in (0,1)
+\end{equation}
+and a triangle $T$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
 with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. 
@@
 \subsection{Intersection Line-Teraherdon (1D-3D)}
-\noteJB{Has to be completed yet, however we consider that we obtain 0,1, or 2 distinguish ICs for all cases including various touch cases. Anyway every IC results from 
-some non-degenerate 1d-2d intersection. We also assume that the ICs are in order according to the orientation of the side which is
-counterclockwise aroung the triangle.}
-We consider a line $p$ and a tetraherdon...
-Tetrahedron has six edges, so six \plucker coordinates and inner products are computed at most. These data are
-passed to the 1D-2D algorithm described above, which is applied to the every face of the tetrahedron face.
+In this section we consider intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
+$S_3$. The used algorithm is based on 1d-2d algorithm and closely follows \cite{platis_fast_2003}. Our modification takes into account
+intersection with a line segment and consistently propagates topological position of ICs.
 
-There might be two intersection corners maximally, which are finally checked that they belong o abscissas.
-If the line has its boundary point inside the tetrahedron, the intersection line must be cut
-and coordinates of intersection corner are interpolated.
-Pathologic cases are again carefully processed so we obtain the most extensive topology information we can.
-See \cite{fris_dp_2015} for detailed description of all possible cases.
+\begin{algorithm}
+  \caption{1d-3d intersection}
+  \label{algo:13d}
+
+  \DontPrintSemicolon
+  \SetKw{and}{and}
+  \SetKw{continue}{continue}
+  \SetKw{break}{break}
+  \KwIn{Tetrahedron $S_3$, line segment $p$.}
+  \KwOut{List of ICs on sorted along $p$.}  
+  $I=\{\}$ 
+  \For{unmarked face $f$ of $S_3$}{
+    $L$ = intersection($p,\ f$)\;
+    \lIf{ $L$ is none or degenerate}{\continue}
+    \lIf{ $L$ is inside the edge $e$}{
+        set $\tau_{S_4} = (1,e)$\;
+        mark faces coincident with $e$
+    }
+    \ElseIf{ $L$ is at the vertex $v$}{
+        set $\tau_{S_4} = (0,v)$\;
+        mark faces coincident with $v$
+    }
+    append $L$ to $I$
+    \lIf{$\abs{I}=2$}{\break} 
+  }
+  \lIf{$\abs{I}=1$ \and   $I$ is outside of $p$}{ erase $I$}
+  \ElseIf{$\abs{I}=2$}{    
+    trim intersection with respect to the line segment $p$ \label{line:trimming}
+  }
+\end{algorithm}
+Algorithm \ref{algo:13d} first compute line-face intersections for every face of $S_4$ avoiding duplicate computation of ICs on edges and at vertices and
+skipping remaining faces once two ICs are found. Tetrahedron has six edges, so 7 \plucker coordinates and 6 inner products are computed at most. Precomputed 
+coordinates and products are passed the 1D-2D algorithm which is performed fro the whole line $p$. After collecting line-tetrahedron ICs,
+we do the line segment trimming \ref{line:trimming}. If both ICs are out of the line segment $p$ we eliminate both of them. If one of the ICs if out of $p$
+we use the closest end point of the line segment instead and interpolate barycentric coordinates of the IC on $S_4$. The topological positions are updated as well.
+The result of the algorithm are zero up to two ICs sorted by the parameter $t$ of the line $p$.
 

### 2016-09-30 suplementary/ESCO Plzen 2016/prezentace/ESCO_2016_brezina.tex

\documentclass[10pt]{beamer} %[handout,red]
\usepackage{amsmath}
\usepackage{graphicx,multimedia,hyperref,xmpmulti}
\usepackage[utf8]{inputenc}
\usepackage[czech]{babel}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SYMBOLS
\def\div{{\rm div}}
\def\Lapl{\Delta}
\def\grad{\nabla}
\def\supp{{\rm supp}}
\def\dist{{\rm dist}}

\def\Tr{{\rm Tr}}
\def\sgn{{\rm sgn}}
\def\to{\rightarrow}
\def\weakto{\rightharpoonup}
\def\imbed{\hookrightarrow}
\def\cimbed{\subset\subset}
\def\range{{\mathcal R}}
\def\argdot{{\hspace{0.18em}\cdot\hspace{0.18em}}}
\def\Distr{{\mathcal D}}
\def\convol{\star}
\def\impl{\Rightarrow}
\DeclareMathOperator*{\esslim}{esslim}
\DeclareMathOperator*{\esssup}{ess\,sup}
\DeclareMathOperator{\ess}{ess}
\DeclareMathOperator{\osc}{osc}
\DeclareMathOperator{\curl}{curl}

% ****************************************** GENERAL MATH NOTATION
\def\Real{{\rm\bf R}}
\def\d{\,{\rm d}}               % differential

\def\vc#1{\mathbf{\boldsymbol{#1}}}     % vector
\def\tn#1{{\mathbb{#1}}}    % tensor
\def\abs#1{\lvert#1\rvert}
\def\Abs#1{\bigl\lvert#1\bigr\rvert}
\def\bigabs#1{\bigl\lvert#1\bigr\rvert}
\def\Bigabs#1{\Big\lvert#1\Big\rvert}
\def\ABS#1{\left\lvert#1\right\rvert}
\def\norm#1{\bigl\Vert#1\bigr\Vert} %norm
\def\close#1{\overline{#1}}
\def\inter#1{#1^\circ}
\def\ol#1{\overline{#1}}
\def\ul#1{\underline{#1}}
\def\eqdef{\mathrel{\mathop:}=}     % defining equivalence
\def\where{\,|\,}                    % "where" separator in set's defs
\def\timeD#1{\dot{\overline{{#1}}}}

% ******************************************* USEFULL MACROS
% enumerate by roman numbers
\def\RomanEnum{\renewcommand{\labelenumi}{\rm (\roman{enumi})}}   
% partial deriv.
\def\prtl{\partial} 
\def\Names#1{{\scshape #1}}
\def\rem#1{{\parskip=0cm\par!! {\sl\small #1} !!}}

\def\Xint#1{\mathchoice
{\XXint\displaystyle\textstyle{#1}}%
{\XXint\textstyle\scriptstyle{#1}}%
{\XXint\scriptstyle\scriptscriptstyle{#1}}%
{\XXint\scriptscriptstyle\scriptscriptstyle{#1}}%
\!\int}
\def\XXint#1#2#3{{\setbox0=\hbox{$#1{#2#3}{\int}$}
\vcenter{\hbox{$#2#3$}}\kern-.5\wd0}}
\def\ddashint{\Xint=}
\def\dashint{\Xint-}

% ******************************************* DOCUMENT NOTATIONS
% document specific
\def\rh{\varrho}
\def\th{\vartheta}
\def\dx{\,\d\vx}
\def\dt{\,\d t}
\def\eps{\varepsilon}
\def\phi{\varphi}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic colors
%%%%%%%%%%%%%%%%%%%%
%\definecolor{background}{RGB}{238, 242, 249}       %grey
\definecolor{background}{RGB}{255,255,255}
% frame titles, section, enumrations, etc. (should match main color of logo)
%\definecolor{cxi}{RGB}{196,18,45}
\definecolor{cxi}{RGB}{225,114,21}
\definecolor{emph}{RGB}{196, 18, 45}
% complementary foregroung color, emphesize some text 
\definecolor{emph2}{RGB}{18, 4, 199}

\def\col{\textcolor}

% Templating stuff
% \beamertemplatetransparentcovereddynamic
%\colorlet{averagebackgroundcolor}{gray}
%\setbeamertemplate{itemize items}[circle]
%\setbeamertemplate{enumerate items}[square]
\setbeamertemplate{section in toc}[square]
%\setbeamercolor*{block title}{fg=white,bg=structure!75!black}
%\setbeamercolor*{block body}{bg=structure!10!averagebackgroundcolor}

%\setbeamercolor*{block title example}{fg=white,bg=beamerexample!75!black}
%\setbeamercolor*{block body example} 
%{bg=beamerexample!10!averagebackgroundcolor}
%\usepackage{beamerthemeshadow}
%\setbeamertemplate{background canvas}{\includegraphics 
%[width=0.3\paperwidth]{logo-cxi-cmyk-cz.pdf}}

\setbeamertemplate{footline}{
    \includegraphics[width=\paperwidth]
    {graphics/fm-spojovaci.png}

    \vspace{-6mm}

    \hspace{5mm}{
        \bf\insertshorttitle~ \textcolor{structure}{$\boldsymbol{|}$} 
        \insertdate
    }

    \vspace{-3.1mm}

    \hspace{\stretch{1}} 
    \textcolor{white}{\insertframenumber/\inserttotalframenumber} \hspace{2mm}

    \vspace{3mm}
}

\setbeamercolor{structure}{fg=cxi, bg=background}
\setbeamertemplate{frametitle}
{
    \begin{flushleft} 
        \bf\large\insertframetitle
    \end{flushleft}
    \par
}

\beamertemplateheadempty
\beamertemplatenavigationsymbolsempty
\beamertemplateshadowblocks

%\AtBeginSection[]
%{
%\frame{\frametitle{Obsah}
%  \tableofcontents[currentsection]
%}
%\addtocounter{framenumber}{-1} 
%}

%***************************************************************************

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%5

%\AtBeginSection[]
%{
% \begin{frame}<beamer>
% \frametitle{Plan}
% \tableofcontents[currentsection]
% \end{frame}
%}

\title[Fast non-matching grids]{
\textcolor{emph2}{Fast intersections of non-matching grids\\ using the Pl\"ucker coordinates.}
\vspace{2ex}
}

\author{{\bf Jan Březina}, Pavel Exner, Jan Stebel}
\institute{Technical University of Liberec, Czech Rep.}
\date{ESCO, June 2016}

\begin{document}
%\setbeamercolor{background canvas}{bg=gray}

{  
    \setbeamercolor{background canvas}{bg=background} 
    \setbeamertemplate{background}
    {

        %\includegraphics[width=0.5\paperwidth]{graphics/logo-cxi-cmyk-en.pdf}
        \includegraphics[width=0.5\paperwidth]{graphics/logo-fm-cmyk-en.pdf}

    }

    \setbeamertemplate{footline}
    {\includegraphics[width=\paperwidth]{graphics/fm-spojovaci.png}

        \vspace{-6mm}
        \hspace{5mm}
        {\bf TECHNICAL UNIVERSITY OF LIBEREC 
            \textcolor{structure}
            {$\boldsymbol{|}$ Fakulty of mechatronics}
        }
        \textcolor{structure}{$\boldsymbol{|}$} fm.tul.cz

        \vspace{-3.1mm}
        \hspace{\stretch{1}} 
        \textcolor{white}{\insertframenumber/\inserttotalframenumber} 
        \hspace{2mm}

        \vspace{3mm}
    }

    \begin{frame}    
        \vspace{1cm}
        {\bf\large\inserttitle}\\
        \vspace{2mm}
        \textit{\insertauthor~ \textcolor{structure}{$\boldsymbol{|}$} \insertdate}
    \end{frame}
}

\begin{frame}{Primary motivation: Geometry with multiscale features}
    \noindent
    \hbox{
    \begin{minipage}{0.5\linewidth}
        \includegraphics[width=\linewidth]{graphics/melechov_scale.pdf}
    \end{minipage}
    \begin{minipage}{0.5\linewidth}
        \begin{itemize}
        \item Candidate locality for a nuclear waste deposit in the Czech Republic.
        \item Plutonic rock with significant fracture zones.
        \item Fracture zones: Small flux, big velocity $\impl$
        \item Possible fast transport of polutants (preferential paths).
        \end{itemize}

        \vspace{2ex}
        \begin{itemize}
        \item Large, but thin fracture zones leads
              to a multiscale problem.
        \item Direct discretization is impractical.
        \item Our approach: fractures as lower dimensional objects.
        \end{itemize}
    \end{minipage}
    }
\end{frame}

\begin{frame}{Integrating accross the fracture}
    \begin{minipage}{0.40\textwidth}
    Coupled 2D domains accross boundary.
    \begin{center}
        \includegraphics[width=\linewidth]{graphics/continuum_model_domain.pdf}
    \end{center}    
    \end{minipage}
    \hspace{1ex}$\longrightarrow$\hspace{1ex}
    \begin{minipage}{0.40\textwidth}
        Coupled 2D continuum with the fracture 1D model.
        \begin{center}
                \includegraphics[width=\linewidth]{graphics/fracture_model_domain.pdf}
        \end{center}
    \end{minipage}

    \vspace{2ex}
    \textcolor{blue}{Related works:}\\
    {\small
    {\bf Martin, Jaffr{\'e}, Roberts} : {\it Modeling Fractures and Barriers ...}, 2005

    \vspace{1ex}
    {\bf Angot, Boyer, Hubert} : {\it Asymptotic and numerical modelling ...}, 2009

    \vspace{1ex}
    {\bf B., Stebel} :  {\it Analysis of Model Error ...}, 2015
    }    
\end{frame}

\begin{frame}{Why we need non-matching grids?}
\begin{center}
\includegraphics[width=0.6\linewidth]{graphics/compatible_noncompatible.pdf} 
\end{center}

\begin{itemize}
 \item resolve dificulties with complex geometry (thousends of fractures)
 \item simplify mesh generation
 \item allow changing geometry (e.g. crack propagation)
 \item possible usage in a multi mesh approach
\end{itemize}

\end{frame}

\begin{frame}{What we need?}
\begin{itemize}
  \item universal algorithm(s): 3D-2D, 2D-1D, 3D-1D, 2D-2D  
  \item fast algorithm: milions of elements, dense fracture networks
  \item robust algorithm, e.g. 
\end{itemize}

\vspace{2ex}
All intersections based on line-triangle intersections.\\

\vspace{2ex}
Inspiration by computer graphics algorithms, ray-triangle.\\
Pl\"ucker coord. apprach. (Platis, Theoharis, 2003) 
\end{frame}

\begin{frame}{Pl\"ucker coordinates}
  The line $p$, direction vector $\vc u$ going through the point $\vc A$.\\
  \textcolor{blue}{Pl\"ucker coordinate:}
  \[
    \pi_p = (\vc u_p, \vc v_q) =( \vc u, \vc u \times \vc A).
  \]

  \vspace{2ex}
  \textcolor{blue}{Scalar product:}
  \[
     \pi_p \cdot \pi_q = \vc U_p \cdot \vc V_q + \vc U_q \cdot \vc V_p,
  \]

  \vspace{2ex}

  \begin{center}
  \includegraphics[scale=0.2]{graphics/plucker_product.pdf} 
  \end{center}
\end{frame}

\begin{frame}{Barycentric coordinates}
    \textcolor{blue}{On triangle:}
        \[
        x_i = \frac{\pi_p \cdot \pi_i}{\sum_{j=1}^{3} \pi_p \cdot \pi_j}
        \]
    \textcolor{blue}{On line $\vc A + t\vc U$:}
        \[
        y_0 = \frac{\abs{\vc X - \vc A}}{\abs{\vc U}}
        \] 
    \textcolor{blue}{On tetrahedra:}
        Append one zero coordinate (depending on the face).
\end{frame}

\begin{frame}{Intersection polygon (2D-3D)}
\begin{itemize}
 \item Need to sort intersections to form convex polygon.
 \item Standard convex hull algorithms ... slow, further float operations.
 \item Reusing signs of Pl\"ucker products, we get correct order ...
\end{itemize}
\end{frame}

\begin{frame}{Intersection polygon (2D-3D)}
    \begin{itemize}
     \item Polygon sides formed by triangle sides (S), tetrahedra faces (F).
     \item Intersection point connect particualar S with particular F.
     \item Order is given by triangle side orientation (SS, SF) or P\"ucker sign (FF).
    \end{itemize}
    \begin{center}
    \includegraphics[scale=0.4]{graphics/polygon_tracing.pdf} 
    \end{center}   
\end{frame}

\begin{frame}{Efficiency (2D-3D)}
    \begin{minipage}{0.45\textwidth}
        \begin{tabular}{l|l}
            algorithm, 2D-3D& FLOPs\\
                      & estimate\\
            \hline\\
            parametric plane & 585\\
            normal plane (reuse) & 765\\
            Moller and Trumbore & 783\\
            Pl\"ucker (reuse) & 306
        \end{tabular}
        \vspace{4em}
    \end{minipage}
    \hspace{2ex}
    \begin{minipage}{0.45\textwidth}
        \begin{center}
            \includegraphics[width=1.2\textwidth]{graphics/intersections_fundamental_speed.pdf}
        \end{center}

    \end{minipage}
\end{frame}

\begin{frame}{Intersection of meshes}
  breath first search, algorithm 2D-3D, 1D-3D:
  \begin{enumerate}
    \item Get next unprocessed 2D element $k$.
    \item Find intersection candidates $\mathcal K$ in 3D mesh.
    \item For $K\in \mathcal K$ check intersection $(k, K)$.  
    \item Push the intersection neigbours into queues: $(k, L) \to Q_3$, $(l, K) \to Q_2$. 
    \item While $(l, L) \in Q_3$ check intersection $(l, L)$. Append queues.
    \item Pop pair from $Q_2$. (move to the next 2D element)
  \end{enumerate}

  \vspace{2ex}
  Issues:
  \begin{itemize}
   \item Need information about element connectivity (preprocessing).
   \item Mark and check already inspected pairs. Marking elements + hashing.
   \item Find the starting intersection. Use AABB (axes aligned bounding boxes) possibly with Bounding Interval Hierarchy. 
   \item Pass already known information with pairs.
   \item Deal with degenerated cases.
  \end{itemize}
\end{frame}

\begin{frame}{Scaling on artificial mesh}
  Cube with two diagonal fractures.

  \vspace{3ex}
  \hspace{-5ex}  
  \begin{minipage}{0.55\textwidth}
    \includegraphics[scale=0.5]{graphics/intersections_test1_cube_speed_scaling.pdf}
    %\vspace{4em}
  \end{minipage}
  \hspace{5ex}
    \begin{minipage}{0.4\textwidth}
    \begin{center}
    \includegraphics[scale=0.2]{graphics/cube_mesh.png} 
    \end{center}
    \end{minipage}
\end{frame}

\begin{frame}{Performance on a real world problem}

    \begin{center}
    \includegraphics[scale=0.25]{graphics/bedrichov_mesh.png}
    \end{center}

    \begin{center}
    \includegraphics[scale=0.55]{graphics/intersections_bedrichov_both_speed.pdf}     
    \end{center}    
\end{frame}

\begin{frame}{Flow123d : \textcolor{black}{\bf flow123d.github.com}}
    \hbox{
        \hspace{6ex}
        \begin{minipage}{\linewidth}
            \includegraphics[scale=0.35]{graphics/real_appl.pdf}
        \end{minipage}
        \hspace{-1.15\linewidth}
        \begin{minipage}{\linewidth}

            \vspace{10ex}
            \begin{itemize}
             \item Software for hydrogeological modeling.
             \item \textcolor{blue}{Models on combination of 3d, 2d, 1d} simplicial elements
             \item Open source, C++
            \end{itemize}
        \end{minipage}
    }
\end{frame}

\begin{frame}{Flow123d - models}
\parindent 4ex

\noindent
\textcolor{emph2}{Darcy Flow}\\
steady and unsteady problems,\\
Lumped Mixed-Hybrid method, $RT_0$ elements\\

\vspace{2ex}
\noindent
\textcolor{emph2}{Solute Transport}\\
explicit FV, pure convection,\\
implicit Discontinuous Galerkin (arbitrary order), diffusion-dispersion

\vspace{2ex}
\noindent
\textcolor{emph2}{Reaction Term}\\
operator splitting\\
equilibrium sorption (fast interpolation algorithm)\\
dual porosity\\
decays, linear reactions

\vspace{2ex}
\noindent
\textcolor{emph2}{Heat transfer}\\
liquid-solid thermal equilibrium,\\
implicit Discontinuous Galerkin

\end{frame}

\begin{frame}{Application of non-matching meshes}
 ... work in progress: ...
\end{frame}

\begin{frame}{Darcy flow, 2D-1D interaction}

 \begin{center}
  \includegraphics[scale=0.2]{graphics/boundary_P1.png}
   % boundary_P1.png: 752x772 pixel, 72dpi, 26.53x27.23 cm, bb=0 0 752 772
  \includegraphics[scale=0.2]{graphics/boundary_P1-comp.png}
   % boundary_P1-comp.png: 753x772 pixel, 72dpi, 26.56x27.23 cm, bb=0 0 753 772
 \end{center}

 {\bf Left: } Pressure head computed by P1 method,\\
              domain $[-1,1] \times [-1,1]$.

 {\bf Right: } Difference between non-compatible P1 coupling \\
 and compatible coupling, log scale, $h=0.01$

\end{frame}

\begin{frame}{Wells: 3D-1D, XFEM}
    Goal: capture log cone aroung wells without increasing n. of DOFs
     \vspace{2ex}
     \begin{minipage}{0.4\linewidth}
         \centering
         \includegraphics[width=0.8\linewidth]{graphics/five_wells_mesh1.pdf}

         \centering
         {\footnotesize adaptive FEM, mesh,\\ 30k elements, 171s}
     \end{minipage}
     \hspace{3em}
     \begin{minipage}{0.4\linewidth}
         \centering
         \includegraphics[width=0.8\linewidth]{graphics/five_wells_mesh2.pdf}

         \centering            
         {\footnotesize XFEM mesh and solution,\\ 1k elements, 17s}
     \end{minipage}

 Key ingredients:
 \begin{itemize}
    \item Find intersections.
    \item Suitable enrichment (for the mixed method).
    \item Adaptive integration in assembly.
  \end{itemize}  
  \vspace{-1ex}
  \hfill\hbox{\includegraphics[width=0.7\linewidth]{graphics/warp_five_wells_alpha.png}}
\end{frame}

\begin{frame}{Elasticity of composits: 3D-1D}
\includegraphics[width=10cm]{graphics-js/matrix-fibers}
\begin{itemize}
\item 3D structure with filament enforcement (polymer composites, stents)
\item 3D-1D non-matching grids, XFEM approach
\end{itemize}

\includegraphics[width=10cm]{graphics-js/T-bend}

\includegraphics[width=10cm]{graphics-js/pipes}
\end{frame}

\begin{frame}{Changing geometry: vocal cord simulation}
\includegraphics[width=10cm]{graphics/vocal_tract.png}

\begin{itemize}
 \item problem with contact - change in topology
 \item possible use of Immersed Boundary Method, need 3D-2D intersections
\end{itemize}
\end{frame}

\begin{frame}{Summary}
\begin{itemize}
 \item Mixed dimesion grids and models as solution of some multisclae problems.
 \item Mesh generation problems could be solved by non-matchin grids.
 \item Family of efficient algorithms for 3D-2D, 3D-1D, 2D-2D, 2D-1D intersection.
 \item flow123d.github.io - mixed dimension approach, full usage of non-matching girds yet to come.
 \item Some other possible applications ...
\end{itemize}

\pause

\vspace{2ex}
\begin{center}
\includegraphics[scale=0.3]{graphics/thank-you-clothesline-752x483.jpg}
\end{center}

\end{frame}

\end{document}

\begin{frame}{GeoMop ... práce na reálných GEO úlohách}
\begin{itemize}
 \item Polo-automatická příprava výpočetních sítí z GIS dat a dalších podkladů.
 \item Grafický editor vstupu pro model.
 \item Nástroj pro jednotné spouštění a monitorování úloh na vzdálených systémech.
 \item Grafický programovací jazyk pro komplexní analytické úlohy: 
 \begin{itemize}   
    \item příprava sítí
    \item kalibrace, citlivostní analýza (Monte-Carlo)
    \item víceškálové modely
    \item postprocesing a vizualizace
 \end{itemize}   
\end{itemize}

\end{frame}

\begin{frame}{Co můžeme nabídnout?}
\begin{itemize}
 \item Matematické znalosti: teorie PDR, numerické metody pro PDR, lineární algebra, statistika
 \item Matematické modely: transportní procesy, mechanika tekutin, mechanika
 \item Zkušenost s použitím různých výpočetních knihoven pro tvorbu vlastního numerického software.
 \item Vizualizace v Paraview.
\end{itemize}

\end{frame}

### 2016-09-30 paper_intersections.tex
introduction and initialization of afront.

@@
 
-\section{Front tracking algorithm}
-Prerequisites:
+\section{Advancing Front Method}
+
+add references...
+% BIH:
+% http://ainc.de/Research/BIH.pdf
+% http://diglib.eg.org/handle/10.2312/EGWR.EGSR06.139-149
+
+Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
+elements of the same lower dimension (1D, 2D), in the space of connected 3D elements, which we shall call a \emph{bulk}. 
+Obtaining all of component-bulk intersections is done in two phases: firstly, we look for the first two elements intersecting each other (initialization); secondly, we prolong the intersection by investigating neighbouring elements (intersection tracking).
+
+To construct the Advancing front algorithm, we shall need:
 \begin{itemize}
-   \item need information about element connectivity (mesh preprocessing)
-%   \item mark and check already inspected pairs. Marking elements + hashing.
-   \item find the starting intersection -- AABB (Axes Aligned Bounding Boxes) 
-   \item possibly create Bounding Interval Hierarchy (BIH)
-%   \item Pass already known information with pairs.
-%   \item Deal with degenerated cases.
+    \item \textbf{element connectivity} -- we assume this data is available from mesh preprocessing,
+    \item \textbf{Axes Aligned Bounding Boxes (AABB)} -- we construct these in order to decide fastly
+                    whether to compute the actual intersection of two elements,
+    \item \textbf{Bounding Interval Hierarchy (BIH)} -- we alternatively create BIH above AABB to fastly search 
+                    created bounding boxes for two coinciding with each other and thus obtaining a candidate pair.
 \end{itemize}
 
-Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same lower dimension (1D, 2D), in the space of 3D elements, which we shall call a \emph{bulk}. 
-Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other. Then we can prolongate the intersection by investigating neighbouring elements.
+The intersection tracking itself can be also seen as a \emph{breadth-first search}
+\footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
+algorithm over the BIH, following the component elements.
 
-It can be seen as a \emph{breadth-first search}
-\footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
-algorithm on the graph of component elements.
+% \textbf{breadth first search} algorithm:
+%   \begin{enumerate}
+%     \item\label{en:first} Get next unprocessed component element $k$.
+%     \item Find intersection candidates $\mathcal K$ in bulk mesh (3D elements).
+%     \item \label{en:q2}For $K\in \mathcal K$ compute intersection $(k, K)$.  
+%     \item Push the intersection neigbours into queues: $(k, L) \to Q_b$, $(l, K) \to Q_c$. 
+%     \item While $(l, L) \in Q_b$ check intersection $(l, L)$. Append queues.
+%     \item Pop pair from $Q_c$. (move to the next component element: go to \ref{en:q2}).
+%     \item If $Q_c$ is empty, go to \ref{en:first}.
+%   \end{enumerate}
 
-\textbf{breadth first search} algorithm:
-  \begin{enumerate}
-    \item\label{en:first} Get next unprocessed component element $k$.
-    \item Find intersection candidates $\mathcal K$ in bulk mesh (3D elements).
-    \item \label{en:q2}For $K\in \mathcal K$ compute intersection $(k, K)$.  
-    \item Push the intersection neigbours into queues: $(k, L) \to Q_b$, $(l, K) \to Q_c$. 
-    \item While $(l, L) \in Q_b$ check intersection $(l, L)$. Append queues.
-    \item Pop pair from $Q_c$. (move to the next component element: go to \ref{en:q2}).
-    \item If $Q_c$ is empty, go to \ref{en:first}.
-  \end{enumerate}
+\paragraph{Initialization}
+We start with selecting an arbitrary 1D or 2D element. Then we search the bulk elements, checking for 
+a collision of bounding boxes, to create a candidate pair. Using only AABB, we need to iterate over
+bulk elements in $O(n)$, $n$ being the number of all elements in our case. Using BIH, we can speed 
+up the search to $O(\log n)$ on average. In later case, we are paying the costs in the construction of BIH,
+which is a quicksort like algorithm running at $O(n\log n)$ on average.
+
+Now that we have provided the first candidate pair, we can look at the scheme in \fig{fig:prolongation} and see us moving from the green box in the left upper corner.
+If there exists an intersection, we start a new component and
+we can procced to tracking the intersection. Otherwise, we select another 1D or 2D element and start over.
 

### 2016-09-30 paper_intersections.tex
Finish afront algorithm description.

@@
 Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same lower dimension (1D, 2D), in the space of connected 3D elements, which we shall call a \emph{bulk}. 
+elements of the same lower dimension (1D, or 2D), in the space of connected 3D elements, which we shall call a \emph{bulk}. 
 Obtaining all of component-bulk intersections is done in two phases: firstly, we look for the first two elements intersecting each other (initialization); secondly, we prolong the intersection by investigating neighbouring elements (intersection tracking).
@@
 Now that we have provided the first candidate pair, we can look at the scheme in \fig{fig:prolongation} and see us moving from the green box in the left upper corner.
-If there exists an intersection, we start a new component and
-we can procced to tracking the intersection. Otherwise, we select another 1D or 2D element and start over.
+If an intersection exists, we have just started a new component and we can procced to tracking the intersection.
+Otherwise, we select another 1D or 2D element and start over.
 
@@
 
-The advancing front algorithm works the same way for both 1D and 2D components and is displayed by the scheme in \fig{fig:prolongation}.
-The main idea is to compute intersections for a component element with all
-possible bulk elements, and then move to a~next neighboring component element. For this reason, we define two
-queues of candidate pairs: a~\emph{bulk queue} and a~\emph{component queue} (yellow boxes in \fig{fig:prolongation}). We shall now describe the algorithm in detail.
+Let us now discuss the advancing front algorithm displayed by the scheme in \fig{fig:prolongation}.
+The main idea is to compute intersections for a component element with all possible bulk elements, and then move to a~next neighboring component element.
+For this reason, we define two
+queues of candidate pairs: a~\emph{bulk queue} and a~\emph{component queue} (yellow boxes).
 
@@
 When both queues are empty, all intersections of a component have been found and we start over by looking for the first intersection of another component.
+
+\notePE{We can discuss further the covering/closing of the elements and component numbering which is not tested
+thoroughly at the moment.
+We can show in a figure the case in 'prolong\_meshes\_13d/prolongation\_13d\_04.msh', where actually 4 components are found (therefore bulk is defined as connected 3D elements).}
 

### 2016-09-30 paper_intersections.tex
First iteration of benchmarks.

@@
 %\newfloat{algorithm}{t}{lop}
+\usepackage{array}
 
@@
 % just for our notes
-\usepackage[usenames,dvipsnames]{color}   %colors
+\usepackage[usenames,dvipsnames]{xcolor}   %colors
 
@@
     \item \textbf{Bounding Interval Hierarchy (BIH)} -- we alternatively create BIH above AABB to fastly search 
-                    created bounding boxes for two coinciding with each other and thus obtaining a candidate pair.
+                    created bounding boxes for two colliding with each other and thus obtaining a candidate pair.
 \end{itemize}
@@
 \section{Benchmarks}
+In this section we present numerical results on several benchmark problems. At first we shall compare 
+the effectivity of our fundamental algorithms for intersections with other approaches.
+
+Next we shall compare our algorithms with different initialization phase (candidate pairs search),
+and using the advancing front method or not. We shall show the results both on a mesh of a real locality
+and an artificial mesh.
+
+\subsection{Fundamental Intersection Algorithms}
+The first benchmark focuses on the fundamental 1D-3D and 2D-3D intersections. We randomly generated
+100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
+In some of the empty cases, the bounding boxes did not collide, so the actual intersection algorithms were skipped.
+A single element pair was computed 100 times to obtain reasonable computational time.
+
+\vspace{2ex}
+\begin{minipage}{\textwidth}
+    \centering
+    \hspace{-30pt}
+  \begin{minipage}[b]{0.44\textwidth}
+    \centering
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}[b]{l|l}
+            algorithm, 2D-3D& FLOPs\\
+                      & estimate\\
+            \hline\\
+            parametric plane & 585\\
+            normal plane (reuse) & 765\\
+            Moller and Trumbore & 783\\
+            Pl\"ucker (reuse) & 306
+    \end{tabular}
+    \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
+                      Only 2D-3D case considered.
+    \label{tab:fundamental_flops}
+    \notePE{comment on different strategies}}
+  \end{minipage}
+  \hfil
+  \begin{minipage}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}
+
+    \captionof{figure}{Effectivity of our algorithms using \plucker coordinates in comparison to \notePE{***}.
+                         One can see 1D-3D case on the left, 2D-3D on the right.}
+    \label{fig:fundamental_speed}
+    \end{minipage}
+\end{minipage}
+\vspace{2ex}
+
+We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
+using \plucker coordinates, red values \notePE{***}.
+The gained speed up factor is approximately 5 in 1D-3D case and 2 in 1D-3D.
+Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.
+
+\subsection{General algorithms}
+
+\begin{center}
+    \renewcommand{\arraystretch}{1.5}
+    \begin{tabular}{>{\centering\arraybackslash}p{20ex}
+                    >{\centering\arraybackslash}p{20ex}
+                    >{\centering\arraybackslash}p{20ex}}
+        \colorbox{NavyBlue}{\textcolor{white}{BIHsearch}} & \colorbox{orange}{BBsearch} & \colorbox{Goldenrod}{BIHonly} \\ \hline
+        BIH(AABB) & AABB & BIH(AABB) \\
+        AFront & AFront & ---
+    \end{tabular}
+\end{center}
+
+\begin{figure}[!htb]
+    \subfloat[interior fractures]{
+        \includegraphics[width=0.49\textwidth]{\figpath bedrichov_fract.pdf}
+        \label{fig:bedrichov_cut}
+    }
+    \hspace{3pt}
+    \subfloat[extending fractures]{
+        \includegraphics[width=0.49\textwidth]{\figpath bedrichov_fract_extend.pdf}
+        \label{fig:bedrichov_extend}
+    }
+    \caption{A mesh of the real locality of Bed{\v r}ichov in the Jizera mountains.
+             We see fractures inside the bulk mesh in the left figure,
+             fractures are extending the bulk mesh.}
+    \label{fig:bedrichov_meshes}
+\end{figure}
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=0.8\textwidth]{\figpath intersections_bedrichov_both_speed.pdf}
+    \caption{Comparison of the algorithms on meshes of Bed{\v r}ichov locality -- interior fractures on the left,
+             extending fractures on the right.}
+    \label{fig:bedrichov_speed}
+\end{figure}
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=0.43\textwidth]{\figpath test1_cube0.pdf}
+    \caption{Artificial mesh -- a cube with two perpendicular planes placed on the diagonals of the cube.}
+    \label{fig:cube_mesh}
+\end{figure}
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
+    \caption{}
+    \label{fig:cube_speed}
+\end{figure}
 

### 2016-09-30 paper_intersections.tex
finished introduction

--- 2016-09-30 paper_intersections.tex
@@
 %\title{Algorithm for Intersections of Nonmatching Grids of Different Dimensions}
-\title{Fast Algorithms for Intersection of Nonmatching Grids Using \plucker coordinates.}
+\title{Fast Algorithms for Intersection of Non-matching Grids Using \plucker coordinates.}
 
@@
 \notePE{How did you decided for 'non-matching' term? Instead of e.g. incompatible or non-conforming?}
+\noteJB{Non-matching grid seems to be the most common.}
 
@@
 The Mortar method \cite{belgacem_mortar_1999} allows domain decomposition, independent meshing of domains, and supports sliding boundaries.
-However our primal motivation is usage of XFEM methods and non-matching meshes of mixed dimension in groundwater models.
+However our primal motivation is usage of XFEM methods \cite{fries_extended/generalized_2010} and non-matching meshes of mixed dimension in groundwater models.
 
@@
 (or incompatible) mesh of mixed dimensions and then apply XFEM to represent jumps of the solution on the fractures or singularities 
-around the wells. The prerequisity for such approach is a fast and robust algorithm for calculating intersections of individual meshes.
+around the wells. The prerequisite for such approach is a fast and robust algorithm for calculating intersections of individual meshes.
 
@@
 The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
-and to compute that intersection.
+and to compute that intersection. The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. 
+Second, compute the intersection for particular pair.
 
-The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. Second, compute the intersection for particular pair.
-In order to get candidate pairs efficiently, the existing algorithms use either various space trees \cite{massing_efficient_2013} or front tracing
-\cite{gander_algorithm_2013} or both \cite{elsheikh_reliable_2012} as in our approach. To compute the actual intersections, we 
-use the \plucker coordinates for the line-triangle intersections and a modification of the  Platis and Theoharis algorithm \cite{platis_fast_2003}
-for the line-tetrahedron intersections. These are used as the building blocks for the triangle-triangle and the triangle-tetrahedron cases.
+According to our knowledge there are lot of works using non-matching grids yet only few of them discuss algorithms how to compute their intersections. 
+Gander and Japhet \cite{gander_algorithm_2013} present the PANG algorithm for 2d-2d and 3d-3d intersections that can be used e.g. for mesh overlapping methods.
+They use the advancing front technique to get candidate pairs in linear time. The algorithm is part of the DUNE library \cite{bastian_towards_2005}.
+Massing, Larson, and Logg \cite{massing_efficient_2013} present an algorithm for 2d-3d intersections as part of their implementation of the Nitche method 
+which is part of the Doplhin project \cite{Dolphin}. They use axes aligned bounding boxes of elements (AABB) and bounding interval hierarchy (BIH) 
+to get intersection candidate pairs of elements, the GTS library \cite{gtslib} is used for 2d-3d intersections. 
+Finally, there is the work of Elsheikh and Elsheikh \cite{elsheikh_reliable_2012} presenting an algorithm for 2d-2d mesh union operation which includes 
+calculation and imprinting of the intersection curves. They exploit binary space partitioning for search of initial intersection and 
+the advancing front method for intersection curve tracking.
 
-\noteJB{Better overview of works, seems that most of works deals with simple intersections, can not find any example of 2d-3d.}
-
-\notePE{Unify the term 'front tracing' 'front tracking' 'advancing front'.}
-Our contribution is twofold:  First, we use the front tracking algorithm both to minimize set of intersection candidates as well 
-to reuse part of calculations made on neighbouring intersections. Second, we present family of efficient algorithms based on \plucker coordinates 
-for computing 1d-2d, 1d-3d, 2d-2d, and 2d-3d intersections of simplicies. The paper is organized as follows \dots
+In this paper we present a new approach to calculation intersections of simplicial elements of different dimensions based on the \plucker coordinates
+further developing the algorithm of Platis and Theoharis \cite{platis_fast_2003} for ray-tetrahedron intersections. Element intersections based on 
+\plucker coordinates are combined with the advancing front method which allows us to reuse \plucker coordinates and their products between neigbouring
+elements and reduce the number of arithmetic operations. The paper is organized as follows. In Section \ref{sec:element intersecitons} the algorithms for
+1d-2d, 1d-3d and 2d-3d intersections of simplices are described. In Section \ref{sec:front advancing} we discuss our implementation of the advancing front 
+technique and usage of AABB and BIH for its initialization. Finally, in Section \ref{sec:benchmarks}, we provide benchmarks and comparison of individual algorithms.
 
 \section{Element Intersections}
-\label{sec:elements_intersections}
+\label{sec:element intersecitons}
 In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
-In particular we are interested in the intersections of 1D-2D, 1D-3D, 2D-2D, 2D-3D pairs of elements. The fundamental idea is to compute intersection of 1D-2D simplices using the 
+In particular we are interested in the intersections of 1D-2D, 1D-3D, 2D-2D, 2D-3D pairs of elements. 
+The fundamental idea is to compute intersection of 1D-2D simplices using the 
 \plucker coordinates and reduce all other cases to this one.
@@
 and degenerate cases higher dimensional cases.
+
+\subsection{Intersection Triangle-Tetrahedron (2D-2D)}
+\noteJB{Just note that this algorithm can also be implemented using 1d-2d, but quite complex to not yet fully tested}
 
@@
 \subsection{Tracking boundary of the intersection polygon}
-
+\label{sec:front advancing}
 \notePE{It seems to me, that we can really describe the prolongation in general, for 1D and 2D, 
@@
 
-\section{Advancing Front Method}
-
-add references...
-% BIH:
-% http://ainc.de/Research/BIH.pdf
-% http://diglib.eg.org/handle/10.2312/EGWR.EGSR06.139-149
+\section{Front tracking algorithm}
+Prerequisites:
+  \begin{itemize}
+   \item need information about element connectivity (mesh preprocessing)
+%   \item mark and check already inspected pairs. Marking elements + hashing.
+   \item find the starting intersection -- AABB (Axes Aligned Bounding Boxes) 
+   \item possibly create Bounding Interval Hierarchy (BIH)
+%   \item Pass already known information with pairs.
+%   \item Deal with degenerated cases.
+  \end{itemize}
 
 Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same lower dimension (1D, 2D), in the space of connected 3D elements, which we shall call a \emph{bulk}. 
-Obtaining all of component-bulk intersections is done in two phases: firstly, we look for the first two elements intersecting each other (initialization); secondly, we prolong the intersection by investigating neighbouring elements (intersection tracking).
+elements of the same lower dimension (1D, 2D), in the space of 3D elements, which we shall call a \emph{bulk}. 
+Obtaining all of the 1D-3D and 2D-3D intersections is based on finding the first two elements intersecting each other. Then we can prolongate the intersection by investigating neighbouring elements.
 
-To construct the Advancing front algorithm, we shall need:
-\begin{itemize}
-    \item \textbf{element connectivity} -- we assume this data is available from mesh preprocessing,
-    \item \textbf{Axes Aligned Bounding Boxes (AABB)} -- we construct these in order to decide fastly
-                    whether to compute the actual intersection of two elements,
-    \item \textbf{Bounding Interval Hierarchy (BIH)} -- we alternatively create BIH above AABB to fastly search 
-                    created bounding boxes for two coinciding with each other and thus obtaining a candidate pair.
-\end{itemize}
+It can be seen as a \emph{breadth-first search}
+\footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
+algorithm on the graph of component elements.
 
-The intersection tracking itself can be also seen as a \emph{breadth-first search}
-\footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
-algorithm over the BIH, following the component elements.
-
-% \textbf{breadth first search} algorithm:
-%   \begin{enumerate}
-%     \item\label{en:first} Get next unprocessed component element $k$.
-%     \item Find intersection candidates $\mathcal K$ in bulk mesh (3D elements).
-%     \item \label{en:q2}For $K\in \mathcal K$ compute intersection $(k, K)$.  
-%     \item Push the intersection neigbours into queues: $(k, L) \to Q_b$, $(l, K) \to Q_c$. 
-%     \item While $(l, L) \in Q_b$ check intersection $(l, L)$. Append queues.
-%     \item Pop pair from $Q_c$. (move to the next component element: go to \ref{en:q2}).
-%     \item If $Q_c$ is empty, go to \ref{en:first}.
-%   \end{enumerate}
-
-\paragraph{Initialization}
-We start with selecting an arbitrary 1D or 2D element. Then we search the bulk elements, checking for 
-a collision of bounding boxes, to create a candidate pair. Using only AABB, we need to iterate over
-bulk elements in $O(n)$, $n$ being the number of all elements in our case. Using BIH, we can speed 
-up the search to $O(\log n)$ on average. In later case, we are paying the costs in the construction of BIH,
-which is a quicksort like algorithm running at $O(n\log n)$ on average.
-
-Now that we have provided the first candidate pair, we can look at the scheme in \fig{fig:prolongation} and see us moving from the green box in the left upper corner.
-If there exists an intersection, we start a new component and
-we can procced to tracking the intersection. Otherwise, we select another 1D or 2D element and start over.
+\textbf{breadth first search} algorithm:
+  \begin{enumerate}
+    \item\label{en:first} Get next unprocessed component element $k$.
+    \item Find intersection candidates $\mathcal K$ in bulk mesh (3D elements).
+    \item \label{en:q2}For $K\in \mathcal K$ compute intersection $(k, K)$.  
+    \item Push the intersection neigbours into queues: $(k, L) \to Q_b$, $(l, K) \to Q_c$. 
+    \item While $(l, L) \in Q_b$ check intersection $(l, L)$. Append queues.
+    \item Pop pair from $Q_c$. (move to the next component element: go to \ref{en:q2}).
+    \item If $Q_c$ is empty, go to \ref{en:first}.
+  \end{enumerate}
 
@@
     \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip.pdf}
-  \caption{Advancing front algorithm for 1D-2D and 2D-3D intersections.}
+  \caption{Prolongation algorithm for 1D-2D and 2D-3D intersections. }
   \label{fig:prolongation}
@@
 
-The advancing front algorithm works the same way for both 1D and 2D components and is displayed by the scheme in \fig{fig:prolongation}.
-The main idea is to compute intersections for a component element with all
+The advancing front algorithm works the same way for both 1D and 2D components and is displayed in \fig{fig:prolongation}. The main idea is to compute intersections for a component element with all 
 possible bulk elements, and then move to a~next neighboring component element. For this reason, we define two
@@
 Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
-Therefore, we iterate over the intersection points and further exploit the topological information.
-There are 3 possible cases (applies both for 1D-3D and 2D-3D), how the intersection might be prolonged:
+Therefore, we iterate over the intersection points and further exploit their topological information.
+There are 3 possible cases (applies both for 1D-3D and 2D-3D):
 \begin{itemize}
@@
             or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
-            push the new candidate pairs [current component element -- bulk neighbor] into the bulk queue and [component neighbor -- bulk neighbor] into the component queue.
+            push the following new candidate pairs into the bulk queue: [current component element -- bulk neighbor], [component neighbor -- bulk neighbor].
     \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
@@
 \section{Benchmarks}
+\label{sec:benchmarks}
 
 \section{Conclusions}
+\label{sec:conclusins}
+
 TODO:
@@
 - optimisation of element intersection - skip unnecessary calculations
-\section{Acknowledgement}
-The paper was supported in part by the Project OP
-VaVpI Centre for Nanomaterials, Advanced Technologies  and Innovations
-CZ.1.05/2.1.00/01.0005.
+%\section{Acknowledgement}
+%The paper was supported in part by the Project OP
+%VaVpI Centre for Nanomaterials, Advanced Technologies  and Innovations
+%CZ.1.05/2.1.00/01.0005.
 

### 2016-09-30 paper_intersections.tex

--- 2016-09-30 paper_intersections.tex
@@
 The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
-and to compute that intersection.
-
-The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. Second, compute the intersection for particular pair.
-In order to get candidate pairs efficiently, the existing algorithms use either various space trees \cite{massing_efficient_2013} or front tracing
-\cite{gander_algorithm_2013} or both \cite{elsheikh_reliable_2012} as in our approach. To compute the actual intersections, we 
-use the \plucker coordinates for the line-triangle intersections and a modification of the  Platis and Theoharis algorithm \cite{platis_fast_2003}
-for the line-tetrahedron intersections. These are used as the building blocks for the triangle-triangle and the triangle-tetrahedron cases.
-
-\noteJB{Better overview of works, seems that most of works deals with simple intersections, can not find any example of 2d-3d.}
-
-\notePE{Unify the term 'front tracing' 'front tracking' 'advancing front'.}
-Our contribution is twofold:  First, we use the front tracking algorithm both to minimize set of intersection candidates as well 
-to reuse part of calculations made on neighbouring intersections. Second, we present family of efficient algorithms based on \plucker coordinates 
-for computing 1d-2d, 1d-3d, 2d-2d, and 2d-3d intersections of simplicies. The paper is organized as follows \dots
+and to compute that intersection. The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. 
+Second, compute the intersection for particular pair.
+
+According to our knowledge there are lot of works using non-matching grids yet only few of them discuss algorithms how to compute their intersections. 
+Gander and Japhet \cite{gander_algorithm_2013} present the PANG algorithm for 2d-2d and 3d-3d intersections that can be used e.g. for mesh overlapping methods.
+They use the advancing front technique to get candidate pairs in linear time. The algorithm is part of the DUNE library \cite{bastian_towards_2005}.
+Massing, Larson, and Logg \cite{massing_efficient_2013} present an algorithm for 2d-3d intersections as part of their implementation of the Nitche method 
+which is part of the Doplhin project \cite{Dolphin}. They use axes aligned bounding boxes of elements (AABB) and bounding interval hierarchy (BIH) 
+to get intersection candidate pairs of elements, the GTS library \cite{gtslib} is used for 2d-3d intersections. 
+Finally, there is the work of Elsheikh and Elsheikh \cite{elsheikh_reliable_2012} presenting an algorithm for 2d-2d mesh union operation which includes 
+calculation and imprinting of the intersection curves. They exploit binary space partitioning for search of initial intersection and 
+the advancing front method for intersection curve tracking.
+
+In this paper we present a new approach to calculation intersections of simplicial elements of different dimensions based on the \plucker coordinates
+further developing the algorithm of Platis and Theoharis \cite{platis_fast_2003} for ray-tetrahedron intersections. Element intersections based on 
+\plucker coordinates are combined with the advancing front method which allows us to reuse \plucker coordinates and their products between neigbouring
+elements and reduce the number of arithmetic operations. The paper is organized as follows. In Section \ref{sec:element intersecitons} the algorithms for
+1d-2d, 1d-3d and 2d-3d intersections of simplices are described. In Section \ref{sec:front advancing} we discuss our implementation of the advancing front 
+technique and usage of AABB and BIH for its initialization. Finally, in Section \ref{sec:benchmarks}, we provide benchmarks and comparison of individual algorithms.
 
 \section{Element Intersections}
-\label{sec:elements_intersections}
+\label{sec:element intersecitons}
 In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
-In particular we are interested in the intersections of 1D-2D, 1D-3D, 2D-2D, 2D-3D pairs of elements. The fundamental idea is to compute intersection of 1D-2D simplices using the 
+In particular we are interested in the intersections of 1D-2D, 1D-3D, 2D-2D, 2D-3D pairs of elements. 
+The fundamental idea is to compute intersection of 1D-2D simplices using the 
 \plucker coordinates and reduce all other cases to this one.
@@
 
+\subsection{Intersection Triangle-Tetrahedron (2D-2D)}
+\noteJB{Just note that this algorithm can also be implemented using 1d-2d, but quite complex to not yet fully tested}
+
 \subsection{Intersection Line-Teraherdon (1D-3D)}
@@
 \section{Benchmarks}
+\label{sec:benchmarks}
 In this section we present numerical results on several benchmark problems. At first we shall compare 
@@
 \section{Conclusions}
+\label{sec:conclusins}
+
 TODO:

### 2016-09-30 paper_intersections.tex
WIP on benchmarks.

--- 2016-09-30 paper_intersections.tex
@@
 using \plucker coordinates, red values \notePE{***}.
-The gained speed up factor is approximately 5 in 1D-3D case and 2 in 1D-3D.
+The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D.
 Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.
@@
 \subsection{General algorithms}
-
-\begin{center}
-    \renewcommand{\arraystretch}{1.5}
+So far, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
+intersection and advancing front method (shortly AFront) to prolong the intersection.
+From now on, we shall refer to an algorithm made of these components \emph{BIHsearch}.
+In this section, we shall compare two additional algorithms \emph{BBsearch} and \emph{BIHonly} to see the effects of BIH and AFront (see Table \ref{tab:search_algorithms}).
+\emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows the AFront.
+The version
+\emph{BIHonly} computes AABB together with BIH, but does not use AFront.
+
+\begin{table}[!htb]
+    \centering
+    \renewcommand{\arraystretch}{1.2}
     \begin{tabular}{>{\centering\arraybackslash}p{20ex}
@@
                     >{\centering\arraybackslash}p{20ex}}
-        \colorbox{NavyBlue}{\textcolor{white}{BIHsearch}} & \colorbox{orange}{BBsearch} & \colorbox{Goldenrod}{BIHonly} \\ \hline
+        \colorbox{NavyBlue}{\textcolor{white}{BIHsearch\vphantom{By}}} & \colorbox{orange}{BBsearch\vphantom{By}} & \colorbox{Goldenrod}{BIHonly\vphantom{By}} \\ \hline
         BIH(AABB) & AABB & BIH(AABB) \\
@@
     \end{tabular}
-\end{center}
+    \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.}
+    \label{tab:search_algorithms}
+\end{table}
+
+Let us now start with the problem on an artificial mesh.
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=0.43\textwidth]{\figpath test1_cube0.pdf}
+    \caption{Artificial mesh -- a cube with two perpendicular planes placed on the diagonals of the cube.
+             The planes are also nonmatching, therefore can be seen as two independent components.}
+    \label{fig:cube_mesh}
+\end{figure}
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
+    \caption{asdf}
+    \label{fig:cube_speed}
+\end{figure}
+
+Next, we study the performance of the intersection algorithms on a mesh of a real problem, see \fig{fig:bedrichov_meshes}. The mesh represents a mountain ridge in the Jizera mountains which 
+includes a system of geological fractures (\fig{fig:bedrichov_cut}). We also used this model to create
+a less real mesh, in which the fractures extend through the bulk surface (\fig{fig:bedrichov_extend}). 
+However, this situation might rather occur in another application than porous media problem.
 
@@
     \label{fig:bedrichov_speed}
-\end{figure}
-
-\begin{figure}[!htb]
-    \centering
-    \includegraphics[width=0.43\textwidth]{\figpath test1_cube0.pdf}
-    \caption{Artificial mesh -- a cube with two perpendicular planes placed on the diagonals of the cube.}
-    \label{fig:cube_mesh}
-\end{figure}
-
-\begin{figure}[!htb]
-    \centering
-    \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
-    \caption{}
-    \label{fig:cube_speed}
 \end{figure}

### 2016-09-30 paper_intersections.tex
Add figure. 23 intersections in progres

--- 2016-09-30 paper_intersections.tex
@@
 In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
-In particular we are interested in the intersections of 1D-2D, 1D-3D, 2D-2D, 2D-3D pairs of elements. 
-The fundamental idea is to compute intersection of 1D-2D simplices using the 
+In particular we address intersection algorithms for 1D-2D, 1D-3D, 2D-3D pairs of elements. We have implemented the case 2D-2D as well however the treatment 
+of the special cases is quite technical and not fully completed yet. The fundamental idea is to compute intersection of 1D-2D simplices using the 
 \plucker coordinates and reduce all other cases to this one.
@@
 
-\subsection{Intersection Triangle-Tetrahedron (2D-2D)}
-\noteJB{Just note that this algorithm can also be implemented using 1d-2d, but quite complex to not yet fully tested}
+%\subsection{Intersection Triangle-Tetrahedron (2D-2D)}
+%\noteJB{Just note that this algorithm can also be implemented using 1d-2d, but quite complex to not yet fully tested}
 
@@
 \subsection{Intersection Triangle-Tetrahedron (2D-3D)}
-The intersection of a triangle $S_2$ and a tetrahedron $S_3$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
+The intersection of a triangle $S_2$ and a tetrahedron $S_3$ is an $n$-side intersection polygon (IP), $n\le 7$. The sides of the polygon
 lie either on sides of $S_2$ or on faces of $S_3$. Thus each vertex (IC) of the polygon
 can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_2$.
-So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
+To get all ICs, we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
 to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
-Computation of the intersection polygon consists of two parts: calculation of side-tetrahedron ICs (Algorithm \ref{algo:colect_23_ip_triangle})
-provides all ICs on the boundary of $S_2$,
-calculation of edge-triangle ICs (Algorithm \ref{algo:collect_23_ip_edges}).
-\notePE{The following sentence is somehow weird.. I would say that we store ICs $I$; to sort $I$ during the computation, we use the two tables; at the end, $I$ is ordered correctly.}
-Correct order of the ICs, stored in the list $I$, is defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$.
-\notePE{The following sentece is a copy of the second sentence is this subsection.} Every side of the intersection polygon
-lies either on a side of $S_2$, or on a face, or on an edge of $S_3$. Let us denote $M_2$ the set of sides of $S_2$ and $M_3$ the set of volume,
-faces, edges, and vertices of $S_3$. Every side of polygon that lies on $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
-and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$.
+Computation of IP consists of three stages: calculation of side-tetrahedron ICs (Algorithm \ref{algo:colect_23_ip_triangle}), 
+calculation of edge-triangle ICs (Algorithm \ref{algo:collect_23_ip_edges}), oredering of ICs (Algorithm \ref{algo:order_23}).
+The intersection corners appended to the list $I$ as they are computed however their order on the polygon boundary is 
+defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
+and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \noteJB{possible figure}). The vertices of the polygon are numbered in the same 
+way as is the order and orientation of the sides of $S_2$, that is counterclockwise around the interiror with normal pointing to us.
 
@@
   $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
-  \For{side $s$ of $S_2$}{ 
+  \For{side $s$ of $S_2$}{ \nllabel{line:one side loop}
     $L$ = intersection($s, S_3$)\;
@@
     \For{$p$ in $L$}{
-        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
+%        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
         \nllabel{line:m4_object}
         $p$ lies on $x\in M_3$\;
+        \lIf{$p$ lies at vertex $v$ of $S_3$}{$x=v$}
         \uIf{$p$ is first in $L$}{
@@
   }  
-  \If{$I[-1] = I[0]$}{
-    $x = F_p[I[-1]]$\;
-    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
-    $F_g[s_2] = I[0]$\;
-    remove $I[-1]$
-  }
+%  \If{$I[-1] = I[0]$}{
+%    $x = F_p[I[-1]]$\;
+%    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
+%    $F_g[s_2] = I[0]$\;
+%    remove $I[-1]$
+%  }
 \end{algorithm}
 
-Algorithm \ref{algo:colect_23_ip_triangle} passes through every side $s$ of the triangle $S_2$ and computes the line-tetrahedron intersection $L$.
-In the regular case we process each of the two ICs in $L$. The IC $p$ is added to the list $I$ unless the last point is the same. 
-This condition is effective just for the first IC in $L$ and merges ICs at the same vertex of $S_2$. Then we identify an object $x\in M_3$ the point
-$p$ lies on (line \ref{line:m4_object}). \notePE{I am not sure, if the term 'object' is clear..}
-
-\notePE{Why calling it vertex $v$ instead of IC $p$ here? What is $y$?}
-If the vertex $v$ is between sides $s_1$, $s_2$, 
-we effectively set connections $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
-is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_3$. The condition at the end deals with the case
-in which two sides intersect the same object $x\in M_3$.
-
-For the regular intersection $L$, we pass through its ICs, as described above. \notePE{For special cases}, we firstly compute ICs
-on the boundary of $S_2$ using the line-tetrahedron intersection algorithm for every side. We store single point intersections into separate list $J$
-and skip filling the connection tables. This happens when the side touches $S_3$ at its edge or vertex. 
-These ICs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
-this is not the case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$. 
-Therefore we keep a separate list $J$ of ICs to deal with this case.
+Algorithm \ref{algo:colect_23_ip_triangle} computes all ICs on the boundary of $S_2$.  It passes through every side $s$ of the triangle $S_2$ 
+and computes the line-tetrahedron intersection $L$.
+If the side is just touching $S_3$ and we get $L$ with single IC. These ICs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} 
+with better topological information, however this is not the case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$.
+To this end we save the IC into separate list $J$ and skip filling of the connection tables.
+In the regular case, we process each of the two ICs in $L$ (loop on line \ref{line:one side loop}). The IC $p$ is added to the list $I$,
+vertices of $S_2$ added twice are merged at final stage. Then (line \ref{line:m4_object}) we identify the \nface $x\in M_3$ 
+the point $p$ lies on and set the tables $F_g$, $F_p$. For the IC at the vertex of $S_2$ we set $x$ to that vertex regardless of its position on $S_3$.
+The backward temporary link on the line \ref{line:back_link43} is used later in Algorithm \ref{algo:collect_23_ip_edges} to allow proper continuation 
+of the IC if it lies on edge or at vertex of $S_3$. The condition at the same line deals with the case that two sides of $S_3$ intersect 
+the same object $x\in M_3$, in such case the back-link is unnecessary and would overwrite the correct link set by previous IC.
 
@@
   \lFor{edge $e$ of $S_3$}{$L[e]$ = intersection($e, S_2$)}  \nllabel{line:12edges}
-  \For{unmarked edge $e$ of $S_3$}{
+  \For{edge $e$ of $S_3$ with non-empty $L[e]$}{
     $p=L[e]$\;
@@
             \nllabel{line:mark_edges}
-            mark all edges coincident with $p$
     }    
@@
          append $p$ to $I$\;
-         $F_g[f_0]=p$\tcp*{overwrite the backlink}
-         $F_p[p]=f_1$\;         
-    }   
-  }
-
-  \lIf{$\abs{I} < 3$}{ return $J$}
-  \lElse{ return $I$ sorted according to connectivity in $F_g$ and $F_p$}
+         $F_g[f_0]=p,\ F_p[p]=f_1$\tcp*{overwrite the backlink}
+    }   
+  }  
 \end{algorithm}
+
+Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
+First, the intersection $L[e]$ is evaluated for every edge $e$. The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position on vertex or edge of $S_3$ already computed 
+in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping edges with none or degenerate $L[e]$.
+For every IC $p=L[e]$ we first get its (generalized) faces that are before and after the IC on IP. For an IC inside the edge $e$
+the function \emph{edge faces}, returns its adjacent faces $f_0$, $f_1$ (see Fig. \ref{fig:edge_faces}). 
+Their order is given by the sign permuted inner products in 1d-2d intersection. The order of faces match 
+the order of sides of IP if the sign is negative. If the sign is positive the function \emph{edge faces} returns face pair $(f_1, f_0)$.
+\begin{figure}[!htb]
+  \begin{center}        
+    \includegraphics[width=0.3\textwidth]{\figpath edge_faces.pdf}
+  \end{center}
+  \caption{Order of faces adjacent to the oriented edge $e$ pointing up.}
+  \label{fig:edge_faces}
+\end{figure}
+
+The function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
+returns a pair of generalized faces (face or edge) possibly adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$.
+On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection corner they are degenerate and 
+not processed anyway.
 
@@
 \end{algorithm}
-
-Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
-The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position on vertex or edge of $S_3$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
-Every edge $e$ of $S_3$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
-IC on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
-uses the sign of the intersection to return the pair of faces ordered correctly. 
-Similarly the function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
-returns a pair of generalized faces (face or edge) possibly adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$.
-On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection corner they are degenerate and 
-not processed anyway.
 
@@
 \begin{algorithm}
-  \caption{2d-3d intersection, finish sort of points}  
+  \caption{2d-3d intersection, order the points}  
   \label{algo:order_23}
@@
   \KwOut{polygon in $K$ in correct order}
-  $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
-  \lFor{ $f$ is face of $S_3$}{$P[ F[1,f] ] = F[0, f]$}
-  $i=0$\;  
-  \lFor{$n=0$ \To $\abs{I}-1$}{
-    $K[n]=I[i]$
-    $i=P[i]$
-  }    
-  \label{algo:order_23}
+
+  \lIf{$\abs{I} < 3$}{ return $J$}
+  \lElse{ return $I$ sorted according to connectivity in $F_g$ and $F_p$}
 \end{algorithm}
+\noteJB{Write correct algo with deduplication of vertices.}
 

### 2016-09-30 paper_intersections.tex
Fix BIB. Few comments to Benchmarks.

@@
 the effectivity of our fundamental algorithms for intersections with other approaches.
+\noteJB{I prefer to call them element intersection. Fundamental intersection seems to epic.}
+\noteJB{We compare just against NGH which we should briefly describe. Neither of the algorithms is optimized. The new one deals correctly with special cases and provides 
+barycentric coordinates (so more work for less time).}
+\noteJB{Also write little about Flow123d here. The language etc.}
 
@@
     \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
-                      Only 2D-3D case considered.
+                      Only 2D-3D case considered.}
     \label{tab:fundamental_flops}
-    \notePE{comment on different strategies}}
+    \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
   \end{minipage}
@@
 
-    \captionof{figure}{Effectivity of our algorithms using \plucker coordinates in comparison to \notePE{***}.
-                         One can see 1D-3D case on the left, 2D-3D on the right.}
+    \captionof{figure}{Efficiency of \plucker approach compared to the legacy NGH code.}
     \label{fig:fundamental_speed}
@@
 We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
-using \plucker coordinates, red values \notePE{***}.
+using \plucker coordinates, red values \notePE{***}NGH.
 The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D.
@@
     \end{tabular}
-    \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.}
+    \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.
+    \noteJB{Just in the text. Possibly use different name for variants.}}
     \label{tab:search_algorithms}

### 2016-09-30 paper_intersections.tex
Improve benchmarks description.

--- 2016-09-30 paper_intersections.tex
@@
 In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
-In particular we address intersection algorithms for 1D-2D, 1D-3D, 2D-3D pairs of elements. We have implemented the case 2D-2D as well however the treatment 
-of the special cases is quite technical and not fully completed yet. The fundamental idea is to compute intersection of 1D-2D simplices using the 
+In particular we are interested in the intersections of 1D-2D, 1D-3D, 2D-2D, 2D-3D pairs of elements. 
+The fundamental idea is to compute intersection of 1D-2D simplices using the 
 \plucker coordinates and reduce all other cases to this one.
@@
 
-%\subsection{Intersection Triangle-Tetrahedron (2D-2D)}
-%\noteJB{Just note that this algorithm can also be implemented using 1d-2d, but quite complex to not yet fully tested}
+\subsection{Intersection Triangle-Tetrahedron (2D-2D)}
+\noteJB{Just note that this algorithm can also be implemented using 1d-2d, but quite complex to not yet fully tested}
 
@@
 \subsection{Intersection Triangle-Tetrahedron (2D-3D)}
-The intersection of a triangle $S_2$ and a tetrahedron $S_3$ is an $n$-side intersection polygon (IP), $n\le 7$. The sides of the polygon
+The intersection of a triangle $S_2$ and a tetrahedron $S_3$ is an $n$-side polygon, $n\le 7$. The sides of the polygon
 lie either on sides of $S_2$ or on faces of $S_3$. Thus each vertex (IC) of the polygon
 can arise either from side-face intersection, or from edge-triangle intersection, or be a vertex of $S_2$.
-To get all ICs, we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
+So we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
 to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
-Computation of IP consists of three stages: calculation of side-tetrahedron ICs (Algorithm \ref{algo:colect_23_ip_triangle}), 
-calculation of edge-triangle ICs (Algorithm \ref{algo:collect_23_ip_edges}), oredering of ICs (Algorithm \ref{algo:order_23}).
-The intersection corners appended to the list $I$ as they are computed however their order on the polygon boundary is 
-defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
-and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \noteJB{possible figure}). The vertices of the polygon are numbered in the same 
-way as is the order and orientation of the sides of $S_2$, that is counterclockwise around the interiror with normal pointing to us.
+Computation of the intersection polygon consists of two parts: calculation of side-tetrahedron ICs (Algorithm \ref{algo:colect_23_ip_triangle})
+provides all ICs on the boundary of $S_2$,
+calculation of edge-triangle ICs (Algorithm \ref{algo:collect_23_ip_edges}).
+\notePE{The following sentence is somehow weird.. I would say that we store ICs $I$; to sort $I$ during the computation, we use the two tables; at the end, $I$ is ordered correctly.}
+Correct order of the ICs, stored in the list $I$, is defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$.
+\notePE{The following sentece is a copy of the second sentence is this subsection.} Every side of the intersection polygon
+lies either on a side of $S_2$, or on a face, or on an edge of $S_3$. Let us denote $M_2$ the set of sides of $S_2$ and $M_3$ the set of volume,
+faces, edges, and vertices of $S_3$. Every side of polygon that lies on $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
+and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$.
 
@@
   $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
-  \For{side $s$ of $S_2$}{ \nllabel{line:one side loop}
+  \For{side $s$ of $S_2$}{ 
     $L$ = intersection($s, S_3$)\;
@@
     \For{$p$ in $L$}{
-%        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
+        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
         \nllabel{line:m4_object}
         $p$ lies on $x\in M_3$\; 
-        \lIf{$p$ lies at vertex $v$ of $S_3$}{$x=v$}
         \uIf{$p$ is first in $L$}{
@@
   }  
-%  \If{$I[-1] = I[0]$}{
-%    $x = F_p[I[-1]]$\;
-%    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
-%    $F_g[s_2] = I[0]$\;
-%    remove $I[-1]$
-%  }
+  \If{$I[-1] = I[0]$}{
+    $x = F_p[I[-1]]$\;
+    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
+    $F_g[s_2] = I[0]$\;
+    remove $I[-1]$
+  }
 \end{algorithm}
 
-Algorithm \ref{algo:colect_23_ip_triangle} computes all ICs on the boundary of $S_2$.  It passes through every side $s$ of the triangle $S_2$ 
-and computes the line-tetrahedron intersection $L$.
-If the side is just touching $S_3$ and we get $L$ with single IC. These ICs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} 
-with better topological information, however this is not the case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$.
-To this end we save the IC into separate list $J$ and skip filling of the connection tables.
-In the regular case, we process each of the two ICs in $L$ (loop on line \ref{line:one side loop}). The IC $p$ is added to the list $I$,
-vertices of $S_2$ added twice are merged at final stage. Then (line \ref{line:m4_object}) we identify the \nface $x\in M_3$ 
-the point $p$ lies on and set the tables $F_g$, $F_p$. For the IC at the vertex of $S_2$ we set $x$ to that vertex regardless of its position on $S_3$.
-The backward temporary link on the line \ref{line:back_link43} is used later in Algorithm \ref{algo:collect_23_ip_edges} to allow proper continuation 
-of the IC if it lies on edge or at vertex of $S_3$. The condition at the same line deals with the case that two sides of $S_3$ intersect 
-the same object $x\in M_3$, in such case the back-link is unnecessary and would overwrite the correct link set by previous IC.
+Algorithm \ref{algo:colect_23_ip_triangle} passes through every side $s$ of the triangle $S_2$ and computes the line-tetrahedron intersection $L$.
+In the regular case we process each of the two ICs in $L$. The IC $p$ is added to the list $I$ unless the last point is the same. 
+This condition is effective just for the first IC in $L$ and merges ICs at the same vertex of $S_2$. Then we identify an object $x\in M_3$ the point
+$p$ lies on (line \ref{line:m4_object}). \notePE{I am not sure, if the term 'object' is clear..}
+
+\notePE{Why calling it vertex $v$ instead of IC $p$ here? What is $y$?}
+If the vertex $v$ is between sides $s_1$, $s_2$, 
+we effectively set connections $F_g[s_1] = v$, $F_g[y]=v$, $F_p[v] = s_2$. The backward temporary link on the line \ref{line:back_link43} 
+is used in Algorithm \ref{algo:collect_23_ip_edges} to fix $F_p[p]$ for the second $p$ lying on an edge or a vertex of $S_3$. The condition at the end deals with the case
+in which two sides intersect the same object $x\in M_3$.
+
+For the regular intersection $L$, we pass through its ICs, as described above. \notePE{For special cases}, we firstly compute ICs
+on the boundary of $S_2$ using the line-tetrahedron intersection algorithm for every side. We store single point intersections into separate list $J$
+and skip filling the connection tables. This happens when the side touches $S_3$ at its edge or vertex. 
+These ICs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} with better topological information, however
+this is not the case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$. 
+Therefore we keep a separate list $J$ of ICs to deal with this case.
 
@@
   \lFor{edge $e$ of $S_3$}{$L[e]$ = intersection($e, S_2$)}  \nllabel{line:12edges}
-  \For{edge $e$ of $S_3$ with non-empty $L[e]$}{
+  \For{unmarked edge $e$ of $S_3$}{
     $p=L[e]$\;
@@
             \nllabel{line:mark_edges}
+            mark all edges coincident with $p$
     }    
@@
          append $p$ to $I$\;
-         $F_g[f_0]=p,\ F_p[p]=f_1$\tcp*{overwrite the backlink}
-    }   
-  }  
+         $F_g[f_0]=p$\tcp*{overwrite the backlink}
+         $F_p[p]=f_1$\;         
+    }   
+  }
+
+  \lIf{$\abs{I} < 3$}{ return $J$}
+  \lElse{ return $I$ sorted according to connectivity in $F_g$ and $F_p$}
 \end{algorithm}
-
-Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
-First, the intersection $L[e]$ is evaluated for every edge $e$. The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position on vertex or edge of $S_3$ already computed 
-in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping edges with none or degenerate $L[e]$.
-For every IC $p=L[e]$ we first get its (generalized) faces that are before and after the IC on IP. For an IC inside the edge $e$
-the function \emph{edge faces}, returns its adjacent faces $f_0$, $f_1$ (see Fig. \ref{fig:edge_faces}). 
-Their order is given by the sign permuted inner products in 1d-2d intersection. The order of faces match 
-the order of sides of IP if the sign is negative. If the sign is positive the function \emph{edge faces} returns face pair $(f_1, f_0)$.
-\begin{figure}[!htb]
-  \begin{center}        
-    \includegraphics[width=0.3\textwidth]{\figpath edge_faces.pdf}
-  \end{center}
-  \caption{Order of faces adjacent to the oriented edge $e$ pointing up.}
-  \label{fig:edge_faces}
-\end{figure}
-
-The function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
-returns a pair of generalized faces (face or edge) possibly adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$.
-On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection corner they are degenerate and 
-not processed anyway.
 
@@
 \end{algorithm}
+
+Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
+The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position on vertex or edge of $S_3$ already computed in Algorithm \ref{algo:colect_23_ip_triangle}. 
+Every edge $e$ of $S_3$ is oriented so that the pair of adjacent faces $f_0$, $f_1$ appears in the same order on the intersection polygon when the 
+IC on $e$ has a negative sign (see Figure \ref{fig:plucker_products}). The function \emph{edge faces}, used on line \ref{line:edge_faces} and later on,
+uses the sign of the intersection to return the pair of faces ordered correctly. 
+Similarly the function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
+returns a pair of generalized faces (face or edge) possibly adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$.
+On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection corner they are degenerate and 
+not processed anyway.
 
@@
 \begin{algorithm}
-  \caption{2d-3d intersection, order the points}  
+  \caption{2d-3d intersection, finish sort of points}  
   \label{algo:order_23}
@@
   \KwOut{polygon in $K$ in correct order}  
-
-  \lIf{$\abs{I} < 3$}{ return $J$}
-  \lElse{ return $I$ sorted according to connectivity in $F_g$ and $F_p$}
+  $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
+  \lFor{ $f$ is face of $S_3$}{$P[ F[1,f] ] = F[0, f]$}
+  $i=0$\;  
+  \lFor{$n=0$ \To $\abs{I}-1$}{
+    $K[n]=I[i]$
+    $i=P[i]$
+  }    
+  \label{algo:order_23}
 \end{algorithm}
-\noteJB{Write correct algo with deduplication of vertices.}
 
@@
 
-We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
+We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
 using \plucker coordinates, red values \notePE{***}.
@@
 intersection and advancing front method (shortly AFront) to prolong the intersection.
-From now on, we shall refer to an algorithm made of these components \emph{BIHsearch}.
+From now on, we shall refer to the algorithm made of these components \emph{BIHsearch}.
 In this section, we shall compare two additional algorithms \emph{BBsearch} and \emph{BIHonly} to see the effects of BIH and AFront (see Table \ref{tab:search_algorithms}).
-\emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows the AFront.
+\emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows AFront.
 The version
@@
 a less real mesh, in which the fractures extend through the bulk surface (\fig{fig:bedrichov_extend}). 
-However, this situation might rather occur in another application than porous media problem.
+However, this situation might rather occur in another application than aporous media problem.
+In total, 28 fractures are in the mesh.
+
+The results for both meshes can be seen in the \fig{fig:bedrichov_speed}, pay attention to the different time
+scales in the graph.
+In the first case, we notice that algorithms using AFront are nearly twice as fast as \emph{BIHonly}.
+The speed up corresponds to the time saved by using AFront instead of searching the whole mesh for candidate pairs.
+Computation of BIH in \emph{BIHsearch} pays off and the algorithm performs better than \emph{BBsearch}.
+
+In the second case, we observe large blow up for \emph{BBsearch}. It is caused by the exterior elements, 
+for which all bulk elements bounding boxes are iterated, so we can be sure there is no intersection.
+This of course is much better performed using BIH.
+
+In contrast to the artificial case on the fractured cube, BIH construction is worth due
+to the presence of more components. Having more fractures inside the bulk would result to even bigger difference.
 

### 2016-09-30 paper_intersections.tex

--- 2016-09-30 paper_intersections.tex
@@
 
-We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
+We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
 using \plucker coordinates, red values \notePE{***}NGH.

### 2016-09-30 paper_intersections.tex
Finished 23d

--- 2016-09-30 paper_intersections.tex
@@
 to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
-Computation of IP consists of three stages: calculation of side-tetrahedron ICs (Algorithm \ref{algo:colect_23_ip_triangle}), 
-calculation of edge-triangle ICs (Algorithm \ref{algo:collect_23_ip_edges}), oredering of ICs (Algorithm \ref{algo:order_23}).
-The intersection corners appended to the list $I$ as they are computed however their order on the polygon boundary is 
+Computation of IP consists of three stages: calculation of side-tetrahedron ICs (Section \ref{sec:sides}), 
+calculation of edge-triangle ICs (Section~\ref{sec:edges}), oredering of ICs (Section~\ref{sec:ordering}).
+The intersection corners are appended to the list $I$ as they are computed however their order on the polygon boundary is 
 defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
-and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \noteJB{possible figure}). The vertices of the polygon are numbered in the same 
-way as is the order and orientation of the sides of $S_2$, that is counterclockwise around the interiror with normal pointing to us.
+and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \noteJB{possible figure}). The vertices of the polygon are oredered in the same 
+way as is the order and orientation of the sides of $S_2$, that is counterclockwise around the interior with normal pointing to us.
+There are special cases when the IP is degenerated to a line or a point. If some IC may possibly be part of the such degenerated IP we put it into the list $J$.
+
+\subsubsection{Intersections on sides of $S_2$}
+\label{sec:sides}
 
 \begin{algorithm}
-  \caption{2d-3d intersection, points on triangle boundary}
+  \caption{2d-3d intersection, ICs on sides of $S_2$}
   \label{algo:colect_23_ip_triangle}
@@
 
+\subsubsection{Intersections on edges of $S_3$}
+\label{sec:edges}
 \begin{algorithm}  
-  \caption{2d-3d intersection, points in triangle interior}
+  \caption{2d-3d intersection, ICs on edges of $S_3$}
   \label{algo:collect_23_ip_edges}
@@
          $q=F_g[x]$\tcp*{$q$ is already computed $p$}
-         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$}
-         \lElse{$F_g[f_0]=q$}
+         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$} \nllabel{line:successor}
+         \lElse{$F_g[f_0]=q$}  \nllabel{line:predecessor}
          $F_g[x]=-1$\tcp*{remove the backlink}
@@
          append $p$ to $I$\; 
-         $F_g[f_0]=p,\ F_p[p]=f_1$\tcp*{overwrite the backlink}
+         $F_g[f_0]=p,\ F_p[p]=f_1$\tcp*{overwrite the backlink} \nllabel{line:insideS2}
     }   
@@
 
-Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
-First, the intersection $L[e]$ is evaluated for every edge $e$. The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position on vertex or edge of $S_3$ already computed 
-in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping edges with none or degenerate $L[e]$.
-For every IC $p=L[e]$ we first get its (generalized) faces that are before and after the IC on IP. For an IC inside the edge $e$
-the function \emph{edge faces}, returns its adjacent faces $f_0$, $f_1$ (see Fig. \ref{fig:edge_faces}). 
-Their order is given by the sign permuted inner products in 1d-2d intersection. The order of faces match 
-the order of sides of IP if the sign is negative. If the sign is positive the function \emph{edge faces} returns face pair $(f_1, f_0)$.
-\begin{figure}[!htb]
+\begin{figure}%[!htb]
   \begin{center}        
@@
 
-The function \emph{vertex faces} (Algorithm \ref{algo:vertex_faces}, described later)
-returns a pair of generalized faces (face or edge) possibly adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$.
-On line \ref{line:mark_edges} we mark all edges coincident with the vertex, since if they have any other intersection corner they are degenerate and 
-not processed anyway.
+Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
+First, the intersection $L[e]$ is evaluated for every edge $e$. The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position on vertex or edge of $S_3$ already computed 
+in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping edges with none or degenerate $L[e]$.
+For every IC $p=L[e]$ we first get its (generalized) faces that would appear before and after the IC on IP assuming that $p$ is inside $S_2$.
+
+For an IC inside the edge $e$
+the function \emph{edge faces}, returns its adjacent faces $f_0$, $f_1$ (see Fig. \ref{fig:edge_faces}). 
+Their order is given by the sign permuted inner products in 1d-2d intersection. The order of faces match 
+the order of sides of IP if the sign is negative. If the sign is positive the function \emph{edge faces} returns face pair $(f_1, f_0)$.
+If the IC is at the vertex $v$ of $S_3$, the function \emph{vertex faces} described later (Algorithm \ref{algo:vertex_faces}) is used.
+It returns a pair of generalized faces (face or edge) adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$. 
+If IC $p$ is inside $S_2$, we add it into $I$ and set the connection tables (line \ref{line:insideS2}). However,
+if $p$ is on boundary of $S_2$ it is already in $I$. Denoting $x$ the \nface of $S_3$ the IC lies on, we use the back-link from $x$ to 
+IC $q\in I$ and if $q$ points back to $x$ we set the new successor $f_1$ to it (line \ref{line:successor}). 
+Otherwise $f_0$ is used as the predecessor of $q$ (line \ref{line:predecessor}).
+
+\subsubsection{Vertex Faces Algorithm}
 
@@
   \uElseIf{ $s$ have 1 degenerate edge $e$}{\nllabel{line:one_degenerated}
-    $f$ is face opposite to $e$
+    $f$ is face opposite to $e$\;
     \uIf{other two edges $e_a$, $e_b$ have different sign}{
         $z=\edgefaces(e_a)$\;
-        replace $g\in z$, $g\ne f$ with $e$
-        \return $z$
+        replace $g\in z$, $g\ne f$ with $e$, \return $z$
     }\lElse{
-        append IC of $v$ to $J$
-        \return anything\;
-    }
-  }
-
+        append IC of $v$ to $J$, \return anything
+    }
+  }  
   \uElseIf{ $s$ have edge $e$ with sign oposite to other two}{ \nllabel{line:different_sign}
@@
   \Else($s$ have all signs same){ \nllabel{line:same_signs}
-    append IC of $v$ to $J$
-    \return anything\;
+    append IC of $v$ to $J$, \return anything\;
   }  
@@
 
-\subsubsection{Vertex Faces Algorithm}
-This function gets an IC $p$ at vertex $v$ of $S_3$ as a parameter. The IC is special vertex case of non-degenerate edge-triangle intersection. 
-The function returns a pair of generalized faces of $S_3$ preceeding and succeeding $p$ on the polygons boundary in the case that $p$ is at interior of $S_2$.
-The basic idea is to use the signs of ICs of the three edges coincident with $v$. 
+This function gets as a parameter IC $p$ at the vertex $v$ of $S_3$ which is a special case of anon-degenerate edge-triangle intersection. 
+We use signs and degenerate indicator of ICs of the three edges coincident with $v$ to return generalized faces of $S_3$ 
+preceding and succeeding $p$ on the polygons boundary assuming $p$ is at interior of $S_2$.
 Possible cases are:
 \begin{itemize}
- \item {\bf All ICs have the same sign.} (line \ref{line:same_signs}) We return any pair of faces.  $S_2$ is touching $S_3$ 
- at the vertex $v$, the polygon degenerates into the single IC $p$, no connection information from table $F$ is necessary.
- \item {\bf Single IC has the opposite sign to the other two.} (line \ref{line:different_sign}) Let $e$ be the edge of the single IC with the different sign. 
- The plane of $S_2$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. The order is detemined by the function \emph{edge faces}.
- \item {\bf Single degenerated IC.} (line \ref{line:one_degenerated}) Let us denote $e$ the edge with degenerated IC and $f$ the face between the other two edges.
- The other two (non-degenerates) edges may have either the opposite sign (the plane is cutting $S_3$) or the same sign (the plane is touching $S_3$ at the edge $e$).
+ \item {\bf Single degenerated IC} (line \ref{line:one_degenerated}){\bf .} Let us denote $e$ the edge with degenerated IC 
+ and $f$ the face between the other two edges.
+ The other two (non-degenerates) edges may have either the opposite sign (the plane is cutting $S_3$) 
+ or the same sign (the plane is touching $S_3$ at the edge $e$).
  In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then the vertex faces function returns $(e, f)$ or $(f, e)$, respectively.
-
- The edge $e$ lies in the the singel edge
- \item {\bf Two degenerated ICs.} (line \ref{line:two_degenerated}) A face of $S_3$ lies in the plane of $S_2$, single edge $e$ have non-degenerate IC.
- We treat the two degenerate edges as special case of faces adjacent to $e$ and return them sorted like the faces given by edge faces of edge $e$.
+ In the second case, we just return anything since there are at most two ICs in IP so the connection tables are not necessary. However, we add 
+ current IC into $J$.
+
+ \item {\bf Two degenerated ICs} (line \ref{line:two_degenerated}){\bf .} A face of $S_3$ lies in the plane of $S_2$. 
+ Let $e$ be the single non-degenerate edge. We treat the two degenerate edges as faces adjacent to $e$ 
+ and return them sorted like the faces given by edge faces of edge $e$.
+
+ \item {\bf Single IC has the opposite sign to the other two} (line \ref{line:different_sign}){\bf .} 
+ Let $e$ be the edge of the single IC with the different sign. 
+ The plane of $S_2$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. 
+ The order is determined by the function \emph{edge faces} called for the edge $e$.
+
+ \item {\bf All ICs have the same sign} (line \ref{line:same_signs}){\bf .} Since $S_2$ is touching $S_3$ 
+ at the vertex $v$, the polygon degenerates into point and thus no connection information is necessary. We add IS to $J$ and return any pair of faces.
 \end{itemize}
@@
 % intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.
-
-Finally in the third part (Algorithm \ref{algo:order_23}), the table $F$ allows us to modify array of successors $P$ and get $I$ in the correct order as the list $K$.
-
-\begin{algorithm}
-  \caption{2d-3d intersection, order the points}  
-  \label{algo:order_23}
-
-  \SetKw{To}{to}
-  \DontPrintSemicolon
-  \KwIn{all points in $I$}
-  \KwOut{polygon in $K$ in correct order}
-
-  \lIf{$\abs{I} < 3$}{ return $J$}
-  \lElse{ return $I$ sorted according to connectivity in $F_g$ and $F_p$}
-\end{algorithm}
-\noteJB{Write correct algo with deduplication of vertices.}
-
- List $in[f]$ contains index of the intersection corner that follows after $f$ on the boundary of traced polygon, 
- similarly $out[f]$ stores index of the intersection corner that preeceeds the face $f$.
-
-Possible cases for processing $L$:
-\begin{enumerate}
- \item Regular case, $L$ consists of two intersections $p$, $q$ sorted by orientation of $s$, laying inside of $s$.
-
- If $p$ is on the edge $e$ of $S_3$ compute sign of intersection($e$, $S_2$), sort the faces $f_0$, $f_1$ coincident with $e$
- and set $in[f_0]$ to index of $p$ in $L$. Similarly if $q$ is on the edge, set $out[f_1]$ to index of $q$ in $L$.
-
- If $p$ is in vertex $v$ of $S_3$, for every face $f$ coincident with $v$ set
- in[$f$] to index of $p$ unless there is some index already set. So, we do not over ride
- entries comming from the edge intersections. Similarly set out[$f$] if $q$ is in vertex of $S_3$.
-
- If $p$ is on face $f_0$ of $S_3$, set $in[f_0]$ to index of $p$. Similarly, if $q$ is on face $f_1$ of $S_3$, set $out[f_1]$ to index of $q$.
- laying on faces $f_p$, $f_q$ of $S_3$.
-
- \item $L$ consists of a single intersection corner $p$ (touching $S_3$)
-
- If $p$ is on edge, compute sign of intersection($e$, $S_2$), sort the faces $f_0$, $f_1$,
- set $in[f_0]$ and $out[f_1]$ to index of $p$.
-
- If $p$
-\end{enumerate}
-
-How tracing works.
-\begin{itemize}
- \item If there are no intersections in vertex of $S_3$. 
-\end{itemize}
-
-intersection polygon
-are found as intersection corners of either triangle side and tetrahedron or tetrahedron edge and triangle.
-Therefore we use both algorithms above for 1D-3D and 1D-2D, respectively. Data are again efficiently passed
-to lower dimensional problems, so
-
-The array of intersection corners is generally not sorted. We use two so called \emph{tracing} algorithms and we
-intend to orient the edges of the polygon in the same direction as the triangle is oriented.
-If one of the intersection corner is pathologic, a general convex hull method is applied using the Monotone 
-chain\footnote{Wikibooks, [online 2016-03-01], 
-      \url{http://en.wikibooks.org/wiki/Algorithm_Implementation/Geometry/Convex_hull/Monotone_chain}} 
-algorithm. The points are sorted using only their barycentric coordinates.
-
-An optimized algorithm has been suggested for non-pathologic cases. At this moment all the collected topology 
-data come into play. The algorithm takes advantage by using only the data already computed and also lowers
-the complexity to $O(N)$, compared with the Monotone chain complexity $O(N\log N)$ 
-($N$ being number of intersection corners).
-
-\subsection{Tracking boundary of the intersection polygon}
-\label{sec:front advancing}
-\notePE{It seems to me, that we can really describe the prolongation in general, for 1D and 2D, 
-refering to them as components. I tried to do so..}
-
-\notePE{We need proper definitions of terms we use: \\
-% \emph{component} is a set of connected elements of the same lower dimension (1D, 2D)\\
-% \emph{bulk} is a set of 3D elements\\
-% or slave, master...
-\emph{candidates pair}  is a pair of a component element and a bulk element, that might intersect
-each other (due to intersection of their bounding boxes or prolongation result)
-\emph{pathologic, special, degenerate case ??}
-}
-
-\notePE{Do you want to use American 'neighbor' or all other English 'neighbour'? (I prefer non-american.. to be unified at the end..)}
+\subsubsection{Ordering of intersections}
+\label{sec:ordering}
+The final stage of the 2d-3d intersection is ordering of ICs. If there are less then 3 ICs in the list $I$ we merge lists $I$ and $J$ remove duplicities
+and get at most 2 distinguish ICs forming a degenerate IP. Otherwise, we start with first IC $p$ in $I$, put it into final list $K$, 
+get its successor \nface $x = F_p(p)$ and its successor IC $q=F_q(x)$. Unless $x$ is vertex of $S_2$, we put $q$ into $K$ and repeat the process until 
+we pass all ICs in $I$.
 

### 2016-09-30 paper_intersections.tex
abstract.

@@
 \begin{abstract}
+We present algorithms for intersections between 1d and 2d unstructured multi component meshes 
+and their intersections a background unstructured 3d mesh. A common algorithm 
+based on the advancing front technique is used for the efficient selection of candidate pairs of 
+simplicial elements. Bounding interval hierarchy (BIH) of axes aligned bounding boxes (AABB) of elements
+is used to initialize the front tracking algorithm. The family of element intersection algorithms
+is build upon a line-triangle intersection algorithm based on the \plucker
+coordinates. These algorithms combined with the advancing front technique can reuse calculations 
+done on the neigbouring elements and reduce the number of arithmetic operations. Barycentric coordinates
+on each of the intersecting elements are provided for every intersection point. Benchmarks 
+of the element intersection algorithms are provided and three variants of the global intersection 
+algorithm are compared on the meshes raising from a hydrogeological application.
 \end{abstract}
@@
 non-matching grid \sep 
-intersections \sep
+mesh intersections \sep
 mixed-dimensional mesh \sep
-\plucker coordinates
+\plucker coordinates \sep 
+advancing front method
 

### 2016-09-30 paper_intersections.tex
Benchmarks - add intro,sw,ngh, minor fixes.

--- 2016-09-30 paper_intersections.tex
@@
 \newcommand{\nfaces}{$n$-faces }
+\newcommand{\ngh}{NGH }
 
@@
 \label{sec:benchmarks}
-In this section we present numerical results on several benchmark problems. At first we shall compare 
-the effectivity of our fundamental algorithms for intersections with other approaches.
-\noteJB{I prefer to call them element intersection. Fundamental intersection seems to epic.}
+
+%done \noteJB{I prefer to call them element intersection. Fundamental intersection seems to epic.}
 \noteJB{We compare just against NGH which we should briefly describe. Neither of the algorithms is optimized. The new one deals correctly with special cases and provides 
@@
 
+In this section, we present numerical results on several benchmark problems. 
+In the beginning, we provide some software development related information.
+Then we compare the performance of our algorithms for element intersections with other approaches.
 Next we shall compare our algorithms with different initialization phase (candidate pairs search),
@@
 
-\subsection{Fundamental Intersection Algorithms}
-The first benchmark focuses on the fundamental 1D-3D and 2D-3D intersections. We randomly generated
+\subsection{Software Flow123d}
+The intersection algorithms are implemented as a part of the software Flow123d~\cite{flow123d}.
+The software is developed with an open source licence at the Technical University in Liberec,
+the implementation is based mostly on C++ language. 
+Flow123d provides models for (un)saturated groundwater flow, transport of solutes possibly
+coupled with first order reactions and heat transfer in fractured porous media. 
+The speciality of the software is that it enables
+computations on complex meshes consisting of simplicial elements of different dimensions. However,
+non-matching meshes are at the moment available only in experimental 1D-2D flow model, using mortar like coupling.
+% This work is the first greater step on the way to dimensional coupling models on non-matching meshes 
+% in Flow123d.
+
+\notePE{check NGH.. how to refer to NGH later?}
+Currently, there is also another implementation of the element intersections in the software (we shall refer to
+it later as \ngh). It uses standard means of analytic geometry for computation of intersections line-line and line-plane.
+This leads to solving a large amount of small linear systems of equations.
+This algorithm also does not provide us barycentric coordinates and topological position of ICs.
+At last, the algorithm cannot handle all of the special cases.
+We must note, that neither the old algorithms nor the new ones are optimised at the moment.
+
+Note, that we use Armadillo~\cite{armadillo_2016}, a C++ linear algebra library, for linear algebra operations.
+Most importantly, all coordinates are represented as Armadillo vectors, so we can use dot and cross product and further vector and matrix operations provided by the library.
+
+\subsection{Element Intersection Algorithms}
+The first benchmark focuses on the 1D-3D and 2D-3D element intersections. We randomly generated
 100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
@@
 
-    \captionof{figure}{Efficiency of \plucker approach compared to the legacy NGH code.}
+    \captionof{figure}{Efficiency of \plucker approach compared to the legacy \ngh code.}
     \label{fig:fundamental_speed}
@@
 We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
-using \plucker coordinates, red values \notePE{***}NGH.
+using \plucker coordinates, red values to \ngh code.
 The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D.
 Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.
+\notePE{Improve and complete...}
 
 \subsection{General algorithms}
-So far, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
+In previous sections, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
 intersection and advancing front method (shortly AFront) to prolong the intersection.
@@
     \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.
-    \noteJB{Just in the text. Possibly use different name for variants.}}
+    \noteJB{Just in the text. Possibly use different name for variants.}
+    \notePE{jsem vzal z posledni prezentace.. prislo mi to prehledny.. vim jak jsem se v diplomce VF hrozne krkolome vracel od grafu k popisu algoritmu..}}
     \label{tab:search_algorithms}
@@
     \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
-    \caption{asdf}
+    \caption{Dependence of the algorithms performance on number of intersection (and mesh refinement). }
     \label{fig:cube_speed}
@@
 In contrast to the artificial case on the fractured cube, BIH construction is worth due
-to the presence of more components. Having more fractures inside the bulk would result to even bigger difference.
+to the presence of more components. Having more fractures inside the bulk would result to more dramatic difference.
 

### 2016-09-30 paper_intersections.tex
Benchmarks - add intro,sw,ngh, minor fixes.

@@
 
-\vspace{2ex}
-\begin{minipage}{\textwidth}
-    \centering
-    \hspace{-30pt}
-  \begin{minipage}[b]{0.44\textwidth}
+% \vspace{2ex}
+% \begin{minipage}{\textwidth}
+%     \centering
+%     \hspace{-30pt}
+%   \begin{minipage}[b]{0.44\textwidth}
+%     \centering
+%     \renewcommand{\arraystretch}{1.2}
+%     \begin{tabular}[b]{l|l}
+%             algorithm, 2D-3D& FLOPs\\
+%                       & estimate\\
+%             \hline\\
+%             parametric plane & 585\\
+%             normal plane (reuse) & 765\\
+%             Moller and Trumbore & 783\\
+%             Pl\"ucker (reuse) & 306
+%     \end{tabular}
+%     \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
+%                       Only 2D-3D case considered.}
+%     \label{tab:fundamental_flops}
+%     \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
+%   \end{minipage}
+%   \hfil
+%   \begin{minipage}[b]{0.5\textwidth}
+%     \centering
+%     \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}
+%     
+%     \captionof{figure}{Efficiency of \plucker approach compared to the legacy \ngh code.}
+%     \label{fig:fundamental_speed}
+%     \end{minipage}
+% \end{minipage}
+% \vspace{2ex}
+
+\begin{table}[!htb]
     \centering
@@
     \end{tabular}
-    \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
+    \caption{Estimation of floating point operations count and comparison of different approaches.
              Only 2D-3D case considered.}
@@
     \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
-  \end{minipage}
-  \hfil
-  \begin{minipage}[b]{0.5\textwidth}
+\end{table}
+
+\begin{figure}[!htb]
     \centering
-    \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}
-
-    \captionof{figure}{Efficiency of \plucker approach compared to the legacy \ngh code.}
+    \includegraphics[width=0.5\textwidth]{\figpath intersections_fundamental_speed.pdf}
+    \caption{Efficiency of \plucker approach compared to the legacy \ngh code.}
     \label{fig:fundamental_speed}
-    \end{minipage}
-\end{minipage}
-\vspace{2ex}
+\end{figure}
 

### 2016-09-30 paper_intersections.tex

--- 2016-09-30 paper_intersections.tex
@@
     \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
-  \end{minipage}
-  \hfil
-  \begin{minipage}[b]{0.5\textwidth}
+\end{table}
+
+\begin{figure}[!htb]
     \centering
-    \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}
-
-    \captionof{figure}{Efficiency of \plucker approach compared to the legacy NGH code.}
+    \includegraphics[width=0.5\textwidth]{\figpath intersections_fundamental_speed.pdf}
+    \caption{Efficiency of \plucker approach compared to the legacy \ngh code.}
     \label{fig:fundamental_speed}
-    \end{minipage}
-\end{minipage}
-\vspace{2ex}
-
-We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
-using \plucker coordinates, red values \notePE{***}NGH.
+\end{figure}
+
+We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
+using \plucker coordinates, red values to \ngh code.
 The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D.
 Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.
+\notePE{Improve and complete...}
 
 \subsection{General algorithms}
-So far, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
+In previous sections, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
 intersection and advancing front method (shortly AFront) to prolong the intersection.
-From now on, we shall refer to an algorithm made of these components \emph{BIHsearch}.
+From now on, we shall refer to the algorithm made of these components \emph{BIHsearch}.
 In this section, we shall compare two additional algorithms \emph{BBsearch} and \emph{BIHonly} to see the effects of BIH and AFront (see Table \ref{tab:search_algorithms}).
-\emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows the AFront.
+\emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows AFront.
 The version
@@
 a less real mesh, in which the fractures extend through the bulk surface (\fig{fig:bedrichov_extend}). 
-However, this situation might rather occur in another application than porous media problem.
+However, this situation might rather occur in another application than aporous media problem.
+In total, 28 fractures are in the mesh.
+
+The results for both meshes can be seen in the \fig{fig:bedrichov_speed}, pay attention to the different time
+scales in the graph.
+In the first case, we notice that algorithms using AFront are nearly twice as fast as \emph{BIHonly}.
+The speed up corresponds to the time saved by using AFront instead of searching the whole mesh for candidate pairs.
+Computation of BIH in \emph{BIHsearch} pays off and the algorithm performs better than \emph{BBsearch}.
+
+In the second case, we observe large blow up for \emph{BBsearch}. It is caused by the exterior elements, 
+for which all bulk elements bounding boxes are iterated, so we can be sure there is no intersection.
+This of course is much better performed using BIH.
+
+In contrast to the artificial case on the fractured cube, BIH construction is worth due
+to the presence of more components. Having more fractures inside the bulk would result to more dramatic difference.
 

### 2016-09-30 paper_intersections.tex
abstract 1

@@
 \newcommand{\nfaces}{$n$-faces }
-\newcommand{\ngh}{NGH }
 
@@
 \begin{abstract}
+The XFEM and Mortar methods can be used in combination with non-matching or non-conforming grids 
+to deal with problems on complex geometries. However the information about the mesh intersection must be provided.
 We present algorithms for intersections between 1d and 2d unstructured multi component meshes 
@@
 \label{sec:benchmarks}
-
-%done \noteJB{I prefer to call them element intersection. Fundamental intersection seems to epic.}
+In this section we present numerical results on several benchmark problems. At first we shall compare 
+the effectivity of our fundamental algorithms for intersections with other approaches.
+\noteJB{I prefer to call them element intersection. Fundamental intersection seems to epic.}
 \noteJB{We compare just against NGH which we should briefly describe. Neither of the algorithms is optimized. The new one deals correctly with special cases and provides 
@@
 
-In this section, we present numerical results on several benchmark problems. 
-In the beginning, we provide some software development related information.
-Then we compare the performance of our algorithms for element intersections with other approaches.
 Next we shall compare our algorithms with different initialization phase (candidate pairs search),
@@
 
-\subsection{Software Flow123d}
-The intersection algorithms are implemented as a part of the software Flow123d~\cite{flow123d}.
-The software is developed with an open source licence at the Technical University in Liberec,
-the implementation is based mostly on C++ language. 
-Flow123d provides models for (un)saturated groundwater flow, transport of solutes possibly
-coupled with first order reactions and heat transfer in fractured porous media. 
-The speciality of the software is that it enables
-computations on complex meshes consisting of simplicial elements of different dimensions. However,
-non-matching meshes are at the moment available only in experimental 1D-2D flow model, using mortar like coupling.
-% This work is the first greater step on the way to dimensional coupling models on non-matching meshes 
-% in Flow123d.
-
-\notePE{check NGH.. how to refer to NGH later?}
-Currently, there is also another implementation of the element intersections in the software (we shall refer to
-it later as \ngh). It uses standard means of analytic geometry for computation of intersections line-line and line-plane.
-This leads to solving a large amount of small linear systems of equations.
-This algorithm also does not provide us barycentric coordinates and topological position of ICs.
-At last, the algorithm cannot handle all of the special cases.
-We must note, that neither the old algorithms nor the new ones are optimised at the moment.
-
-Note, that we use Armadillo~\cite{armadillo_2016}, a C++ linear algebra library, for linear algebra operations.
-Most importantly, all coordinates are represented as Armadillo vectors, so we can use dot and cross product and further vector and matrix operations provided by the library.
-
-\subsection{Element Intersection Algorithms}
-The first benchmark focuses on the 1D-3D and 2D-3D element intersections. We randomly generated
+\subsection{Fundamental Intersection Algorithms}
+The first benchmark focuses on the fundamental 1D-3D and 2D-3D intersections. We randomly generated
 100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
@@
 
-% \vspace{2ex}
-% \begin{minipage}{\textwidth}
-%     \centering
-%     \hspace{-30pt}
-%   \begin{minipage}[b]{0.44\textwidth}
-%     \centering
-%     \renewcommand{\arraystretch}{1.2}
-%     \begin{tabular}[b]{l|l}
-%             algorithm, 2D-3D& FLOPs\\
-%                       & estimate\\
-%             \hline\\
-%             parametric plane & 585\\
-%             normal plane (reuse) & 765\\
-%             Moller and Trumbore & 783\\
-%             Pl\"ucker (reuse) & 306
-%     \end{tabular}
-%     \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
-%                       Only 2D-3D case considered.}
-%     \label{tab:fundamental_flops}
-%     \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
-%   \end{minipage}
-%   \hfil
-%   \begin{minipage}[b]{0.5\textwidth}
-%     \centering
-%     \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}
-%     
-%     \captionof{figure}{Efficiency of \plucker approach compared to the legacy \ngh code.}
-%     \label{fig:fundamental_speed}
-%     \end{minipage}
-% \end{minipage}
-% \vspace{2ex}
-
-\begin{table}[!htb]
+\vspace{2ex}
+\begin{minipage}{\textwidth}
+    \centering
+    \hspace{-30pt}
+  \begin{minipage}[b]{0.44\textwidth}
     \centering
@@
     \end{tabular}
-    \caption{Estimation of floating point operations count and comparison of different approaches.
+    \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
                       Only 2D-3D case considered.}
@@
     \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
-\end{table}
-
-\begin{figure}[!htb]
+  \end{minipage}
+  \hfil
+  \begin{minipage}[b]{0.5\textwidth}
     \centering
-    \includegraphics[width=0.5\textwidth]{\figpath intersections_fundamental_speed.pdf}
-    \caption{Efficiency of \plucker approach compared to the legacy \ngh code.}
+    \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}
+
+    \captionof{figure}{Efficiency of \plucker approach compared to the legacy NGH code.}
     \label{fig:fundamental_speed}
-\end{figure}
-
-We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
-using \plucker coordinates, red values to \ngh code.
+    \end{minipage}
+\end{minipage}
+\vspace{2ex}
+
+We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond the presented algorithms
+using \plucker coordinates, red values \notePE{***}NGH.
 The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D.
 Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.
-\notePE{Improve and complete...}
 
 \subsection{General algorithms}
-In previous sections, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
+So far, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
 intersection and advancing front method (shortly AFront) to prolong the intersection.
-From now on, we shall refer to the algorithm made of these components \emph{BIHsearch}.
+From now on, we shall refer to an algorithm made of these components \emph{BIHsearch}.
 In this section, we shall compare two additional algorithms \emph{BBsearch} and \emph{BIHonly} to see the effects of BIH and AFront (see Table \ref{tab:search_algorithms}).
-\emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows AFront.
+\emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows the AFront.
 The version
@@
     \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.
-    \noteJB{Just in the text. Possibly use different name for variants.}
-    \notePE{jsem vzal z posledni prezentace.. prislo mi to prehledny.. vim jak jsem se v diplomce VF hrozne krkolome vracel od grafu k popisu algoritmu..}}
+    \noteJB{Just in the text. Possibly use different name for variants.}}
     \label{tab:search_algorithms}
@@
     \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
-    \caption{Dependence of the algorithms performance on number of intersection (and mesh refinement). }
+    \caption{asdf}
     \label{fig:cube_speed}
@@
 a less real mesh, in which the fractures extend through the bulk surface (\fig{fig:bedrichov_extend}). 
-However, this situation might rather occur in another application than aporous media problem.
-In total, 28 fractures are in the mesh.
-
-The results for both meshes can be seen in the \fig{fig:bedrichov_speed}, pay attention to the different time
-scales in the graph.
-In the first case, we notice that algorithms using AFront are nearly twice as fast as \emph{BIHonly}.
-The speed up corresponds to the time saved by using AFront instead of searching the whole mesh for candidate pairs.
-Computation of BIH in \emph{BIHsearch} pays off and the algorithm performs better than \emph{BBsearch}.
-
-In the second case, we observe large blow up for \emph{BBsearch}. It is caused by the exterior elements, 
-for which all bulk elements bounding boxes are iterated, so we can be sure there is no intersection.
-This of course is much better performed using BIH.
-
-In contrast to the artificial case on the fractured cube, BIH construction is worth due
-to the presence of more components. Having more fractures inside the bulk would result to more dramatic difference.
+However, this situation might rather occur in another application than porous media problem.
 

### 2016-09-30 paper_intersections.tex
Unify dimension notation d-D.

--- 2016-09-30 paper_intersections.tex
@@
 \label{sec:element intersecitons}
-In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
-In particular we address intersection algorithms for 1D-2D, 1D-3D, 2D-3D pairs of elements. We have implemented the case 2D-2D as well however the treatment 
-of the special cases is quite technical and not fully completed yet. The fundamental idea is to compute intersection of 1D-2D simplices using the 
+In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3d ambient space. 
+In particular we address intersection algorithms for 1d-2d, 1d-3d, 2d-3d pairs of elements. We have implemented the case 2d-2d as well however the treatment 
+of the special cases is quite technical and not fully completed yet. The fundamental idea is to compute intersection of 1d-2d simplices using the 
 \plucker coordinates and reduce all other cases to this one.
@@
 \subsection{\plucker Coordinates}
-\plucker coordinates represent a line in 3D space.
+\plucker coordinates represent a line in 3d space.
 Considering a line $p$, given by a point $\vc A$ and its directional vector $\vc{u}$, 
@@
 
-\subsection{Intersection Line-Triangle (1D-2D)}
+\subsection{Intersection Line-Triangle (1d-2d)}
 Let us consider a line segment $p$ with parametric equation 
@@
 
-%\subsection{Intersection Triangle-Tetrahedron (2D-2D)}
+%\subsection{Intersection Triangle-Tetrahedron (2d-2d)}
 %\noteJB{Just note that this algorithm can also be implemented using 1d-2d, but quite complex to not yet fully tested}
 
-\subsection{Intersection Line-Teraherdon (1D-3D)}
+\subsection{Intersection Line-Teraherdon (1d-3d)}
 In this section we consider intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
@@
 skipping remaining faces once two ICs are found. Tetrahedron has six edges, so 7 \plucker coordinates and 6 inner products are computed at most. Precomputed 
-coordinates and products are passed the 1D-2D algorithm which is performed fro the whole line $p$. After collecting line-tetrahedron ICs,
+coordinates and products are passed the 1d-2d algorithm which is performed fro the whole line $p$. After collecting line-tetrahedron ICs,
 we do the line segment trimming \ref{line:trimming}. If both ICs are out of the line segment $p$ we eliminate both of them. If one of the ICs if out of $p$
@@
 
-\subsection{Intersection Triangle-Tetrahedron (2D-3D)}
+\subsection{Intersection Triangle-Tetrahedron (2d-3d)}
 The intersection of a triangle $S_2$ and a tetrahedron $S_3$ is an $n$-side intersection polygon (IP), $n\le 7$. The sides of the polygon
@@
 Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same lower dimension (1D, or 2D), in the space of connected 3D elements, which we shall call a \emph{bulk}. 
+elements of the same lower dimension (1d, or 2d), in the space of connected 3d elements, which we shall call a \emph{bulk}. 
 Obtaining all of component-bulk intersections is done in two phases: firstly, we look for the first two elements intersecting each other (initialization); secondly, we prolong the intersection by investigating neighbouring elements (intersection tracking).
@@
 %     \item\label{en:first} Get next unprocessed component element $k$.
-%     \item Find intersection candidates $\mathcal K$ in bulk mesh (3D elements).
+%     \item Find intersection candidates $\mathcal K$ in bulk mesh (3d elements).
 %     \item \label{en:q2}For $K\in \mathcal K$ compute intersection $(k, K)$.  
@@
 \paragraph{Initialization}
-We start with selecting an arbitrary 1D or 2D element. Then we search the bulk elements, checking for 
+We start with selecting an arbitrary 1d or 2d element. Then we search the bulk elements, checking for 
 a collision of bounding boxes, to create a candidate pair. Using only AABB, we need to iterate over
@@
 If an intersection exists, we have just started a new component and we can procced to tracking the intersection.
-Otherwise, we select another 1D or 2D element and start over.
+Otherwise, we select another 1d or 2d element and start over.
 
@@
     \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip.pdf}
-  \caption{Advancing front algorithm for 1D-2D and 2D-3D intersections.}
+  \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
   \label{fig:prolongation}
@@
 Therefore, we iterate over the intersection points and further exploit the topological information.
-There are 3 possible cases (applies both for 1D-3D and 2D-3D), how the intersection might be prolonged:
+There are 3 possible cases (applies both for 1d-3d and 2d-3d), how the intersection might be prolonged:
 \begin{itemize}
@@
 % two queues with element pairs as candidates for further intersection. If the intersection edge 
-% (point of line in 1D, edge of polygon in 2D) is inside the tetrahedron, not on its surface, we
+% (point of line in 1d, edge of polygon in 2d) is inside the tetrahedron, not on its surface, we
 % get a neighbouring element of the component and push it back together with the current tetrahedron into 
@@
 % (line or triangle), i.e. is on the surface of tetrahedron, we get a neighbouring element of the tetrahedron
-% and push it back together with the current slave element into \emph{3D prolongation queue}.
+% and push it back together with the current slave element into \emph{3d prolongation queue}.
 
@@
 thoroughly at the moment.
-We can show in a figure the case in 'prolong\_meshes\_13d/prolongation\_13d\_04.msh', where actually 4 components are found (therefore bulk is defined as connected 3D elements).}
-
-% The algorithm is now unified for 1D and 2D in contrast to \cite{fris_dp_2015}, where the component prolongation
+We can show in a figure the case in 'prolong\_meshes\_13d/prolongation\_13d\_04.msh', where actually 4 components are found (therefore bulk is defined as connected 3d elements).}
+
+% The algorithm is now unified for 1d and 2d in contrast to \cite{fris_dp_2015}, where the component prolongation
 % queue is emptied at first.
 
-% \subsubsection{1D-3D prolongation}
+% \subsubsection{1d-3d prolongation}
 % 1d-3d prolongation logic
 % IC is:
-% - 1D element node
+% - 1d element node
 %     - inside tetrahedron
-%         - get the neighboring 1D element
-%         - push to component queue candidate pair [1D neigbor -- tetrahedron]
+%         - get the neighboring 1d element
+%         - push to component queue candidate pair [1d neigbor -- tetrahedron]
 %     - on the surface of tetrahedron
@@
 %         - push to bulk queue new candidates pairs:
-%             - [current 1D element -- tetrahedron neighbor]
-%             - [1D neighbor -- tetragedron neighbor]
+%             - [current 1d element -- tetrahedron neighbor]
+%             - [1d neighbor -- tetragedron neighbor]
 %             - check whether the candidate pair has not been computed yet
@@
 %                the element is not closed then -- not fully covered with tetrahedrons)
-% - inside 1D element
+% - inside 1d element
 %     - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
 %     - get the tetrahedron neighbors on the faces
-%     - push to bulk queue candidate pair [current 1D element -- tetrahedron neighbor]
+%     - push to bulk queue candidate pair [current 1d element -- tetrahedron neighbor]
 %     - check whether the candidate pair has not been computed yet
@@
 % \begin{itemize}
-%     \item \textbf{IC lies at 1D element node and inside 3D element} \\
-%             We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
-%     \item \textbf{IC lies at 1D element node and on the surface of 3D element} \\
-%             We find all the faces of 3D element in which the IC lies (1 face, or 2 faces (IC on an edge), 
-%             or 3 faces (IC at a node)). We find the corresponding neghboring 3D elements over the faces and
-%             push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
+%     \item \textbf{IC lies at 1d element node and inside 3d element} \\
+%             We find the neighboring 1d element over the node and push a new candidate pair [1d neighbor -- current 3d element] into component queue.
+%     \item \textbf{IC lies at 1d element node and on the surface of 3d element} \\
+%             We find all the faces of 3d element in which the IC lies (1 face, or 2 faces (IC on an edge), 
+%             or 3 faces (IC at a node)). We find the corresponding neghboring 3d elements over the faces and
+%             push the following new candidates pairs into the bulk queue: [current 1d element -- 3d neighbor], [1d neighbor -- 3d neighbor].
 %             If the candidates pair has been investigated already, we skip it.
-%     \item \textbf{IC lies inside 1D element (therefore must be on the surface of 3D element)} \\
-%             The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
-%             there is no 1D neighbor.
+%     \item \textbf{IC lies inside 1d element (therefore must be on the surface of 3d element)} \\
+%             The same as before, but we push only [current 1d element -- 3d neighbor] candidates pairs, since
+%             there is no 1d neighbor.
 % \end{itemize}
@@
 % IC is:
-% - inside 2D element side
-%     - inside 3D element
-%         - get the neighboring 2D elements over the side
-%         - push to component queue candidates pair [2D neigbor -- current 3D element]
-% - inside the face of 3D element
-%     - get the neighboring 3D element over the face
-%     - push to bulk queue candidate pair [2D neighbor -- 3D element]
+% - inside 2d element side
+%     - inside 3d element
+%         - get the neighboring 2d elements over the side
+%         - push to component queue candidates pair [2d neigbor -- current 3d element]
+% - inside the face of 3d element
+%     - get the neighboring 3d element over the face
+%     - push to bulk queue candidate pair [2d neighbor -- 3d element]
 % 
@@
 % IC is:
-% - on 2D element side
-%     - find 2D element sides (if at node) and the corresponding neighbors
-%     - inside 3D element
-%         - push to component queue candidates pairs [2D neigbor -- current 3D element]
-%     - on the surface of 3D element
+% - on 2d element side
+%     - find 2d element sides (if at node) and the corresponding neighbors
+%     - inside 3d element
+%         - push to component queue candidates pairs [2d neigbor -- current 3d element]
+%     - on the surface of 3d element
 %         - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
-%         - get the 3D neighbors over the faces
+%         - get the 3d neighbors over the faces
 %         - push to bulk queue new candidates pairs
-%             - [current 2D element -- 3D neighbor]
-%             - [2D neighbor -- 3D neighbor] (all combinations)
+%             - [current 2d element -- 3d neighbor]
+%             - [2d neighbor -- 3d neighbor] (all combinations)
 %             - check whether the candidate pair has not been computed yet
-% - inside the 2D element (=> on the surface of 3D element)
+% - inside the 2d element (=> on the surface of 3d element)
 %     - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
-%     - get the 3D neighbors over the faces
-%     - push to bulk queue new candidates pairs [current 2D element -- 3D neighbor]
+%     - get the 3d neighbors over the faces
+%     - push to bulk queue new candidates pairs [current 2d element -- 3d neighbor]
 %     - check whether the candidate pair has not been computed yet
@@
 computations on complex meshes consisting of simplicial elements of different dimensions. However,
-non-matching meshes are at the moment available only in experimental 1D-2D flow model, using mortar like coupling.
+non-matching meshes are at the moment available only in experimental 1d-2d flow model, using mortar like coupling.
 % This work is the first greater step on the way to dimensional coupling models on non-matching meshes 
@@
 \subsection{Element Intersection Algorithms}
-The first benchmark focuses on the 1D-3D and 2D-3D element intersections. We randomly generated
+The first benchmark focuses on the 1d-3d and 2d-3d element intersections. We randomly generated
 100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
@@
 %     \begin{tabular}[b]{l|l}
-%             algorithm, 2D-3D& FLOPs\\
+%             algorithm, 2d-3d& FLOPs\\
 %                       & estimate\\
@@
 %     \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
-%                       Only 2D-3D case considered.}
+%                       Only 2d-3d case considered.}
 %     \label{tab:fundamental_flops}
@@
     \begin{tabular}[b]{l|l}
-            algorithm, 2D-3D& FLOPs\\
+            algorithm, 2d-3d& FLOPs\\
                       & estimate\\
@@
     \caption{Estimation of floating point operations count and comparison of different approaches.
-             Only 2D-3D case considered.}
+             Only 2d-3d case considered.}
     \label{tab:fundamental_flops}
@@
 using \plucker coordinates, red values to \ngh code.
-The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D.
+The gained speed up factor is approximately 5 in 1d-3d case and 2 in 2d-3d.
 Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.
@@
 TODO:
-- line intersection tracking for accelerate 2D-2D intersections
+- line intersection tracking for accelerate 2d-2d intersections
 - better handling of special cases in paarticular in relation to prolongations
@@
 
-\cite{sladkova_bakalarka} Space-time DG with adaptive mesh, need integration of product of functions on different meshes (in 2D). An algorithm 
-for computing triangle-triangle intersections in 2D.
+\cite{sladkova_bakalarka} Space-time DG with adaptive mesh, need integration of product of functions on different meshes (in 2d). An algorithm 
+for computing triangle-triangle intersections in 2d.
 
@@
 
-\cite{gander_algorithm_2013} Full algorithm for 2d=3D called PANG. Implemented in DUNE in 2010 (Bastian). Other software (Hecht, MpCCI). 
+\cite{gander_algorithm_2013} Full algorithm for 2d=3d called PANG. Implemented in DUNE in 2010 (Bastian). Other software (Hecht, MpCCI). 
 Triangle-Triangle and Tetra-Triangle intersections done similarly as in aur approach: set of points including vertices and then sort them countercolckwise.

### 2016-09-30 paper_intersections.tex
Minor corrections and improvements.

@@
 %\title{Algorithm for Intersections of Nonmatching Grids of Different Dimensions}
-\title{Fast Algorithms for Intersection of Non-matching Grids Using \plucker coordinates.}
+\title{Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.}
 
@@
 We present algorithms for intersections between 1d and 2d unstructured multi component meshes 
-and their intersections a background unstructured 3d mesh. A common algorithm 
-based on the advancing front technique is used for the efficient selection of candidate pairs of 
+and their intersections with a background unstructured 3d mesh. A common algorithm 
+based on the advancing front technique is used for the efficient selection of candidate pairs among 
 simplicial elements. Bounding interval hierarchy (BIH) of axes aligned bounding boxes (AABB) of elements
 is used to initialize the front tracking algorithm. The family of element intersection algorithms
-is build upon a line-triangle intersection algorithm based on the \plucker
-coordinates. These algorithms combined with the advancing front technique can reuse calculations 
-done on the neigbouring elements and reduce the number of arithmetic operations. Barycentric coordinates
+is built upon a line-triangle intersection algorithm based on the \plucker
+coordinates. These algorithms combined with the advancing front technique can reuse the results of calculations 
+performed on the neigbouring elements and reduce the number of arithmetic operations. Barycentric coordinates
 on each of the intersecting elements are provided for every intersection point. Benchmarks 
-of the element intersection algorithms are provided and three variants of the global intersection 
+of the element intersection algorithms are presented and three variants of the global intersection 
 algorithm are compared on the meshes raising from a hydrogeological application.
@@
 
-We denote $S_i$ a simplicial element with $i+1$ vertices (of dimension $i$). We call vertices, edges, faces and simlices itself the \nfaces and we denote
+We denote $S_i$ a simplicial element with $i+1$ vertices (of dimension $i$). We call vertices, edges, faces and simplices itself the \nfaces and we denote
 $M_i$ the set of all \nfaces of the simplex $S_i$.
@@
 
-\subsection{Intersection Line-Teraherdon (1d-3d)}
+\subsection{Intersection Line-Tetrahedron (1d-3d)}
 In this section we consider intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
@@
 To get all ICs, we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
-to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
+to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner products, one for every side-edge pair.
 Computation of IP consists of three stages: calculation of side-tetrahedron ICs (Section \ref{sec:sides}), 
@@
 defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
-and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \noteJB{possible figure}). The vertices of the polygon are oredered in the same 
+and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \noteJB{possible figure}). The vertices of the polygon are ordered in the same 
 way as is the order and orientation of the sides of $S_2$, that is counterclockwise around the interior with normal pointing to us.
@@
   }  
-  \uElseIf{ $s$ have edge $e$ with sign oposite to other two}{ \nllabel{line:different_sign}
+  \uElseIf{ $s$ have edge $e$ with sign opposite to other two}{ \nllabel{line:different_sign}
     \return edge faces($e$)\;

### 2016-09-30 paper_intersections.tex
Minor corrections in introduction.

@@
 \section{Introduction}
-\notePE{How did you decided for 'non-matching' term? Instead of e.g. incompatible or non-conforming?}
-\noteJB{Non-matching grid seems to be the most common.}
-
 The grid intersection algorithms are crucial for several techniques that try to overcome some limitations of the classical finite element method.
@@
 The realistic models of groundwater processes including the transport processes and geomechanics have to deal with 
-a complex nature of geological formations including the fractures and wells. Although of small scale, these features may have significant impact 
+a complex nature of geological formations including fractures and wells. Although of a small scale, these features may have significant impact 
 on the global behavior of the system and their representation in the numerical model is imperative.
@@
 already adopted by some groundwater simulation software, e.g FeFlow \cite{trefry_feflow:_2007} and Flow123d \cite{flow123d}.
-Nevertheless as the complexity of the geometry increase (e.g. when lot of fractures are randomly generated) the compatible meshing becomes painful or even 
-impossible. In order to avoid these difficulties we may discretize the continuum and every fracture and well independently getting a non-matching 
+Nevertheless as the complexity of the geometry increase (e.g. when lots of fractures are randomly generated) the compatible meshing becomes painful or even 
+impossible. In order to avoid these difficulties we may discretize the continuum and every fracture and well independently, getting a non-matching 
 (or incompatible) mesh of mixed dimensions and then apply XFEM to represent jumps of the solution on the fractures or singularities 
@@
 and to compute that intersection. The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. 
-Second, compute the intersection for particular pair.
-
-According to our knowledge there are lot of works using non-matching grids yet only few of them discuss algorithms how to compute their intersections. 
+Second, compute the intersection of a particular pair.
+
+According to our knowledge, there are lots of works using non-matching grids, yet only few of them discuss algorithms how to compute their intersections. 
 Gander and Japhet \cite{gander_algorithm_2013} present the PANG algorithm for 2d-2d and 3d-3d intersections that can be used e.g. for mesh overlapping methods.
@@
 to get intersection candidate pairs of elements, the GTS library \cite{gtslib} is used for 2d-3d intersections. 
-Finally, there is the work of Elsheikh and Elsheikh \cite{elsheikh_reliable_2012} presenting an algorithm for 2d-2d mesh union operation which includes 
+Finally, there is the work of A. Elsheikh and M. Elsheikh \cite{elsheikh_reliable_2012} presenting an algorithm for 2d-2d mesh union operation which includes 
 calculation and imprinting of the intersection curves. They exploit binary space partitioning for search of initial intersection and 
@@
 
-In this paper we present a new approach to calculation intersections of simplicial elements of different dimensions based on the \plucker coordinates
+In this paper we present a new approach to intersection calculation of simplicial elements of different dimensions based on the \plucker coordinates,
 further developing the algorithm of Platis and Theoharis \cite{platis_fast_2003} for ray-tetrahedron intersections. Element intersections based on 
 \plucker coordinates are combined with the advancing front method which allows us to reuse \plucker coordinates and their products between neigbouring
-elements and reduce the number of arithmetic operations. The paper is organized as follows. In Section \ref{sec:element intersecitons} the algorithms for
-1d-2d, 1d-3d and 2d-3d intersections of simplices are described. In Section \ref{sec:front advancing} we discuss our implementation of the advancing front 
-technique and usage of AABB and BIH for its initialization. Finally, in Section \ref{sec:benchmarks}, we provide benchmarks and comparison of individual algorithms.
+elements and reduce the number of arithmetic operations.
+
+The paper is organized as follows. In Section \ref{sec:element intersecitons} the algorithms for
+1d-2d, 1d-3d and 2d-3d intersections of simplices are described. In Section \ref{sec:front_advancing} we discuss our implementation of the advancing front 
+technique and usage of AABB and BIH for its initialization. Finally, in Section \ref{sec:benchmarks}, we present benchmarks and comparison of individual algorithms.
 
@@
 \section{Advancing Front Method}
-
+\label{sec:front_advancing}
 add references...

### 2016-09-30 paper_intersections.tex
Corrections until sec 2-3.

@@
 In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3d ambient space. 
-In particular we address intersection algorithms for 1d-2d, 1d-3d, 2d-3d pairs of elements. We have implemented the case 2d-2d as well however the treatment 
+In particular we address intersection algorithms for 1d-2d, 1d-3d, 2d-3d pairs of elements. We have implemented the case 2d-2d as well, however the treatment 
 of the special cases is quite technical and not fully completed yet. The fundamental idea is to compute intersection of 1d-2d simplices using the 
@@
 for each intersecting element $K$ of the pair. The pair $\tau_K = (d_K, i_K)$
-we call the topological position of the IC on $K$.
+is called the topological position of the IC on $K$.
 
@@
 the \plucker coordinates of $p$ are defined as
-\[ \pi_p = (\vc{u}_p, \vc{v}_p) = (\vc{u}_p, \vc{u}_p\times A). \]
+\[ \pi_p = (\vc{u}_p, \vc{v}_p) = (\vc{u}_p, \vc{u}_p\times \vc A). \]
 Further we use a permuted inner product
@@
 The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
-is an intersection point $X$ on the $p$ and inside the triangle $T$. 
-The barycentric coordinates of $X$ on $T$ are
+is an intersection point $\vc X$ on the $p$ and inside the triangle $T$. 
+The barycentric coordinates of $\vc X$ on $T$ are
 \begin{equation}
@@
 Using the barycentric coordinates the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
-The line $p$ have \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
+The line $p$ has \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
 Combining these two expressions we get
@@
 \]
-The point $X$ is inside of $T$ if and only if $w_i>0$ for all $i=0,1,2$.
+The point $\vc X$ is inside of $T$ if and only if $w_i>0$ for all $i=0,1,2$.
 \end{proof}
-Having the barycentric coordinates of $X$ on $T$, we can compute also its local coordinate on $p$ from its parametric form:
+Having the barycentric coordinates of $\vc X$ on $T$, we can compute also its local coordinate on $p$ from its parametric form:
 \begin{equation}
@@
     \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
-    \item If any $w_i$ is less then $\epsilon$ there is no intersection, return empty IP.  
-    \item If all $w_i$ are greater then $\epsilon$, we set $\tau_T = (2, 0)$ for the IC.
-    \item If one $w_i$ is less then $\epsilon$, intersection on edge $s_i$, we set $\tau_T =(1,i)$.
-    \item If two $w_i$ are less then $\epsilon$, intersection in the vertex $V_i$, we set $\tau_T=(0,,i)$.
-    \item \label{item:coplanar} If all $w_i$ are less then $\epsilon$, the line is coplanar with the triangle, both objects are 
+    \item If any $w_i$ is less than $\epsilon$, there is no intersection, return empty IP.  
+    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_T = (2, 0)$ for the IC.
+    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_T =(1,i)$.
+    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_T=(0,i)$.
+    \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
         projected to the plane $x_i=0$ where $i$ is the index of maximal component of the triangle's normal vector.
-        Every pair $p$, $s_i$ is checked for an intersection on $T$ boundary either inside $s_i$ or in a vertex $V_i$ setting the topological info $\tau_T$ to 
-        $(1, i)$ or $(0, i)$ respectively. At most two ICs are obtained.
+        Every pair $p$, $s_i$ is checked for an intersection on $T$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_T$ to 
+        $(1, i)$ or $(0, i)$, respectively. At most two ICs are obtained.
     \item For each IC the barycentric coordinates $(1-t, t)$ on the line $p$ are computed according to \eqref{eq:line}. 
@@
 
-The check for the same sign of the inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
+Checking the same sign of the inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
 line with respect to the triangle. Adaptive-precision evaluation of the geometric predicates was designed by Schewchuk \cite{shewchuk_adaptive_1997}
@@
 The algorithms for 1d-3d and 2d-3d intersections use simpler version of the 1d-2d intersection algorithm, in particular the search for ICs in the coplanar case 
-(item \ref{item:coplanar}) is not necessary and the test in the last point is not performed.
-and degenerate cases higher dimensional cases.
+(item \ref{item:coplanar}) is not necessary, and the test in the last point is not performed.
+%and degenerate cases higher dimensional cases.
 

### 2016-09-30 paper_intersections.tex
Fix 13d intersections.

@@
 \subsection{Intersection Line-Triangle (1d-2d)}
+\notePE{I would stick to chosen notation - triangle $S_3$, and possibly renamed side $s_i$...}
 Let us consider a line segment $p$ with parametric equation 
@@
 \subsection{Intersection Line-Tetrahedron (1d-3d)}
-In this section we consider intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
-$S_3$. The used algorithm is based on 1d-2d algorithm and closely follows \cite{platis_fast_2003}. Our modification takes into account
-intersection with a line segment and consistently propagates topological position of ICs.
+\notePE{degenerate not defined yet.. do you call it coplanar now?}
+In this section we consider an intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
+$S_4$. The used algorithm is based on the 1d-2d algorithm and closely follows \cite{platis_fast_2003}. Our modification takes into account
+intersection with the line segment and consistently propagates topological position of ICs.
 
@@
   \SetKw{break}{break}
-  \KwIn{Tetrahedron $S_3$, line segment $p$.}
-  \KwOut{List of ICs on sorted along $p$.}  
-  $I=\{\}$ 
-  \For{unmarked face $f$ of $S_3$}{
-    $L$ = intersection($p,\ f$)\;
+  \KwIn{Tetrahedron $S_4$, line segment $p$.}
+  \KwOut{List $I$ of ICs sorted along $p$.}  
+  $I=\{\}$\; 
+  \For{unmarked face $f$ of $S_4$}{
+    $L$ = intersection($p,\ f$)\; \label{line:13-intersection}
     \lIf{ $L$ is none or degenerate}{\continue}
-    \lIf{ $L$ is inside the edge $e$}{
+    \If{ $L$ is inside the edge $e$}{
         set $\tau_{S_4} = (1,e)$\;
@@
     }
-    append $L$ to $I$
+    append $L$ to $I$\; \label{line:13-append}
     \lIf{$\abs{I}=2$}{\break}
   }
-  \lIf{$\abs{I}=1$ \and   $I$ is outside of $p$}{ erase $I$}
+  \lIf{$\abs{I}=1$ \and   $I$ is outside of $p$}{ erase $I$} \label{line:trimming}
   \ElseIf{$\abs{I}=2$}{    
-    trim intersection with respect to the line segment $p$ \label{line:trimming}
+    trim intersection with respect to the line segment $p$
   }
 \end{algorithm}
-Algorithm \ref{algo:13d} first compute line-face intersections for every face of $S_4$ avoiding duplicate computation of ICs on edges and at vertices and
-skipping remaining faces once two ICs are found. Tetrahedron has six edges, so 7 \plucker coordinates and 6 inner products are computed at most. Precomputed 
-coordinates and products are passed the 1d-2d algorithm which is performed fro the whole line $p$. After collecting line-tetrahedron ICs,
-we do the line segment trimming \ref{line:trimming}. If both ICs are out of the line segment $p$ we eliminate both of them. If one of the ICs if out of $p$
+Algorithm \ref{algo:13d} first computes line-face intersections for every face of $S_4$.
+Tetrahedron has six edges, so 7 \plucker coordinates and 6 permuted inner products are computed at most.
+Precomputed coordinates and products are passed into the 1d-2d algorithm which is performed for the whole line $p$ (line \ref{line:13-intersection}).
+If no IC is found, or coplanar case occurs in line-face computation, we continue to the next face.
+Note, ICs that would be created in coplanar case are to be found as ICs with the other faces, since they lie on edges.
+Next, IC can be on an edge or at a vertex; then we set the correct topological position and mark the adjacent faces
+to be skipped, since there cannot be another IC (and coplanar case has been checked already).
+Finally at the line \ref{line:13-append}, we append the IC to the result and check whether the maximal amount of 
+ICs has been reached.
+
+After collecting line-tetrahedron ICs,
+we do the line segment trimming from the line \ref{line:trimming} further. 
+If we have only one IC, we check that it actually lies inside the line segment (otherwise, we throw it away).
+If we have two ICs, and if both lie outside the line segment $p$, we eliminate both of them. 
+If one of the ICs lies out of $p$,
 we use the closest end point of the line segment instead and interpolate barycentric coordinates of the IC on $S_4$. The topological positions are updated as well.
-The result of the algorithm are zero up to two ICs sorted by the parameter $t$ of the line $p$.
+The result of the algorithm is 0, 1, or 2 ICs, sorted by the parameter $t$ in the direction of the line $p$.
 

### 2016-09-30 paper_intersections.tex
Define degenerate, fix back simplex dim number.

@@
 \subsection{Intersection Line-Triangle (1d-2d)}
-\notePE{I would stick to chosen notation - triangle $S_3$, and possibly renamed side $s_i$...}
+\notePE{I would stick to chosen notation - triangle $S_2$, and possibly renamed side $s_i$...}
 Let us consider a line segment $p$ with parametric equation 
@@
 
+We shall call every IC, that was created in the coplanar case, \emph{degenerate} since these will later
+special treatment.
+
 Checking the same sign of the inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
@@
 In this section we consider an intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
-$S_4$. The used algorithm is based on the 1d-2d algorithm and closely follows \cite{platis_fast_2003}. Our modification takes into account
+$S_3$. The used algorithm is based on the 1d-2d algorithm and closely follows \cite{platis_fast_2003}. Our modification takes into account
 intersection with the line segment and consistently propagates topological position of ICs.
@@
   \SetKw{break}{break}
-  \KwIn{Tetrahedron $S_4$, line segment $p$.}
+  \KwIn{Tetrahedron $S_3$, line segment $p$.}
   \KwOut{List $I$ of ICs sorted along $p$.}  
   $I=\{\}$\; 
-  \For{unmarked face $f$ of $S_4$}{
+  \For{unmarked face $f$ of $S_3$}{
     $L$ = intersection($p,\ f$)\; \label{line:13-intersection}
@@
     \If{ $L$ is inside the edge $e$}{
-        set $\tau_{S_4} = (1,e)$\;
+        set $\tau_{S_3} = (1,e)$\;
         mark faces coincident with $e$
@@
     \ElseIf{ $L$ is at the vertex $v$}{
-        set $\tau_{S_4} = (0,v)$\;
+        set $\tau_{S_3} = (0,v)$\;
         mark faces coincident with $v$
@@
 \end{algorithm}
-Algorithm \ref{algo:13d} first computes line-face intersections for every face of $S_4$.
+Algorithm \ref{algo:13d} first computes line-face intersections for every face of $S_3$.
 Tetrahedron has six edges, so 7 \plucker coordinates and 6 permuted inner products are computed at most.
@@
 If one of the ICs lies out of $p$,
-we use the closest end point of the line segment instead and interpolate barycentric coordinates of the IC on $S_4$. The topological positions are updated as well.
+we use the closest end point of the line segment instead and interpolate barycentric coordinates of the IC on $S_3$. The topological positions are updated as well.
 The result of the algorithm is 0, 1, or 2 ICs, sorted by the parameter $t$ in the direction of the line $p$.

### 2016-10-01 paper_intersections.tex
Partly reviewed sec 3

--- 2016-09-30 paper_intersections.tex
@@
 %\title{Algorithm for Intersections of Nonmatching Grids of Different Dimensions}
-\title{Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.}
+\title{Fast Algorithms for Intersection of Non-matching Grids Using \plucker coordinates.}
 
@@
 We present algorithms for intersections between 1d and 2d unstructured multi component meshes 
-and their intersections with a background unstructured 3d mesh. A common algorithm 
-based on the advancing front technique is used for the efficient selection of candidate pairs among 
+and their intersections a background unstructured 3d mesh. A common algorithm 
+based on the advancing front technique is used for the efficient selection of candidate pairs of 
 simplicial elements. Bounding interval hierarchy (BIH) of axes aligned bounding boxes (AABB) of elements
 is used to initialize the front tracking algorithm. The family of element intersection algorithms
-is built upon a line-triangle intersection algorithm based on the \plucker
-coordinates. These algorithms combined with the advancing front technique can reuse the results of calculations 
-performed on the neigbouring elements and reduce the number of arithmetic operations. Barycentric coordinates
+is build upon a line-triangle intersection algorithm based on the \plucker
+coordinates. These algorithms combined with the advancing front technique can reuse calculations 
+done on the neigbouring elements and reduce the number of arithmetic operations. Barycentric coordinates
 on each of the intersecting elements are provided for every intersection point. Benchmarks 
-of the element intersection algorithms are presented and three variants of the global intersection 
+of the element intersection algorithms are provided and three variants of the global intersection 
 algorithm are compared on the meshes raising from a hydrogeological application.
@@
 \section{Introduction}
+\notePE{How did you decided for 'non-matching' term? Instead of e.g. incompatible or non-conforming?}
+\noteJB{Non-matching grid seems to be the most common.}
+
 The grid intersection algorithms are crucial for several techniques that try to overcome some limitations of the classical finite element method.
@@
 The realistic models of groundwater processes including the transport processes and geomechanics have to deal with 
-a complex nature of geological formations including fractures and wells. Although of a small scale, these features may have significant impact 
+a complex nature of geological formations including the fractures and wells. Although of small scale, these features may have significant impact 
 on the global behavior of the system and their representation in the numerical model is imperative.
@@
 already adopted by some groundwater simulation software, e.g FeFlow \cite{trefry_feflow:_2007} and Flow123d \cite{flow123d}.
-Nevertheless as the complexity of the geometry increase (e.g. when lots of fractures are randomly generated) the compatible meshing becomes painful or even 
-impossible. In order to avoid these difficulties we may discretize the continuum and every fracture and well independently, getting a non-matching 
+Nevertheless as the complexity of the geometry increase (e.g. when lot of fractures are randomly generated) the compatible meshing becomes painful or even 
+impossible. In order to avoid these difficulties we may discretize the continuum and every fracture and well independently getting a non-matching 
 (or incompatible) mesh of mixed dimensions and then apply XFEM to represent jumps of the solution on the fractures or singularities 
@@
 and to compute that intersection. The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. 
-Second, compute the intersection of a particular pair.
-
-According to our knowledge, there are lots of works using non-matching grids, yet only few of them discuss algorithms how to compute their intersections. 
+Second, compute the intersection for particular pair.
+
+According to our knowledge there are lot of works using non-matching grids yet only few of them discuss algorithms how to compute their intersections. 
 Gander and Japhet \cite{gander_algorithm_2013} present the PANG algorithm for 2d-2d and 3d-3d intersections that can be used e.g. for mesh overlapping methods.
@@
 to get intersection candidate pairs of elements, the GTS library \cite{gtslib} is used for 2d-3d intersections. 
-Finally, there is the work of A. Elsheikh and M. Elsheikh \cite{elsheikh_reliable_2012} presenting an algorithm for 2d-2d mesh union operation which includes 
+Finally, there is the work of Elsheikh and Elsheikh \cite{elsheikh_reliable_2012} presenting an algorithm for 2d-2d mesh union operation which includes 
 calculation and imprinting of the intersection curves. They exploit binary space partitioning for search of initial intersection and 
@@
 
-In this paper we present a new approach to intersection calculation of simplicial elements of different dimensions based on the \plucker coordinates,
+In this paper we present a new approach to calculation intersections of simplicial elements of different dimensions based on the \plucker coordinates
 further developing the algorithm of Platis and Theoharis \cite{platis_fast_2003} for ray-tetrahedron intersections. Element intersections based on 
 \plucker coordinates are combined with the advancing front method which allows us to reuse \plucker coordinates and their products between neigbouring
-elements and reduce the number of arithmetic operations.
-
-The paper is organized as follows. In Section \ref{sec:element intersecitons} the algorithms for
-1d-2d, 1d-3d and 2d-3d intersections of simplices are described. In Section \ref{sec:front_advancing} we discuss our implementation of the advancing front 
-technique and usage of AABB and BIH for its initialization. Finally, in Section \ref{sec:benchmarks}, we present benchmarks and comparison of individual algorithms.
+elements and reduce the number of arithmetic operations. The paper is organized as follows. In Section \ref{sec:element intersecitons} the algorithms for
+1d-2d, 1d-3d and 2d-3d intersections of simplices are described. In Section \ref{sec:front advancing} we discuss our implementation of the advancing front 
+technique and usage of AABB and BIH for its initialization. Finally, in Section \ref{sec:benchmarks}, we provide benchmarks and comparison of individual algorithms.
 
@@
 \label{sec:element intersecitons}
-In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3d ambient space. 
-In particular we address intersection algorithms for 1d-2d, 1d-3d, 2d-3d pairs of elements. We have implemented the case 2d-2d as well, however the treatment 
-of the special cases is quite technical and not fully completed yet. The fundamental idea is to compute intersection of 1d-2d simplices using the 
+In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3D ambient space. 
+In particular we address intersection algorithms for 1D-2D, 1D-3D, 2D-3D pairs of elements. We have implemented the case 2D-2D as well however the treatment 
+of the special cases is quite technical and not fully completed yet. The fundamental idea is to compute intersection of 1D-2D simplices using the 
 \plucker coordinates and reduce all other cases to this one.
 
-We denote $S_i$ a simplicial element with $i+1$ vertices (of dimension $i$). We call vertices, edges, faces and simplices itself the \nfaces and we denote
+We denote $S_i$ a simplicial element with $i+1$ vertices (of dimension $i$). We call vertices, edges, faces and simlices itself the \nfaces and we denote
 $M_i$ the set of all \nfaces of the simplex $S_i$.
@@
 for each intersecting element $K$ of the pair. The pair $\tau_K = (d_K, i_K)$
-is called the topological position of the IC on $K$.
+we call the topological position of the IC on $K$.
 
 \subsection{\plucker Coordinates}
-\plucker coordinates represent a line in 3d space.
+\plucker coordinates represent a line in 3D space.
 Considering a line $p$, given by a point $\vc A$ and its directional vector $\vc{u}$, 
 the \plucker coordinates of $p$ are defined as
-\[ \pi_p = (\vc{u}_p, \vc{v}_p) = (\vc{u}_p, \vc{u}_p\times \vc A). \]
+\[ \pi_p = (\vc{u}_p, \vc{v}_p) = (\vc{u}_p, \vc{u}_p\times A). \]
 Further we use a permuted inner product
@@
 
-\subsection{Intersection Line-Triangle (1d-2d)}
+\subsection{Intersection Line-Triangle (1D-2D)}
 Let us consider a line segment $p$ with parametric equation 
@@
 The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
-is an intersection point $\vc X$ on the $p$ and inside the triangle $T$. 
-The barycentric coordinates of $\vc X$ on $T$ are
+is an intersection point $X$ on the $p$ and inside the triangle $T$. 
+The barycentric coordinates of $X$ on $T$ are
 \begin{equation}
@@
 Using the barycentric coordinates the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
-The line $p$ has \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
+The line $p$ have \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
 Combining these two expressions we get
@@
 \]
-The point $\vc X$ is inside of $T$ if and only if $w_i>0$ for all $i=0,1,2$.
+The point $X$ is inside of $T$ if and only if $w_i>0$ for all $i=0,1,2$.
 \end{proof}
-Having the barycentric coordinates of $\vc X$ on $T$, we can compute also its local coordinate on $p$ from its parametric form:
+Having the barycentric coordinates of $X$ on $T$, we can compute also its local coordinate on $p$ from its parametric form:
 \begin{equation}
@@
     \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
-    \item If any $w_i$ is less than $\epsilon$, there is no intersection, return empty IP.  
-    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_T = (2, 0)$ for the IC.
-    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_T =(1,i)$.
-    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_T=(0,i)$.
-    \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
+    \item If any $w_i$ is less then $\epsilon$ there is no intersection, return empty IP.  
+    \item If all $w_i$ are greater then $\epsilon$, we set $\tau_T = (2, 0)$ for the IC.
+    \item If one $w_i$ is less then $\epsilon$, intersection on edge $s_i$, we set $\tau_T =(1,i)$.
+    \item If two $w_i$ are less then $\epsilon$, intersection in the vertex $V_i$, we set $\tau_T=(0,,i)$.
+    \item \label{item:coplanar} If all $w_i$ are less then $\epsilon$, the line is coplanar with the triangle, both objects are 
         projected to the plane $x_i=0$ where $i$ is the index of maximal component of the triangle's normal vector.
-        Every pair $p$, $s_i$ is checked for an intersection on $T$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_T$ to 
-        $(1, i)$ or $(0, i)$, respectively. At most two ICs are obtained.
+        Every pair $p$, $s_i$ is checked for an intersection on $T$ boundary either inside $s_i$ or in a vertex $V_i$ setting the topological info $\tau_T$ to 
+        $(1, i)$ or $(0, i)$ respectively. At most two ICs are obtained.
     \item For each IC the barycentric coordinates $(1-t, t)$ on the line $p$ are computed according to \eqref{eq:line}. 
@@
 
-Checking the same sign of the inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
+The check for the same sign of the inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
 line with respect to the triangle. Adaptive-precision evaluation of the geometric predicates was designed by Schewchuk \cite{shewchuk_adaptive_1997}
@@
 The algorithms for 1d-3d and 2d-3d intersections use simpler version of the 1d-2d intersection algorithm, in particular the search for ICs in the coplanar case 
-(item \ref{item:coplanar}) is not necessary, and the test in the last point is not performed.
-%and degenerate cases higher dimensional cases.
-
-%\subsection{Intersection Triangle-Tetrahedron (2d-2d)}
+(item \ref{item:coplanar}) is not necessary and the test in the last point is not performed.
+and degenerate cases higher dimensional cases.
+
+%\subsection{Intersection Triangle-Tetrahedron (2D-2D)}
 %\noteJB{Just note that this algorithm can also be implemented using 1d-2d, but quite complex to not yet fully tested}
 
-\subsection{Intersection Line-Tetrahedron (1d-3d)}
+\subsection{Intersection Line-Teraherdon (1D-3D)}
 In this section we consider intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
@@
 skipping remaining faces once two ICs are found. Tetrahedron has six edges, so 7 \plucker coordinates and 6 inner products are computed at most. Precomputed 
-coordinates and products are passed the 1d-2d algorithm which is performed fro the whole line $p$. After collecting line-tetrahedron ICs,
+coordinates and products are passed the 1D-2D algorithm which is performed fro the whole line $p$. After collecting line-tetrahedron ICs,
 we do the line segment trimming \ref{line:trimming}. If both ICs are out of the line segment $p$ we eliminate both of them. If one of the ICs if out of $p$
@@
 
-\subsection{Intersection Triangle-Tetrahedron (2d-3d)}
+\subsection{Intersection Triangle-Tetrahedron (2D-3D)}
 The intersection of a triangle $S_2$ and a tetrahedron $S_3$ is an $n$-side intersection polygon (IP), $n\le 7$. The sides of the polygon
@@
 To get all ICs, we have to compute at most 12 side-face intersections and at most 6 edge-triangle intersections. However,
-to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner products, one for every side-edge pair.
+to this end we only need to compute 9 \plucker coordinates (3 sides, 6 edges) and 18 permuted inner produts, one for every side-edge pair.
 Computation of IP consists of three stages: calculation of side-tetrahedron ICs (Section \ref{sec:sides}), 
@@
 defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
-and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \noteJB{possible figure}). The vertices of the polygon are ordered in the same 
+and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \noteJB{possible figure}). The vertices of the polygon are oredered in the same 
 way as is the order and orientation of the sides of $S_2$, that is counterclockwise around the interior with normal pointing to us.
@@
   }  
-  \uElseIf{ $s$ have edge $e$ with sign opposite to other two}{ \nllabel{line:different_sign}
+  \uElseIf{ $s$ have edge $e$ with sign oposite to other two}{ \nllabel{line:different_sign}
     \return edge faces($e$)\;
@@
 
-\section{Advancing Front Method}
-\label{sec:front_advancing}
-add references...
-% BIH:
-% http://ainc.de/Research/BIH.pdf
-% http://diglib.eg.org/handle/10.2312/EGWR.EGSR06.139-149
-
-Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same lower dimension (1d, or 2d), in the space of connected 3d elements, which we shall call a \emph{bulk}. 
-Obtaining all of component-bulk intersections is done in two phases: firstly, we look for the first two elements intersecting each other (initialization); secondly, we prolong the intersection by investigating neighbouring elements (intersection tracking).
-
-To construct the Advancing front algorithm, we shall need:
-\begin{itemize}
-    \item \textbf{element connectivity} -- we assume this data is available from mesh preprocessing,
-    \item \textbf{Axes Aligned Bounding Boxes (AABB)} -- we construct these in order to decide fastly
-                    whether to compute the actual intersection of two elements,
-    \item \textbf{Bounding Interval Hierarchy (BIH)} -- we alternatively create BIH above AABB to fastly search 
-                    created bounding boxes for two colliding with each other and thus obtaining a candidate pair.
-\end{itemize}
-
-The intersection tracking itself can be also seen as a \emph{breadth-first search}
-\footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
-algorithm over the BIH, following the component elements.
+\section{Global mesh intersection algorithm}
+\noteJB{References already in introduction, possible references to some computer graphics book for AABB and BIH}
+Having the algorithms for element-element intersections we can proceed to the mesh intersection algorithm. 
+We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) and then the 1d-2d and 2d-2d intersections use the 3d mesh
+to get the intersection pair candidates.  Element intersections for the particular component and bulk mesh 
+are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
+secondly, we prolong the intersection by investigating neighbouring elements (front tracking).
+\noteJB{Not sure that "prolong" is the right verb.}
 
@@
 %     \item\label{en:first} Get next unprocessed component element $k$.
-%     \item Find intersection candidates $\mathcal K$ in bulk mesh (3d elements).
+%     \item Find intersection candidates $\mathcal K$ in bulk mesh (3D elements).
 %     \item \label{en:q2}For $K\in \mathcal K$ compute intersection $(k, K)$.  
@@
 \paragraph{Initialization}
-We start with selecting an arbitrary 1d or 2d element. Then we search the bulk elements, checking for 
-a collision of bounding boxes, to create a candidate pair. Using only AABB, we need to iterate over
-bulk elements in $O(n)$, $n$ being the number of all elements in our case. Using BIH, we can speed 
-up the search to $O(\log n)$ on average. In later case, we are paying the costs in the construction of BIH,
-which is a quicksort like algorithm running at $O(n\log n)$ on average.
-
-Now that we have provided the first candidate pair, we can look at the scheme in \fig{fig:prolongation} and see us moving from the green box in the left upper corner.
-If an intersection exists, we have just started a new component and we can procced to tracking the intersection.
-Otherwise, we select another 1d or 2d element and start over.
+We choose an arbitrary element of the component mesh and check it intersection with all elements of the bulk mesh.
+The process is accelerated by computing the axis aligned bounding box (AABB) for every element and use intersection of the bounding boxes
+as a fast indicator for possible intersection of the elements. This step takes $O(N)$ time with respect to the number of elements of the bulk mesh $N$.
+For the small number of components $k$ and if they are contained inside the bulk mesh the total time of initialization may be still linear $O(kn)$. However,
+for more complex cases we organize the bounding boxes of the bulk mesh into the bounding interval hierarchy (BIH) \cite{EGWR:EGSR06:139-149} 
+a data structure in principle equivalent 
+to R-trees \cite{guttman_r-trees:_1984}, \cite{nam_comparative_2004}. The creation time is $O(N\log(N/n))$ and the lookup time $O(\log(N/n))$ where $n$ is number
+of the bulk elements in the leaf nodes of the tree.
+
+\paragraph{Advancing Front Method}
+The advancing front algorithm requires and employ the neigbouring information for the elements within the component as well as within the bulk mesh.
+It can be viewed as the breadth first search algorithm for a graph which vertices are intersection polygons and edges are sides shared by
+two polygons. Side every side of IP is on the boundary of either component or the bulk element we can distinguish bulk and component edges and correspondingly 
+the \emph{bulk queue} and the \emph{component queue}.
 
@@
     \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip.pdf}
-  \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
+  \caption{Advancing front algorithm for 1D-2D and 2D-3D intersections.}
   \label{fig:prolongation}
@@
 
-Let us now discuss the advancing front algorithm displayed by the scheme in \fig{fig:prolongation}.
+The scheme of the advancing front algorithm is displayed by the scheme in \fig{fig:prolongation}. 
 The main idea is to compute intersections for a component element with all possible bulk elements, and then move to a~next neighboring component element. 
-For this reason, we define two
-queues of candidate pairs: a~\emph{bulk queue} and a~\emph{component queue} (yellow boxes).
-
-On input we consider a candidate pair, for which a non-empty intersection is computed.
+So the bulk queue is emptied before the component queue (see yellow boxes).
+
+On the input we consider a candidate pair provided be the initialization (top-left corner).
 Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
-Therefore, we iterate over the intersection points and further exploit the topological information.
-There are 3 possible cases (applies both for 1d-3d and 2d-3d), how the intersection might be prolonged:
+Therefore, we iterate over the intersection corners and further exploit their topological position on the component element $C$ and the bulk element $B$.
+There are 3 possible cases (applies both for 1D-3D and 2D-3D), how the intersection might be prolonged:
 \begin{itemize}
-    \item \textbf{IP lies on the component element side and inside the bulk element} \\
-            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
+    \item \textbf{IC on the boundary of $C$  and inside $B$} \\
+            We find all the sides coincident with the \nface of IC on $C$ component element in which the IP lies (IP can be at node and connect more sides).
             Next, we find the component neighboring elements over the sides and push all new candidate pairs
@@
             Note, that there can be more than one neighbor on a side, if the component has branches.
-    \item \textbf{IP lies on the component element side and on the surface of the bulk element} \\
+    \item \textbf{IC on the boundary of both $C$ and $B$} \\
             We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
@@
             push the new candidate pairs [current component element -- bulk neighbor] into the bulk queue and [component neighbor -- bulk neighbor] into the component queue.
-    \item \textbf{IP lies inside component element (therefore must be on the surface of bulk element)} \\
+    \item \textbf{IC inside the component element and on the boundary of the bulk element)} \\
             We proceed as in previous case, but we push only [current component element -- bulk neighbor] candidate pairs, since there is no component neighbor.
@@
 % two queues with element pairs as candidates for further intersection. If the intersection edge 
-% (point of line in 1d, edge of polygon in 2d) is inside the tetrahedron, not on its surface, we
+% (point of line in 1D, edge of polygon in 2D) is inside the tetrahedron, not on its surface, we
 % get a neighbouring element of the component and push it back together with the current tetrahedron into 
@@
 % (line or triangle), i.e. is on the surface of tetrahedron, we get a neighbouring element of the tetrahedron
-% and push it back together with the current slave element into \emph{3d prolongation queue}.
+% and push it back together with the current slave element into \emph{3D prolongation queue}.
 
@@
 thoroughly at the moment.
-We can show in a figure the case in 'prolong\_meshes\_13d/prolongation\_13d\_04.msh', where actually 4 components are found (therefore bulk is defined as connected 3d elements).}
-
-% The algorithm is now unified for 1d and 2d in contrast to \cite{fris_dp_2015}, where the component prolongation
+We can show in a figure the case in 'prolong\_meshes\_13d/prolongation\_13d\_04.msh', where actually 4 components are found (therefore bulk is defined as connected 3D elements).}
+
+% The algorithm is now unified for 1D and 2D in contrast to \cite{fris_dp_2015}, where the component prolongation
 % queue is emptied at first.
 
-% \subsubsection{1d-3d prolongation}
+% \subsubsection{1D-3D prolongation}
 % 1d-3d prolongation logic
 % IC is:
-% - 1d element node
+% - 1D element node
 %     - inside tetrahedron
-%         - get the neighboring 1d element
-%         - push to component queue candidate pair [1d neigbor -- tetrahedron]
+%         - get the neighboring 1D element
+%         - push to component queue candidate pair [1D neigbor -- tetrahedron]
 %     - on the surface of tetrahedron
@@
 %         - push to bulk queue new candidates pairs:
-%             - [current 1d element -- tetrahedron neighbor]
-%             - [1d neighbor -- tetragedron neighbor]
+%             - [current 1D element -- tetrahedron neighbor]
+%             - [1D neighbor -- tetragedron neighbor]
 %             - check whether the candidate pair has not been computed yet
@@
 %                the element is not closed then -- not fully covered with tetrahedrons)
-% - inside 1d element
+% - inside 1D element
 %     - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
 %     - get the tetrahedron neighbors on the faces
-%     - push to bulk queue candidate pair [current 1d element -- tetrahedron neighbor]
+%     - push to bulk queue candidate pair [current 1D element -- tetrahedron neighbor]
 %     - check whether the candidate pair has not been computed yet
@@
 % \begin{itemize}
-%     \item \textbf{IC lies at 1d element node and inside 3d element} \\
-%             We find the neighboring 1d element over the node and push a new candidate pair [1d neighbor -- current 3d element] into component queue.
-%     \item \textbf{IC lies at 1d element node and on the surface of 3d element} \\
-%             We find all the faces of 3d element in which the IC lies (1 face, or 2 faces (IC on an edge), 
-%             or 3 faces (IC at a node)). We find the corresponding neghboring 3d elements over the faces and
-%             push the following new candidates pairs into the bulk queue: [current 1d element -- 3d neighbor], [1d neighbor -- 3d neighbor].
+%     \item \textbf{IC lies at 1D element node and inside 3D element} \\
+%             We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
+%     \item \textbf{IC lies at 1D element node and on the surface of 3D element} \\
+%             We find all the faces of 3D element in which the IC lies (1 face, or 2 faces (IC on an edge), 
+%             or 3 faces (IC at a node)). We find the corresponding neghboring 3D elements over the faces and
+%             push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
 %             If the candidates pair has been investigated already, we skip it.
-%     \item \textbf{IC lies inside 1d element (therefore must be on the surface of 3d element)} \\
-%             The same as before, but we push only [current 1d element -- 3d neighbor] candidates pairs, since
-%             there is no 1d neighbor.
+%     \item \textbf{IC lies inside 1D element (therefore must be on the surface of 3D element)} \\
+%             The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
+%             there is no 1D neighbor.
 % \end{itemize}
@@
 % IC is:
-% - inside 2d element side
-%     - inside 3d element
-%         - get the neighboring 2d elements over the side
-%         - push to component queue candidates pair [2d neigbor -- current 3d element]
-% - inside the face of 3d element
-%     - get the neighboring 3d element over the face
-%     - push to bulk queue candidate pair [2d neighbor -- 3d element]
+% - inside 2D element side
+%     - inside 3D element
+%         - get the neighboring 2D elements over the side
+%         - push to component queue candidates pair [2D neigbor -- current 3D element]
+% - inside the face of 3D element
+%     - get the neighboring 3D element over the face
+%     - push to bulk queue candidate pair [2D neighbor -- 3D element]
 % 
@@
 % IC is:
-% - on 2d element side
-%     - find 2d element sides (if at node) and the corresponding neighbors
-%     - inside 3d element
-%         - push to component queue candidates pairs [2d neigbor -- current 3d element]
-%     - on the surface of 3d element
+% - on 2D element side
+%     - find 2D element sides (if at node) and the corresponding neighbors
+%     - inside 3D element
+%         - push to component queue candidates pairs [2D neigbor -- current 3D element]
+%     - on the surface of 3D element
 %         - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
-%         - get the 3d neighbors over the faces
+%         - get the 3D neighbors over the faces
 %         - push to bulk queue new candidates pairs
-%             - [current 2d element -- 3d neighbor]
-%             - [2d neighbor -- 3d neighbor] (all combinations)
+%             - [current 2D element -- 3D neighbor]
+%             - [2D neighbor -- 3D neighbor] (all combinations)
 %             - check whether the candidate pair has not been computed yet
-% - inside the 2d element (=> on the surface of 3d element)
+% - inside the 2D element (=> on the surface of 3D element)
 %     - get all faces in which the IC lies (1 face, or 2 faces (edge), or 3 faces (node))
-%     - get the 3d neighbors over the faces
-%     - push to bulk queue new candidates pairs [current 2d element -- 3d neighbor]
+%     - get the 3D neighbors over the faces
+%     - push to bulk queue new candidates pairs [current 2D element -- 3D neighbor]
 %     - check whether the candidate pair has not been computed yet
@@
 computations on complex meshes consisting of simplicial elements of different dimensions. However,
-non-matching meshes are at the moment available only in experimental 1d-2d flow model, using mortar like coupling.
+non-matching meshes are at the moment available only in experimental 1D-2D flow model, using mortar like coupling.
 % This work is the first greater step on the way to dimensional coupling models on non-matching meshes 
@@
 \subsection{Element Intersection Algorithms}
-The first benchmark focuses on the 1d-3d and 2d-3d element intersections. We randomly generated
+The first benchmark focuses on the 1D-3D and 2D-3D element intersections. We randomly generated
 100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
@@
 %     \begin{tabular}[b]{l|l}
-%             algorithm, 2d-3d& FLOPs\\
+%             algorithm, 2D-3D& FLOPs\\
 %                       & estimate\\
@@
 %     \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
-%                       Only 2d-3d case considered.}
+%                       Only 2D-3D case considered.}
 %     \label{tab:fundamental_flops}
@@
     \begin{tabular}[b]{l|l}
-            algorithm, 2d-3d& FLOPs\\
+            algorithm, 2D-3D& FLOPs\\
                       & estimate\\
@@
     \caption{Estimation of floating point operations count and comparison of different approaches.
-             Only 2d-3d case considered.}
+             Only 2D-3D case considered.}
     \label{tab:fundamental_flops}
@@
 using \plucker coordinates, red values to \ngh code.
-The gained speed up factor is approximately 5 in 1d-3d case and 2 in 2d-3d.
+The gained speed up factor is approximately 5 in 1D-3D case and 2 in 2D-3D.
 Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.
@@
 TODO:
-- line intersection tracking for accelerate 2d-2d intersections
+- line intersection tracking for accelerate 2D-2D intersections
 - better handling of special cases in paarticular in relation to prolongations
@@
 
-\cite{sladkova_bakalarka} Space-time DG with adaptive mesh, need integration of product of functions on different meshes (in 2d). An algorithm 
-for computing triangle-triangle intersections in 2d.
+\cite{sladkova_bakalarka} Space-time DG with adaptive mesh, need integration of product of functions on different meshes (in 2D). An algorithm 
+for computing triangle-triangle intersections in 2D.
 
@@
 
-\cite{gander_algorithm_2013} Full algorithm for 2d=3d called PANG. Implemented in DUNE in 2010 (Bastian). Other software (Hecht, MpCCI). 
+\cite{gander_algorithm_2013} Full algorithm for 2d=3D called PANG. Implemented in DUNE in 2010 (Bastian). Other software (Hecht, MpCCI). 
 Triangle-Triangle and Tetra-Triangle intersections done similarly as in aur approach: set of points including vertices and then sort them countercolckwise.

### 2016-10-01 paper_intersections.tex

--- 2016-09-30 paper_intersections.tex
@@
 
-\section{Advancing Front Method}
+\section{Global mesh intersection algorithm}
 \label{sec:front_advancing}
-add references...
-% BIH:
-% http://ainc.de/Research/BIH.pdf
-% http://diglib.eg.org/handle/10.2312/EGWR.EGSR06.139-149
-
-Consider now a complex mesh of combined dimensions consisting of \emph{components}, which are sets of connected
-elements of the same lower dimension (1d, or 2d), in the space of connected 3d elements, which we shall call a \emph{bulk}. 
-Obtaining all of component-bulk intersections is done in two phases: firstly, we look for the first two elements intersecting each other (initialization); secondly, we prolong the intersection by investigating neighbouring elements (intersection tracking).
-
-To construct the Advancing front algorithm, we shall need:
-\begin{itemize}
-    \item \textbf{element connectivity} -- we assume this data is available from mesh preprocessing,
-    \item \textbf{Axes Aligned Bounding Boxes (AABB)} -- we construct these in order to decide fastly
-                    whether to compute the actual intersection of two elements,
-    \item \textbf{Bounding Interval Hierarchy (BIH)} -- we alternatively create BIH above AABB to fastly search 
-                    created bounding boxes for two colliding with each other and thus obtaining a candidate pair.
-\end{itemize}
-
-The intersection tracking itself can be also seen as a \emph{breadth-first search}
-\footnote{Wiki, [online 2016-03-01], \url{https://en.wikipedia.org/wiki/Breadth-first_search}}
-algorithm over the BIH, following the component elements.
+Having the algorithms for element-element intersections we can proceed to the mesh intersection algorithm. 
+We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) and then the 1d-2d and 2d-2d intersections use the 3d mesh
+to get the intersection pair candidates.  Element intersections for the particular component and bulk mesh 
+are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
+secondly, we prolong the intersection by investigating neighbouring elements (front tracking).
+\noteJB{Not sure that "prolong" is the right verb.}
 
@@
 
-Let us now discuss the advancing front algorithm displayed by the scheme in \fig{fig:prolongation}.
+The scheme of the advancing front algorithm is displayed by the scheme in \fig{fig:prolongation}. 
 The main idea is to compute intersections for a component element with all possible bulk elements, and then move to a~next neighboring component element. 
-For this reason, we define two
-queues of candidate pairs: a~\emph{bulk queue} and a~\emph{component queue} (yellow boxes).
-
-On input we consider a candidate pair, for which a non-empty intersection is computed.
+So the bulk queue is emptied before the component queue (see yellow boxes).
+
+On the input we consider a candidate pair provided be the initialization (top-left corner).
 Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
-Therefore, we iterate over the intersection points and further exploit the topological information.
+Therefore, we iterate over the intersection corners and further exploit their topological position on the component element $C$ and the bulk element $B$.
 There are 3 possible cases (applies both for 1d-3d and 2d-3d), how the intersection might be prolonged:
 \begin{itemize}
-    \item \textbf{IP lies on the component element side and inside the bulk element} \\
-            We find all the sides of component element in which the IP lies (IP can be at node and connect more sides).
+    \item \textbf{IC on the boundary of $C$  and inside $B$} \\
+            We find all the sides coincident with the \nface of IC on $C$ component element in which the IP lies (IP can be at node and connect more sides).
             Next, we find the component neighboring elements over the sides and push all new candidate pairs

### 2016-10-01 paper_intersections.tex
Section 3 changes

@@
 Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
-Therefore, we iterate over the intersection corners and further exploit their topological position on the component element $C$ and the bulk element $B$.
+Therefore, we iterate over the intersection corners and further exploit their topological position on the component element $c$ and the bulk element $b$.
 There are 3 possible cases (applies both for 1d-3d and 2d-3d), how the intersection might be prolonged:
 \begin{itemize}
-    \item \textbf{IC on the boundary of $C$  and inside $B$} \\
-            We find all the sides coincident with the \nface of IC on $C$ component element in which the IP lies (IP can be at node and connect more sides).
-            Next, we find the component neighboring elements over the sides and push all new candidate pairs
-            [component neighbor -- current bulk element] into the component queue.
-            Note, that there can be more than one neighbor on a side, if the component has branches.
-    \item \textbf{IC on the boundary of both $C$ and $B$} \\
-            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
-            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
-            push the new candidate pairs [current component element -- bulk neighbor] into the bulk queue and [component neighbor -- bulk neighbor] into the component queue.
-    \item \textbf{IC inside the component element and on the boundary of the bulk element)} \\
-            We proceed as in previous case, but we push only [current component element -- bulk neighbor] candidate pairs, since there is no component neighbor.
+    \item \textbf{IC on the boundary of $c$  and inside $b$} \\
+            We find all the sides $S$ coincident with the \nface of $c$ on which IC lies. Then we get all component
+            elements $C'$ neighbouring with $c$ over any side$s\in S$. And finally, we push all pairs $(c',b)$, $c'\in C'$ 
+            into the component queue.
+            Note, that $c$ can have more then one neighbour component elements over the single side $s$, i.e. branches are allowed.
+    \item \textbf{IC on the boundary of both $c$ and $b$} \\
+            We find all the faces $F$ coincident with the \nface of $b$ on which IC lies. 
+            Then we get all neighbours $B'$ through all faces in $F$ as in the previous case.
+            We push pairs $(c, b')$, $b'\in B'$ into the bulk queue and pairs $(c', b')$, $c'\in C'$, $b'\in B'$ into the component queue.
+    \item \textbf{IC inside of $c$ anf on the boundary of $b$)} \\
+            We proceed as in previous case, and push pairs $(c, b')$, $b'\in B'$ into the bulk queue.
 \end{itemize}
-
-If the candidate pair has been found already, we skip it.
-We also see that the candidate pairs are of three types:
-[current component element -- bulk neighbor],
-[component neighbor -- current bulk element], 
-[component neighbor -- bulk neighbor],
-from which only the first one goes into the bulk queue, trying to cover the whole component element.
+\noteJB{Can we just use two (not excluded) cases one for IB on boundary of $c$ second for CI on boundary of $b$ ?}
+
+We also see that the candidate pairs are of three types: $(c, b')$, $(c', b)$, $(c',b')$
+from which only the first one goes into the bulk queue, trying to cover current component element $c$ before we proceed to the next one.
+
+When the pair is taken from either of the queues we check if the pair was computed and possibly skip it. 
+To this end every component element keeps a hash of the bulk elements with which we have called the intersection test.
 
@@
 
-Then we empty the two queues. 
-We pop out new candidate pairs from the \emph{bulk queue} as long as it is not empty and for every new intersection computed, we repeat the previous part (means that we can further fill both queues).
-The \emph{bulk queue} is empty when the component element is fully covered by bulk elements, or
-when there is no bulk neighbor to which we can advance.
-Then we can pop a new candidate pair from \emph{component prolongation queue} and process it.
-When both queues are empty, all intersections of a component have been found and we start over by looking for the first intersection of another component.
-
-\notePE{We can discuss further the covering/closing of the elements and component numbering which is not tested
-thoroughly at the moment.
+%Then we empty the two queues. 
+%We pop out new candidate pairs from the \emph{bulk queue} as long as it is not empty and for every new intersection computed, 
+%we repeat the previous part (means that we can further fill both queues).
+%The \emph{bulk queue} is empty when the component element is fully covered by bulk elements, or
+%when there is no bulk neighbor to which we can advance.
+%Then we can pop a new candidate pair from \emph{component prolongation queue} and process it.
+%When both queues are empty, all intersections of a component have been found and we start over by looking for the first intersection of another component.
+
+%\notePE{We can discuss further the covering/closing of the elements and component numbering which is not tested
+%thoroughly at the moment.
 We can show in a figure the case in 'prolong\_meshes\_13d/prolongation\_13d\_04.msh', where actually 4 components are found (therefore bulk is defined as connected 3d elements).}

### 2016-10-01 paper_intersections.tex
Minor corrections in 23d.

@@
 Computation of IP consists of three stages: calculation of side-tetrahedron ICs (Section \ref{sec:sides}), 
-calculation of edge-triangle ICs (Section~\ref{sec:edges}), oredering of ICs (Section~\ref{sec:ordering}).
-The intersection corners are appended to the list $I$ as they are computed however their order on the polygon boundary is 
+calculation of edge-triangle ICs (Section~\ref{sec:edges}), ordering of ICs (Section~\ref{sec:ordering}).
+The intersection corners are appended to the list $I$ as they are computed, however their order on the polygon boundary is 
 defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
@@
 way as is the order and orientation of the sides of $S_2$, that is counterclockwise around the interior with normal pointing to us.
-There are special cases when the IP is degenerated to a line or a point. If some IC may possibly be part of the such degenerated IP we put it into the list $J$.
+There are special cases when the IP is degenerated to a line or a point. 
+\notePE{next sentence: how should I understand 'may possibly be'; 'an IC' instead of 'some IC'}
+If some IC may possibly be part of the such degenerated IP we put it into the list $J$.
 
@@
 %        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
-        \nllabel{line:m4_object}
-        $p$ lies on $x\in M_3$\;
-        \lIf{$p$ lies at vertex $v$ of $S_3$}{$x=v$}
-        \uIf{$p$ is first in $L$}{
+        $p$ lies on $x\in M_3$\; \nllabel{line:m4_object}
+        \lIf{$p$ lies at the vertex $v$ of $S_3$}{$x=v$}
+        \uIf{$p$ is the first in $L$}{
             $F_g[x] = p$,\ $F_p[p] = s$\;
@@
 and computes the line-tetrahedron intersection $L$.
-If the side is just touching $S_3$ and we get $L$ with single IC. These ICs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} 
+If the side is just touching $S_3$, we get $L$ with a single IC. These ICs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} 
 with better topological information, however this is not the case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$.
 To this end we save the IC into separate list $J$ and skip filling of the connection tables.
+\notePE{here it is weird... there is no line appending the IC into resulting list.. Which is the resulting list??
+I find the reference to 'line:one side loop' also incorrect..}
 In the regular case, we process each of the two ICs in $L$ (loop on line \ref{line:one side loop}). The IC $p$ is added to the list $I$,
@@
 of the IC if it lies on edge or at vertex of $S_3$. The condition at the same line deals with the case that two sides of $S_3$ intersect 
-the same object $x\in M_3$, in such case the back-link is unnecessary and would overwrite the correct link set by previous IC.
+the same object $x\in M_3$, in such case the backlink is unnecessary and would overwrite the correct link set by previous IC.
 
@@
     }    
-    \uIf{ $p$ is on boundary of $S_2$ }{
+    \uIf{ $p$ is on the boundary of $S_2$ }{
          $p$ lies on edge or at vertex $x \in M_3$\;
@@
 Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
-First, the intersection $L[e]$ is evaluated for every edge $e$. The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position on vertex or edge of $S_3$ already computed 
-in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping edges with none or degenerate $L[e]$.
-For every IC $p=L[e]$ we first get its (generalized) faces that would appear before and after the IC on IP assuming that $p$ is inside $S_2$.
-
-For an IC inside the edge $e$
-the function \emph{edge faces}, returns its adjacent faces $f_0$, $f_1$ (see Fig. \ref{fig:edge_faces}). 
-Their order is given by the sign permuted inner products in 1d-2d intersection. The order of faces match 
+First, the intersection $L[e]$ is evaluated for every edge $e$.
+The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position at the vertex or on the edge of $S_3$ already computed
+in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping the edges with none or degenerate $L[e]$.
+For every IC $p=L[e]$ we first get its (generalized) faces that would appear before and after the IC on IP, assuming that $p$ is inside $S_2$.
+
+The function \emph{edge faces} returns the adjacent faces $f_0$, $f_1$ to the edge $e$, on which the IC lies (see the situation in \fig{fig:edge_faces}). 
+The faces are sorted using the sign of the permuted inner product in 1d-2d intersection. The order of faces matches 
 the order of sides of IP if the sign is negative. If the sign is positive the function \emph{edge faces} returns face pair $(f_1, f_0)$.
@@
 It returns a pair of generalized faces (face or edge) adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$. 
-If IC $p$ is inside $S_2$, we add it into $I$ and set the connection tables (line \ref{line:insideS2}). However,
+If IC $p$ is inside $S_2$, we add it into $I$ and set the connection tables (line \ref{line:insideS2}). 
+However,
 if $p$ is on boundary of $S_2$ it is already in $I$. Denoting $x$ the \nface of $S_3$ the IC lies on, we use the back-link from $x$ to 

### 2016-10-01 paper_intersections.tex
Improve prolongation scheme, delete pdf.
Improve advancing front algorithm.

@@
 \usepackage{subfig}
+
+% alphabetical enumeration
+\usepackage{enumitem}
 
@@
 
-\section{Global mesh intersection algorithm}
+\section{Global Mesh Intersection Algorithm}
 \label{sec:front_advancing}
 Having the algorithms for element-element intersections we can proceed to the mesh intersection algorithm. 
-We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) and then the 1d-2d and 2d-2d intersections use the 3d mesh
-to get the intersection pair candidates.  Element intersections for the particular component and bulk mesh 
+We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) and then the 1d-2d and 2d-2d intersections using the 3d mesh to get the intersection pair candidates.
+Element intersections for the particular component and bulk mesh 
 are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
@@
 \paragraph{Initialization}
-We choose an arbitrary element of the component mesh and check it intersection with all elements of the bulk mesh.
-The process is accelerated by computing the axis aligned bounding box (AABB) for every element and use intersection of the bounding boxes
+We choose an arbitrary element of the component mesh and check its intersection with all elements of the bulk mesh.
+This process is accelerated by computing the axis aligned bounding box (AABB) for every element and use intersection of the bounding boxes
 as a fast indicator for possible intersection of the elements. This step takes $O(N)$ time with respect to the number of elements of the bulk mesh $N$.
-For the small number of components $k$ and if they are contained inside the bulk mesh the total time of initialization may be still linear $O(kn)$. However,
-for more complex cases we organize the bounding boxes of the bulk mesh into the bounding interval hierarchy (BIH) \cite{EGWR:EGSR06:139-149} 
+If the number of components $k$ is small and if the components are contained inside the bulk mesh, the total time of initialization may still be linear $O(kn)$ \notePE{I believe you ment $O(kN)$ here}.
+However,
+for more complex cases we organize the bounding boxes of the bulk mesh into the bounding interval hierarchy (BIH) \cite{EGWR:EGSR06:139-149},
 a data structure in principle equivalent 
@@
 \paragraph{Advancing Front Method}
-The advancing front algorithm requires and employ the neigbouring information for the elements within the component as well as within the bulk mesh.
+The advancing front method requires the neigbouring information for the elements within the components as well as within the bulk mesh.
 It can be viewed as the breadth first search algorithm for a graph which vertices are intersection polygons and edges are sides shared by
-two polygons. Side every side of IP is on the boundary of either component or the bulk element we can distinguish bulk and component edges and correspondingly 
-the \emph{bulk queue} and the \emph{component queue}.
-
+two polygons.
+Since every side of IP is on the boundary of either component or bulk element, we can distinguish the bulk and component edges.
+Correspondingly, we save new candidate pairs into a~\emph{bulk queue} or
+a~\emph{component queue} to be subsequently processed later.
+The scheme of the advancing front algorithm is displayed by the scheme in \fig{fig:prolongation},
+where the queues are represented by the yellow boxes.
 %
@@
   \centering    
-    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip.pdf}
+    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_new.pdf}
   \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
@@
 
-The scheme of the advancing front algorithm is displayed by the scheme in \fig{fig:prolongation}. 
-The main idea is to compute intersections for a component element with all possible bulk elements, and then move to a~next neighboring component element. 
-So the bulk queue is emptied before the component queue (see yellow boxes).
-
-On the input we consider a candidate pair provided be the initialization (top-left corner).
-Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
+The key idea behind the two queues is to compute intersections for a component element with all possible bulk elements at first, and then move to a~next neighboring component element.
+So the bulk queue is emptied before the component queue.
+
+On the input, we consider a candidate pair provided by the initialization (the top-left corner of the scheme).
+If a nonempty intersection is found, we look for new candidate pairs among the neighboring elements
+(see the white block 'Cycle over ICs').
 Therefore, we iterate over the intersection corners and further exploit their topological position on the component element $c$ and the bulk element $b$.
 There are 3 possible cases (applies both for 1d-3d and 2d-3d), how the intersection might be prolonged:
-\begin{itemize}
+\begin{enumerate}[label=(\alph*)]
     \item \textbf{IC on the boundary of $c$  and inside $b$} \\
             We find all the sides $S$ coincident with the \nface of $c$ on which IC lies. Then we get all component
-            elements $C'$ neighbouring with $c$ over any side$s\in S$. And finally, we push all pairs $(c',b)$, $c'\in C'$ 
+            elements $C'$ neighboring with $c$ over any side $s\in S$. And finally, we push all pairs $(c',b)$, $c'\in C'$ 
             into the component queue.
-            Note, that $c$ can have more then one neighbour component elements over the single side $s$, i.e. branches are allowed.
+            Note that $c$ can have more then one neighbour component elements over the single side $s$, i.e. branches are allowed.
+    \item \textbf{IC inside of $c$ anf on the boundary of $b$} \label{enum:prolong2}\\
+            We find all the faces $F$ coincident with the \nface of $b$ on which IC lies. 
+            Then we get all bulk elements $B'$ neighboring with $b$ over any face $f\in F$,
+            analogically to the previous case.
+            Finally, we push the new candidate pairs $(c, b')$, $b'\in B'$ into the bulk queue.
     \item \textbf{IC on the boundary of both $c$ and $b$} \\
-            We find all the faces $F$ coincident with the \nface of $b$ on which IC lies. 
-            Then we get all neighbours $B'$ through all faces in $F$ as in the previous case.
-            We push pairs $(c, b')$, $b'\in B'$ into the bulk queue and pairs $(c', b')$, $c'\in C'$, $b'\in B'$ into the component queue.
-    \item \textbf{IC inside of $c$ anf on the boundary of $b$)} \\
-            We proceed as in previous case, and push pairs $(c, b')$, $b'\in B'$ into the bulk queue.
-\end{itemize}
-\noteJB{Can we just use two (not excluded) cases one for IB on boundary of $c$ second for CI on boundary of $b$ ?}
-
-We also see that the candidate pairs are of three types: $(c, b')$, $(c', b)$, $(c',b')$
-from which only the first one goes into the bulk queue, trying to cover current component element $c$ before we proceed to the next one.
-
-When the pair is taken from either of the queues we check if the pair was computed and possibly skip it. 
+            This situation includes both previously described cases. Therefore, we obtain new candidate pairs
+            $(c', b)$, $c'\in C'$ and $(c, b')$, $b'\in B'$ and push them into the component queue and the bulk queue, respectively.
+\end{enumerate}
+% \noteJB{Can we just use two (not excluded) cases one for IB on boundary of $c$ second for CI on boundary of $b$ ?}
+When the pair is taken from either of the queues, we check whether the pair has been already computed and possibly skip it. 
 To this end every component element keeps a hash of the bulk elements with which we have called the intersection test.
+
+At the end, we see that the candidate pairs are of two types: $(c, b')$ and $(c', b)$,
+from which the first one goes into the bulk queue, trying to fully cover current component element 
+$c$ before we proceed to the next one. We are able recognize the case when the component element 
+does not lie inside the bulk elements with its full volume -- we end up in situation \ref{enum:prolong2},
+but there are no more bulk neighboring elements to prolong the intersection to. Then we mark this component
+element as \emph{open}, so it can be later found by initialization algorithm and possibly
+covered by other bulk elements but as different component.
 

### 2016-10-01 paper_intersections.tex
front tracking algorithm

--- 2016-10-01 paper_intersections.tex
@@
 non-matching grid \sep
-mesh intersections \sep
+non-conforming mesh \sep
+mesh intersection \sep
 mixed-dimensional mesh \sep
@@
 \label{sec:front_advancing}
-Having the algorithms for element-element intersections we can proceed to the mesh intersection algorithm. 
-We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) and then the 1d-2d and 2d-2d intersections use the 3d mesh
-to get the intersection pair candidates.  Element intersections for the particular component and bulk mesh 
-are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
+Having the algorithms for element-element intersections at our disposal we can proceed to the mesh intersection algorithm. 
+We consider the composed mesh $\mathcal T$ containing the 3d mesh $\mathcal T_1$ that we shall call a bulk mesh $\mathcal T_b$. Any other 
+mesh $\mathcal T_i$, with dimensions $d_i < 3$, $i=1,\dots, N_{\mathcal T}$ we shall call a component mesh. 
+We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) using the advancing front algorithm which is described in Sections 
+\ref{sec:initialization}, \ref{sec:front} and then the 1d-2d and 2d-2d 
+intersections use the bulk mesh to get the intersection pair candidates, the Section \ref{sec:compnents}.
+
+Let us consider a single pair of the component mesh $\mathcal T_c$ and the bulk mesh $\mathcal T_b$. 
+Element intersections for this pair of meshes are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
 secondly, we prolong the intersection by investigating neighbouring elements (front tracking).
@@
 
-\paragraph{Initialization}
+\subsection{Initialization}
+\label{sec:initialization}
+\noteJB{Possibly move this afte Advancing front section since it is in fact single step in the main loop.}
 We choose an arbitrary element of the component mesh and check it intersection with all elements of the bulk mesh.
@@
 
-\paragraph{Advancing Front Method}
-The advancing front algorithm requires and employ the neigbouring information for the elements within the component as well as within the bulk mesh.
-It can be viewed as the breadth first search algorithm for a graph which vertices are intersection polygons and edges are sides shared by
-two polygons. Side every side of IP is on the boundary of either component or the bulk element we can distinguish bulk and component edges and correspondingly 
-the \emph{bulk queue} and the \emph{component queue}.
+\subsection{Advancing Front Method}
+\label{front}
+The advancing front algorithm requires and employ the neigbouring information for the elements within the component mesh $\mathcal T_c$ 
+as well as within the bulk mesh $\mathcal T_b$. It can be viewed as the breadth first search algorithm for a graph where graph vertices are 
+intersection polygons and graph edges are sides shared by two polygons. Side every side of IP is on the boundary of either 
+component or the bulk element, we can distinguish bulk and component edges and correspondingly the \emph{component queue} $Q_c$ and the \emph{bulk queue} $Q_b$.
+
+\begin{algorithm}
+  \caption{Advancing front algorithm}  
+  \label{algo:advancing front}
+
+  \SetKw{return}{return}
+  \SetKw{edgefaces}{edge faces}
+  \DontPrintSemicolon
+  %\KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
+  %\KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
+  mark all $c\in \mathcal T_c$ unvisited\;
+  \For{unvisited $c\in\mathcal T_c$}{
+    mark $c$ visited\;
+    find list $L$ of intersection candidates\;
+    append $L$ to queue $Q_c$\;
+    \For{$(c, b) \in Q_c$}{
+        mark $c$ visited\;
+        push $(c,b)$ into $Q_b$\;
+        \For{$(c, b) \in Q_b$}{            
+            list $I$ of ICs of $(c,b)$ intersection\;
+            \For{$p\in I$}{
+                \If{$p$ on boundary of $c$}{
+                    get neighbours $C'$\;
+                    \tcp{check pair if unvisited, mark visited}
+                    enqueue $(c', b)$ into $Q_c$ for all $c'\in C'$ 
+                }
+                \If{$p$ on boundary of $b$}{
+                    get neighbours $B'$\;
+                    \If{$B'$ is empty and not on boundary of $c$}{mark $c$ unvisited}
+                    enqueue $(c, b')$ into $Q_b$ for all $b'\in B'$ 
+                }                
+                \noteJB{Questionable}\;
+                \If{$p$ on both boundaries}{
+                    enqueue $(c', b')$ into $Q_c$ for all $b'\in B',\ c'\in C'$ 
+                }
+            }
+
+        }
+    }
+  }
+
+\end{algorithm}
 
@@
     \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip.pdf}
+    %\input{\figpath prolongation_scheme_ip.pdf_tex}
   \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
@@
 The scheme of the advancing front algorithm is displayed by the scheme in \fig{fig:prolongation}. 
+First, we mark all component elements $c\in\mathcal T_c$ unvisited. The for every unvisited element $c\in \mathcal T_c$, we mark it visited
+then find intersection candidate pair $(c,b)$, $b\in\mathcal T_b$ 
+and initialize the front tracking for every unvisited .
 The main idea is to compute intersections for a component element with all possible bulk elements, and then move to a~next neighboring component element. 
@@
 To this end every component element keeps a hash of the bulk elements with which we have called the intersection test.
+
+\subsection{Intersections between component meshes}
+\label{sec:components}
 

### 2016-10-01 paper_intersections.tex

--- 2016-10-01 paper_intersections.tex
@@
 \label{sec:front_advancing}
-Having the algorithms for element-element intersections we can proceed to the mesh intersection algorithm. 
-We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) and then the 1d-2d and 2d-2d intersections using the 3d mesh to get the intersection pair candidates.
-Element intersections for the particular component and bulk mesh 
-are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
+Having the algorithms for element-element intersections at our disposal we can proceed to the mesh intersection algorithm. 
+We consider the composed mesh $\mathcal T$ containing the 3d mesh $\mathcal T_1$ that we shall call a bulk mesh $\mathcal T_b$. Any other 
+mesh $\mathcal T_i$, with dimensions $d_i < 3$, $i=1,\dots, N_{\mathcal T}$ we shall call a component mesh. 
+We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) using the advancing front algorithm which is described in Sections 
+\ref{sec:initialization}, \ref{sec:front} and then the 1d-2d and 2d-2d 
+intersections use the bulk mesh to get the intersection pair candidates, the Section \ref{sec:compnents}.
+
+Let us consider a single pair of the component mesh $\mathcal T_c$ and the bulk mesh $\mathcal T_b$. 
+Element intersections for this pair of meshes are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
 secondly, we prolong the intersection by investigating neighbouring elements (front tracking).
@@
 
-\paragraph{Initialization}
+\subsection{Initialization}
+\label{sec:initialization}
+\noteJB{Possibly move this afte Advancing front section since it is in fact single step in the main loop.}
 We choose an arbitrary element of the component mesh and check its intersection with all elements of the bulk mesh.
@@
 as a fast indicator for possible intersection of the elements. This step takes $O(N)$ time with respect to the number of elements of the bulk mesh $N$.
-If the number of components $k$ is small and if the components are contained inside the bulk mesh, the total time of initialization may still be linear $O(kn)$ \notePE{I believe you ment $O(kN)$ here}.
-However,
+If the number of components $k$ is small and if the components are contained inside the bulk mesh, the total time of initialization may still be linear $O(kN)$. However,
 for more complex cases we organize the bounding boxes of the bulk mesh into the bounding interval hierarchy (BIH) \cite{EGWR:EGSR06:139-149},
@@
 
-\paragraph{Advancing Front Method}
-The advancing front method requires the neigbouring information for the elements within the components as well as within the bulk mesh.
-It can be viewed as the breadth first search algorithm for a graph which vertices are intersection polygons and edges are sides shared by
-two polygons.
-Since every side of IP is on the boundary of either component or bulk element, we can distinguish the bulk and component edges.
-Correspondingly, we save new candidate pairs into a~\emph{bulk queue} or
-a~\emph{component queue} to be subsequently processed later.
-The scheme of the advancing front algorithm is displayed by the scheme in \fig{fig:prolongation},
-where the queues are represented by the yellow boxes.
+\subsection{Advancing Front Method}
+\label{front}
+The advancing front algorithm requires the neigbouring information for the elements within the component mesh $\mathcal T_c$ 
+as well as within the bulk mesh $\mathcal T_b$. It can be viewed as the breadth first search algorithm for a graph where graph vertices are 
+intersection polygons and graph edges are sides shared by two polygons. Since every side of IP is on the boundary of either 
+the component element or the bulk element, we can distinguish bulk and component edges. 
+Correspondingly the candidate paris are enqueued into \emph{component queue} $Q_c$ and the \emph{bulk queue} $Q_b$, respectively.
+
+\begin{algorithm}
+  \caption{Advancing front algorithm}  
+  \label{algo:advancing front}
+
+  \SetKw{return}{return}
+  \SetKw{edgefaces}{edge faces}
+  \DontPrintSemicolon
+  %\KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
+  %\KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
+  mark all $c\in \mathcal T_c$ unvisited\;
+  \For{unvisited $c\in\mathcal T_c$}{
+    mark $c$ visited\;
+    find list $L$ of intersection candidates\;
+    append $L$ to queue $Q_c$\;
+    \For{$(c, b) \in Q_c$}{
+        mark $c$ visited\;
+        push $(c,b)$ into $Q_b$\;
+        \For{$(c, b) \in Q_b$}{            
+            list $I$ of ICs of $(c,b)$ intersection\;
+            \For{$p\in I$}{
+                \If{$p$ on boundary of $c$}{
+                    get neighbours $C'$\;
+                    \tcp{check pair if unvisited, mark visited}
+                    enqueue $(c', b)$ into $Q_c$ for all $c'\in C'$ 
+                }
+                \If{$p$ on boundary of $b$}{
+                    get neighbours $B'$\;
+                    \If{$B'$ is empty and not on boundary of $c$}{mark $c$ unvisited}
+                    enqueue $(c, b')$ into $Q_b$ for all $b'\in B'$ 
+                }                
+                \noteJB{Questionable}\;
+                \If{$p$ on both boundaries}{
+                    enqueue $(c', b')$ into $Q_c$ for all $b'\in B',\ c'\in C'$ 
+                }
+            }
+
+        }
+    }
+  }
+
+\end{algorithm}
+
 %
@@
 \end{figure}
+
+First, we mark all component elements $c\in\mathcal T_c$ unvisited. The for every unvisited element $c\in \mathcal T_c$, we mark it visited
+then find intersection candidate pair $(c,b)$, $b\in\mathcal T_b$ 
+and initialize the front tracking for every unvisited .
 
@@
 covered by other bulk elements but as different component.
+
+\subsection{Intersections between component meshes}
+\label{sec:components}
 

### 2016-10-01 paper_intersections.tex
Theoretical FLOPS counts.

@@
 \subsection{Intersection Line-Triangle (1d-2d)}
+\label{sec:1d-2d}
 \notePE{I would stick to chosen notation - triangle $S_2$, and possibly renamed side $s_i$...}
@@
 In the beginning, we provide some software development related information.
-Then we compare the performance of our algorithms for element intersections with other approaches.
+Then we compare the performance of our algorithms for element intersections with other approaches \noteJB{they are all ours}.
 Next we shall compare our algorithms with different initialization phase (candidate pairs search),
@@
 \subsection{Software Flow123d}
-The intersection algorithms are implemented as a part of the software Flow123d~\cite{flow123d}.
-The software is developed with an open source licence at the Technical University in Liberec,
-the implementation is based mostly on C++ language. 
-Flow123d provides models for (un)saturated groundwater flow, transport of solutes possibly
-coupled with first order reactions and heat transfer in fractured porous media. 
-The speciality of the software is that it enables
-computations on complex meshes consisting of simplicial elements of different dimensions. However,
+The implementation of the presented algorithms is part of the open source software Flow123d~\cite{flow123d}.
+The C++ is used as principal language. Flow123d provides models for saturated and unsaturated groundwater flow,
+soulute transport with sorption, and  heat transfer. Mixed finite elements, finite volumes, and discontinuous Galerkin method are 
+used. All equations are consistently formulated for meshes of mixed dimensions.  However,
 non-matching meshes are at the moment available only in experimental 1d-2d flow model, using mortar like coupling.
@@
 % in Flow123d.
-
-\notePE{check NGH.. how to refer to NGH later?}
-Currently, there is also another implementation of the element intersections in the software (we shall refer to
-it later as \ngh). It uses standard means of analytic geometry for computation of intersections line-line and line-plane.
-This leads to solving a large amount of small linear systems of equations.
-This algorithm also does not provide us barycentric coordinates and topological position of ICs.
-At last, the algorithm cannot handle all of the special cases.
-We must note, that neither the old algorithms nor the new ones are optimised at the moment.
-
-Note, that we use Armadillo~\cite{armadillo_2016}, a C++ linear algebra library, for linear algebra operations.
-Most importantly, all coordinates are represented as Armadillo vectors, so we can use dot and cross product and further vector and matrix operations provided by the library.
+Part of the software is also a legacy code for element intersections that we refer to as \ngh.
+
+% \notePE{check NGH.. how to refer to NGH later?}
+% Currently, there is also another implementation of the element intersections in the software (we shall refer to
+% it later as \ngh). \noteJB{Desribe later different ways how to compute line-tringle intersection}. 
+% It uses standard means of analytic geometry for computation of intersections line-line and line-plane.
+% This leads to solving a large amount of small linear systems of equations. \noteJB{And computing orientation determinants}
+% This algorithm also does not provide us barycentric coordinates and topological position of ICs. \noteJB{Although it could be done in principle.}
+% At last, the algorithm cannot handle all of the special cases.
+% We must note, that neither the old algorithms nor the new ones are particularly optimised at the moment.
+
+%Note, that we use Armadillo~\cite{armadillo_2016}, a C++ linear algebra library, for linear algebra operations. 
+%Most importantly, all coordinates are represented as Armadillo vectors, so we can use dot and cross product and 
+%further vector and matrix operations provided by the library.
+
+\subsection{Theoretical comparison}
+Before presenting the results of our benchmarks, let us try to estimate the number of arithmetic operations performed during 1d-3d and 2d-3d element intersections
+as we use different algorithms for the elementary line-triangle intersection. We consider 4 algorithms for the line-triangle intersections: \plucker algorithm 
+described in Section \ref{sec:1d-2d}, the legacy code \ngh, the plane clipping algorithm due to Haines \cite{haines_fast_1991}, the minimum storage
+algorithm due to Möller and Trumbore (MT) \cite{moller_fast_1997}. Raw numbers of arithemtic operations are summarized in Table \ref{tab:fundamental_flops}.
+For the \plucker and \ngh we count FLOPS from the implementation of individual intersection algorithms, for Haines and MT we estimated FLOPS in theoretical 
+implementation. In particular we account for reuse of the calculations in \plucker and Haines algorithms. Conclusions from this census are:
+algorithms based on the \plucker coordinates should be competitive with state of art algorithms in the case of 1d-3d and 2d-3d intersections. The expected performance
+for the 1d-2d case seems to be poor however these intersections are computed after 1d-3d and 2d-3d so the \plucker coordinates may be reused, then we get 
+quite competitive $45$ FLOPS. Similarly we may expect better times in remaining two intersection cases when we account for the reuse of calculation between elements.
+Compared to the legacy code \ngh the \plucker algorithm for 1d-3d should be about $2.5\times$ faster and the 2d-3d about $5\times$ faster.
+
+\noteJB{Need better timing for \plucker with respect to NGH in 
+2d-3d  case. Could it be due to polygon tracing?}
+
+\begin{table}[!htb]
+    \caption{Raw number of FLOPS used by different intersection algorithms.}    
+    \label{tab:fundamental_flops}
+    \centering
+    \renewcommand{\arraystretch}{1.2}
+    \begin{tabular}[b]{l|lll}
+            algorithm           & 1d-2d         & 1d-3d         & 2d-3d \\                      
+            \hline\\
+            \plucker           & 92            & 198           & 426\\
+            Haines              & 51            & 177           & 469\\
+            Moller and Trumbore & 42            & 168           & 756\\
+            \ngh                & 119           & 476           & 2142\\
+    \end{tabular}
+
+\end{table}
 
@@
 
-\begin{table}[!htb]
-    \centering
-    \renewcommand{\arraystretch}{1.2}
-    \begin{tabular}[b]{l|l}
-            algorithm, 2d-3d& FLOPs\\
-                      & estimate\\
-            \hline\\
-            parametric plane & 585\\
-            normal plane (reuse) & 765\\
-            Moller and Trumbore & 783\\
-            Pl\"ucker (reuse) & 306
-    \end{tabular}
-    \caption{Estimation of floating point operations count and comparison of different approaches.
-             Only 2d-3d case considered.}
-    \label{tab:fundamental_flops}
-    \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
-\end{table}
-
 \begin{figure}[!htb]
@@
 
-\cite{sukumar_extended_2000} - Use {\emph geometric predicates} incircle and orientation. Use mesh of bounding boxes to search for intersection candidates. 
-Only use point queries for all vertices of triangle/tetrahedron. Use compatible partitioning of elements by the crack elements.
-
-\cite{boon_robust_2016} Robust discretization of porous media. Complete error analysis with mortar non-compatible case. Seems they use normal fluxes accros
-fracture instead of pressure traces. This allows conforming discretization and error results.
-
-\cite{reichenberger_mixed-dimensional_2006} Finite volume method, fully implicit two phase flow. Cite usage of FRAC3D generator.
-
-\cite{sladkova_bakalarka} Space-time DG with adaptive mesh, need integration of product of functions on different meshes (in 2d). An algorithm 
-for computing triangle-triangle intersections in 2d.
-
-\cite{pichot_generalized_2012} DFN + MHFEM. Mortar method for intersections. Focused on formulation not on intersections.
-
-\cite{flemisch_non-matching_2012} (Barbara) Mortad, non=matching, acustics. Theory, structured gird case. No complex intersections.
-
-\cite{mustapha_hybrid_2014} Patent for curiosity.
-
-\cite{mittal_immersed_2005} Immersed boundary. ??
-
-\cite{owen_survey_1998} ??
-
-\cite{kuznetsov_overlapping_1998}
-
-\cite{platis_fast_2003} Original algorithm for line-thetrahedra intersections.
-
-\cite{haines_fast_1991} Line-convex Polyhedra intersections using generalisation of line-clipping algorithm
-
-USED:
-\cite{massing_efficient_2013} - Implementation of the Nitche method in Fenics. They need 2d-3d intersections, but only for distribution od quadrature points. 
-So they do not store whole intersection data, but only the quad points. The boundary of one domain is partitioned into intersections with elements of the other domain.
-Use {\\emph collision relations} ( pairs of faces of boundary and elmements of the background mesh) and {\emph collision maps} 
-( map face to all intersections and background element to all intersections, can be constructed from the collision relation), They cite books from computer graphics ..
-Mention geometric predicates. Present algorithms for:  find intersection candidates, comput intersections, integrate over complex domains.
-
-\cite{elsheikh_reliable_2012} Claim to provide robust algorithm covering all tiangle-trinagle degenerate cases. Basic idea is the same as our: use some tree 
-(Binary SPace Tree) structure to find initial point on intersection curve and trace the curve in both directions. Quite clever data structure for the mesh. Adaptive precision 
-geometric predicates. Store topological information about the intersection corners (point on triangle, edge, vertex). Resolve various degenerate cases, 
-dicuss mesh optimization after subdivision.
-
-\cite{gander_algorithm_2013} Full algorithm for 2d=3d called PANG. Implemented in DUNE in 2010 (Bastian). Other software (Hecht, MpCCI). 
-Triangle-Triangle and Tetra-Triangle intersections done similarly as in aur approach: set of points including vertices and then sort them countercolckwise.
-Local intersection algorithm do not provide neighbouring information so the traversal algorithm do not use it.
-
-Review of algorithms: \cite{gander_algorithm_2009}
-
-\cite{bournival_mesh-geometry_2008} Application of mixed-dimensional approach in mechanics. Beam and shell elements ...
+% \cite{sukumar_extended_2000} - Use {\emph geometric predicates} incircle and orientation. Use mesh of bounding boxes to search for intersection candidates. 
+% Only use point queries for all vertices of triangle/tetrahedron. Use compatible partitioning of elements by the crack elements.
+% 
+% \cite{boon_robust_2016} Robust discretization of porous media. Complete error analysis with mortar non-compatible case. Seems they use normal fluxes accros
+% fracture instead of pressure traces. This allows conforming discretization and error results.
+% 
+% \cite{reichenberger_mixed-dimensional_2006} Finite volume method, fully implicit two phase flow. Cite usage of FRAC3D generator. 
+% 
+% \cite{sladkova_bakalarka} Space-time DG with adaptive mesh, need integration of product of functions on different meshes (in 2d). An algorithm 
+% for computing triangle-triangle intersections in 2d.
+% 
+% \cite{pichot_generalized_2012} DFN + MHFEM. Mortar method for intersections. Focused on formulation not on intersections. 
+% 
+% \cite{flemisch_non-matching_2012} (Barbara) Mortad, non=matching, acustics. Theory, structured gird case. No complex intersections.
+% 
+% \cite{mustapha_hybrid_2014} Patent for curiosity.
+% 
+% \cite{mittal_immersed_2005} Immersed boundary. ??
+% 
+% \cite{owen_survey_1998} ??
+% 
+% \cite{kuznetsov_overlapping_1998}
+% 
+% \cite{platis_fast_2003} Original algorithm for line-thetrahedra intersections.
+% 
+% \cite{haines_fast_1991} Line-convex Polyhedra intersections using generalisation of line-clipping algorithm
+% 
+% 
+% USED:
+% \cite{massing_efficient_2013} - Implementation of the Nitche method in Fenics. They need 2d-3d intersections, but only for distribution od quadrature points. 
+% So they do not store whole intersection data, but only the quad points. The boundary of one domain is partitioned into intersections with elements of the other domain.
+% Use {\\emph collision relations} ( pairs of faces of boundary and elmements of the background mesh) and {\emph collision maps} 
+% ( map face to all intersections and background element to all intersections, can be constructed from the collision relation), They cite books from computer graphics ..
+% Mention geometric predicates. Present algorithms for:  find intersection candidates, comput intersections, integrate over complex domains.
+% 
+% \cite{elsheikh_reliable_2012} Claim to provide robust algorithm covering all tiangle-trinagle degenerate cases. Basic idea is the same as our: use some tree 
+% (Binary SPace Tree) structure to find initial point on intersection curve and trace the curve in both directions. Quite clever data structure for the mesh. Adaptive precision 
+% geometric predicates. Store topological information about the intersection corners (point on triangle, edge, vertex). Resolve various degenerate cases, 
+% dicuss mesh optimization after subdivision.
+% 
+% 
+% \cite{gander_algorithm_2013} Full algorithm for 2d=3d called PANG. Implemented in DUNE in 2010 (Bastian). Other software (Hecht, MpCCI). 
+% Triangle-Triangle and Tetra-Triangle intersections done similarly as in aur approach: set of points including vertices and then sort them countercolckwise.
+% Local intersection algorithm do not provide neighbouring information so the traversal algorithm do not use it.
+% 
+% Review of algorithms: \cite{gander_algorithm_2009}
+% 
+% 
+% \cite{bournival_mesh-geometry_2008} Application of mixed-dimensional approach in mechanics. Beam and shell elements ...
 

### 2016-10-01 paper_intersections.tex
Improve tracking alg, comment also on component numbers.

--- 2016-10-01 paper_intersections.tex
@@
 \ref{sec:initialization}, \ref{sec:front} and then the 1d-2d and 2d-2d 
-intersections use the bulk mesh to get the intersection pair candidates, the Section \ref{sec:compnents}.
+intersections use the bulk mesh to get the intersection pair candidates, the Section \ref{sec:components}.
 
@@
 %     \item\label{en:first} Get next unprocessed component element $k$.
-%     \item Find intersection candidates $\mathcal K$ in bulk mesh (3d elements).
+%     \item Find intersection candidates $\mathcal K$ in bulk mesh (3d elements).W
 %     \item \label{en:q2}For $K\in \mathcal K$ compute intersection $(k, K)$.  
@@
 \subsection{Advancing Front Method}
-\label{front}
+\label{sec:front}
 The advancing front algorithm requires the neigbouring information for the elements within the component mesh $\mathcal T_c$ 
@@
 the component element or the bulk element, we can distinguish bulk and component edges. 
-Correspondingly the candidate paris are enqueued into \emph{component queue} $Q_c$ and the \emph{bulk queue} $Q_b$, respectively.
-
+Correspondingly the candidate pairs are enqueued into \emph{component queue} $Q_c$ and the \emph{bulk queue} $Q_b$, respectively.
+
+The key idea behind the two queues is to compute intersections for a component element with all possible bulk elements at first, and then move to a~next neighboring component element.
+So the bulk queue is emptied before the component queue.
 \begin{algorithm}
@@
   mark all $c\in \mathcal T_c$ unvisited\;
+  $\gamma=0$ \tcp*{component number}
   \For{unvisited $c\in\mathcal T_c$}{
-    mark $c$ visited\;
+    increment $\gamma$\;
     find list $L$ of intersection candidates\;
@@
             list $I$ of ICs of $(c,b)$ intersection\;
+            set $\gamma$ into IP\;
             \For{$p\in I$}{
@@
                 }                
-                \noteJB{Questionable}\;
-                \If{$p$ on both boundaries}{
-                    enqueue $(c', b')$ into $Q_c$ for all $b'\in B',\ c'\in C'$ 
-                }
+%                 \noteJB{Questionable}\;
+%                 \If{$p$ on both boundaries}{
+%                     enqueue $(c', b')$ into $Q_c$ for all $b'\in B',\ c'\in C'$ 
+%                 }
             }
@@
   \centering    
-    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_new.pdf}
+    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_pe_new.pdf}
   \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
@@
 
-First, we mark all component elements $c\in\mathcal T_c$ unvisited. The for every unvisited element $c\in \mathcal T_c$, we mark it visited
-then find intersection candidate pair $(c,b)$, $b\in\mathcal T_b$ 
-and initialize the front tracking for every unvisited .
-
-The key idea behind the two queues is to compute intersections for a component element with all possible bulk elements at first, and then move to a~next neighboring component element.
-So the bulk queue is emptied before the component queue.
-
-On the input, we consider a candidate pair provided by the initialization (the top-left corner of the scheme).
-If a nonempty intersection is found, we look for new candidate pairs among the neighboring elements
-(see the white block 'Cycle over ICs').
+First, we mark all component elements $c\in\mathcal T_c$ unvisited. Then for every unvisited element $c\in \mathcal T_c$, we find all intersection candidate pairs $(c,b)$, $b\in\mathcal T_b$.
+We note at this point, that we also increment the so called \emph{component number} $\gamma$ in this cycle, and
+save it for every intersection polygon IP which is found during the front tracking. This way, we shall
+later know to which component a given IP belongs to, which will become important in Section \ref{sec:components}.
+Then, we check every (c,b) whether it has not been processed yet and if so, we enqueue it into the component queue.
+This is from where the front tracking starts, see the top-left corner of the scheme in \fig{fig:prolongation}.
+
+We pop a first candidate pair (c,b) from the component queue and compute the intersection.
+If the intersection exists, we look for new candidate pairs among the neighboring elements
+(see the white block 'For every IC').
 Therefore, we iterate over the intersection corners and further exploit their topological position on the component element $c$ and the bulk element $b$.
-There are 3 possible cases (applies both for 1d-3d and 2d-3d), how the intersection might be prolonged:
+We look for two types of candidate pairs (applies both for 1d-3d and 2d-3d):
 \begin{enumerate}[label=(\alph*)]
@@
             Finally, we push the new candidate pairs $(c, b')$, $b'\in B'$ into the bulk queue.
-    \item \textbf{IC on the boundary of both $c$ and $b$} \\
-            This situation includes both previously described cases. Therefore, we obtain new candidate pairs
-            $(c', b)$, $c'\in C'$ and $(c, b')$, $b'\in B'$ and push them into the component queue and the bulk queue, respectively.
+%     \item \textbf{IC on the boundary of both $c$ and $b$} \\
+%             This situation includes both previously described cases. Therefore, we obtain new candidate pairs
+%             $(c', b)$, $c'\in C'$ and $(c, b')$, $b'\in B'$ and push them into the component queue and the bulk queue, respectively.
 \end{enumerate}
 % \noteJB{Can we just use two (not excluded) cases one for IB on boundary of $c$ second for CI on boundary of $b$ ?}
+We see that $(c, b')$ can prolong the intersection over a bulk element face, on the other hand $(c', b)$ may prolong the intersection over the component side.
+If the IC lies both on the boundaries of $c$ and $b$,
+we obtain candidate pairs of both types.
 When the pair is taken from either of the queues, we check whether the pair has been already computed and possibly skip it. 
@@
 
-At the end, we see that the candidate pairs are of two types: $(c, b')$ and $(c', b)$,
-from which the first one goes into the bulk queue, trying to fully cover current component element 
-$c$ before we proceed to the next one. We are able recognize the case when the component element 
-does not lie inside the bulk elements with its full volume -- we end up in situation \ref{enum:prolong2},
-but there are no more bulk neighboring elements to prolong the intersection to. Then we mark this component
-element as \emph{open}, so it can be later found by initialization algorithm and possibly
-covered by other bulk elements but as different component.
+After we finish the cycle over ICs, we start emptying the queues. We empty the bulk queue first,
+trying to fully cover the current component element $c$ before we proceed to the next one. 
+We are able to recognize a specific case when the component element 
+does not lie inside the bulk elements with its full volume -- we end up in the situation \ref{enum:prolong2},
+but there are no more bulk neighboring elements to prolong the intersection to, $B'=\emptyset$.
+Then we mark this component element $c$ as \emph{unvisited}, so it can be later found by initialization algorithm and possibly covered by other bulk elements.
+See this condition also in the $C'$ branch in IC cycle in \fig{fig:prolongation}.
+Note that every time this happens, the possible further intersection
+of the current $c$ will be seen as different component with increased component number $m$. \notePE{possible figure prolongation13d-04}
 

### 2016-10-01 paper_intersections.tex
Element intersection benchmark.

--- 2016-10-01 paper_intersections.tex
@@
 100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
-In some of the empty cases, the bounding boxes did not collide, so the actual intersection algorithms were skipped. 
-A single element pair was computed 100 times to obtain reasonable computational time.
+Only the pairs with non-colliding bounding boxes were included to the timing.  
+Every element pair was computed 100 times to obtain reasonable computational time.
+\noteJB{According to the results the time of single pair is on average 2e-5s. Normal system times have resolution about 20ms, hi-resolution timers
+used in profiler have resolution about 1ms. So we need at least 10000 calls per single pair to get meaningful results.}
 
@@
 We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
-using \plucker coordinates, red values to \ngh code.
-The gained speed up factor is approximately 5 in 1d-3d case and 2 in 2d-3d.
-Further we provide estimated count of floating point operations for different approaches in the Table \ref{tab:fundamental_flops}.
-\notePE{Improve and complete...}
+using \plucker coordinates, red values to \ngh code. The gained speed up factor is approximately 5 in 1d-3d case and 2 in 2d-3d. 
+\noteJB{Just the opposite what we expect. Just by chance?}
 

### 2016-10-01 paper_intersections.tex
Intersections between components.

@@
 \label{sec:components}
+We consider here the situation that components are in the interior of 3D bulk mesh. After we compute
+all component-bulk intersections, we use it to easily find all the component-component intersection candidates.
+If the bulk element intersects more than one component element, than we can create candidates from these.
+
+Let us start with description of how we store the intersection results, which will be of great importance here.
+For each element intersection, we save the following data: reference to component and bulk element, barycentric coordinates on both and index of the component.
+These objects are stored in separate vectors for each pair
+of dimensions. Further we define a matrix (\emph{intersection map}) which has as many rows as there are elements in the mesh.
+At each row (element), we save the references to all other elements, having intersection with element corresponding to this row, and references to the actual intersection data.
+
+The algorithm for 2d-2d intersections goes as follows. We iterate over all 2d-3d intersections, respectively over
+the bulk elements having some intersections with 2d components. We look at the intersection map at the
+bulk element row and collect all elements that have 2d-3d intersection with it.
+Now comes in play the component number $\gamma$. If $\gamma$ is equal for both component elements, then 
+these are part of a single continuous component and we do not compute any intersection.
+Otherwise we obtain a new candidate pair, for which IP can be computed.
+
+The algorithm for 1d-2d is analogical, only we do not have to check the component number.
+Note that this way, we do not obtain any intersection in the exterior of bulk mesh.
+If such problem is of our interest, we find the candidate pairs using the search algorithms as in
+initialization phase of advancing front method.
 

### 2016-10-01 paper_intersections.tex
Finished benchmarks
- need to review the element intersection timing
- what about the superlinear time compplexity of the FS+AF algorithm?

--- 2016-10-01 paper_intersections.tex
@@
 
+\noteJB{Mention the hardware configuration to get an context for the timing.}
+
 % \vspace{2ex}
@@
 
-\subsection{General algorithms}
-In previous sections, we have suggested an intersection algorithm that uses axes aligned bounding boxes, BIH to find initial
-intersection and advancing front method (shortly AFront) to prolong the intersection.
-From now on, we shall refer to the algorithm made of these components \emph{BIHsearch}.
-In this section, we shall compare two additional algorithms \emph{BBsearch} and \emph{BIHonly} to see the effects of BIH and AFront (see Table \ref{tab:search_algorithms}).
-\emph{BBsearch} does not use BIH, but searches for the initial intersection using only AABB, and then follows AFront.
-The version
-\emph{BIHonly} computes AABB together with BIH, but does not use AFront.
-
-\begin{table}[!htb]
-    \centering
-    \renewcommand{\arraystretch}{1.2}
-    \begin{tabular}{>{\centering\arraybackslash}p{20ex}
-                    >{\centering\arraybackslash}p{20ex}
-                    >{\centering\arraybackslash}p{20ex}}
-        \colorbox{NavyBlue}{\textcolor{white}{BIHsearch\vphantom{By}}} & \colorbox{orange}{BBsearch\vphantom{By}} & \colorbox{Goldenrod}{BIHonly\vphantom{By}} \\ \hline
-        BIH(AABB) & AABB & BIH(AABB) \\
-        AFront & AFront & ---
-    \end{tabular}
-    \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.
-    \noteJB{Just in the text. Possibly use different name for variants.}
-    \notePE{jsem vzal z posledni prezentace.. prislo mi to prehledny.. vim jak jsem se v diplomce VF hrozne krkolome vracel od grafu k popisu algoritmu..}}
-    \label{tab:search_algorithms}
-\end{table}
-
-Let us now start with the problem on an artificial mesh.
+\subsection{Global Mesh Intersections}
+The global mesh intersection algorithm for a composed mesh $\mathcal T$ presented in Section \ref{sec:front_advancing} has been
+implemented in three variants. First variant, use a full search (FS) over the bulk mesh to get initial pair for the advancing front algorithm (AF).
+Second variant, use the BIH to accelerate the initialization of the AF algorithm. Third variant doesn't use AF at all and relies only on the BIH. 
+In this section, we compare these three variants (FS+AF, BIH+AF, BIH) on one artificial composed mesh and one raising from a real hydrogeological simulation.
+
+% \begin{table}[!htb]
+%     \centering
+%     \renewcommand{\arraystretch}{1.2}
+%     \begin{tabular}{>{\centering\arraybackslash}p{20ex}
+%                     >{\centering\arraybackslash}p{20ex}
+%                     >{\centering\arraybackslash}p{20ex}}
+%         \colorbox{NavyBlue}{\textcolor{white}{BIHsearch\vphantom{By}}} & \colorbox{orange}{BBsearch\vphantom{By}} & \colorbox{Goldenrod}{BIHonly\vphantom{By}} \\ \hline
+%         BIH(AABB) & AABB & BIH(AABB) \\
+%         AFront & AFront & ---
+%     \end{tabular}
+%     \caption{Structure of the general algorithms. 'AFront' stands for the proposed advancing front method.
+%     \noteJB{Just in the text. Possibly use different name for variants.}
+%     \notePE{jsem vzal z posledni prezentace.. prislo mi to prehledny.. vim jak jsem se v diplomce VF hrozne krkolome vracel od grafu k popisu algoritmu..}}
+%     \label{tab:search_algorithms}
+% \end{table}
+% 
+% Let us now start with the problem on an artificial mesh.
+
+An artificial test composed mesh consists of a cube with two diagonal rectangles. A sequence of meshes was prepared with increasing number of intersections ranging
+form $0.1$ up to $2.0$ milions. The mesh size varies from $33e+3$ up to $2e+6$ elements including both the 2d and 3d. The timing for the three compared variants
+of the mesh intersection algorithm is shown on \fig{fig:cube_speed}. As the number of component meshes is low and they are completely 
+inside of the bulk mesh the FS+AF variant was the fastest and with smallest grow as expected. On the other hand the BIH variant is constantly by th 20\%
+slower then the BIH+AF variant. That is roughly related to the average fraction of the non-intersecting 3d element in the bounding box of a 2d element.
+The slightly larger grow of the BIH algorithm is masked by the common superlinear grow with power about $1.1$ which we do not completely understand.
+\noteJB{???}
 
@@
 
-Next, we study the performance of the intersection algorithms on a mesh of a real problem, see \fig{fig:bedrichov_meshes}. The mesh represents a mountain ridge in the Jizera mountains which 
-includes a system of geological fractures (\fig{fig:bedrichov_cut}). We also used this model to create
-a less real mesh, in which the fractures extend through the bulk surface (\fig{fig:bedrichov_extend}). 
-However, this situation might rather occur in another application than aporous media problem.
-In total, 28 fractures are in the mesh.
+Next, we study the performance of the intersection algorithms on a mesh of a real problem, see \fig{fig:bedrichov_meshes}.
+The mesh represents a mountain ridge above a water supply tunnel in Bed{\v r}ichov in the Jizera mountains.
+The mesh includes a system of geological fractures (\fig{fig:bedrichov_cut}). In order to study influence of the component elements poking out of
+the bulk mesh we also prepared a mesh with the artificialy extended fractures (\fig{fig:bedrichov_extend}). 
+Each of these meshes contains 28 fractures in 9 2d components and single 1d component, the tunel.
 
 The results for both meshes can be seen in the \fig{fig:bedrichov_speed}, pay attention to the different time
-scales in the graph.
-In the first case, we notice that algorithms using AFront are nearly twice as fast as \emph{BIHonly}.
-The speed up corresponds to the time saved by using AFront instead of searching the whole mesh for candidate pairs.
-Computation of BIH in \emph{BIHsearch} pays off and the algorithm performs better than \emph{BBsearch}.
-
-In the second case, we observe large blow up for \emph{BBsearch}. It is caused by the exterior elements, 
-for which all bulk elements bounding boxes are iterated, so we can be sure there is no intersection.
-This of course is much better performed using BIH.
-
-In contrast to the artificial case on the fractured cube, BIH construction is worth due
-to the presence of more components. Having more fractures inside the bulk would result to more dramatic difference.
+scales in the graph. In the first case, we notice that FS+AF and BIH+AF algorithms are nearly twice as fast as \emph{BIHonly}.
+The fraction of the non-intersectiong 3d elements in boundaing boxes of the 2d elements is higher as the 3d elements are on average smaller then the 2d elements.
+Creation of the BIH in the BIH+AF variant pays off and the algorithm performs better than the FS+AF variant.
+This in the contrast to the cube test case since the number (10) of the component meshes is higher.
+
+In the second case, we observe large blow up for the FS+AF variant. It is caused by the exterior comonent elements, 
+for which all the bulk elements bounding boxes are iterated before the algorithm concludes there is no intersection.
+This case is clearly treated by both BIH and BIH+AF variants much better.
 

### 2016-10-01 paper_intersections.tex
Conclusion

@@
 \label{sec:conclusins}
-
-TODO:
-- line intersection tracking for accelerate 2d-2d intersections
-- better handling of special cases in paarticular in relation to prolongations
-- better calculation reuse (pass with prolongations)
-- optimisation of element intersection - skip unnecessary calculations
-%\section{Acknowledgement}
-%The paper was supported in part by the Project OP
-%VaVpI Centre for Nanomaterials, Advanced Technologies  and Innovations
-%CZ.1.05/2.1.00/01.0005.
+We present a family of the algorithms for computing intersection polygons for pairs of simplicial elements.
+The algorithms are based on the \plucker coordinates of the edges which may be reused between elements.
+A unified algorithm for the intersections of the meshes of a composed mesh was demonstrated. All algorithms were 
+tested and compared on a set of benchmark problems. In the near future, we want to perform an optimization of 
+the algorithms and in particular use them in XFEM and Mortar 
+like methods for problems in porous media.
+
+\section{Acknowledgement}
+The paper was supported in part by the Project OP VaVpI Centre for Nanomaterials, Advanced Technologies  and Innovations
+CZ.1.05/2.1.00/01.0005.
 

### 2016-10-01 paper_intersections.tex
Polishing front tracking.

@@
 We consider the composed mesh $\mathcal T$ containing the 3d mesh $\mathcal T_1$ that we shall call a bulk mesh $\mathcal T_b$. Any other 
-mesh $\mathcal T_i$, with dimensions $d_i < 3$, $i=1,\dots, N_{\mathcal T}$ we shall call a component mesh. 
-We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) using the advancing front algorithm which is described in Sections 
+mesh $\mathcal T_i$, with dimension $d_i < 3$, $i=1,\dots, N_{\mathcal T}$, we shall call a component mesh. 
+We first compute all component-bulk mesh intersections that is (1d-3d and 2d-3d) using the advancing front algorithm which we shell describe in Sections 
 \ref{sec:initialization}, \ref{sec:front} and then the 1d-2d and 2d-2d 
-intersections use the bulk mesh to get the intersection pair candidates, the Section \ref{sec:components}.
-
-Let us consider a single pair of the component mesh $\mathcal T_c$ and the bulk mesh $\mathcal T_b$. 
-Element intersections for this pair of meshes are obtained in two phases: firstly, we look for the first two elements intersecting each other (initialization); 
-secondly, we prolong the intersection by investigating neighbouring elements (front tracking).
-\noteJB{Not sure that "prolong" is the right verb.}
+intersections are computed using the bulk mesh to get the intersection pair candidates. This step is described in Section \ref{sec:components}.
+
+Let us consider a single pair of the component mesh $\mathcal T_c$ and the bulk mesh~$\mathcal T_b$. 
+Element intersections for this pair of meshes are obtained in two phases: firstly, we look for the 
+first pair $(c,b)$ of the component and the bulk element with a non-empty intersection (the initialization); 
+secondly, we prolong the intersection by investigating neighbouring elements (the front tracking).
 
@@
 \label{sec:initialization}
-\noteJB{Possibly move this afte Advancing front section since it is in fact single step in the main loop.}
-We choose an arbitrary element of the component mesh and check its intersection with all elements of the bulk mesh.
-This process is accelerated by computing the axis aligned bounding box (AABB) for every element and use intersection of the bounding boxes
-as a fast indicator for possible intersection of the elements. This step takes $O(N)$ time with respect to the number of elements of the bulk mesh $N$.
-If the number of components $k$ is small and if the components are contained inside the bulk mesh, the total time of initialization may still be linear $O(kN)$. However,
-for more complex cases we organize the bounding boxes of the bulk mesh into the bounding interval hierarchy (BIH) \cite{EGWR:EGSR06:139-149},
-a data structure in principle equivalent 
-to R-trees \cite{guttman_r-trees:_1984}, \cite{nam_comparative_2004}. The creation time is $O(N\log(N/n))$ and the lookup time $O(\log(N/n))$ where $n$ is number
-of the bulk elements in the leaf nodes of the tree.
+Given a component element $c$, we have to find an intersecting bulk element $b$.
+If this step is done only few times the optimal way it to iterate overt the bulk mesh and test every element for the intersection.
+This process may be accelerated using the axis aligned bounding box (AABB) for every element and use intersection of the bounding boxes
+as a fast indicator for possible intersection of the elements. This step takes time $O(N)$ with respect to the number of elements of the bulk mesh $N$.
+If the number of components $k$ is small and if the components are contained inside the bulk mesh, the total time of the initialization 
+may still be linear $O(kN)$. However, for more complex cases we organize the bounding boxes of the bulk mesh into the bounding interval
+hierarchy (BIH) \cite{EGWR:EGSR06:139-149} a data structure in principle equivalent 
+to the R-trees \cite{guttman_r-trees:_1984}, \cite{nam_comparative_2004}. The construction of a BIH takes time $O(N\log(N/n))$ 
+and the lookup time is $O(\log(N/n))$ where $n$ is the number of the bulk elements in the leaf nodes of the tree.
 
@@
 The advancing front algorithm requires the neigbouring information for the elements within the component mesh $\mathcal T_c$ 
-as well as within the bulk mesh $\mathcal T_b$. It can be viewed as the breadth first search algorithm for a graph where graph vertices are 
-intersection polygons and graph edges are sides shared by two polygons. Since every side of IP is on the boundary of either 
+as well as within the bulk mesh $\mathcal T_b$. It can be viewed as the breadth first search algorithm for a graph where the graph vertices are 
+the intersection polygons and the graph edges are the sides shared by two polygons. Since every side of IP is on the boundary of either 
 the component element or the bulk element, we can distinguish bulk and component edges. 
-Correspondingly the candidate pairs are enqueued into \emph{component queue} $Q_c$ and the \emph{bulk queue} $Q_b$, respectively.
-
-The key idea behind the two queues is to compute intersections for a component element with all possible bulk elements at first, and then move to a~next neighboring component element.
-So the bulk queue is emptied before the component queue.
-\begin{algorithm}
-  \caption{Advancing front algorithm}  
-  \label{algo:advancing front}
-
-  \SetKw{return}{return}
-  \SetKw{edgefaces}{edge faces}
-  \DontPrintSemicolon
-  %\KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
-  %\KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
-  mark all $c\in \mathcal T_c$ unvisited\;
-  $\gamma=0$ \tcp*{component number}
-  \For{unvisited $c\in\mathcal T_c$}{
-    increment $\gamma$\;
-    find list $L$ of intersection candidates\;
-    append $L$ to queue $Q_c$\;
-    \For{$(c, b) \in Q_c$}{
-        mark $c$ visited\;
-        push $(c,b)$ into $Q_b$\;
-        \For{$(c, b) \in Q_b$}{            
-            list $I$ of ICs of $(c,b)$ intersection\;
-            set $\gamma$ into IP\;
-            \For{$p\in I$}{
-                \If{$p$ on boundary of $c$}{
-                    get neighbours $C'$\;
-                    \tcp{check pair if unvisited, mark visited}
-                    enqueue $(c', b)$ into $Q_c$ for all $c'\in C'$ 
-                }
-                \If{$p$ on boundary of $b$}{
-                    get neighbours $B'$\;
-                    \If{$B'$ is empty and not on boundary of $c$}{mark $c$ unvisited}
-                    enqueue $(c, b')$ into $Q_b$ for all $b'\in B'$ 
-                }                
-%                 \noteJB{Questionable}\;
-%                 \If{$p$ on both boundaries}{
-%                     enqueue $(c', b')$ into $Q_c$ for all $b'\in B',\ c'\in C'$ 
+Correspondingly we use a \emph{component queue} $Q_c$ and a \emph{bulk queue} $Q_b$ where we shall place intersection candidate pairs $(c,b)$.
+In order to process every pair $(c,b)$ only once, we check if the pair was already processed before it is enqueued into one of the queues.
+Only if the pair was not yet processed we mark it processed and push it into the queue. Since the number of possible pairs is to big we can not have a flag array
+which may allow constant time checks. Therefore, we keep a hash table of the processed pairs which allows the constant check in the average.
+
+The key idea behind the two queues is to compute intersections for a component element with all possible bulk elements at first,
+and then move to a~next neighboring component element. So the bulk queue is emptied before the component queue.
+% \begin{algorithm}
+%   \caption{Advancing front algorithm}  
+%   \label{algo:advancing front}
+%   
+%   \SetKw{return}{return}
+%   \SetKw{edgefaces}{edge faces}
+%   \DontPrintSemicolon
+%   %\KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
+%   %\KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
+%   mark all $c\in \mathcal T_c$ unvisited\;
+%   $\gamma=0$ \tcp*{component number}
+%   \For{unvisited $c\in\mathcal T_c$}{
+%     increment $\gamma$\;
+%     find list $L$ of intersection candidates\;
+%     append $L$ to queue $Q_c$\;
+%     \For{$(c, b) \in Q_c$}{
+%         mark $c$ visited\;
+%         push $(c,b)$ into $Q_b$\;
+%         \For{$(c, b) \in Q_b$}{            
+%             list $I$ of ICs of $(c,b)$ intersection\;
+%             set $\gamma$ into IP\;
+%             \For{$p\in I$}{
+%                 \If{$p$ on boundary of $c$}{
+%                     get neighbours $C'$\;
+%                     \tcp{check pair if unvisited, mark visited}
+%                     enqueue $(c', b)$ into $Q_c$ for all $c'\in C'$ 
 %                 }
-            }
-
-        }
-    }
-  }
-
-\end{algorithm}
+%                 \If{$p$ on boundary of $b$}{
+%                     get neighbours $B'$\;
+%                     \If{$B'$ is empty and not on boundary of $c$}{mark $c$ unvisited}
+%                     enqueue $(c, b')$ into $Q_b$ for all $b'\in B'$ 
+%                 }                
+% %                 \noteJB{Questionable}\;
+% %                 \If{$p$ on both boundaries}{
+% %                     enqueue $(c', b')$ into $Q_c$ for all $b'\in B',\ c'\in C'$ 
+% %                 }
+%             }        
+%             
+%         }
+%     }
+%   }
+%   
+% \end{algorithm}
 
@@
 
-First, we mark all component elements $c\in\mathcal T_c$ unvisited. Then for every unvisited element $c\in \mathcal T_c$, we find all intersection candidate pairs $(c,b)$, $b\in\mathcal T_b$.
-We note at this point, that we also increment the so called \emph{component number} $\gamma$ in this cycle, and
-save it for every intersection polygon IP which is found during the front tracking. This way, we shall
-later know to which component a given IP belongs to, which will become important in Section \ref{sec:components}.
-Then, we check every (c,b) whether it has not been processed yet and if so, we enqueue it into the component queue.
-This is from where the front tracking starts, see the top-left corner of the scheme in \fig{fig:prolongation}.
-
-We pop a first candidate pair (c,b) from the component queue and compute the intersection.
-If the intersection exists, we look for new candidate pairs among the neighboring elements
-(see the white block 'For every IC').
-Therefore, we iterate over the intersection corners and further exploit their topological position on the component element $c$ and the bulk element $b$.
-We look for two types of candidate pairs (applies both for 1d-3d and 2d-3d):
+First, we mark all component elements $c\in\mathcal T_c$ as unvisited. 
+For every unvisited element $c\in \mathcal T_c$, 
+we find some intersection candidate pairs $\{$(c,b)$, $b\in\mathcal T_b$\}$ and
+into the queue $Q_c$.
+Then we increment the \emph{component number} $\gamma$, which we use to 
+mark all intersection polygons we shall find until the queue $Q_c$ becomes empty.
+This way, we shall later know to which component a given IP belongs to, 
+which will become important in Section \ref{sec:components}.
+This is from where the front tracking starts, see the top-left corner of the scheme in 
+\fig{fig:prolongation}.
+
+We dequeue the first candidate pair $(c,b)$ from $Q_c$ and compute the IP.
+If the intersection exists, we look for the new candidate pairs among the neighboring elements
+(see the big white block in \fig{fig:prolongation}).
+Therefore, we iterate over ICs of the IP and further exploit their topological position on the component element $c$ and the bulk element $b$.
+For every IC one or both of the following cases may happen:
 \begin{enumerate}[label=(\alph*)]
-    \item \textbf{IC on the boundary of $c$  and inside $b$} \\
+    \item \textbf{IC is on the boundary of $c$  and inside $b$.} \\
             We find all the sides $S$ coincident with the \nface of $c$ on which IC lies. Then we get all component
             elements $C'$ neighboring with $c$ over any side $s\in S$. And finally, we push all pairs $(c',b)$, $c'\in C'$ 
-            into the component queue.
-            Note that $c$ can have more then one neighbour component elements over the single side $s$, i.e. branches are allowed.
-    \item \textbf{IC inside of $c$ anf on the boundary of $b$} \label{enum:prolong2}\\
+            into the component queue. Note that $c$ can have more then one neighbour component elements over the single side $s$, i.e. branches are allowed.
+    \item \textbf{IC is inside $c$ and on the boundary of $b$.} \label{enum:prolong2}\\
             We find all the faces $F$ coincident with the \nface of $b$ on which IC lies. 
@@
             Finally, we push the new candidate pairs $(c, b')$, $b'\in B'$ into the bulk queue.
-%     \item \textbf{IC on the boundary of both $c$ and $b$} \\
-%             This situation includes both previously described cases. Therefore, we obtain new candidate pairs
-%             $(c', b)$, $c'\in C'$ and $(c, b')$, $b'\in B'$ and push them into the component queue and the bulk queue, respectively.
+            However, if the list $B'$ is empty, which means that the component element $c$ pokes out of the bulk mesh,
+            we mark the element $c$ as unvisited again. This way we have chance to find possible other intersection of the element
+            $c$ with the bulk mesh in the main loop. Note that every time this happens, the possible further intersection 
+            of the current $c$ will be seen as different component with increased component number $m$. 
+            \notePE{possible figure prolongation13d-04}
+
 \end{enumerate}
-% \noteJB{Can we just use two (not excluded) cases one for IB on boundary of $c$ second for CI on boundary of $b$ ?}
-We see that $(c, b')$ can prolong the intersection over a bulk element face, on the other hand $(c', b)$ may prolong the intersection over the component side.
-If the IC lies both on the boundaries of $c$ and $b$,
-we obtain candidate pairs of both types.
-When the pair is taken from either of the queues, we check whether the pair has been already computed and possibly skip it. 
-To this end every component element keeps a hash of the bulk elements with which we have called the intersection test.
-
-After we finish the cycle over ICs, we start emptying the queues. We empty the bulk queue first,
+We see that $(c, b')$ can prolong the intersection over a bulk element face, on the other hand $(c', b)$ 
+may prolong the intersection over the component side. If the IC lies both on the boundaries of $c$ and $b$,
+we obtain candidate pairs of both types. Having all ICs processed, we continue emptying the queues. We empty the bulk queue first,
 trying to fully cover the current component element $c$ before we proceed to the next one.
-We are able to recognize a specific case when the component element 
-does not lie inside the bulk elements with its full volume -- we end up in the situation \ref{enum:prolong2},
-but there are no more bulk neighboring elements to prolong the intersection to, $B'=\emptyset$.
-Then we mark this component element $c$ as \emph{unvisited}, so it can be later found by initialization algorithm and possibly covered by other bulk elements.
-See this condition also in the $C'$ branch in IC cycle in \fig{fig:prolongation}.
-Note that every time this happens, the possible further intersection
-of the current $c$ will be seen as different component with increased component number $m$. \notePE{possible figure prolongation13d-04}
 
@@
 \label{sec:components}
-We consider here the situation that components are in the interior of 3D bulk mesh. After we compute
+We consider here the situation that components are in the interior of the 3d bulk mesh. After we compute
 all component-bulk intersections, we use it to easily find all the component-component intersection candidates.
@@
 Let us start with description of how we store the intersection results, which will be of great importance here.
-For each element intersection, we save the following data: reference to component and bulk element, barycentric coordinates on both and index of the component.
-These objects are stored in separate vectors for each pair
-of dimensions. Further we define a matrix (\emph{intersection map}) which has as many rows as there are elements in the mesh.
-At each row (element), we save the references to all other elements, having intersection with element corresponding to this row, and references to the actual intersection data.
-
-The algorithm for 2d-2d intersections goes as follows. We iterate over all 2d-3d intersections, respectively over
+For each element intersection, we save the following data: reference to component and bulk element, 
+barycentric coordinates on both and index of the component. These objects are stored in separate vectors for each pair 
+of dimensions. Further we define a sparse matrix (\emph{intersection map}) which has as many rows as there are elements in the mesh.
+At each row (element), we save the references to all other elements, having intersection with element corresponding to this row, 
+and references to the actual intersection data.
+
+The algorithm for 2d-2d intersections works as follows. We iterate over all 2d-3d intersections, respectively over
 the bulk elements having some intersections with 2d components. We look at the intersection map at the

### 2016-10-01 paper_intersections.tex
Improve plucker product figure.
SGS acknowledgement.
Fix math.

@@
 \begin{figure}[!htb]
-  \begin{center}        
-    \includegraphics[width=0.7\textwidth]{\figpath plucker_product.pdf}
-%    \includegraphics{\figpath plucker_products.pdf}
-  \end{center}
+    \centering    
+    \subfloat[$\pi_p\odot \pi_i < 0 \;\forall i$]{
+        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_a.pdf}
+    }
+    \subfloat[$\pi_p\odot \pi_i = 0 \, \exists i$ \newline special case]{
+        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_b.pdf}
+    }
+    \subfloat[$\pi_p\odot \pi_i > 0 \;\forall i$]{
+        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_c.pdf}
+    }
     \caption{Sign of the permuted inner product is related to the relative position of the two oriented lines.          
             Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
-           \notePE{circle dot permuted inner product}}
+    }
     \label{fig:plucker_products}
 \end{figure}
+
+% \begin{figure}[!htb]
+%   \begin{center}        
+%     \includegraphics[width=0.7\textwidth]{\figpath plucker_product.pdf}
+% %    \includegraphics{\figpath plucker_products.pdf}
+%   \end{center}
+%   \caption{Sign of the permuted inner product is related to the relative position of the two oriented lines.
+Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
+%            \notePE{circle dot permuted inner product}}
+%   \label{fig:plucker_products}
+% \end{figure}
 
@@
 For every unvisited element $c\in \mathcal T_c$, 
-we find some intersection candidate pairs $\{$(c,b)$, $b\in\mathcal T_b$\}$ and
+we find some intersection candidate pairs $\{(c,b), b\in\mathcal T_b\}$ and
 into the queue $Q_c$.
@@
 
+The work of P. Exner was supported by the Ministry of Education of the Czech Republic within the SGS project no. 21176/115 of the Technical University of Liberec.
+
 %% The Appendices part is started with the command \appendix;

### 2016-10-01 paper_intersections.tex
remove element benchmarks

--- 2016-10-01 paper_intersections.tex
@@
             Moller and Trumbore & 42            & 168           & 756\\
-            \ngh                & 119           & 476           & 2142\\
+            \ngh                & 127           & 508           & 2286\\
     \end{tabular}
@@
 
-\subsection{Element Intersection Algorithms}
-The first benchmark focuses on the 1d-3d and 2d-3d element intersections. We randomly generated
-100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
-Only the pairs with non-colliding bounding boxes were included to the timing.  
-Every element pair was computed 100 times to obtain reasonable computational time.
-\noteJB{According to the results the time of single pair is on average 2e-5s. Normal system times have resolution about 20ms, hi-resolution timers
-used in profiler have resolution about 1ms. So we need at least 10000 calls per single pair to get meaningful results.}
-
-\noteJB{Mention the hardware configuration to get an context for the timing.}
-
-% \vspace{2ex}
-% \begin{minipage}{\textwidth}
+% \subsection{Element Intersection Algorithms}
+% The first benchmark focuses on the 1d-3d and 2d-3d element intersections. We randomly generated
+% 100000 element pairs inside a unit cube, from which approximately 65\% have nonempty intersection.
+% Only the pairs with non-colliding bounding boxes were included to the timing.  
+% Every element pair was computed 100 times to obtain reasonable computational time.
+% \noteJB{According to the results the time of single pair is on average 2e-5s. Normal system times have resolution about 20ms, hi-resolution timers
+% used in profiler have resolution about 1ms. So we need at least 10000 calls per single pair to get meaningful results.}
+% 
+% \noteJB{Mention the hardware configuration to get an context for the timing.}
+% 
+% \begin{figure}[!htb]
 %     \centering
-%     \hspace{-30pt}
-%   \begin{minipage}[b]{0.44\textwidth}
-%     \centering
-%     \renewcommand{\arraystretch}{1.2}
-%     \begin{tabular}[b]{l|l}
-%             algorithm, 2d-3d& FLOPs\\
-%                       & estimate\\
-%             \hline\\
-%             parametric plane & 585\\
-%             normal plane (reuse) & 765\\
-%             Moller and Trumbore & 783\\
-%             Pl\"ucker (reuse) & 306
-%     \end{tabular}
-%     \captionof{table}{Estimation of floating point operations count and comparison of different approaches.
-%                       Only 2d-3d case considered.}
-%     \label{tab:fundamental_flops}
-%     \notePE{comment on different strategies}\noteJB{Rather put into text. I shall comment that.}
-%   \end{minipage}
-%   \hfil
-%   \begin{minipage}[b]{0.5\textwidth}
-%     \centering
-%     \includegraphics[width=\textwidth]{\figpath intersections_fundamental_speed.pdf}
-%     
-%     \captionof{figure}{Efficiency of \plucker approach compared to the legacy \ngh code.}
+%     \includegraphics[width=0.5\textwidth]{\figpath intersections_fundamental_speed.pdf}
+%     \caption{Efficiency of \plucker approach compared to the legacy \ngh code.}
 %     \label{fig:fundamental_speed}
-%     \end{minipage}
-% \end{minipage}
-% \vspace{2ex}
-
-\begin{figure}[!htb]
-    \centering
-    \includegraphics[width=0.5\textwidth]{\figpath intersections_fundamental_speed.pdf}
-    \caption{Efficiency of \plucker approach compared to the legacy \ngh code.}
-    \label{fig:fundamental_speed}
-\end{figure}
-
-We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
-using \plucker coordinates, red values to \ngh code. The gained speed up factor is approximately 5 in 1d-3d case and 2 in 2d-3d. 
-\noteJB{Just the opposite what we expect. Just by chance?}
+% \end{figure}
+% 
+% We see the benchmark results in the \fig{fig:fundamental_speed}. Green values correspond to the presented algorithms
+% using \plucker coordinates, red values to \ngh code. The gained speed up factor is approximately 5 in 1d-3d case and 2 in 2d-3d. 
+% \noteJB{Just the opposite what we expect. Just by chance?}
 

### 2016-10-02 paper_intersections.tex
Add figure with components.

--- 2016-10-01 paper_intersections.tex
@@
             However, if the list $B'$ is empty, which means that the component element $c$ pokes out of the bulk mesh,
-            we mark the element $c$ as unvisited again. This way we have chance to find possible other intersection of the element
+            we mark the element $c$ as unvisited again. This way we have a chance to find possible other intersection of the element
             $c$ with the bulk mesh in the main loop. Note that every time this happens, the possible further intersection 
-            of the current $c$ will be seen as different component with increased component number $m$. 
-            \notePE{possible figure prolongation13d-04}
-
+            of the current $c$ will be seen as different component with increased component number $m$
+            (see an example situation in \fig{fig:components}). 
 \end{enumerate}
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=0.55\textwidth]{\figpath components.pdf}
+    \caption{The two tetrahedra 1,2 do not make a compact bulk. Therefore four initializations are needed,
+    to find all the intersections with three 1D elements: 3-1, 5-1, 4-2, 5-2; creating four independent components. Advancing front method cannot play any part in this situation.}
+    \label{fig:components}
+\end{figure}
+
 We see that $(c, b')$ can prolong the intersection over a bulk element face, on the other hand $(c', b)$ 

### 2016-10-02 paper_intersections.tex
Replace correct prolongation scheme.
Fix benchmarks header

--- 2016-10-01 paper_intersections.tex
@@
 %done \noteJB{I prefer to call them element intersection. Fundamental intersection seems to epic.}
-\noteJB{We compare just against NGH which we should briefly describe. Neither of the algorithms is optimized. The new one deals correctly with special cases and provides 
-barycentric coordinates (so more work for less time).}
-\noteJB{Also write little about Flow123d here. The language etc.}
 
@@
 In the beginning, we provide some software development related information.
-Then we compare the performance of our algorithms for element intersections with other approaches \noteJB{they are all ours}.
+Then analyze theoretical number of FLOPS in our element intersection algorithms with 
+other state of art algorithms.
 Next we shall compare our algorithms with different initialization phase (candidate pairs search),

### 2016-10-02 paper_intersections.tex

@@
   \centering    
-    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_pe_new.pdf}
+    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_jb_fix_italic.pdf}
   \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}

### 2016-10-02 paper_intersections.tex
Add figure for tracing.

@@
 defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
-and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \noteJB{possible figure}). The vertices of the polygon are ordered in the same 
+and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \fig{fig:tracing}). The vertices of the polygon are ordered in the same 
 way as is the order and orientation of the sides of $S_2$, that is counterclockwise around the interior with normal pointing to us.
@@
 If some IC may possibly be part of the such degenerated IP we put it into the list $J$.
+
+\begin{figure}[!htb]
+    \centering    
+    \includegraphics[width=0.65\textwidth]{\figpath tracing.pdf}
+    \caption{Example of an intersection 2D-3D, demonstrating the ICs ordering. We see at every 
+    intersection polygon corner $p_i$ which \nfaces it lies on. Looking at $p_0$, the connection table entries
+    are: $F_g[s_2]=p_0$, $F_p[p_0]=s_0$. For the other ICs we have: $F_g[s_0]=p_1$, $F_p[p_1]=f_1$, $F_g[f_1]=p_2$, $F_p[p_2]=f_2$ and $F_g[f_2]=p_3$, $F_p[p_3]=s_2$.}
+    \label{fig:tracing}
+\end{figure}
 

### 2016-10-02 paper_intersections.tex
First spellcheck.

@@
 coordinates. These algorithms combined with the advancing front technique can reuse the results of calculations 
-performed on the neigbouring elements and reduce the number of arithmetic operations. Barycentric coordinates
+performed on the neighbouring elements and reduce the number of arithmetic operations. Barycentric coordinates
 on each of the intersecting elements are provided for every intersection point. Benchmarks 
@@
 Massing, Larson, and Logg \cite{massing_efficient_2013} present an algorithm for 2d-3d intersections as part of their implementation of the Nitche method 
-which is part of the Doplhin project \cite{Dolphin}. They use axes aligned bounding boxes of elements (AABB) and bounding interval hierarchy (BIH) 
+which is part of the Dolfin project \cite{Dolphin}. They use axes aligned bounding boxes of elements (AABB) and bounding interval hierarchy (BIH) 
 to get intersection candidate pairs of elements, the GTS library \cite{gtslib} is used for 2d-3d intersections. 
@@
 further developing the algorithm of Platis and Theoharis \cite{platis_fast_2003} for ray-tetrahedron intersections. Element intersections based on 
-\plucker coordinates are combined with the advancing front method which allows us to reuse \plucker coordinates and their products between neigbouring
+\plucker coordinates are combined with the advancing front method which allows us to reuse \plucker coordinates and their products between neighboring
 elements and reduce the number of arithmetic operations.
@@
 first pair $(c,b)$ of the component and the bulk element with a non-empty intersection (the initialization); 
-secondly, we prolong the intersection by investigating neighbouring elements (the front tracking).
+secondly, we prolong the intersection by investigating neighboring elements (the front tracking).
 
@@
 to the R-trees \cite{guttman_r-trees:_1984}, \cite{nam_comparative_2004}. The construction of a BIH takes time $O(N\log(N/n))$ 
-and the lookup time is $O(\log(N/n))$ where $n$ is the number of the bulk elements in the leaf nodes of the tree.
+and the search time is $O(\log(N/n))$ where $n$ is the number of the bulk elements in the leaf nodes of the tree.
 
@@
 \label{sec:front}
-The advancing front algorithm requires the neigbouring information for the elements within the component mesh $\mathcal T_c$ 
+The advancing front algorithm requires the neighboring information for the elements within the component mesh $\mathcal T_c$ 
 as well as within the bulk mesh $\mathcal T_b$. It can be viewed as the breadth first search algorithm for a graph where the graph vertices are 
@@
 %                 \If{$p$ on boundary of $c$}{
-%                     get neighbours $C'$\;
+%                     get neighbors $C'$\;
 %                     \tcp{check pair if unvisited, mark visited}
@@
 %                 \If{$p$ on boundary of $b$}{
-%                     get neighbours $B'$\;
+%                     get neighbors $B'$\;
 %                     \If{$B'$ is empty and not on boundary of $c$}{mark $c$ unvisited}
@@
             elements $C'$ neighboring with $c$ over any side $s\in S$. And finally, we push all pairs $(c',b)$, $c'\in C'$ 
-            into the component queue. Note that $c$ can have more then one neighbour component elements over the single side $s$, i.e. branches are allowed.
+            into the component queue. Note that $c$ can have more then one neighbor component elements over the single side $s$, i.e. branches are allowed.
     \item \textbf{IC is inside $c$ and on the boundary of $b$.} \label{enum:prolong2}\\
@@
 % (point of line in 1d, edge of polygon in 2d) is inside the tetrahedron, not on its surface, we
-% get a neighbouring element of the component and push it back together with the current tetrahedron into 
+% get a neighboring element of the component and push it back together with the current tetrahedron into 
 % \emph{component prolongation queue}. If the intersection edge is inside the \emph{slave} element 
-% (line or triangle), i.e. is on the surface of tetrahedron, we get a neighbouring element of the tetrahedron
+% (line or triangle), i.e. is on the surface of tetrahedron, we get a neighboring element of the tetrahedron
 % and push it back together with the current slave element into \emph{3d prolongation queue}.
@@
 The C++ is used as principal language. Flow123d provides models for saturated and unsaturated groundwater flow,
-soulute transport with sorption, and  heat transfer. Mixed finite elements, finite volumes, and discontinuous Galerkin method are 
+solute transport with sorption, and  heat transfer. Mixed finite elements, finite volumes, and discontinuous Galerkin method are 
 used. All equations are consistently formulated for meshes of mixed dimensions.  However,
@@
 described in Section \ref{sec:1d-2d}, the legacy code \ngh, the plane clipping algorithm due to Haines \cite{haines_fast_1991}, the minimum storage
-algorithm due to Möller and Trumbore (MT) \cite{moller_fast_1997}. Raw numbers of arithemtic operations are summarized in Table \ref{tab:fundamental_flops}.
+algorithm due to Möller and Trumbore (MT) \cite{moller_fast_1997}. Raw numbers of arithmetic operations are summarized in Table \ref{tab:fundamental_flops}.
 For the \plucker and \ngh we count FLOPS from the implementation of individual intersection algorithms, for Haines and MT we estimated FLOPS in theoretical 
@@
 An artificial test composed mesh consists of a cube with two diagonal rectangles. A sequence of meshes was prepared with increasing number of intersections ranging
-form $0.1$ up to $2.0$ milions. The mesh size varies from $33e+3$ up to $2e+6$ elements including both the 2d and 3d. The timing for the three compared variants
+form $0.1$ up to $2.0$ millions. The mesh size varies from $33e+3$ up to $2e+6$ elements including both the 2d and 3d. The timing for the three compared variants
 of the mesh intersection algorithm is shown on \fig{fig:cube_speed}. As the number of component meshes is low and they are completely 
-inside of the bulk mesh the FS+AF variant was the fastest and with smallest grow as expected. On the other hand the BIH variant is constantly by th 20\%
+inside of the bulk mesh the FS+AF variant was the fastest and with smallest grow as expected. On the other hand the BIH variant is constantly by 20\%
 slower then the BIH+AF variant. That is roughly related to the average fraction of the non-intersecting 3d element in the bounding box of a 2d element.
@@
     \caption{Artificial mesh -- a cube with two perpendicular planes placed on the diagonals of the cube.
-             The planes are also nonmatching, therefore can be seen as two independent components.}
+             The planes are also non-matching, therefore can be seen as two independent components.}
     \label{fig:cube_mesh}
@@
 The mesh includes a system of geological fractures (\fig{fig:bedrichov_cut}). In order to study influence of the component elements poking out of
-the bulk mesh we also prepared a mesh with the artificialy extended fractures (\fig{fig:bedrichov_extend}). 
-Each of these meshes contains 28 fractures in 9 2d components and single 1d component, the tunel.
+the bulk mesh we also prepared a mesh with the artificially extended fractures (\fig{fig:bedrichov_extend}). 
+Each of these meshes contains 28 fractures in 9 2d components and single 1d component, the tunnel.
 
@@
 scales in the graph. In the first case, we notice that FS+AF and BIH+AF algorithms are nearly twice as fast as \emph{BIHonly}.
-The fraction of the non-intersectiong 3d elements in boundaing boxes of the 2d elements is higher as the 3d elements are on average smaller then the 2d elements.
+The fraction of the non-intersecting 3d elements in bounding boxes of the 2d elements is higher as the 3d elements are on average smaller then the 2d elements.
 Creation of the BIH in the BIH+AF variant pays off and the algorithm performs better than the FS+AF variant.
@@
 
-In the second case, we observe large blow up for the FS+AF variant. It is caused by the exterior comonent elements, 
+In the second case, we observe large blow up for the FS+AF variant. It is caused by the exterior component elements, 
 for which all the bulk elements bounding boxes are iterated before the algorithm concludes there is no intersection.
@@
 % Triangle-Triangle and Tetra-Triangle intersections done similarly as in aur approach: set of points including vertices and then sort them countercolckwise.
-% Local intersection algorithm do not provide neighbouring information so the traversal algorithm do not use it.
+% Local intersection algorithm do not provide neighboring information so the traversal algorithm do not use it.
 % 

### 2016-10-02 paper_intersections.tex
Minor corrections till 1d3d.

@@
 already adopted by some groundwater simulation software, e.g FeFlow \cite{trefry_feflow:_2007} and Flow123d \cite{flow123d}.
-Nevertheless as the complexity of the geometry increase (e.g. when lots of fractures are randomly generated) the compatible meshing becomes painful or even 
+Nevertheless as the complexity of the geometry increases (e.g. when lots of fractures are randomly generated) the compatible meshing becomes painful or even 
 impossible. In order to avoid these difficulties we may discretize the continuum and every fracture and well independently, getting a non-matching 
 (or incompatible) mesh of mixed dimensions and then apply XFEM to represent jumps of the solution on the fractures or singularities 
-around the wells. The prerequisite for such approach is a fast and robust algorithm for calculating intersections of individual meshes.
+at the wells. The prerequisite for such approach is a fast and robust algorithm for calculating intersections of individual meshes.
 
@@
 The mesh intersection problem is to find all pairs of elements $L\in \mathcal{T}_i$, $K\in \mathcal{T}_j$, $i\ne j$ that have non-empty intersection 
-and to compute that intersection. The mesh intersection problem consists of the two parts: First, generate a set of candidate pairs $(K, L)$. 
-Second, compute the intersection of a particular pair.
+and to compute that intersection.
+The mesh intersection problem consists of the two parts: the first, generating a set of candidate pairs $(K, L)$; the second, computing the intersection of a particular pair.
 
@@
 Gander and Japhet \cite{gander_algorithm_2013} present the PANG algorithm for 2d-2d and 3d-3d intersections that can be used e.g. for mesh overlapping methods.
-They use the advancing front technique to get candidate pairs in linear time. The algorithm is part of the DUNE library \cite{bastian_towards_2005}.
+They use the advancing front technique to get candidate pairs in linear time. The algorithm is part of the library DUNE \cite{bastian_towards_2005}.
 Massing, Larson, and Logg \cite{massing_efficient_2013} present an algorithm for 2d-3d intersections as part of their implementation of the Nitche method 
-which is part of the Dolfin project \cite{Dolphin}. They use axes aligned bounding boxes of elements (AABB) and bounding interval hierarchy (BIH) 
+which is part of the project Dolfin \cite{Dolphin}. They use axes aligned bounding boxes of elements (AABB) and bounding interval hierarchy (BIH) 
 to get intersection candidate pairs of elements, the GTS library \cite{gtslib} is used for 2d-3d intersections. 
 Finally, there is the work of A. Elsheikh and M. Elsheikh \cite{elsheikh_reliable_2012} presenting an algorithm for 2d-2d mesh union operation which includes 
-calculation and imprinting of the intersection curves. They exploit binary space partitioning for search of initial intersection and 
-the advancing front method for intersection curve tracking.
+calculation and imprinting of the intersection curves. They exploit the binary space partitioning for searching of the initial intersection and 
+the advancing front method for the intersection curve tracking.
 
@@
 \label{sec:element intersecitons}
-In this section, we present algorithms for computing intersection of a pair of simplicial elements of a~different dimension in the 3d ambient space. 
+In this section, we present algorithms for computing the intersection of a pair of simplicial elements of a~different dimension in the 3d ambient space. 
 In particular we address intersection algorithms for 1d-2d, 1d-3d, 2d-3d pairs of elements. We have implemented the case 2d-2d as well, however the treatment 
@@
 for each intersecting element $K$ of the pair. The pair $\tau_K = (d_K, i_K)$
-is called the topological position of the IC on $K$.
+is called the \emph{topological position} of the IC on $K$.
 
@@
 \[ \pi_p = (\vc{u}_p, \vc{v}_p) = (\vc{u}_p, \vc{u}_p\times \vc A). \]
-Further we use a permuted inner product
+Further we denote a permuted inner product
 \[\pi_p \odot \pi_q = \vc{u}_p\cdot \vc{v}_q + \vc{u}_q \cdot \vc{v}_p. \]
@@
 \begin{enumerate}
-    \item Compute or reuse \plucker coordinates and permuted inner products: $\pi_p$, $\pi_i$, $\pi_s \odot \pi_i$, for $i=1,2,3$.
+    \item Compute or reuse \plucker coordinates and permuted inner products: $\pi_p$, $\pi_{s_i}$, $\pi_p \odot \pi_{s_i}$, for $i=1,2,3$.
     \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
@@
     \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
-        projected to the plane $x_i=0$ where $i$ is the index of maximal component of the triangle's normal vector.
+        projected to the plane $x_i=0$ where $i$ is the index of the maximal component of the triangle's normal vector.
         Every pair $p$, $s_i$ is checked for an intersection on $T$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_T$ to 
@@
 
-We shall call every IC, that was created in the coplanar case, \emph{degenerate} since these will later
-special treatment.
-
-Checking the same sign of the inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
+We shall call every IC, that is created in the coplanar case, \emph{degenerate} since these will later need special treatment.
+
+Checking the same sign of the permuted inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
 line with respect to the triangle. Adaptive-precision evaluation of the geometric predicates was designed by Schewchuk \cite{shewchuk_adaptive_1997}
@@
 \subsection{Intersection Line-Tetrahedron (1d-3d)}
-\notePE{degenerate not defined yet.. do you call it coplanar now?}
+%\notePE{degenerate not defined yet.. do you call it coplanar now?}
 In this section we consider an intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 

### 2016-10-02 cube_scale/get_data.py
Add cube scale data and summary

@@ -1,0 +1,86 @@
+import json
+import numpy as np
+
+'''
+def get_frame(data, addr):
+    frame=data
+    for (level,idx) in enumerate(addr):        
+        if "children" in frame:
+            childs=frame["children"]
+            if idx >= len(childs):
+                print "Error: idx {} greater then number of child {} at level {}".format(idx, len(childs), level)
+                return None
+            else:
+                frame=childs[idx]
+        else:
+            print "No childs at level {}".format(level)
+            return None
+    return frame    
+'''
+
+def get_frame_tag(data, tag):
+    if (data["tag"] == tag):
+        return data   
+    for child in data.get("children", []):        
+        frame = get_frame_tag(child, tag)
+        if (frame != None):
+            return frame 
+    return None
+
+def get_frame_tags(data, tags):
+    frame =data
+    for tag in tags:
+        frame = get_frame_tag(frame, tag)        
+        if frame == None:
+            return None
+    return frame    
+
+class ProfilerTable:
+    def __init__(self, n_tests):
+        self.table = {}
+        self.n_tests = n_tests
+        
+    
+    def append(self, i_test, frame, item):        
+        if frame == None:
+            return
+        if not frame["tag"] in self.table:
+            self.table[frame["tag"]]=[0]*self.n_tests
+            
+        self.table[frame["tag"]][i_test] = frame[item]
+        #print self.table
+        
+    def save(self, f_name):
+        with open(f_name, "w") as out_file:    
+            for (tag, values) in self.table.iteritems():
+                row='"' + tag + '"'
+                for value in values:
+                    row+=", {}".format(value)
+                out_file.write(row+"\n")
+    
+    def statistics(self, f_name):
+        
+
+def algorithm_variant(f_base, subdata):
+    table = ProfilerTable(7)
+    for i_test in range(0, 7):    
+        f_name=f_base + "{}.msh.log".format(i_test)
+        with open(f_name) as data_file:    
+            data = json.load(data_file)
+            frame_0  = data["children"][0]
+            table.append(i_test, get_frame_tag(frame_0, "MESH - setup topology"), "cumul-time-min")
+            table.append(i_test, get_frame_tag(frame_0, "Intersections 2D-3D"), "cumul-time-min")        
+            table.append(i_test, get_frame_tag(frame_0, "Intersection initialization"), "cumul-time-min")
[…]

### 2016-10-02 paper_intersections.tex
Capitalize headings.

@@
 
-\subsubsection{Intersections on sides of $S_2$}
+\subsubsection{Intersections on Sides of $S_2$}
 \label{sec:sides}
@@
 
-\subsubsection{Intersections on edges of $S_3$}
+\subsubsection{Intersections on Edges of $S_3$}
 \label{sec:edges}
@@
 % intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.
-\subsubsection{Ordering of intersections}
+\subsubsection{Ordering of Intersections}
 \label{sec:ordering}
@@
 
-\subsection{Intersections between component meshes}
+\subsection{Intersections Between Component Meshes}
 \label{sec:components}
@@
 
-\subsection{Theoretical comparison}
+\subsection{Theoretical Comparison}
 Before presenting the results of our benchmarks, let us try to estimate the number of arithmetic operations performed during 1d-3d and 2d-3d element intersections

### 2016-10-02 paper_intersections.tex
New plots for the scaling benchmark.

--- 2016-10-02 paper_intersections.tex
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{\figpath intersections_test1_cube_speed_scaling.pdf}
-    \caption{Dependence of the algorithms performance on number of intersection (and mesh refinement). }
+    \includegraphics[width=1.0\textwidth]{\figpath cube_scale.pdf}
+    \caption{Time complexity for the initialization phase (left) with respect to total mesh size and the intersection algorithm (right) with respect to the size of the component mesh.}
     \label{fig:cube_speed}

### 2016-10-02 paper_intersections.tex
Some corrections and comments on 2d-3d.

--- 2016-10-02 paper_intersections.tex
@@
 %\notePE{degenerate not defined yet.. do you call it coplanar now?}
+\notePE{If we stick to $S_2$ in the section before, we can change line segment $p$ into $S_1$ here.}
 In this section we consider an intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
@@
   \SetKw{continue}{continue}
-  \KwIn{input data}
-  \KwOut{List of ICs on sorted output data}  
+  \KwIn{input data \notePE{$S_2$ and $S_3$}}
+  \KwOut{List \notePE{$I$} of ICs on sides of \notePE{$S_2$, what output data??} sorted output data}  
   $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
@@
   \DontPrintSemicolon
-  \KwIn{$I$ with ICs on $S_2$ boundary, partially filled $F$}
+  \KwIn{\notePE{this should go to previous Alg.} $I$ with ICs on $S_2$ boundary, partially filled $F$}
   \KwOut{all ICs in $I$, complete $F$}
@@
   \end{center}
-  \caption{Order of faces adjacent to the oriented edge $e$ pointing up.}
+  \caption{Order of faces adjacent to the oriented edge $e$ pointing towards us.}
   \label{fig:edge_faces}
@@
 The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position at the vertex or on the edge of $S_3$ already computed
-in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping the edges with none or degenerate $L[e]$.
-For every IC $p=L[e]$ we first get its (generalized) faces that would appear before and after the IC on IP, assuming that $p$ is inside $S_2$.
+in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping the edges with none or degenerate\notePE{not in algorithm} $L[e]$.
+For every intersection corner $p=L[e]$, we first get its (generalized) faces that would appear before and after the IC on IP, assuming that $p$ is inside $S_2$.
 
@@
 However,
-if $p$ is on boundary of $S_2$ it is already in $I$. Denoting $x$ the \nface of $S_3$ the IC lies on, we use the back-link from $x$ to 
-IC $q\in I$ and if $q$ points back to $x$ we set the new successor $f_1$ to it (line \ref{line:successor}). 
+if $p$ is on boundary of $S_2$ it is already in $I$. Denoting $x$ the \nface of $S_3$ the IC lies on, we use the backlink from $x$ to 
+IC $q\in I$ and if $q$ points back to $x$, we set the new successor $f_1$ to it (line \ref{line:successor}). 
 Otherwise $f_0$ is used as the predecessor of $q$ (line \ref{line:predecessor}).
@@
   \KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
-  \KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
+  \KwOut{\notePE{I don't like the word conincident here - vertex lies on the edge}$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
   $e_0,\ e_1,\ e_2$ edges coincident with $v$ oriented out of $v$
@@
 
-This function gets as a parameter IC $p$ at the vertex $v$ of $S_3$ which is a special case of anon-degenerate edge-triangle intersection. 
-We use signs and degenerate indicator of ICs of the three edges coincident with $v$ to return generalized faces of $S_3$ 
+The function in Algorithm \ref{algo:vertex_faces} gets as a parameter IC $p$ at the vertex $v$ of $S_3$ which is a special case of a non-degenerate edge-triangle intersection. 
+We use the signs $s[:]$ \notePE{I do not understand properly what the signs are: in alg.
+is definition $s[i] = L[e_i]$, but in $L$ are ICs..
+I don't remember defining the the sign of IC before - the 4.
+case is called 'All ICS have same sign'} and the degenerate indicator of ICs of the three edges \notePE{again coincident} coincident with $v$ to return generalized faces of $S_3$
 preceding and succeeding $p$ on the polygons boundary assuming $p$ is at interior of $S_2$.
 Possible cases are:
+\notePE{I feel that calling the edges 'degenerate' because degenerate IC lies on them is little confusing..}
 \begin{itemize}
- \item {\bf Single degenerated IC} (line \ref{line:one_degenerated}){\bf .} Let us denote $e$ the edge with degenerated IC 
+ \item {\bf Single degenerate IC} (line \ref{line:one_degenerated}){\bf .} Let us denote $e$ the edge with degenerate IC 
  and $f$ the face between the other two edges.
- The other two (non-degenerates) edges may have either the opposite sign (the plane is cutting $S_3$) 
+ The other two (non-degenerate) edges may have either the opposite sign (the plane is cutting $S_3$) 
  or the same sign (the plane is touching $S_3$ at the edge $e$).
@@
 
- \item {\bf Two degenerated ICs} (line \ref{line:two_degenerated}){\bf .} A face of $S_3$ lies in the plane of $S_2$. 
+ \item {\bf Two degenerate ICs} (line \ref{line:two_degenerated}){\bf .} A face of $S_3$ lies in the plane of $S_2$. 
  Let $e$ be the single non-degenerate edge. We treat the two degenerate edges as faces adjacent to $e$ 
@@
  \item {\bf All ICs have the same sign} (line \ref{line:same_signs}){\bf .} Since $S_2$ is touching $S_3$ 
- at the vertex $v$, the polygon degenerates into point and thus no connection information is necessary. We add IS to $J$ and return any pair of faces.
+ at the vertex $v$, the polygon degenerates into a point and thus no connection information is necessary. We add IC to $J$ and return any pair of faces.
 \end{itemize}

### 2016-10-02 paper_intersections.tex
Improve notation in 12d and 13d.

@@
 \label{sec:1d-2d}
-\notePE{I would stick to chosen notation - triangle $S_2$, and possibly renamed side $s_i$...}
-Let us consider a line segment $p$ with parametric equation 
+Let us consider a line $p$ with parametric equation 
 \begin{equation}
     \label{eq:line_parametric}
-    \vc X = \vc A + t\vc u,\ t\in (0,1)
+    \vc X = \vc A + t\vc u,
 \end{equation}
-and a triangle $T$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
+on which a line segment $S_1$ is defined by $t\in [0,1]$ and a triangle $S_3$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
 with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. 
@@
 The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
-is an intersection point $\vc X$ on the $p$ and inside the triangle $T$. 
-The barycentric coordinates of $\vc X$ on $T$ are
+is an intersection point $\vc X$ on the $p$ and inside the triangle $S_3$. 
+The barycentric coordinates of $\vc X$ on $S_3$ are
 \begin{equation}
@@
 \]
-The point $\vc X$ is inside of $T$ if and only if $w_i>0$ for all $i=0,1,2$.
+The point $\vc X$ is inside $S_3$ if and only if $w_i>0$ for all $i=0,1,2$.
 \end{proof}
-Having the barycentric coordinates of $\vc X$ on $T$, we can compute also its local coordinate on $p$ from its parametric form:
+Having the barycentric coordinates of $\vc X$ on $S_3$, we can compute also its local coordinate on $p$ from its parametric form:
 \begin{equation}
@@
     \item If any $w_i$ is less than $\epsilon$, there is no intersection, return empty IP.  
-    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_T = (2, 0)$ for the IC.
-    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_T =(1,i)$.
-    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_T=(0,i)$.
+    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_3} = (2, 0)$ for the IC.
+    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_3} =(1,i)$.
+    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_3}=(0,i)$.
     \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
         projected to the plane $x_i=0$ where $i$ is the index of the maximal component of the triangle's normal vector.
-        Every pair $p$, $s_i$ is checked for an intersection on $T$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_T$ to 
+        Every pair $p$, $s_i$ is checked for an intersection on $S_3$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_{S_3}$ to 
         $(1, i)$ or $(0, i)$, respectively. At most two ICs are obtained.
     \item For each IC the barycentric coordinates $(1-t, t)$ on the line $p$ are computed according to \eqref{eq:line}. 
-    \item If $t\in (-\epsilon, \epsilon)$ or $t\in (1-\epsilon, 1+\epsilon)$, we set $\tau_p = (0,0)$ or $\tau_p = (0,1)$, respectively.
+    \item If $t\in (-\epsilon, \epsilon)$ or $t\in (1-\epsilon, 1+\epsilon)$,
+        we set the end point of $S_1$: $\tau_{S_1} = (0,0)$ or $\tau_{S_1} = (0,1)$, respectively.
     \item If $t\notin (-\epsilon, 1+\epsilon)$, the IC is eliminated.
@@
 \subsection{Intersection Line-Tetrahedron (1d-3d)}
-%\notePE{degenerate not defined yet.. do you call it coplanar now?}
-\notePE{If we stick to $S_2$ in the section before, we can change line segment $p$ into $S_1$ here.}
-In this section we consider an intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
+In this section we consider an intersection of a line segment $S_1$, defined by an interval $t\in [0,1]$ of the line $p$ defined in \eqref{eq:line_parametric}, with a tetrahedron 
 $S_3$. The used algorithm is based on the 1d-2d algorithm and closely follows \cite{platis_fast_2003}. Our modification takes into account
@@
   \SetKw{break}{break}
-  \KwIn{Tetrahedron $S_3$, line segment $p$.}
+  \KwIn{Line segment $S_1$ of line $p$, Tetrahedron $S_3$.}
   \KwOut{List $I$ of ICs sorted along $p$.}  
@@
   }
-  \lIf{$\abs{I}=1$ \and   $I$ is outside of $p$}{ erase $I$} \label{line:trimming}
+  \lIf{$\abs{I}=1$ \and   $I$ is outside of $S_1$}{ erase $I$} \label{line:trimming}
   \ElseIf{$\abs{I}=2$}{    
-    trim intersection with respect to the line segment $p$
+    trim intersection with respect to the line segment $S_1$
   }
@@
 we do the line segment trimming from the line \ref{line:trimming} further. 
-If we have only one IC, we check that it actually lies inside the line segment (otherwise, we throw it away).
-If we have two ICs, and if both lie outside the line segment $p$, we eliminate both of them. 
-If one of the ICs lies out of $p$,
-we use the closest end point of the line segment instead and interpolate barycentric coordinates of the IC on $S_3$. The topological positions are updated as well.
+If we have only one IC, we check that it actually lies inside $S_1$ (otherwise, we throw it away).
+If we have two ICs, and if both lie outside $S_1$, we eliminate both of them. 
+If one of the ICs lies out of $S_1$,
+we use the closest end point of the line segment instead and interpolate barycentric coordinates of the IC on $S_3$. The topological positions $\tau_{S_1}$ and $\tau_{S_3}$ are updated as well.
 The result of the algorithm is 0, 1, or 2 ICs, sorted by the parameter $t$ in the direction of the line $p$.

### 2016-10-02 paper_intersections.tex
Corrections of coincident etc.

--- 2016-10-02 paper_intersections.tex
@@
 for each intersecting element $K$ of the pair. The pair $\tau_K = (d_K, i_K)$
-is called the \emph{topological position} of the IC on $K$.
+is called the \emph{topological position} of the IC on $K$. Moreover, as every IC is result of some permuted
+inner product of the \plucker coordinates (see Section \label{sec:1d-2d}), we store the sign of the product as well.
 
@@
 \label{sec:1d-2d}
-\notePE{I would stick to chosen notation - triangle $S_2$, and possibly renamed side $s_i$...}
 Let us consider a line segment $p$ with parametric equation 
@@
 \end{equation}
-and a triangle $T$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
+and a triangle $S_2$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
 with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. 
@@
 The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
-is an intersection point $\vc X$ on the $p$ and inside the triangle $T$. 
-The barycentric coordinates of $\vc X$ on $T$ are
+is an intersection point $\vc X$ on the $p$ and inside the triangle $S_2$. 
+The barycentric coordinates of $\vc X$ on $S_2$ are
 \begin{equation}
@@
 \]
-The point $\vc X$ is inside of $T$ if and only if $w_i>0$ for all $i=0,1,2$.
+The point $\vc X$ is inside of $S_2$ if and only if $w_i>0$ for all $i=0,1,2$.
 \end{proof}
-Having the barycentric coordinates of $\vc X$ on $T$, we can compute also its local coordinate on $p$ from its parametric form:
+Having the barycentric coordinates of $\vc X$ on $S_2$, we can compute also its local coordinate on $p$ from its parametric form:
 \begin{equation}
@@
     \item If any $w_i$ is less than $\epsilon$, there is no intersection, return empty IP.  
-    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_T = (2, 0)$ for the IC.
-    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_T =(1,i)$.
-    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_T=(0,i)$.
+    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_2} = (2, 0)$ for the IC.
+    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_2} =(1,i)$.
+    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_2}=(0,i)$.
     \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
         projected to the plane $x_i=0$ where $i$ is the index of the maximal component of the triangle's normal vector.
-        Every pair $p$, $s_i$ is checked for an intersection on $T$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_T$ to 
+        Every pair $p$, $s_i$ is checked for an intersection on $S_2$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_T$ to 
         $(1, i)$ or $(0, i)$, respectively. At most two ICs are obtained.
@@
 and used for 2d-2d mesh intersections in \cite{elsheikh_reliable_2012}. However, we rather apply a fixed tolerance check for the zero 
-barycentric coordinates and consistently keep the topological positions in this and related algorithms. \noteJB{Can we make the algorithm 
-\emph{parsimonious} in the spirit of the Fortune \cite{fortune_stable_1989} quoted by Schewchuk? 
-Seems that our problem is more local than the line example that was proven to be NP-hard.}
+barycentric coordinates and consistently keep the topological positions in this and related algorithms.
+
+%\noteJB{Can we make the algorithm 
+%\emph{parsimonious} in the spirit of the Fortune \cite{fortune_stable_1989} quoted by Schewchuk? 
+%Seems that our problem is more local than the line example that was proven to be NP-hard.}
 
@@
 \subsection{Intersection Line-Tetrahedron (1d-3d)}
-%\notePE{degenerate not defined yet.. do you call it coplanar now?}
 \notePE{If we stick to $S_2$ in the section before, we can change line segment $p$ into $S_1$ here.}
@@
         set $\tau_{S_3} = (1,e)$\;
-        mark faces coincident with $e$
+        mark faces incident to $e$
     }
@@
         set $\tau_{S_3} = (0,v)$\;
-        mark faces coincident with $v$
+        mark faces incident with $v$
     }
@@
 There are special cases when the IP is degenerated to a line or a point. 
-\notePE{next sentence: how should I understand 'may possibly be'; 'an IC' instead of 'some IC'}
-If some IC may possibly be part of the such degenerated IP we put it into the list $J$.
+If we obtain an IC during the calculation that may possibly be part a degenerated IP but
+we can not decide it at the moment we put that IC into the list $J$.
 
@@
     \includegraphics[width=0.65\textwidth]{\figpath tracing.pdf}
-    \caption{Example of an intersection 2D-3D, demonstrating the ICs ordering. We see at every 
+    \caption{Example of an intersection 2d-3d, demonstrating the ICs ordering. We see at every 
     intersection polygon corner $p_i$ which \nfaces it lies on. Looking at $p_0$, the connection table entries
@@
   \SetKw{continue}{continue}
-  \KwIn{input data \notePE{$S_2$ and $S_3$}}
-  \KwOut{List \notePE{$I$} of ICs on sides of \notePE{$S_2$, what output data??} sorted output data}  
+  \KwIn{$S_2$ and $S_3$}
+  \KwOut{List $I$ with ICs on sides of $S_2$}  
   $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
-  \For{side $s$ of $S_2$}{ \nllabel{line:one side loop}
+  \For{side $s$ of $S_2$}{ 
     $L$ = intersection($s, S_3$)\;
@@
     }
-    \For{$p$ in $L$}{
+    \For{$p$ in $L$}{ \nllabel{line:one side loop}
+        append $p$ to $I$
 %        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
@@
 To this end we save the IC into separate list $J$ and skip filling of the connection tables.
-\notePE{here it is weird... there is no line appending the IC into resulting list.. Which is the resulting list??
-I find the reference to 'line:one side loop' also incorrect..}
+%\notePE{here it is weird... there is no line appending the IC into resulting list.. Which is the resulting list??
+%I find the reference to 'line:one side loop' also incorrect..}
 In the regular case, we process each of the two ICs in $L$ (loop on line \ref{line:one side loop}). The IC $p$ is added to the list $I$,
@@
   \DontPrintSemicolon
-  \KwIn{\notePE{this should go to previous Alg.} $I$ with ICs on $S_2$ boundary, partially filled $F$}
-  \KwOut{all ICs in $I$, complete $F$}
+  \KwIn{$I$ with ICs on $S_2$ boundary, partially filled $F_p$, $F_g$}
+  \KwOut{all ICs in $I$, complete $F_p$, $F_g$}
 
   \lFor{edge $e$ of $S_3$}{$L[e]$ = intersection($e, S_2$)}  \nllabel{line:12edges}
-  \For{edge $e$ of $S_3$ with non-empty $L[e]$}{
+  \For{edge $e$ of $S_3$ with regular $L[e]$}{
     $p=L[e]$\;
@@
 Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
-First, the intersection $L[e]$ is evaluated for every edge $e$.
-The loop produces ICs in the interior of $S_2$ and possibly those ICs with special position at the vertex or on the edge of $S_3$ already computed
-in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping the edges with none or degenerate\notePE{not in algorithm} $L[e]$.
+First, the intersection $L[e]$ is evaluated for every edge $e$. The loop produces ICs in the interior of $S_2$ and 
+possibly those ICs with special position at the vertex or on the edge of $S_3$ already computed 
+in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping the edges with none or degenerate $L[e]$.
 For every intersection corner $p=L[e]$, we first get its (generalized) faces that would appear before and after the IC on IP, assuming that $p$ is inside $S_2$.
@@
   \KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
-  \KwOut{\notePE{I don't like the word conincident here - vertex lies on the edge}$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
-  $e_0,\ e_1,\ e_2$ edges coincident with $v$ oriented out of $v$
+  \KwOut{pair of \nfaces incident with $v$ that is intersected by the plane of $S_2$}
+  $e_0,\ e_1,\ e_2$ edges incident with $v$ oriented out of $v$\;   
   $s[i] = L[e_i]$, for $i=0,1,2$, \;
@@
 
-The function in Algorithm \ref{algo:vertex_faces} gets as a parameter IC $p$ at the vertex $v$ of $S_3$ which is a special case of a non-degenerate edge-triangle intersection. 
-We use the signs $s[:]$ \notePE{I do not understand properly what the signs are: in alg.
-is definition $s[i] = L[e_i]$, but in $L$ are ICs..
-I don't remember defining the the sign of IC before - the 4.
-case is called 'All ICS have same sign'} and the degenerate indicator of ICs of the three edges \notePE{again coincident} coincident with $v$ to return generalized faces of $S_3$
-preceding and succeeding $p$ on the polygons boundary assuming $p$ is at interior of $S_2$.
+The function in Algorithm \ref{algo:vertex_faces} gets as a parameter IC $p$ at the vertex $v$ of $S_3$ 
+which is a special case of a non-degenerate edge-triangle intersection. There are three
+edges incident with the vertex $v$, results $s[i]$ of their intersections with $S_2$ may be one of: no IC, 
+degenerate IC, positive IC and negative IC. Accordingly we call the edge: without intersection, degenerate, positive, or negative. 
+We use these edge idicators to return generalized faces of $S_3$ preceding and succeeding $p$ on the polygons boundary assuming $p$ is at interior of $S_2$.
 Possible cases are:
-\notePE{I feel that calling the edges 'degenerate' because degenerate IC lies on them is little confusing..}
 \begin{itemize}
@@
 % 
-% and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
+% and need to insert them into $I$ to correct place. To this end we exploit additional information about incidence of points
 % with faces of $S_3$.
@@
 %   %\KwIn{vertex $v$ of $S_3$, $L[:]$ intersection results for edges of $S_3$}
-%   %\KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, coincident with $v$ and intersected by the plane of $S_2$}
+%   %\KwOut{$(x_1, x_2)$, $x_1, x_2 \in M_3$, incident with $v$ and intersected by the plane of $S_2$}
 %   mark all $c\in \mathcal T_c$ unvisited\;
@@
     \item \textbf{IC is on the boundary of $c$  and inside $b$.} \\
-            We find all the sides $S$ coincident with the \nface of $c$ on which IC lies. Then we get all component
+            We find all the sides $S$ of $c$ incident with the \nface of $c$ on which IC lies. Then we get all component
             elements $C'$ neighboring with $c$ over any side $s\in S$. And finally, we push all pairs $(c',b)$, $c'\in C'$ 
@@
     \item \textbf{IC is inside $c$ and on the boundary of $b$.} \label{enum:prolong2}\\
-            We find all the faces $F$ coincident with the \nface of $b$ on which IC lies. 
+            We find all the faces $F$ of $b$ incident with the \nface of $b$ on which IC lies. 
             Then we get all bulk elements $B'$ neighboring with $b$ over any face $f\in F$,

### 2016-10-02 paper_intersections.tex

@@
 \label{sec:1d-2d}
-Let us consider a line segment $p$ with parametric equation 
+Let us consider a line $p$ with parametric equation 
 \begin{equation}
     \label{eq:line_parametric}
-    \vc X = \vc A + t\vc u,\ t\in (0,1)
+    \vc X = \vc A + t\vc u,
 \end{equation}
-and a triangle $S_2$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
+on which a line segment $S_1$ is defined by $t\in [0,1]$ and a triangle $S_3$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
 with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. 
@@
 The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
-is an intersection point $\vc X$ on the $p$ and inside the triangle $S_2$. 
-The barycentric coordinates of $\vc X$ on $S_2$ are
+is an intersection point $\vc X$ on the $p$ and inside the triangle $S_3$. 
+The barycentric coordinates of $\vc X$ on $S_3$ are
 \begin{equation}
@@
 \]
-The point $\vc X$ is inside of $S_2$ if and only if $w_i>0$ for all $i=0,1,2$.
+The point $\vc X$ is inside $S_3$ if and only if $w_i>0$ for all $i=0,1,2$.
 \end{proof}
-Having the barycentric coordinates of $\vc X$ on $S_2$, we can compute also its local coordinate on $p$ from its parametric form:
+Having the barycentric coordinates of $\vc X$ on $S_3$, we can compute also its local coordinate on $p$ from its parametric form:
 \begin{equation}
@@
     \item If any $w_i$ is less than $\epsilon$, there is no intersection, return empty IP.  
-    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_2} = (2, 0)$ for the IC.
-    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_2} =(1,i)$.
-    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_2}=(0,i)$.
+    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_3} = (2, 0)$ for the IC.
+    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_3} =(1,i)$.
+    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_3}=(0,i)$.
     \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
         projected to the plane $x_i=0$ where $i$ is the index of the maximal component of the triangle's normal vector.
-        Every pair $p$, $s_i$ is checked for an intersection on $S_2$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_T$ to 
+        Every pair $p$, $s_i$ is checked for an intersection on $S_3$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_{S_3}$ to 
         $(1, i)$ or $(0, i)$, respectively. At most two ICs are obtained.
     \item For each IC the barycentric coordinates $(1-t, t)$ on the line $p$ are computed according to \eqref{eq:line}. 
-    \item If $t\in (-\epsilon, \epsilon)$ or $t\in (1-\epsilon, 1+\epsilon)$, we set $\tau_p = (0,0)$ or $\tau_p = (0,1)$, respectively.
+    \item If $t\in (-\epsilon, \epsilon)$ or $t\in (1-\epsilon, 1+\epsilon)$,
+        we set the end point of $S_1$: $\tau_{S_1} = (0,0)$ or $\tau_{S_1} = (0,1)$, respectively.
     \item If $t\notin (-\epsilon, 1+\epsilon)$, the IC is eliminated.
@@
 \subsection{Intersection Line-Tetrahedron (1d-3d)}
-\notePE{If we stick to $S_2$ in the section before, we can change line segment $p$ into $S_1$ here.}
-In this section we consider an intersection of a line segment $p$ given by the parametric equation \eqref{eq:line_parametric} with a tetrahedron 
+In this section we consider an intersection of a line segment $S_1$, defined by an interval $t\in [0,1]$ of the line $p$ defined in \eqref{eq:line_parametric}, with a tetrahedron 
 $S_3$. The used algorithm is based on the 1d-2d algorithm and closely follows \cite{platis_fast_2003}. Our modification takes into account

### 2016-10-02 paper_intersections.tex
Minor language corrections.

@@
 for each intersecting element $K$ of the pair. The pair $\tau_K = (d_K, i_K)$
-is called the \emph{topological position} of the IC on $K$. Moreover, as every IC is result of some permuted
-inner product of the \plucker coordinates (see Section \label{sec:1d-2d}), we store the sign of the product as well.
+is called the \emph{topological position} of the IC on $K$. Moreover, as every IC is a result of a permuted
+inner product of some \plucker coordinates (see Section \label{sec:1d-2d}), we store the sign of the product as well.
 
@@
 There are special cases when the IP is degenerated to a line or a point. 
-If we obtain an IC during the calculation that may possibly be part a degenerated IP but
-we can not decide it at the moment we put that IC into the list $J$.
+If we obtain an IC during the calculation that may possibly be a part a degenerate IP, which
+we cannot decide at the moment, we put that IC into the list $J$.
 
@@
     \includegraphics[width=0.65\textwidth]{\figpath tracing.pdf}
-    \caption{Example of an intersection 2d-3d, demonstrating the ICs ordering. We see at every 
+    \caption{An example of an intersection 2d-3d, demonstrating the ICs ordering. We see at every 
     intersection polygon corner $p_i$ which \nfaces it lies on. Looking at $p_0$, the connection table entries

### 2016-10-02 paper_intersections.tex
Minor language corrections.

@@
 \end{equation}
-on which a line segment $S_1$ is defined by $t\in [0,1]$ and a triangle $S_3$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
+on which a line segment $S_1$ is defined by $t\in [0,1]$ and a triangle $S_2$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
 with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$. 
@@
 The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
-is an intersection point $\vc X$ on the $p$ and inside the triangle $S_3$. 
-The barycentric coordinates of $\vc X$ on $S_3$ are
+is an intersection point $\vc X$ on the $p$ and inside the triangle $S_2$. 
+The barycentric coordinates of $\vc X$ on $S_2$ are
 \begin{equation}
@@
 \]
-The point $\vc X$ is inside $S_3$ if and only if $w_i>0$ for all $i=0,1,2$.
+The point $\vc X$ is inside $S_2$ if and only if $w_i>0$ for all $i=0,1,2$.
 \end{proof}
-Having the barycentric coordinates of $\vc X$ on $S_3$, we can compute also its local coordinate on $p$ from its parametric form:
+Having the barycentric coordinates of $\vc X$ on $S_2$, we can compute also its local coordinate on $p$ from its parametric form:
 \begin{equation}
@@
     \item If any $w_i$ is less than $\epsilon$, there is no intersection, return empty IP.  
-    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_3} = (2, 0)$ for the IC.
-    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_3} =(1,i)$.
-    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_3}=(0,i)$.
+    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_2} = (2, 0)$ for the IC.
+    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_2} =(1,i)$.
+    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_2}=(0,i)$.
     \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
         projected to the plane $x_i=0$ where $i$ is the index of the maximal component of the triangle's normal vector.
-        Every pair $p$, $s_i$ is checked for an intersection on $S_3$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_{S_3}$ to 
+        Every pair $p$, $s_i$ is checked for an intersection on $S_2$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_{S_2}$ to 
         $(1, i)$ or $(0, i)$, respectively. At most two ICs are obtained.

### 2016-10-02 paper_intersections.tex
Hopefully final improvement to prolongation scheme.
Some improvements in 2d2d section.

@@
   \centering    
-    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_jb_fix_italic.pdf}
+    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_pe_final.pdf}
   \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
@@
 \label{sec:components}
-We consider here the situation that components are in the interior of the 3d bulk mesh. After we compute
-all component-bulk intersections, we use it to easily find all the component-component intersection candidates.
-If the bulk element intersects more than one component element, than we can create candidates from these.
-
-Let us start with description of how we store the intersection results, which will be of great importance here.
-For each element intersection, we save the following data: reference to component and bulk element, 
-barycentric coordinates on both and index of the component. These objects are stored in separate vectors for each pair 
-of dimensions. Further we define a sparse matrix (\emph{intersection map}) which has as many rows as there are elements in the mesh.
-At each row (element), we save the references to all other elements, having intersection with element corresponding to this row, 
-and references to the actual intersection data.
-
-The algorithm for 2d-2d intersections works as follows. We iterate over all 2d-3d intersections, respectively over
+We consider here the situation where components are in the interior of the 3d bulk mesh. After we compute
+all component-bulk intersections, we use it to easily find all the component-component intersection candidate
+pairs.
+If the bulk element intersects more than one component element, then we look for candidate pairs only among these.
+
+Let us start with the description of how we store the intersection results, which will be of great importance here.
+For each element intersection, we save the following data: references to the component and bulk element, 
+the barycentric coordinates on both and the index of the component.
+These objects are stored in separate vectors for each pair of dimensions.
+Further we define a matrix (\emph{intersection map}) which has as many rows as there are elements in the mesh.
+At each row, we save the references to all other elements, having intersection with the element corresponding to this row, and references to the actual intersection data.
+
+The algorithm for 2d-2d intersections works as follows. We iterate over all 2d-3d intersections, in fact over
 the bulk elements having some intersections with 2d components. We look at the intersection map at the
 bulk element row and collect all elements that have 2d-3d intersection with it.
-Now comes in play the component number $\gamma$. If $\gamma$ is equal for both component elements, then 
+Then we create all possible pairs from the collected component elements.
+Now comes in play the component number $\gamma$. If the elements of a single pair have $\gamma$ equal, then 
 these are part of a single continuous component and we do not compute any intersection.

### 2016-10-02 paper_intersections.tex

@@
 In the beginning, we provide some software development related information.
-Then analyze theoretical number of FLOPS in our element intersection algorithms with 
+Then we analyze the theoretical number of FLOPS in our element intersection algorithms with 
 other state of art algorithms.
-Next we shall compare our algorithms with different initialization phase (candidate pairs search),
-and using the advancing front method or not. We shall show the results both on a mesh of a real locality
+Next we compare our algorithms with different initialization phase (candidate pairs search),
+and using the advancing front method or not. We show the results both on a mesh of a real locality
 and an artificial mesh.
@@
 The global mesh intersection algorithm for a composed mesh $\mathcal T$ presented in Section \ref{sec:front_advancing} has been
-implemented in three variants. First variant, use a full search (FS) over the bulk mesh to get initial pair for the advancing front algorithm (AF).
-Second variant, use the BIH to accelerate the initialization of the AF algorithm. Third variant doesn't use AF at all and relies only on the BIH. 
+implemented in three variants. First variant uses a full search (FS) over the bulk mesh to get the initial pair for the advancing front algorithm (AF).
+Second variant uses the BIH to accelerate the initialization of the AF algorithm. Third variant doesn't use AF at all and relies only on the BIH. 
 In this section, we compare these three variants (FS+AF, BIH+AF, BIH) on one artificial composed mesh and one raising from a real hydrogeological simulation.
@@
 of the mesh intersection algorithm is shown on \fig{fig:cube_speed}. As the number of component meshes is low and they are completely 
-inside of the bulk mesh the FS+AF variant was the fastest and with smallest grow as expected. On the other hand the BIH variant is constantly by 20\%
-slower then the BIH+AF variant. That is roughly related to the average fraction of the non-intersecting 3d element in the bounding box of a 2d element.
-The slightly larger grow of the BIH algorithm is masked by the common superlinear grow with power about $1.1$ which we do not completely understand.
+inside of the bulk mesh the FS+AF variant is the fastest and with the smallest growth as expected.
+On the other hand the BIH variant is constantly slower by 20\% than the BIH+AF variant.
+That is roughly related to the average fraction of the non-intersecting 3d element in the bounding box of a 2d element.
+The slightly larger growth of the BIH algorithm is masked by the common superlinear growth with power about $1.1$ which we do not completely understand.
 \noteJB{???}
@@
 the bulk mesh we also prepared a mesh with the artificially extended fractures (\fig{fig:bedrichov_extend}). 
-Each of these meshes contains 28 fractures in 9 2d components and single 1d component, the tunnel.
+Each of these meshes contains \notePE{what is the 9 number??} 28 fractures in 9 2d components and a single 1d component, the tunnel.
 

### 2016-10-02 paper_intersections.tex
Suggestions for classification.
banchmarks modification

@@
 % in Flow123d.
-Part of the software is also a legacy code for element intersections that we refer to as \ngh.
+%Part of the software is also a legacy code for element intersections that we refer to as \ngh.
 
@@
 \subsection{Theoretical Comparison}
-Before presenting the results of our benchmarks, let us try to estimate the number of arithmetic operations performed during 1d-3d and 2d-3d element intersections
-as we use different algorithms for the elementary line-triangle intersection. We consider 4 algorithms for the line-triangle intersections: \plucker algorithm 
-described in Section \ref{sec:1d-2d}, the legacy code \ngh, the plane clipping algorithm due to Haines \cite{haines_fast_1991}, the minimum storage
-algorithm due to Möller and Trumbore (MT) \cite{moller_fast_1997}. Raw numbers of arithmetic operations are summarized in Table \ref{tab:fundamental_flops}.
-For the \plucker and \ngh we count FLOPS from the implementation of individual intersection algorithms, for Haines and MT we estimated FLOPS in theoretical 
-implementation. In particular we account for reuse of the calculations in \plucker and Haines algorithms. Conclusions from this census are:
-algorithms based on the \plucker coordinates should be competitive with state of art algorithms in the case of 1d-3d and 2d-3d intersections. The expected performance
-for the 1d-2d case seems to be poor however these intersections are computed after 1d-3d and 2d-3d so the \plucker coordinates may be reused, then we get 
-quite competitive $45$ FLOPS. Similarly we may expect better times in remaining two intersection cases when we account for the reuse of calculation between elements.
-Compared to the legacy code \ngh the \plucker algorithm for 1d-3d should be about $2.5\times$ faster and the 2d-3d about $5\times$ faster.
-
-\noteJB{Need better timing for \plucker with respect to NGH in 
-2d-3d  case. Could it be due to polygon tracing?}
+It proved to be a bit problematic to compare the presented algorithms for element-element intersections to any of the state of art
+algorithms e.g. from the field of computer graphics. The algorithms for computer graphics applications are specialized for
+the 1d-2d and 1d-3d cases and they provide different output information then our algorithms. Moreover our implementation 
+is not yet fully optimized to be on par with the fine tuned implementations. Instead, we present a theoretical comparison 
+in terms of estimated number of floating point operations (FLOPS) performed by individual algorithms. As the intersection 
+algorithms works on small data they should not be limited by the memory access, thus such comparison may be realistic.
+
+We consider 3 algorithms for the line-triangle intersections: \plucker algorithm 
+described in Section \ref{sec:1d-2d}, the algorithm based on the plane clipping due to Haines \cite{haines_fast_1991}, and the minimum storage
+algorithm due to M{\" o}ller and Trumbore (MT) \cite{moller_fast_1997}. For the later two algorithms we have considered strightforward modifications
+to make them return qualitatively same output as our algorithms for 1d-2d, 1d-3d, and 2d-3d cases.
+Estimated numbers of FLOPS for all cases are summarized in Table \ref{tab:fundamental_flops}.
+For the \plucker, we count FLOPS actually made by the implementation of individual intersection algorithms. For Haines and MT, 
+we estimated number of FLOPS in theoretical implementations. In particular we account for reuse of the calculations in \plucker and Haines algorithms. 
+Conclusions from this census are: algorithms based on the \plucker coordinates should be competitive with state of art algorithms in the case of 1d-3d 
+and 2d-3d intersections. The expected performance for the 1d-2d case seems to be poor however these intersections are computed after 1d-3d and 2d-3d 
+so the \plucker coordinates may be reused. Considering this scenario we get quite competitive $45$ FLOPS. 
+Similarly we may expect better times in remaining two intersection cases when the \plucker coordinates and their products 
+are reused by neighbouring elements.
 
@@
             Haines              & 51            & 177           & 469\\
-            Moller and Trumbore & 42            & 168           & 756\\
-            \ngh                & 127           & 508           & 2286\\
+            Moller and Trumbore & 42            & 168           & 756
     \end{tabular}
@@
 Second variant uses the BIH to accelerate the initialization of the AF algorithm. Third variant doesn't use AF at all and relies only on the BIH. 
-In this section, we compare these three variants (FS+AF, BIH+AF, BIH) on one artificial composed mesh and one raising from a real hydrogeological simulation.
+In this section, we compare these three variants (FS+AF, BIH+AF, BIH) on one artificial composed mesh and one mesh raising from a real hydrogeological simulation.
 
@@
 
-An artificial test composed mesh consists of a cube with two diagonal rectangles. A sequence of meshes was prepared with increasing number of intersections ranging
-form $0.1$ up to $2.0$ millions. The mesh size varies from $33e+3$ up to $2e+6$ elements including both the 2d and 3d. The timing for the three compared variants
-of the mesh intersection algorithm is shown on \fig{fig:cube_speed}. As the number of component meshes is low and they are completely 
-inside of the bulk mesh the FS+AF variant is the fastest and with the smallest growth as expected.
-On the other hand the BIH variant is constantly slower by 20\% than the BIH+AF variant.
+The artificial composed mesh consists of a cube and two diagonal rectangular 2d meshes (see \fig{fig:fig:cube_mesh}). The bulk mesh 
+A sequence of meshes was prepared with increasing number of elements ranging
+form $33$ up to $2000$ thousands of elements. The mesh step for the bulk mesh was always about half the mesh step of the component mesh. 
+The number of the bulk-component intersections varies from $0.1$ up to $2.0$ millions. The timing for the three compared variants
+of the mesh intersection algorithm is shown on \fig{fig:cube_speed}. Every algorithm consists of the initialization phase which process all elements of the mesh 
+and the intersection phase which depends only on the number of elements in the component mesh. In these terms both phases of all three variants exhibits almost 
+linear time complexity. As the number of component meshes is low and they are completely inside of the bulk mesh the FS+AF variant is the fastest in particular
+due to fast initialization. On the other hand the BIH variant is about two times slower than the BIH+AF variant during the intersection phase. 
 That is roughly related to the average fraction of the non-intersecting 3d element in the bounding box of a 2d element.
-The slightly larger growth of the BIH algorithm is masked by the common superlinear growth with power about $1.1$ which we do not completely understand.
-\noteJB{???}
 

### 2016-10-02 paper_intersections.tex
Fix caption and fractures in benchmarks

@@
 \newcommand{\fig}[1]{\hyperref[#1]{Figure \ref{#1}}}
-\newcommand{\figpath}{figures/}
+\newcommand{\figpath}{}
 
@@
     \includegraphics[width=0.55\textwidth]{\figpath components.pdf}
-    \caption{The two tetrahedra 1,2 do not make a compact bulk. Therefore four initializations are needed,
-    to find all the intersections with three 1D elements: 3-1, 5-1, 4-2, 5-2; creating four independent components. Advancing front method cannot play any part in this situation.}
+    \caption{For a non-convex bulk domain a situation as this may happen. The 1d elements 3,4,5 extends out of the bulk mesh.
+    Therefore four initializations are needed, to find all four 1d-3d intersections every one forming an independent component. 
+    Advancing front method cannot play any part in this situation.}
     \label{fig:components}
@@
 the bulk mesh we also prepared a mesh with the artificially extended fractures (\fig{fig:bedrichov_extend}). 
-Each of these meshes contains \notePE{what is the 9 number??} 28 fractures in 9 2d components and a single 1d component, the tunnel.
+Each of these meshes contains 28 fractures however some of them are connected in the conforming way so there is 9 separated 2d components and a 
+single 1d component, the tunnel.
 
@@
 Creation of the BIH in the BIH+AF variant pays off and the algorithm performs better than the FS+AF variant.
-This in the contrast to the cube test case since the number (10) of the component meshes is higher.
+This in the contrast to the cube test case since the number of the component meshes is higher.
 

### 2016-10-07 paper_intersections.tex
Final fixes.

@@
 
-\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
-\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
+%\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
+%\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
+\newcommand{\noteJB}[1]{}
+\newcommand{\notePE}[1]{}
+
 \newcommand{\plucker}{Pl\"{u}cker }
@@
 %% or \MSC[2008] code \sep code (2000 is the default)
-%\MSC[2010] 65N30 \sep %    Finite elements, Rayleigh-Ritz and Galerkin methods, finite methods
-%\MSC[2010] 35J05  %    Laplacian operator, reduced wave equation (Helmholtz equation), Poisson equation
-
+\MSC[2010] 65M60 \sep %    Finite elements, Rayleigh-Ritz and Galerkin methods, finite methods
+\MSC[2010] 65D18  %    Computer graphics, image analysis, and computational geometry [See also 51N05, 68U05]
+
+% suggestions:
+
+% Real and complex geometry
+%	51M04   	Elementary problems in Euclidean geometries
+%	51M05   	Euclidean geometries (general) and generalizations
+
+% 76S05   	Flows in porous media; filtration; seepage
+
+% Numerical approximation and computational geometry (primarily algorithms) {For theory, see 41-XX and 68Uxx}
+% 		65D18   	Computer graphics, image analysis, and computational geometry [See also 51N05, 68U05]
+
+% Computing methodologies and applications
+% 		68U01   	General
+% 		68U05   	Computer graphics; computational geometry [See also 65D18]
+
+%	Special subfields of solid mechanics
+%	74L05   	Geophysical solid mechanics [See also 86-XX]
+%	74L10   	Soil and rock mechanics
+
+% Partial differential equations, initial value and time-dependent initial-boundary value problems
+% 	65M50   	Mesh generation and refinement
+%       65M55   	Multigrid methods; domain decomposition
+%	65M60   	Finite elements, Rayleigh-Ritz and Galerkin methods, finite methods
+
+% Partial differential equations, boundary value problems
+%        65N50   	Mesh generation and refinement
+%	65N55   	Multigrid methods; domain decomposition
 \end{keyword}
@@
 is called the \emph{topological position} of the IC on $K$. Moreover, as every IC is a result of a permuted
-inner product of some \plucker coordinates (see Section \label{sec:1d-2d}), we store the sign of the product as well.
+inner product of some \plucker coordinates (see Section \ref{sec:1d-2d}), we store the sign of the product as well.
 
@@
 
-\subsubsection{Intersections on Sides of $S_2$}
+\subsubsection{Intersections on Sides of Triangle}
 \label{sec:sides}
@@
 
-\subsubsection{Intersections on Edges of $S_3$}
+\subsubsection{Intersections on Edges of Tetrahedron}
 \label{sec:edges}
@@
 
-The artificial composed mesh consists of a cube and two diagonal rectangular 2d meshes (see \fig{fig:fig:cube_mesh}). The bulk mesh 
+The artificial composed mesh consists of a cube and two diagonal rectangular 2d meshes (see \fig{fig:cube_mesh}). The bulk mesh 
 A sequence of meshes was prepared with increasing number of elements ranging

### 2016-11-26 paper_intersections.tex
Improve notation and explanation of plucker coordinates.

@@
 \newcommand{\fig}[1]{\hyperref[#1]{Figure \ref{#1}}}
-\newcommand{\figpath}{}
+% \newcommand{\figpath}{}
+\newcommand{\figpath}{figures/}
 
@@
 \plucker coordinates represent a line in 3d space.
-Considering a line $p$, given by a point $\vc A$ and its directional vector $\vc{u}$, 
+Considering a line $p$, given by a point $\vc A$ and its directional vector $\vc{u}_p$, 
 the \plucker coordinates of $p$ are defined as
-\[ \pi_p = (\vc{u}_p, \vc{v}_p) = (\vc{u}_p, \vc{u}_p\times \vc A). \]
-Further we denote a permuted inner product
+\[ \pi_p = (\vc{u}_p, \vc{v}_p),\; \vc{v}_p = \vc{u}_p\times \vc A. \]
+Further, having two lines $p$ and $q$ with \plucker coordinates $\pi_p$ and $\pi_q$, we denote a permuted inner product
 \[\pi_p \odot \pi_q = \vc{u}_p\cdot \vc{v}_q + \vc{u}_q \cdot \vc{v}_p. \]
 
-The sign of the permuted inner product gives us the relative position of the two lines, 
-see \fig{fig:plucker_products}.
+The sign of the permuted inner product tells us the relative position of two lines, 
+which is demonstrated on an example of a relative position of a line and a triangle sides in \fig{fig:plucker_products}.
 
@@
     \centering
-    \subfloat[$\pi_p\odot \pi_i < 0 \;\forall i$]{
+    \subfloat[$\pi_p\odot \pi_{s_i} < 0 \;\forall i$]{
         \includegraphics[width=0.3\textwidth]{\figpath plucker_product_a.pdf}
     }
-    \subfloat[$\pi_p\odot \pi_i = 0 \, \exists i$ \newline special case]{
+    \subfloat[$\pi_p\odot \pi_{s_i} = 0 \, \exists i$ \newline special]{
         \includegraphics[width=0.3\textwidth]{\figpath plucker_product_b.pdf}
     }
-    \subfloat[$\pi_p\odot \pi_i > 0 \;\forall i$]{
+    \subfloat[$\pi_p\odot \pi_{s_i} > 0 \;\forall i$]{
         \includegraphics[width=0.3\textwidth]{\figpath plucker_product_c.pdf}
     }
-    \caption{Sign of the permuted inner product is related to the relative position of the two oriented lines.          
+    \caption{Different relative positions of a line $p$ and a triangle with sides $s_i$, $i=0,1,2$. 
+            Signs of the permuted inner products depend on orientation of lines.          
             Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
+            We see that in cases a and c the products have the same sign.
     }

### 2016-11-30 paper_intersections.tex
Another improvement of plucker signs explanation.

@@
 
-%\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
-%\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
-\newcommand{\noteJB}[1]{}
-\newcommand{\notePE}[1]{}
+\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
+\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
+% \newcommand{\noteJB}[1]{}
+% \newcommand{\notePE}[1]{}
 
@@
 
-The sign of the permuted inner product tells us the relative position of two lines, 
-which is demonstrated on an example of a relative position of a line and a triangle sides in \fig{fig:plucker_products}.
+The sign of the permuted inner product tells us the relative position of two lines. 
+We shall demonstrate this on an example of a relative position of a line and triangle sides in \fig{fig:plucker_products}.
+The permuted inner products have the same sign in cases a and c, which will be later used as an indicator
+that an intersection inside the triangle exists.
+If any $\pi_p\odot \pi_{s_i}$ is zero, as in case b, it means that the lines $p$ and $s_i$ are intersecting each other
+(note that $s_i$ are considered as infinite lines at the moment).
+Any other situation not depicted in \fig{fig:plucker_products} is charaterized by different signs of permuted inner products.
 
@@
             Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
-            We see that in cases a and c the products have the same sign.
     }
@@
     \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
-    \item If any $w_i$ is less than $\epsilon$, there is no intersection, return empty IP.  
+    \item If any $w_i$ is less than $-\epsilon$ \notePE{I believe there was minus missing.}, there is no intersection, return empty IP. 
+          Compare \fig{fig:plucker_products} and \eqref{eq:bary_centric} for better insight.
     \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_2} = (2, 0)$ for the IC.
@@
 %% End of file `elsarticle-template-harv.tex'.
-
--

### 2016-11-30 paper_intersections.tex
Fix notation in proof of barycentric coords.
Make the proof of barycentric coordinates clearer.

@@
 with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$.
+\notePE{I think adding figure with node and side numbering would make it easier to read.}
 \begin{lemma}
@@
 \begin{proof}
-Using the barycentric coordinates the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
+Using the barycentric coordinates, the intersection point can be expressed as $\vc X = \vc V_0 + w_1 \vc s_2 - w_2 \vc s_1$.
 The line $p$ has \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
-Combining these two expressions we get
+Combining these two expressions and substituing for $\vc V_0-\vc V_2=\vc s_1$, we get for side $\vc s_1$
 \[
@@
 Since $\vc s_0 + \vc s_1 + \vc s_2=0$ we have $ \vc s_1 \times \vc s_2 = \vc s_2 \times \vc s_0 = \vc s_0 \times \vc s_1$ and thus
-\[
-   \pi_p \odot \pi_{s_i} = -w_i \vc u \cdot (\vc v_1 \times \vc v_2).
-\]
+\begin{eqnarray}
+   \pi_p \odot \pi_{s_i} &=& -w_i \vc u \cdot (\vc s_1 \times \vc s_2), \label{eq:bary_centric_part1}\\
+   \sum_{i=0}^{2} \pi_p \odot \pi_{s_i} &=& - \vc u \cdot (\vc s_1 \times \vc s_2). \label{eq:bary_centric_part2}
+\end{eqnarray}
+The result \eqref{eq:bary_centric} then follows directly from combination of \eqref{eq:bary_centric_part1} and \eqref{eq:bary_centric_part2}.
 The point $\vc X$ is inside $S_2$ if and only if $w_i>0$ for all $i=0,1,2$.

### 2016-11-30 paper_intersections.tex
Add figures for vertex faces function.

@@
 
+\begin{figure}[!htb]
+    \centering    
+    \includegraphics[width=0.9\textwidth]{\figpath vertex_faces.pdf}
+    \caption{Possible cases processed in the function \emph{vertex faces}.
+             Only the main features refered in text are denoted: tetrahedorn vertex $v$, edge $e$, face $f$ (stripes).}
+    \label{fig:vertex_faces}
+\end{figure}
+
 The function in Algorithm \ref{algo:vertex_faces} gets as a parameter IC $p$ at the vertex $v$ of $S_3$ 
@@
 We use these edge idicators to return generalized faces of $S_3$ preceding and succeeding $p$ on the polygons boundary assuming $p$ is at interior of $S_2$.
-Possible cases are:
+Possible cases are (see also \fig{fig:vertex_faces} a-e):
 \begin{itemize}
@@
  and $f$ the face between the other two edges.
- The other two (non-degenerate) edges may have either the opposite sign (the plane is cutting $S_3$) 
- or the same sign (the plane is touching $S_3$ at the edge $e$).
+ The other two (non-degenerate) edges may have either the opposite sign (the plane is cutting $S_3$, see case b in \fig{fig:vertex_faces}) 
+ or the same sign (the plane is touching $S_3$ at the edge $e$, see case a).
  In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then the vertex faces function returns $(e, f)$ or $(f, e)$, respectively.
@@
 
- \item {\bf Two degenerate ICs} (line \ref{line:two_degenerated}){\bf .} A face of $S_3$ lies in the plane of $S_2$. 
+ \item {\bf Two degenerate ICs} (line \ref{line:two_degenerated}){\bf .} A face of $S_3$ lies in the plane of $S_2$,
+ see case c in \fig{fig:vertex_faces}. 
  Let $e$ be the single non-degenerate edge. We treat the two degenerate edges as faces adjacent to $e$ 
@@
  Let $e$ be the edge of the single IC with the different sign. 
- The plane of $S_2$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$. 
+ The plane of $S_2$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$,
+ see case d in \fig{fig:vertex_faces}.
  The order is determined by the function \emph{edge faces} called for the edge $e$.
@@
  \item {\bf All ICs have the same sign} (line \ref{line:same_signs}){\bf .} Since $S_2$ is touching $S_3$ 
- at the vertex $v$, the polygon degenerates into a point and thus no connection information is necessary. We add IC to $J$ and return any pair of faces.
+ at the vertex $v$, the polygon degenerates into a point and thus no connection information is necessary.
+ We add IC to $J$ and return any pair of faces. See case e in \fig{fig:vertex_faces}.
 \end{itemize}

### 2016-12-12 paper_intersections.tex
Algorithms for SIMPLICIAL meshes.

@@
 to deal with problems on complex geometries. However the information about the mesh intersection must be provided.
-We present algorithms for intersections between 1d and 2d unstructured multi component meshes 
+We present algorithms for intersections between 1d and 2d unstructured multi component simplicial meshes 
 and their intersections with a background unstructured 3d mesh. A common algorithm 
@@
 of the element intersection algorithms are presented and three variants of the global intersection 
-algorithm are compared on the meshes raising from a hydrogeological application.
+algorithm are compared on the meshes raising from a hydrogeological applications.
 \end{abstract}
@@
 
-In this paper we present a new approach to intersection calculation of simplicial elements of different dimensions based on the \plucker coordinates,
-further developing the algorithm of Platis and Theoharis \cite{platis_fast_2003} for ray-tetrahedron intersections. Element intersections based on 
-\plucker coordinates are combined with the advancing front method which allows us to reuse \plucker coordinates and their products between neighboring
+In this paper we present a new approach to the mesh intersectionn problem based on the \plucker coordinates,
+further developing the algorithm of Platis and Theoharis \cite{platis_fast_2003} for ray-tetrahedron intersections. 
+Presented intersection algorithms for pairs of simplicial elements of different dimensions are based on \plucker coordinates.
+These algorithms are combined with the advancing front method which allows us to reuse \plucker coordinates and their products between neighboring
 elements and reduce the number of arithmetic operations.

### 2016-12-12 paper_intersections.tex
Fractures explained.

@@
 The realistic models of groundwater processes including the transport processes and geomechanics have to deal with 
-a complex nature of geological formations including fractures and wells. Although of a small scale, these features may have significant impact 
-on the global behavior of the system and their representation in the numerical model is imperative.
+a complex nature of geological formations containing various small scale features as fractures (or fractured zones) and wells. 
+Although of small scale, these features may have significant impact 
+on the global behavior of the system and their representation in the numerical model is imperative. For example the fractures may form preferential 
+paths which allow much faster transport that can not be fully captured by eqivalent continuum.
 One possible approach is to model fractures and wells as lower dimensional objects and introduce their coupling with the surrounding continuum. 

### 2016-12-12 paper_intersections.tex
Motivation improved.
Describe and discuss \epsilon.

@@
 at the wells. The prerequisite for such approach is a fast and robust algorithm for calculating intersections of individual meshes.
+Although it is (currently) out of our interest the non-matching mesh approach allows a time evolving network of fractures necessary e.g. in 
+modeling of hydraulic fracking.
 
@@
     \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
-    \item If any $w_i$ is less than $-\epsilon$ \notePE{I believe there was minus missing.}, there is no intersection, return empty IP. 
+    \item If any $w_i$ is less than $-\epsilon$ (see definition bellow), there is no intersection, return empty IP. 
           Compare \fig{fig:plucker_products} and \eqref{eq:bary_centric} for better insight.
@@
         projected to the plane $x_i=0$ where $i$ is the index of the maximal component of the triangle's normal vector.
-        Every pair $p$, $s_i$ is checked for an intersection on $S_2$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_{S_2}$ to 
-        $(1, i)$ or $(0, i)$, respectively. At most two ICs are obtained.
+        Every pair $p$, $s_i$ is checked for an intersection on $S_2$ boundary either inside $s_i$ or at a vertex $V_i$, 
+        setting the topological info $\tau_{S_2}$ to 
+        $(1, i)$ or $(0, i)$, respectively. The ICs (at most two of them) obtained in this coplanar case will be called 
+        \emph{degenerate} and will later need special treatment.
     \item For each IC the barycentric coordinates $(1-t, t)$ on the line $p$ are computed according to \eqref{eq:line}. 
@@
 
-We shall call every IC, that is created in the coplanar case, \emph{degenerate} since these will later need special treatment.
-
-Checking the same sign of the permuted inner products can be viewed as a geometric predicate for the presence of the intersection and orientation of the 
-line with respect to the triangle. Adaptive-precision evaluation of the geometric predicates was designed by Schewchuk \cite{shewchuk_adaptive_1997}
-and used for 2d-2d mesh intersections in \cite{elsheikh_reliable_2012}. However, we rather apply a fixed tolerance check for the zero 
-barycentric coordinates and consistently keep the topological positions in this and related algorithms.
+The algorithm depends on the parameter $\epsilon$ used as a common tolerance parameter for detection of ICs with special positions. First, it is used 
+in the sign check for permuted inner products, second, it is used for position check on the line. Only these two kinds of geometric predicates are used 
+through the all intersection algorithms. Currently, we use just fixed value $\epsilon=10^{-9}$. It works on all realistic meshes we deal with, but we are aware 
+of problems with possible unconsistent results of two different, but logically related predicates. Adaptive-precision evaluation of 
+the geometric predicates was designed by Schewchuk \cite{shewchuk_adaptive_1997} and used for 2d-2d mesh intersections in \cite{elsheikh_reliable_2012}
+in order to deal with these inconsistencies. It is a topic for future work to understand dependency between our geometric predicates
+and decide if the adaptive-precision is the only way to guarantee the correctness of the algorithm even for various corner cases.
 

### 2016-12-13 paper_intersections.tex
Fix some typos, run spellcheck.

@@
 of the element intersection algorithms are presented and three variants of the global intersection 
-algorithm are compared on the meshes raising from a hydrogeological applications.
+algorithm are compared on the meshes raising from hydrogeological applications.
 \end{abstract}
@@
 on the global behavior of the system and their representation in the numerical model is imperative. For example the fractures may form preferential 
-paths which allow much faster transport that can not be fully captured by eqivalent continuum.
+paths which allow much faster transport that cannot be fully captured by equivalent continuum.
 One possible approach is to model fractures and wells as lower dimensional objects and introduce their coupling with the surrounding continuum. 
@@
 at the wells. The prerequisite for such approach is a fast and robust algorithm for calculating intersections of individual meshes.
-Although it is (currently) out of our interest the non-matching mesh approach allows a time evolving network of fractures necessary e.g. in 
+Although it is (currently) out of our interest, the non-matching mesh approach allows a time evolving network of fractures necessary e.g. in 
 modeling of hydraulic fracking.
@@
 
-In this paper we present a new approach to the mesh intersectionn problem based on the \plucker coordinates,
+In this paper we present a new approach to the mesh intersection problem based on the \plucker coordinates,
 further developing the algorithm of Platis and Theoharis \cite{platis_fast_2003} for ray-tetrahedron intersections. 
@@
 (note that $s_i$ are considered as infinite lines at the moment).
-Any other situation not depicted in \fig{fig:plucker_products} is charaterized by different signs of permuted inner products.
+Any other situation not depicted in \fig{fig:plucker_products} is characterized by different signs of permuted inner products.
 
@@
 The line $p$ has \plucker coordinates $(\vc u, \vc u \times \vc X)$ since these are invariant to change of the initial point. 
-Combining these two expressions and substituing for $\vc V_0-\vc V_2=\vc s_1$, we get for side $\vc s_1$
+Combining these two expressions and substituting for $\vc V_0-\vc V_2=\vc s_1$, we get for side $\vc s_1$
 \[
@@
 through the all intersection algorithms. Currently, we use just fixed value $\epsilon=10^{-9}$. It works on all realistic meshes we deal with, but we are aware 
-of problems with possible unconsistent results of two different, but logically related predicates. Adaptive-precision evaluation of 
+of problems with possible inconsistent results of two different, but logically related predicates. Adaptive-precision evaluation of 
 the geometric predicates was designed by Schewchuk \cite{shewchuk_adaptive_1997} and used for 2d-2d mesh intersections in \cite{elsheikh_reliable_2012}
@@
     \caption{Possible cases processed in the function \emph{vertex faces}.
-             Only the main features refered in text are denoted: tetrahedorn vertex $v$, edge $e$, face $f$ (stripes).}
+             Only the main features referred in text are denoted: tetrahedron vertex $v$, edge $e$, face $f$ (stripes).}
     \label{fig:vertex_faces}
@@
 degenerate IC, positive IC and negative IC. Accordingly we call the edge: without intersection, degenerate, positive, or negative. 
-We use these edge idicators to return generalized faces of $S_3$ preceding and succeeding $p$ on the polygons boundary assuming $p$ is at interior of $S_2$.
+We use these edge indicators to return generalized faces of $S_3$ preceding and succeeding $p$ on the polygons boundary assuming $p$ is at interior of $S_2$.
 Possible cases are (see also \fig{fig:vertex_faces} a-e):
@@
 described in Section \ref{sec:1d-2d}, the algorithm based on the plane clipping due to Haines \cite{haines_fast_1991}, and the minimum storage
-algorithm due to M{\" o}ller and Trumbore (MT) \cite{moller_fast_1997}. For the later two algorithms we have considered strightforward modifications
+algorithm due to M{\" o}ller and Trumbore (MT) \cite{moller_fast_1997}. For the later two algorithms we have considered straightforward modifications
 to make them return qualitatively same output as our algorithms for 1d-2d, 1d-3d, and 2d-3d cases.
@@
 Similarly we may expect better times in remaining two intersection cases when the \plucker coordinates and their products 
-are reused by neighbouring elements.
+are reused by neighboring elements.
 

### 2016-12-14 paper_intersections.tex
Add references for Plucker coords.

--- 2016-12-12 paper_intersections.tex
@@
 \subsection{\plucker Coordinates}
-\plucker coordinates represent a line in 3d space.
-Considering a line $p$, given by a point $\vc A$ and its directional vector $\vc{u}_p$, 
+\plucker coordinates represent a line in 3d space. The definition properties and more general context from computational 
+geometry can be found e.g. in \cite{dorst_geometric_2007} or \cite{joswig_polyhedral_2013}.
+Considering a line $p$, given by a point $\vc A_p$ and its directional vector $\vc{u}_p$, 
 the \plucker coordinates of $p$ are defined as

### 2016-12-14 paper_intersections.tex
Remaining review notes.
- fixed some figures
- added some figures
- improved text where appropriate

@@
 \newcommand{\fig}[1]{\hyperref[#1]{Figure \ref{#1}}}
+\newcommand{\algo}[1]{\hyperref[#1]{Algorithm \ref{#1}}}
+
 % \newcommand{\figpath}{}
@@
 In this section, we present algorithms for computing the intersection of a pair of simplicial elements of a~different dimension in the 3d ambient space. 
-In particular we address intersection algorithms for 1d-2d, 1d-3d, 2d-3d pairs of elements. We have implemented the case 2d-2d as well, however the treatment 
-of the special cases is quite technical and not fully completed yet. The fundamental idea is to compute intersection of 1d-2d simplices using the 
-\plucker coordinates and reduce all other cases to this one.
+In particular we address intersection algorithms for 1d-2d, 1d-3d, 2d-3d pairs of elements.  The fundamental idea is to compute intersection of 1d-2d 
+simplices using the \plucker coordinates and reduce all other cases to this one. We have implemented the case 2d-2d as well, however the treatment 
+of all special cases is quite technical and not fully tested yet.
 
@@
 \begin{itemize}
- \item the barycentric coordinate $\vc w_K$ of IC on $K$,
- \item the dimension $d_K$ of the most specific \nface the IC lies on,
+ \item The barycentric coordinate $\vc w_K$ of IC on $K$.
+ \item The dimension $d_K$ of the smallest dimension \nface the IC lies on, e.g. IC on an edge have $d_K=1$ although it also lies on the connected faces.
  \item the local index $i_K$ of that \nface on $K$,
@@
 the \plucker coordinates of $p$ are defined as
-\[ \pi_p = (\vc{u}_p, \vc{v}_p),\; \vc{v}_p = \vc{u}_p\times \vc A. \]
+\[ \pi_p = (\vc{u}_p, \vc{v}_p),\; \vc{v}_p = \vc{u}_p\times \vc A_p. \]
+This representation is independent on choice of $A_p$ since $\vc{u}_p\times (\vc A_p + t \vc u) = \vc{u}_p\times \vc A_p$.
 Further, having two lines $p$ and $q$ with \plucker coordinates $\pi_p$ and $\pi_q$, we denote a permuted inner product
@@
 
-The sign of the permuted inner product tells us the relative position of two lines. 
-We shall demonstrate this on an example of a relative position of a line and triangle sides in \fig{fig:plucker_products}.
-The permuted inner products have the same sign in cases a and c, which will be later used as an indicator
-that an intersection inside the triangle exists.
-If any $\pi_p\odot \pi_{s_i}$ is zero, as in case b, it means that the lines $p$ and $s_i$ are intersecting each other
-(note that $s_i$ are considered as infinite lines at the moment).
-Any other situation not depicted in \fig{fig:plucker_products} is charaterized by different signs of permuted inner products.
+The sign of the permuted inner product is non-zero if $p$ and $q$ are skew lines and is positive if $q$ is oriented counterclockwise and 
+negative if $q$ is oriented clockwise looking in the $p$ direction. This can be used to determine relative position 
+of the line $p$ and the triangle. This is demonstrated in \fig{fig:plucker_products}.
+The permuted inner products of triangle sides with the line $p$ have common sign, cases (a) and (c), if and only if the 
+line intersect the triangle inside. If any $\pi_p\odot \pi_{s_i}$ is zero, as in the case (b), 
+it means that the lines $p$ and $s_i$ are coplanar.
 
@@
     \subfloat[$\pi_p\odot \pi_{s_i} < 0 \;\forall i$]{
-        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_a.pdf}
-    }
-    \subfloat[$\pi_p\odot \pi_{s_i} = 0 \, \exists i$ \newline special]{
-        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_b.pdf}
-    }
+        \includegraphics[width=0.25\textwidth]{\figpath plucker_product_a.pdf}
+    }
+    \hspace{2ex}
+    \subfloat[$\pi_p\odot \pi_{s_i} = 0 \, \exists i$, \newline special case]{
+        \includegraphics[width=0.25\textwidth]{\figpath plucker_product_b.pdf}
+    }
+    \hspace{2ex}
     \subfloat[$\pi_p\odot \pi_{s_i} > 0 \;\forall i$]{
-        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_c.pdf}
-    }
-    \caption{Different relative positions of a line $p$ and a triangle with sides $s_i$, $i=0,1,2$. 
-            Signs of the permuted inner products depend on orientation of lines.          
-            Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
+        \includegraphics[width=0.25\textwidth]{\figpath plucker_product_c.pdf}
+    }
+    \caption{Different relative positions of the line $p$ and a triangle with sides $s_i$, $i=0,1,2$. 
+            Dashed parts are behind the triangle. Signs of the permuted inner products depend on orientation of lines,
+            the line $p$ is coplanar with some side in the case (b).
     }
@@
 on which a line segment $S_1$ is defined by $t\in [0,1]$ and a triangle $S_2$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
-with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$.
-\notePE{I think adding figure with node and side numbering would make it easier to read.}
+with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$, see \fig{fig:triangle_notation}
+
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=0.5\textwidth]{\figpath triangle_notation.pdf}
+    \caption{Notation for Lemma \ref{lemma_barycentric}.    }
+    \label{fig:triangle_notation}
+\end{figure}
+
 \begin{lemma}
+\label{lemma_barycentric}
 The permuted inner products $\pi_p \odot \pi_{s_i},\, i=0,1,2$ have the same non-zero sign if and only if there
@@
 
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[width=0.9\textwidth]{\figpath 1d-2d_cases.pdf}
+    \caption{Some possible cases of the 1d-2d algorithm.}
+    \label{fig:1d2d_cases}
+\end{figure}
+
 The calculation of the intersection proceeds as follows:
@@
     \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
-    \item If any $w_i$ is less than $-\epsilon$ (see definition bellow), there is no intersection, return empty IP. 
-          Compare \fig{fig:plucker_products} and \eqref{eq:bary_centric} for better insight.
-    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_2} = (2, 0)$ for the IC.
-    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_2} =(1,i)$.
-    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_2}=(0,i)$.
+    \item If any $w_i$ is less than $-\epsilon$ (see definition bellow), there is no intersection, return empty IP. \fig{fig:1d2d_cases}, (a).          
+    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_2} = (2, 0)$ for the IC. \fig{fig:1d2d_cases}, (b).
+    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_2} =(1,i)$. \fig{fig:1d2d_cases}, (c).
+    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_2}=(0,i)$. \fig{fig:1d2d_cases}, (d).
     \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
@@
 \end{algorithm}
-Algorithm \ref{algo:13d} first computes line-face intersections for every face of $S_3$.
+\algo{algo:13d} first computes line-face intersections for every face of $S_3$.
 Tetrahedron has six edges, so 7 \plucker coordinates and 6 permuted inner products are computed at most. 
-Precomputed coordinates and products are passed into the 1d-2d algorithm which is performed for the whole line $p$ (line \ref{line:13-intersection}).
-If no IC is found, or coplanar case occurs in line-face computation, we continue to the next face.
-Note, ICs that would be created in coplanar case are to be found as ICs with the other faces, since they lie on edges.
+Precomputed coordinates and products are passed into the 1d-2d algorithm which is performed for the whole 
+line $p$ (line \ref{line:13-intersection}).
+If no IC is found, or coplanar case occurs in line-face computation, we continue to the next face. Note, ICs that would 
+be created in coplanar case are to be found as ICs with the other faces, since they lie on edges.
 Next, IC can be on an edge or at a vertex; then we set the correct topological position and mark the adjacent faces
@@
 
-Algorithm \ref{algo:colect_23_ip_triangle} computes all ICs on the boundary of $S_2$.  It passes through every side $s$ of the triangle $S_2$ 
+\algo{algo:colect_23_ip_triangle} computes all ICs on the boundary of $S_2$.  It passes through every side $s$ of the triangle $S_2$ 
 and computes the line-tetrahedron intersection $L$.
-If the side is just touching $S_3$, we get $L$ with a single IC. These ICs will be rediscovered again in Algorithm \ref{algo:collect_23_ip_edges} 
+If the side is just touching $S_3$, we get $L$ with a single IC. These ICs will be rediscovered again in \algo{algo:collect_23_ip_edges} 
 with better topological information, however this is not the case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$.
@@
 the point $p$ lies on and set the tables $F_g$, $F_p$. For the IC at the vertex of $S_2$ we set $x$ to that vertex regardless of its position on $S_3$.
-The backward temporary link on the line \ref{line:back_link43} is used later in Algorithm \ref{algo:collect_23_ip_edges} to allow proper continuation 
+The backward temporary link on the line \ref{line:back_link43} is used later in \algo{algo:collect_23_ip_edges} to allow proper continuation 
 of the IC if it lies on edge or at vertex of $S_3$. The condition at the same line deals with the case that two sides of $S_3$ intersect 
@@
     \Else($p$ at the vertex $v$ of $S_3$){       
-            $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{Algorithm \ref{algo:vertex_faces}}
+            $(f_0,\ f_1)$ = \vertexfaces($v$,$L$)   \tcp*{\algo{algo:vertex_faces}}
             \nllabel{line:mark_edges}
@@
 
-Algorithm \ref{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
+\algo{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
 First, the intersection $L[e]$ is evaluated for every edge $e$. The loop produces ICs in the interior of $S_2$ and 
 possibly those ICs with special position at the vertex or on the edge of $S_3$ already computed 
-in Algorithm \ref{algo:colect_23_ip_triangle}. Then we pass through once again skipping the edges with none or degenerate $L[e]$.
+in \algo{algo:colect_23_ip_triangle}. Then we pass through once again skipping the edges with none or degenerate $L[e]$.
 For every intersection corner $p=L[e]$, we first get its (generalized) faces that would appear before and after the IC on IP, assuming that $p$ is inside $S_2$.
@@
 the order of sides of IP if the sign is negative. If the sign is positive the function \emph{edge faces} returns face pair $(f_1, f_0)$.
-If the IC is at the vertex $v$ of $S_3$, the function \emph{vertex faces} described later (Algorithm \ref{algo:vertex_faces}) is used.
+If the IC is at the vertex $v$ of $S_3$, the function \emph{vertex faces} described later (\algo{algo:vertex_faces}) is used.
 It returns a pair of generalized faces (face or edge) adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$. 
@@
 
-The function in Algorithm \ref{algo:vertex_faces} gets as a parameter IC $p$ at the vertex $v$ of $S_3$ 
+The function in \algo{algo:vertex_faces} gets as a parameter IC $p$ at the vertex $v$ of $S_3$ 
 which is a special case of a non-degenerate edge-triangle intersection. There are three
@@
  and $f$ the face between the other two edges.
- The other two (non-degenerate) edges may have either the opposite sign (the plane is cutting $S_3$, see case b in \fig{fig:vertex_faces}) 
- or the same sign (the plane is touching $S_3$ at the edge $e$, see case a).
+ The other two (non-degenerate) edges may have either the opposite sign (the plane is cutting $S_3$, see \fig{fig:vertex_faces}, (a)) 
+ or the same sign (the plane is touching $S_3$ at the edge $e$, see \fig{fig:vertex_faces}, (b)).
  In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then the vertex faces function returns $(e, f)$ or $(f, e)$, respectively.
@@
  \item {\bf Two degenerate ICs} (line \ref{line:two_degenerated}){\bf .} A face of $S_3$ lies in the plane of $S_2$,
- see case c in \fig{fig:vertex_faces}. 
+ see \fig{fig:vertex_faces}, (c). 
  Let $e$ be the single non-degenerate edge. We treat the two degenerate edges as faces adjacent to $e$ 
@@
  The plane of $S_2$ separates $e$ from the other two edges so it goes through the faces adjacent to $e$,
- see case d in \fig{fig:vertex_faces}.
+ see \fig{fig:vertex_faces}, (d).
  The order is determined by the function \emph{edge faces} called for the edge $e$.
@@
  at the vertex $v$, the polygon degenerates into a point and thus no connection information is necessary.
- We add IC to $J$ and return any pair of faces. See case e in \fig{fig:vertex_faces}.
+ We add IC to $J$ and return any pair of faces, see \fig{fig:vertex_faces}, (e) .
 \end{itemize}
@@
 \begin{table}[!htb]
-    \caption{Raw number of FLOPS used by different intersection algorithms.}    
+    \caption{Raw number of FLOPs used by different intersection algorithms. Second row contains estimated effective number of FLOPs per intersection
+    accounting for reuse of edges through the mesh intersection assuming edges of 2d and 3d elements are used twice (conservative). }    
     \label{tab:fundamental_flops}
@@
             \plucker           & 92            & 198           & 426\\
+            \plucker (edge reuse)& 42           & 138            & 264\\
             Haines              & 51            & 177           & 469\\

### 2016-12-20 paper_intersections.tex
Small typos and fixes, remove initials at references.

@@
 to get intersection candidate pairs of elements, the GTS library \cite{gtslib} is used for 2d-3d intersections. 
-Finally, there is the work of A. Elsheikh and M. Elsheikh \cite{elsheikh_reliable_2012} presenting an algorithm for 2d-2d mesh union operation which includes 
+Finally, there is the work of Elsheikh and Elsheikh \cite{elsheikh_reliable_2012} presenting an algorithm for 2d-2d mesh union operation which includes 
 calculation and imprinting of the intersection curves. They exploit the binary space partitioning for searching of the initial intersection and 
@@
 Presented intersection algorithms for pairs of simplicial elements of different dimensions are based on \plucker coordinates.
-These algorithms are combined with the advancing front method which allows us to reuse \plucker coordinates and their products between neighboring
+These algorithms are combined with the advancing front method which allows us to reuse \plucker coordinates and their products among neighboring
 elements and reduce the number of arithmetic operations.
@@
 \[ \pi_p = (\vc{u}_p, \vc{v}_p),\; \vc{v}_p = \vc{u}_p\times \vc A_p. \]
-This representation is independent on choice of $A_p$ since $\vc{u}_p\times (\vc A_p + t \vc u) = \vc{u}_p\times \vc A_p$.
+This representation is independent of the choice of $A_p$ since $\vc{u}_p\times (\vc A_p + t \vc u) = \vc{u}_p\times \vc A_p$.
 Further, having two lines $p$ and $q$ with \plucker coordinates $\pi_p$ and $\pi_q$, we denote a permuted inner product
@@
 The permuted inner products of triangle sides with the line $p$ have common sign, cases (a) and (c), if and only if the 
-line intersect the triangle inside. If any $\pi_p\odot \pi_{s_i}$ is zero, as in the case (b), 
+line intersects the triangle inside. If any $\pi_p\odot \pi_{s_i}$ is zero, as in the case (b), 
 it means that the lines $p$ and $s_i$ are coplanar.
@@
             Dashed parts are behind the triangle. Signs of the permuted inner products depend on orientation of lines,
-            the line $p$ is coplanar with some side in the case (b).
+            the line $p$ is coplanar with a side in the case (b).
     }
@@
 on which a line segment $S_1$ is defined by $t\in [0,1]$ and a triangle $S_2$ given by vertices $(\vc V_0, \vc V_1, \vc V_2)$ 
-with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$, see \fig{fig:triangle_notation}
+with oriented sides $s_i=(\vc V_j, \vc V_k)$, $j=(i+1)\text{ mod }3$, $k=(i+2)\text{ mod }3$, see \fig{fig:triangle_notation}.
 

### 2016-12-28 paper_intersections.tex
Unify interesection figures, colors.
Fix 2d3d (WIP)

--- 2016-12-14 paper_intersections.tex
@@
   \label{eq:bary_centric}
-   w_i = \frac{\pi_p \odot \pi_{s_i}}{ \sum_{j=0}^{2} \pi_p \odot \pi_{s_i} }.
+   w_i = \frac{\pi_p \odot \pi_{s_i}}{w},\quad w=\sum_{i=0}^{2} \pi_p \odot \pi_{s_i}.
 \end{equation}
@@
 calculation of edge-triangle ICs (Section~\ref{sec:edges}), ordering of ICs (Section~\ref{sec:ordering}).
-The intersection corners are appended to the list $I$ as they are computed, however their order on the polygon boundary is 
-defined by the \emph{connection tables} $F_g(:)$ and $F_p(:)$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an IC given by $F_g[x]$ 
-and every IC $p$ is followed by the side that lies on $F_p[p]\in M_2\cup M_3$ (see \fig{fig:tracing}). The vertices of the polygon are ordered in the same 
-way as is the order and orientation of the sides of $S_2$, that is counterclockwise around the interior with normal pointing to us.
-There are special cases when the IP is degenerated to a line or a point. 
-If we obtain an IC during the calculation that may possibly be a part a degenerate IP, which
-we cannot decide at the moment, we put that IC into the list $J$.
 
@@
     intersection polygon corner $p_i$ which \nfaces it lies on. Looking at $p_0$, the connection table entries
-    are: $F_g[s_2]=p_0$, $F_p[p_0]=s_0$. For the other ICs we have: $F_g[s_0]=p_1$, $F_p[p_1]=f_1$, $F_g[f_1]=p_2$, $F_p[p_2]=f_2$ and $F_g[f_2]=p_3$, $F_p[p_3]=s_2$.}
+    are: $F_c[s_2]=p_0$, $F_f[p_0]=s_0$. For the other ICs we have: $F_c[s_0]=p_1$, $F_f[p_1]=f_1$, $F_c[f_1]=p_2$, $F_f[p_2]=f_2$ and $F_c[f_2]=p_3$, $F_f[p_3]=s_2$.}
     \label{fig:tracing}
@@
 
+\subsubsection{Successor tables}
+The intersection corners are appended to the list $I$ as they are computed, however their order on the polygon boundary is 
+given indirectly by the \emph{successor tables} $F_c[:]$ and $F_f[:]$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an 
+IC given by $F_c[x]$ and every IC $p$ is followed by the side of the intersection polygon that lies on the \nface $F_f[p]\in M_2\cup M_3$ (see \fig{fig:tracing}).
+For every IC $u$, we shall also find two $n$-faces $x$, $y$ incident with the two sides of the resulting IP that are neighbouring with the IC $u$. 
+The order of $n$-faces $x$, $y$ have to match the orientation of the IP which is the same as the orientation of $S_2$ triangle, 
+that is counterclockwise around the interior with normal pointing to us.
+Having $x$, $y$ in right order, we set $F_c[x]=u$, $F_f[u]=y$.
+
+This simple approach works well even for most of the degenerated ICs, however in order to deal with some special cases and 
+with duplicity of ICs in vertices, we further mark by the backlink $F_c[y]=u$ the $n$-faces that success some IC but still do not poses its successors.
+If $y$ already have the backlink we swap $x$ and $y$. The result is the {\emph set links} operation formalized in Algorithm \ref{algo:set_links}.
+\begin{algorithm}
+  \caption{2d-3d intersection, set links}
+  \label{algo:set_links}
+  \DontPrintSemicolon  
+  \SetKw{continue}{continue}
+  \KwIn{$n$-face $x$, IC $p$, $n$-face $y$}
+  \If{$F_f[F_c[y]]=y$}{
+    swap $x$ and $y$ \tcp*{$y$ success an IC already}
+  }
+  $F_c[x]=u$, $F_f[u]=y$\;
+  \lIf{$F_c[y]$ is unset}{ $F_c[y] = u$}
+\end{algorithm}
+
 \subsubsection{Intersections on Sides of Triangle}
 \label{sec:sides}
-
-\begin{algorithm}
-  \caption{2d-3d intersection, ICs on sides of $S_2$}
-  \label{algo:colect_23_ip_triangle}
-
-  \DontPrintSemicolon
-  \SetKw{continue}{continue}
-  \KwIn{$S_2$ and $S_3$}
-  \KwOut{List $I$ with ICs on sides of $S_2$}  
-  $F_g(:)=-1,\ F_p(:)=-1$\tcp*{Unset links.} 
-  \For{side $s$ of $S_2$}{ 
-    $L$ = intersection($s, S_3$)\;
-    \lIf{ $\abs{L} = 0$}{\continue}
-    \lIf{ $\abs{L} = 1$}{
-        append $p$ to $J$
-        \continue
-    }
-    \For{$p$ in $L$}{ \nllabel{line:one side loop}
-        append $p$ to $I$
-%        \lIf{$p \ne I[-1]$ }{append $p$ to $I$}
-        $p$ lies on $x\in M_3$\; \nllabel{line:m4_object}
-        \lIf{$p$ lies at the vertex $v$ of $S_3$}{$x=v$}
-        \uIf{$p$ is the first in $L$}{
-            $F_g[x] = p$,\ $F_p[p] = s$\;
-        }
-        \Else($p$ is the last in $L$){
-            $F_g[s] = p,\ F_p[p] = x$\;
-            \lIf{$F_g[x] = -1$}{$F_g[x] = p$} \nllabel{line:back_link43}
-        }
-    }
-  }  
-%  \If{$I[-1] = I[0]$}{
-%    $x = F_p[I[-1]]$\;
-%    \If{$F_g[x]]=I[-1]$}{$F_g[x]=I[0]$}
-%    $F_g[s_2] = I[0]$\;
-%    remove $I[-1]$
-%  }
-\end{algorithm}
-
 \algo{algo:colect_23_ip_triangle} computes all ICs on the boundary of $S_2$.  It passes through every side $s$ of the triangle $S_2$ 
-and computes the line-tetrahedron intersection $L$.
+and computes the line-tetrahedron intersection $L$. In the regular case ($\abs{L}=2$), we process each IC in $L$ (loop on line \ref{line:one side loop}).
+
+The IC $p$ is added to the list $I$, vertices of $S_2$ added twice are merged at final stage. 
+Then (line \ref{line:m4_object}) we identify the \nface $x\in M_3$ 
+the point $p$ lies on and set the tables $F_c$, $F_f$. For the IC at the vertex of $S_2$ we set $x$ to that vertex regardless of its position on $S_3$.
+The backward temporary link on the line \ref{line:back_link43} is used later in \algo{algo:collect_23_ip_edges} to allow proper continuation 
+of the IC if it lies on edge or at vertex of $S_3$. The condition at the same line deals with the case that two sides of $S_3$ intersect 
+the same object $x\in M_3$, in such case the backlink is unnecessary and would overwrite the correct link set by previous IC.
+
 If the side is just touching $S_3$, we get $L$ with a single IC. These ICs will be rediscovered again in \algo{algo:collect_23_ip_edges} 
@@
 %I find the reference to 'line:one side loop' also incorrect..}
-In the regular case, we process each of the two ICs in $L$ (loop on line \ref{line:one side loop}). The IC $p$ is added to the list $I$,
-vertices of $S_2$ added twice are merged at final stage. Then (line \ref{line:m4_object}) we identify the \nface $x\in M_3$ 
-the point $p$ lies on and set the tables $F_g$, $F_p$. For the IC at the vertex of $S_2$ we set $x$ to that vertex regardless of its position on $S_3$.
-The backward temporary link on the line \ref{line:back_link43} is used later in \algo{algo:collect_23_ip_edges} to allow proper continuation 
-of the IC if it lies on edge or at vertex of $S_3$. The condition at the same line deals with the case that two sides of $S_3$ intersect 
-the same object $x\in M_3$, in such case the backlink is unnecessary and would overwrite the correct link set by previous IC.
+
+\begin{algorithm}
+  \caption{2d-3d intersection, ICs on sides of $S_2$}
+  \label{algo:colect_23_ip_triangle}
+
+  \DontPrintSemicolon
+  \SetKw{continue}{continue}
+  \KwIn{$S_2$ and $S_3$}
+  \KwOut{List $I$ with ICs on sides of $S_2$}  
+  $F_c(:)=-1,\ F_f(:)=-1$\tcp*{Unset links.} 
+  \For{side $s$ of $S_2$}{ 
+    $L$ = intersection($s, S_3$)\;
+    \For{$p$ in $L$}{ \nllabel{line:one side loop}
+        $p$ lies on $n$-faces $x\in M_2$ and $y\in M_3$\;
+        \If{$\abs{L} = 1$}{
+            deal with special case \tcp*{side $s$ touching $S_3$}
+        }
+        append $p$ to $I$
+        \uIf{$x$ is the vertex of $S_2$}{
+            set links($x$, $p$, $s$)
+        }
+        \Else{
+            set links($y$, $p$, $x$)
+        }
+    }
+  }  
+\end{algorithm}
 
@@
   \DontPrintSemicolon
-  \KwIn{$I$ with ICs on $S_2$ boundary, partially filled $F_p$, $F_g$}
-  \KwOut{all ICs in $I$, complete $F_p$, $F_g$}
+  \KwIn{$I$ with ICs on $S_2$ boundary, partially filled $F_f$, $F_c$}
+  \KwOut{all ICs in $I$, complete $F_f$, $F_c$}
 
@@
          $p$ lies on edge or at vertex $x \in M_3$\;
-         $q=F_g[x]$\tcp*{$q$ is already computed $p$}
-         \lIf{$F_p[q]=x$}{$F_p[q]=f_1$} \nllabel{line:successor}
-         \lElse{$F_g[f_0]=q$}  \nllabel{line:predecessor}
-         $F_g[x]=-1$\tcp*{remove the backlink}
+         $q=F_c[x]$\tcp*{$q$ is already computed $p$}
+         \lIf{$F_f[q]=x$}{$F_f[q]=f_1$} \nllabel{line:successor}
+         \lElse{$F_c[f_0]=q$}  \nllabel{line:predecessor}
+         $F_c[x]=-1$\tcp*{remove the backlink}
     }
@@
          append $p$ to $I$\; 
-         $F_g[f_0]=p,\ F_p[p]=f_1$\tcp*{overwrite the backlink} \nllabel{line:insideS2}
+         $F_c[f_0]=p,\ F_f[p]=f_1$\tcp*{overwrite the backlink} \nllabel{line:insideS2}
     }   
@@
   \SetKw{return}{return}
-  \SetKw{edgefaces}{edge faces}
+  \SetKw{edgefaces}{EdgeFaces}
   \DontPrintSemicolon
@@
   \uIf{$s[:]$ have 1 non-degenerate edge $e$}{ \nllabel{line:two_degenerated}
-    \return pair of degenerate edges sorted according to \edgefaces($e$)    
+    \return pair of degenerate edges sorted according to $\edgefaces($e$)$    
   }
@@
   \uElseIf{ $s$ have edge $e$ with sign opposite to other two}{ \nllabel{line:different_sign}
-    \return edge faces($e$)\;
+    \return $\edgefaces(e)$\;
   }
@@
 and get at most 2 distinguish ICs forming a degenerate IP. Otherwise, we start with first IC $p$ in $I$, put it into final list $K$, 
-get its successor \nface $x = F_p(p)$ and its successor IC $q=F_q(x)$. Unless $x$ is vertex of $S_2$, we put $q$ into $K$ and repeat the process until 
+get its successor \nface $x = F_f(p)$ and its successor IC $q=F_q(x)$. Unless $x$ is vertex of $S_2$, we put $q$ into $K$ and repeat the process until 
 we pass all ICs in $I$.

### 2016-12-28 paper_intersections.tex

@@
     \centering    
-    \includegraphics[width=0.65\textwidth]{\figpath tracing.pdf}
+    \includegraphics[width=0.65\textwidth]{\figpath tracing_color.pdf}
     \caption{An example of an intersection 2d-3d, demonstrating the ICs ordering. We see at every 
@@
   \begin{center}        
-    \includegraphics[width=0.3\textwidth]{\figpath edge_faces.pdf}
+    \includegraphics[width=0.3\textwidth]{\figpath edge_faces_color.pdf}
   \end{center}

### 2016-12-31 paper_intersections.tex
Fix 1d2d and 2d3d case.
- add epsilon description and numerical instability issues
- rewrite description of 2d3d algorithms to match actuall implementation

@@
     \item Compute or reuse \plucker coordinates and permuted inner products: $\pi_p$, $\pi_{s_i}$, $\pi_p \odot \pi_{s_i}$, for $i=1,2,3$.
+    \item \label{item:zero_total} If the total $w$ of the products is less then $\epsilon L_1 L_2^2$ jump to the coplanar case in the step \ref{item:coplanar}.
     \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
@@
 
-The algorithm depends on the parameter $\epsilon$ used as a common tolerance parameter for detection of ICs with special positions. First, it is used 
+In order to make the test in the step \ref{item:zero_total} independent of the  scale of elements, we use characteristic lengths $L_1$ and $L_2$ of $S_1$ and $S_2$ respectively.
+Further, the algorithm depends on the parameter $\epsilon$ used as a common tolerance parameter for detection of ICs with special positions. First, it is used 
 in the sign check for permuted inner products, second, it is used for position check on the line. Only these two kinds of geometric predicates are used 
-through the all intersection algorithms. Currently, we use just fixed value $\epsilon=10^{-9}$. It works on all realistic meshes we deal with, but we are aware 
-of problems with possible inconsistent results of two different, but logically related predicates. Adaptive-precision evaluation of 
+through the all intersection algorithms. Currently, we use just fixed value $\epsilon=10^{-9}$. This value is close to the machine epsilon ($10^{-16}$ 
+of the double precision 
+arithmetic, while far enough to keep precision of the further calculations. Let us note that the algorithm is susceptible to the loss of significance 
+due to cancellation during evaluation of the products. Nevertheless, the algorithm works on all realistic meshes we deal with.
+
+Other problem that would deserve further investigation is possible inconsistent result of two different, but logically related predicates. 
+Adaptive-precision evaluation of 
 the geometric predicates was designed by Schewchuk \cite{shewchuk_adaptive_1997} and used for 2d-2d mesh intersections in \cite{elsheikh_reliable_2012}
@@
 The algorithms for 1d-3d and 2d-3d intersections use simpler version of the 1d-2d intersection algorithm, in particular the search for ICs in the coplanar case 
-(item \ref{item:coplanar}) is not necessary, and the test in the last point is not performed.
+(step \ref{item:coplanar}) is not necessary, and the test in the last point is not performed.
 %and degenerate cases higher dimensional cases.
@@
 \subsubsection{Successor tables}
-The intersection corners are appended to the list $I$ as they are computed, however their order on the polygon boundary is 
-given indirectly by the \emph{successor tables} $F_c[:]$ and $F_f[:]$. Every side of the polygon that lies on \nface $x\in M_2\cup M_3$ is followed by an 
-IC given by $F_c[x]$ and every IC $p$ is followed by the side of the intersection polygon that lies on the \nface $F_f[p]\in M_2\cup M_3$ (see \fig{fig:tracing}).
-For every IC $u$, we shall also find two $n$-faces $x$, $y$ incident with the two sides of the resulting IP that are neighbouring with the IC $u$. 
-The order of $n$-faces $x$, $y$ have to match the orientation of the IP which is the same as the orientation of $S_2$ triangle, 
+The intersection corners are appended to the list $I$ as they are computed, however their order on IP is 
+given indirectly by the \emph{successor tables} $F_c[:]$ and $F_f[:]$. Every side of IP that lies on \nface $x\in M_2\cup M_3$ is followed by an 
+IC given by $F_c[x]$ and every IC $p$ is followed by the side of IP that lies on the \nface $y=F_f[p]\in M_2\cup M_3$ (see \fig{fig:tracing}).
+After an IC $p$ is computed, we also obtain two $n$-faces $x$, $y$ incident with the two IP's sides that are neighbouring with the IC. 
+Order of the $n$-faces $x$, $y$ have to match the orientation of the IP which is the same as the orientation of $S_2$ triangle, 
 that is counterclockwise around the interior with normal pointing to us.
@@
 This simple approach works well even for most of the degenerated ICs, however in order to deal with some special cases and 
-with duplicity of ICs in vertices, we further mark by the backlink $F_c[y]=u$ the $n$-faces that success some IC but still do not poses its successors.
-If $y$ already have the backlink we swap $x$ and $y$. The result is the {\emph set links} operation formalized in Algorithm \ref{algo:set_links}.
+with duplicity of ICs in vertices, we further mark by a \emph{backlink} $F_c[y]=u$ the $n$-faces that success some IC but still do not possess its successors.
+If $y$ already have the backlink we swap $x$ and $y$. The result is the \emph{set links} (SL) operation formalized in Algorithm \ref{algo:set_links}.
 \begin{algorithm}
@@
 \label{sec:sides}
-\algo{algo:colect_23_ip_triangle} computes all ICs on the boundary of $S_2$.  It passes through every side $s$ of the triangle $S_2$ 
-and computes the line-tetrahedron intersection $L$. In the regular case ($\abs{L}=2$), we process each IC in $L$ (loop on line \ref{line:one side loop}).
-
-The IC $p$ is added to the list $I$, vertices of $S_2$ added twice are merged at final stage. 
-Then (line \ref{line:m4_object}) we identify the \nface $x\in M_3$ 
-the point $p$ lies on and set the tables $F_c$, $F_f$. For the IC at the vertex of $S_2$ we set $x$ to that vertex regardless of its position on $S_3$.
-The backward temporary link on the line \ref{line:back_link43} is used later in \algo{algo:collect_23_ip_edges} to allow proper continuation 
-of the IC if it lies on edge or at vertex of $S_3$. The condition at the same line deals with the case that two sides of $S_3$ intersect 
-the same object $x\in M_3$, in such case the backlink is unnecessary and would overwrite the correct link set by previous IC.
-
-If the side is just touching $S_3$, we get $L$ with a single IC. These ICs will be rediscovered again in \algo{algo:collect_23_ip_edges} 
-with better topological information, however this is not the case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$.
-To this end we save the IC into separate list $J$ and skip filling of the connection tables.
-%\notePE{here it is weird... there is no line appending the IC into resulting list.. Which is the resulting list??
-%I find the reference to 'line:one side loop' also incorrect..}
+\algo{algo:colect_23_ip_triangle} computes all ICs on the boundary of $S_2$.  It passes through the sides of the triangle $S_2$ 
+computing  the line-tetrahedron intersection $L$ for every side $s$. 
+In the regular case ($\abs{L}=2$), we process each IC in $L$ (line \ref{line:one side loop}).
+The IC $p$ is appended to $I$ and successor tables are set using the SL operation. If $p$ is at the vertex of
+$S_2$ the links connect the vertex with the $S_2$ side. In both cases SL  is called with the side $s$ as the target $n$-face
+since SL correctly swap $n$-faces if the side is already used as the target. The vertex ICs put twice into $I$ and are merged
+in the final step.
+
+The case $\abs{L}=1$ can happen only if the boundary of $S_2$ touches the boundary of $S_3$. These ICs will be 
+rediscovered again in \algo{algo:collect_23_ip_edges} with better topological information, however this is not the 
+case if the touched edge $e$ of $S_3$ is coplanar with $S_2$ and the IC is inside of $e$.
+To this end we call SL with $e$ as the target which allows to use backlink and get already computed IC if it is rediscovered later on.
+The ICs at vertices of $S_2$ are treated differently, but follows the same idea. The ICs at vertices of $S_3$ are skipped.
 
@@
     \For{$p$ in $L$}{ \nllabel{line:one side loop}
-        $p$ lies on $n$-faces $x\in M_2$ and $y\in M_3$\;
+        $p$ lies on $n$-face $x\in M_2$ and $y\in M_3$\;
         \If{$\abs{L} = 1$}{
@@
         }
-        append $p$ to $I$
+        append $p$ to $I$\;
         \uIf{$x$ is the vertex of $S_2$}{
@@
         \Else{
-            set links($y$, $p$, $x$)
+            set links($y$, $p$, $x$) \tcp*{$x$ is $s$}
         }
@@
     }    
+    append $p$ to $I$\; 
     \uIf{ $p$ is on the boundary of $S_2$ }{
          $p$ lies on edge or at vertex $x \in M_3$\;
-         $q=F_c[x]$\tcp*{$q$ is already computed $p$}
-         \lIf{$F_f[q]=x$}{$F_f[q]=f_1$} \nllabel{line:successor}
-         \lElse{$F_c[f_0]=q$}  \nllabel{line:predecessor}
-         $F_c[x]=-1$\tcp*{remove the backlink}
-    }
+         \uIf{$x$ have backlink}{
+            set links($x$, $p$, $f_1$) 
+         }\nllabel{line:successor}
          \Else{
-         append $p$ to $I$\; 
-         $F_c[f_0]=p,\ F_f[p]=f_1$\tcp*{overwrite the backlink} \nllabel{line:insideS2}
+            set links($f_0$, $p$, $x$)
+         }  \nllabel{line:predecessor}
+    }
+    \Else{
+         set links ($f_0$, $p$, $f_1$) \nllabel{line:insideS2}
     }   
@@
   \begin{center}        
-    \includegraphics[width=0.3\textwidth]{\figpath edge_faces_color.pdf}
+    \includegraphics[width=0.3\textwidth]{\figpath edge_faces.pdf}
   \end{center}
@@
 
-\algo{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$ (line \ref{line:12edges}).
-First, the intersection $L[e]$ is evaluated for every edge $e$. The loop produces ICs in the interior of $S_2$ and 
-possibly those ICs with special position at the vertex or on the edge of $S_3$ already computed 
-in \algo{algo:colect_23_ip_triangle}. Then we pass through once again skipping the edges with none or degenerate $L[e]$.
-For every intersection corner $p=L[e]$, we first get its (generalized) faces that would appear before and after the IC on IP, assuming that $p$ is inside $S_2$.
-
-The function \emph{edge faces} returns the adjacent faces $f_0$, $f_1$ to the edge $e$, on which the IC lies (see the situation in \fig{fig:edge_faces}). 
+\algo{algo:collect_23_ip_edges} uses the line-triangle intersection algorithm for the edges of $S_3$.
+First, the intersection $L[e]$ is evaluated for every edge $e$ (line \ref{line:12edges}).  Then we pass through once 
+again skipping the edges with none or degenerate IC. For every intersection corner $p=L[e]$, we first get $n$-faces 
+that would appear before and after the IC on IP.
+
+The function \emph{edge faces} (line \ref{line:edge_faces}) returns the adjacent faces $f_0$, $f_1$ to the edge $e$
+on which the IC lies (see the situation in \fig{fig:edge_faces}). 
 The faces are sorted using the sign of the permuted inner product in 1d-2d intersection. The order of faces matches 
 the order of sides of IP if the sign is negative. If the sign is positive the function \emph{edge faces} returns face pair $(f_1, f_0)$.
-If the IC is at the vertex $v$ of $S_3$, the function \emph{vertex faces} described later (\algo{algo:vertex_faces}) is used.
-It returns a pair of generalized faces (face or edge) adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$. 
-If IC $p$ is inside $S_2$, we add it into $I$ and set the connection tables (line \ref{line:insideS2}). 
-However,
-if $p$ is on boundary of $S_2$ it is already in $I$. Denoting $x$ the \nface of $S_3$ the IC lies on, we use the backlink from $x$ to 
-IC $q\in I$ and if $q$ points back to $x$, we set the new successor $f_1$ to it (line \ref{line:successor}). 
-Otherwise $f_0$ is used as the predecessor of $q$ (line \ref{line:predecessor}).
+If the IC is at the vertex $v$ of $S_3$, the function \emph{vertex faces} described later (Alogorithm \algo{algo:vertex_faces}) is used.
+It returns a pair of $n$-faces (face or edge) adjacent to the IC $L[e]$ at the vertex $v$ of $S_3$. 
+Then $p$ is appended to $I$. If IC $p$ is inside $S_2$, the obtained pair of $n$-faces is directly used to set links (line \ref{line:insideS2}).
+However, if $p$ is on the boundary of $S_2$ ($n$-face $x$), just one of the faces is used, complemented with $x$. Presence of the backlink 
+is used to determine the right face.
 
@@
 
-  \uIf{$s[:]$ have 1 non-degenerate edge $e$}{ \nllabel{line:two_degenerated}
-    \return pair of degenerate edges sorted according to $\edgefaces($e$)$    
-  }
-
-  \uElseIf{ $s$ have 1 degenerate edge $e$}{\nllabel{line:one_degenerated}
-    $f$ is face opposite to $e$\;
+  \uIf{ $s[:]$ contains 1 degenerate edge $e$}{\nllabel{line:one_degenerated}
+    Let $f$ be the face opposite to $e$.\;
     \uIf{other two edges $e_a$, $e_b$ have different sign}{
@@
     }\lElse{
-        append IC of $v$ to $J$, \return anything
-    }
-  }  
-  \uElseIf{ $s$ have edge $e$ with sign opposite to other two}{ \nllabel{line:different_sign}
+        \return $(v, e)$
+    }
+  }
+
+  \uElseIf{$s[:]$ contains 1 non-degenerate edge $e$}{ \nllabel{line:two_degenerated}
+    \return pair of degenerate edges sorted according to $\edgefaces($e$)$    
+  }
+
+  \uElseIf{ $s[:]$ contains edge $e$ with the sign opposite to the other two}{ \nllabel{line:different_sign}
     \return $\edgefaces(e)$\;
@@
 
-  \Else($s$ have all signs same){ \nllabel{line:same_signs}
-    append IC of $v$ to $J$, \return anything\;
+  \Else($s[:]$ have all signs same){ \nllabel{line:same_signs}
+    \return $(v, v)$\;
   }  
@@
 edges incident with the vertex $v$, results $s[i]$ of their intersections with $S_2$ may be one of: no IC, 
-degenerate IC, positive IC and negative IC. Accordingly we call the edge: without intersection, degenerate, positive, or negative. 
+degenerate IC, positive IC and negative IC. Accordingly we say the edge is: without intersection, degenerate, positive, or negative. 
 We use these edge indicators to return generalized faces of $S_3$ preceding and succeeding $p$ on the polygons boundary assuming $p$ is at interior of $S_2$.
@@
  or the same sign (the plane is touching $S_3$ at the edge $e$, see \fig{fig:vertex_faces}, (b)).
- In the first case, the call of edge faces for $e$ returns $(f_x,f)$ or $(f,f_x)$, then the vertex faces function returns $(e, f)$ or $(f, e)$, respectively.
- In the second case, we just return anything since there are at most two ICs in IP so the connection tables are not necessary. However, we add 
- current IC into $J$.
+ In the first case, the call $edge\ faces(e)$ returns $(f_x,f)$ or $(f,f_x)$, then the vertex faces function returns $(e, f)$ or $(f, e)$, respectively.
+ In the second case,  there must be another IC on $e$, either at $S_2$ boundary or at the other end of $e$.
+ In both cases the edge $e$ is the common $n$-face of the two intersection points thus we return 
+ $(v,e)$ taking the edge as the target object.
 
@@
  \item {\bf All ICs have the same sign} (line \ref{line:same_signs}){\bf .} Since $S_2$ is touching $S_3$ 
- at the vertex $v$, the polygon degenerates into a point and thus no connection information is necessary.
- We add IC to $J$ and return any pair of faces, see \fig{fig:vertex_faces}, (e) .
+ at the vertex $v$, \fig{fig:vertex_faces}, (e), the polygon degenerates into a point and thus no connection information is necessary.
+ We just return $(v,v)$.
 \end{itemize}
 
-% Either all signs are equal ($S_2$ touching $S_3$) wee , or
-% a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the 
-% 
-% 
-% and need to insert them into $I$ to correct place. To this end we exploit additional information about incidence of points
-% with faces of $S_3$.
-Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_2$ belongs to a face $f$ of $S_3$; we know from the order of the points
-% whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
-% Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
-% intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.
 \subsubsection{Ordering of Intersections}
 \label{sec:ordering}
-The final stage of the 2d-3d intersection is ordering of ICs. If there are less then 3 ICs in the list $I$ we merge lists $I$ and $J$ remove duplicities
-and get at most 2 distinguish ICs forming a degenerate IP. Otherwise, we start with first IC $p$ in $I$, put it into final list $K$, 
-get its successor \nface $x = F_f(p)$ and its successor IC $q=F_q(x)$. Unless $x$ is vertex of $S_2$, we put $q$ into $K$ and repeat the process until 
-we pass all ICs in $I$.
+The final stage of the 2d-3d intersection is ordering of ICs. We start with the first IC in $I$ and follow the 
+successor tables until we return back. The ICs are copied into the result vector, skipping the duplicities.
+Special treatment must be done for degenerate cases with less then $3$ ICs as they may not form a cycle.
 
